### 2023-05-10 ms.qmd
Basic stuff

---
docx: 
reference-doc: "./bib/tmpl.docx"
bibliography: "./bib/refs.bib"
execute:
  echo: false
  error: false
  cache: false
  warning: false
crossref:  
  fig-title: Figure    # (default is "Figure")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.   # (default is "Table")
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup

pacman::p_load(tidyverse, flextable)
```

## Introduction

 [@ODea2019]

```{r, dataload}
#| label: dataload
#| echo: false
#| warning: false

# Load data
	data  <-  read.csv("./output/data/data_activity.csv")
```

## Results

@fig-fig1

We calculated $R^2$ as follows

$$
R^2 = \frac{SS_{reg}}{SS_{tot}}
$$ {#eq-r2}

@eq-r2

```{r, fig1}
#| label: fig-fig1
#| fig-cap: "Activity budget of the focal group of chacma baboons (Papio ursinus) at the Cape Peninsula, South Africa, during the study period. The data are presented as the mean percentage of time spent in each activity category per hour (± SE)."

data %>% ggplot(aes(x = Lizard_id))  + geom_histogram()

```

We have a total of `r length(unique(data$Lizard_id))`

```{r,tb1}
#| label: tbl-tb1
#| tbl-cap: "Summary of the data"

tab <- data %>% 
  group_by(Lizard_id) %>% 
  summarise(
    n = n()
  ) 
flextable(tab[2:3,])
```

# References

### 2023-05-10 R/1_data_process.R

@@ -1,0 +1,21 @@
+####################################
+# 1_data_process
+####################################
+
+## Load packages
+	intstall.packages("pacman")
+	pacman::p_load(tidyverse, readxl)
+
+## Load data	
+	              activ_files <- list.files("./data/Activity/")
+	       data_activity_list <- lapply(activ_files, function(x) read_xlsx(paste0("./data/Activity/", x))[-c(1:3),])
+	names(data_activity_list) <- activ_files
+
+## Merge
+	data_activity <- dplyr::bind_rows(data_activity_list, .id = "id")
+
+
+
+# At the end of processing you write the file
+	write_csv(data_activity, "./output/data/data_activity.csv")
+

### 2023-06-20 ms.qmd
Updates

@@
 
+## Methods
+
+### Subjects
+
+The subjects in our experiments were juveniles from two species of skinks, the common garden skink (*L.
+guichenoti*) and the rainbow skink or delicate skink (*Lampropholis delicata*).
+These are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia (Chapple et al.
+2011).
+They also have similar breeding periods, but with some differences in reproductive output: while *L.
+delicata* lays 1 to 6 eggs in only one clutch per season, *L.
+guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season (Chapple et al.
+2011; 2014).
+This difference in reproductive output through the breeding season may involve different degree of sensitivity to maternal effects and its interaction with other aspects of early environment.
+
+### Husbandry
+
+*Breeding colony* -- We tested juveniles coming from a breeding colony established in the lab since 2019.
+There is a total of 270 and 180 adults of *L.
+delicata* and *L.* guichenoti respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+Enclosures are provided with non-stick matting, shelter, and several small water dishes.
+Water is given daily, and they are fed approx.
+40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
+Crickets are dusted with calcium weekly and multivitamin and calcium biweekly.
+To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
+Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
+
+*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
+We checked for the presence of eggs in the boxes three days a week.
+After collection, we measured length and width of eggs with a digital calliper to the nearest 0.1 mm and weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
+The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
+
+*Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
+After hatchling, we measured juveniles\' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
+During this period, they were sprayed water every day and received 3-6 small *A.
+domestica* crickets three times a week.
+All care otherwise follows similar protocols to adults (see above).
+
+Two weeks before we started the training phase (see below), lizards were moved to the experimental arena (Fig.
+1c) for acclimatation.
+The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
+These new enclosures were placed in two rooms in 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
+The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
+During acclimatation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum.* We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
+The rooms temperature was set to between 22-24 Celsius.
+We tested temperatures with laser temperature guns to ensure such a set up established a thermal gradient and we there were no significant differences between treatments or species (see Supplementary Material).
+
+### CORT and Temperature manipulation
+
+To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (\'Cold\' -- 23ºC ± 3ºC or \'Hot\' -- 30ºC ± 3ºC) in a 2x2 factorial design (Fig.
+1a).
+We first allocated eggs to one of two different treatments: in one of the treatments, eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); while eggs in the other group (Control treatment) received an equal volume of the vehicle.
+CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
+Then, eggs were incubated in one of the two previously mentioned temperature regimes (\'Cold\' or \'Hot\') until hatching.
+The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
+
+INSERT Fig 1
+
+### Learning
+
+To estimate learning skills, we tested skinks\' ability to locate a food reward in a series of behavioural tasks (Fig.
+2) (see Leal and Powell, 2012; Clark *et al.*, 2013).
+First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
+We divided this training phase into three stages (see Fig.
+2): in the first stage, lizards had to eat a small, frozen cricket (*A.
+domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure; in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps; and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage.
+Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
+At the end of the experiment, we recorded whether the cricket has been consumed or not.
+Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials.
+This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase (see Supplementary material).
+
+In the next phase, we trained lizards to associate between colour and a food reward (colour association task in Fig.
+2).
+The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour.
+We placed the food reward (small, frozen, *A.
+domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in one ramp.
+The food reward was placed in all three wells to avoid the use of chemical cues to determine the correct choice; our lids had a series of small holes on the top for the same reason.
+The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours (REF).
+To control for potential colour preference that could bias our results, we split the subjects in two groups counterbalanced by treatment and species; in one group the correct choice (i.e., the ramp with non-covered cricket) was the blue one in the associative task and red in the reversal, while we did the opposite for the other half.
+In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
+Lizards were tested in this task once a day for 35 days.
+
+After the colour association phase, we performed a choice reversal task.
+This task was like the colour association test, except that the attainability of prey was indicated by a different colour, requiring the lizards to form a novel association between the new colour and the food reward.
+This test was done once a day for 40 days.
+
+ All trials were done daily between the 6^th^ of March until the 26^th^ of June 2023, beginning at 11 am until 12 pm.
+Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.
+Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not.
+
+INSERT Fig 2
+
+### Statistical analyses
+
 ## Results

### 2023-06-21 ms.qmd
Updates

@@
 
-The subjects in our experiments were juveniles from two species of skinks, the common garden skink (*L.
-guichenoti*) and the rainbow skink or delicate skink (*Lampropholis delicata*).
-These are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia (Chapple et al.
-2011).
+The subjects in our experiments were juveniles from two species of skinks, the common garden skink (*Lampropholis guichenoti*) and the rainbow skink or delicate skink (*L.
+delicata*).
+These are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia ([@chapple2011]).
 They also have similar breeding periods, but with some differences in reproductive output: while *L.
 delicata* lays 1 to 6 eggs in only one clutch per season, *L.
-guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season (Chapple et al.
-2011; 2014).
+guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season ([@chapple2011]; 2014).
 This difference in reproductive output through the breeding season may involve different degree of sensitivity to maternal effects and its interaction with other aspects of early environment.
@@
 We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured length and width of eggs with a digital calliper to the nearest 0.1 mm and weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
 Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
@@
 *Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
-After hatchling, we measured juveniles\' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+After hatchling, we measured juveniles' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
 We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
@@
 
-To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (\'Cold\' -- 23ºC ± 3ºC or \'Hot\' -- 30ºC ± 3ºC) in a 2x2 factorial design (Fig.
+To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (Fig.
 1a).
@@
 CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
-Then, eggs were incubated in one of the two previously mentioned temperature regimes (\'Cold\' or \'Hot\') until hatching.
+Then, eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching.
 The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
@@
 
-To estimate learning skills, we tested skinks\' ability to locate a food reward in a series of behavioural tasks (Fig.
+To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (Fig.
 2) (see Leal and Powell, 2012; Clark *et al.*, 2013).

### 2023-06-21 ms.qmd
Updates Methods

@@
 delicata*).
-These are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia ([@chapple2011]).
+These are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia ([@chapple_know_2011]).
 They also have similar breeding periods, but with some differences in reproductive output: while *L.
 delicata* lays 1 to 6 eggs in only one clutch per season, *L.
-guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season ([@chapple2011]; 2014).
+guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season ([@chapple_know_2011]; [@chapple_biology_2014]).
 This difference in reproductive output through the breeding season may involve different degree of sensitivity to maternal effects and its interaction with other aspects of early environment.
@@
 To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (Fig.
-2) (see Leal and Powell, 2012; Clark *et al.*, 2013).
+2) (see [@leal_behavioural_2012]; [@clark_colour_2014]).
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).

### 2023-10-13 ms.qmd
Updates

@@
 [@ODea2019]
-
-```{r, dataload}
-#| label: dataload
-#| echo: false
-#| warning: false
-
-# Load data
-	data  <-  read.csv("./output/data/data_activity.csv")
-```
 
@@
 
-@fig-fig1
+```{r, dataload}
+#| label: dataload
+#| echo: false
+#| warning: false
+
+# Load packages
+pacman::p_load(tidyverse, flextable, brms, ggplot2)
+
+# Load data
+	data  <-  read.csv("./data/Learning.csv")
+```
+
+```{r, dataclean}
+#| label: dataclean
+#| echo: false
+#| warning: false
+
+# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
+
+data_associative <- data %>%
+  group_by(lizard_id) %>%
+  mutate(
+    trial_associative = ifelse(!is.na(trial_associative), min(trial_associative, na.rm = TRUE), NA),
+    trial_associative = trial_associative - min(trial_associative, na.rm = TRUE) + 1
+  ) %>%
+  ungroup()
+
+# Split data
+deli <- data_associative %>% filter (species == "delicata")
+guich <- data_associative %>% filter (species == "guichenoti")
+
+```
 

### 2023-10-16 ms.qmd
Updates

--- 2023-06-21 ms.qmd
@@
 
-@fig-fig1
+```{r, dataload}
+#| label: dataload
+#| echo: false
+#| warning: false
+
+# Load packages
+pacman::p_load(tidyverse, flextable, brms, ggplot2)
+
+# Load data
+	data  <-  read.csv("./data/Learning.csv")
+```
+
+```{r, dataclean}
+#| label: dataclean
+#| echo: false
+#| warning: false
+
+# Removing individuals who did not participate (more than 15 NAs)
+data_associative <- data %>%
+  group_by(lizard_id) %>%
+  filter(sum(is.na(FC_associative)) <= 15) %>%
+  ungroup()
+data_associative <- as.data.frame(data_associative)
+
+# Removing trials [36-40] (Only in associative)
+data_associative <- data_associative %>%
+group_by(lizard_id) %>%
+filter(trial_associative <= 35) %>%
+ungroup()
+data_associative <- as.data.frame(data_associative)
+
+# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
+
+data_associative <- data_associative %>%
+  group_by(lizard_id) %>%
+  mutate(
+    first_non_na = min(which(!is.na(FC_associative))),
+    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
+    filter(Associative_Trial >= 1) %>%
+   ungroup()
+
+data_associative <- as.data.frame(data_associative)
+write.csv(data_associative, file= "./output/Checking/data_associative.csv")
+
+# Split data
+deli_associative <- data_associative %>% filter (species == "delicata")
+guich_associative <- data_associative %>% filter (species == "guichenoti")
+
+```
 

### 2023-10-16 .vdoc.r

@@ -1,0 +1,155 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+
+pacman::p_load(tidyverse, flextable)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: dataload
+#| echo: false
+#| warning: false
+ 
+# Load packages
+pacman::p_load(tidyverse, flextable, brms, ggplot2)
+
+# Load data
+	data  <-  read.csv("./data/Learning.csv")
+#
+#
+#
+#| label: dataclean
+#| echo: false
+#| warning: false
+
+# Removing individuals who did not participate (more than 15 NAs)
+data_associative <- data %>%
+  group_by(lizard_id) %>%
+  filter(sum(is.na(FC_associative)) <= 15) %>%
+  ungroup()
+data_associative <- as.data.frame(data_associative)
+
+# Removing trials [36-40] (Only in associative)
+data_associative <- data_associative %>%
+group_by(lizard_id) %>%
+filter(trial_associative <= 35) %>%
+ungroup()
+data_associative <- as.data.frame(data_associative)
+
+# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
+
+data_associative <- data_associative %>%
+  group_by(lizard_id) %>%
+  mutate(
+    first_non_na = min(which(!is.na(FC_associative))),
+    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
+    filter(Associative_Trial >= 1) %>%
+   ungroup()
+  
+data_associative <- as.data.frame(data_associative)
+write.csv(data_associative, file= "./output/Checking/data_associative.csv")
+
+# Split data
+deli_associative <- data_associative %>% filter (species == "delicata")
+guich_associative <- data_associative %>% filter (species == "guichenoti")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-fig1
[…]

### 2023-10-16 ms.qmd
Updates

@@
 # Load packages
-pacman::p_load(tidyverse, flextable, brms, ggplot2)
+pacman::p_load(tidyverse, flextable, brms, ggplot2,lme4, zoo)
 
@@
 
+```{r, models}
+#| label: dataclean
+#| echo: false
+#| warning: false
+
+null <- glmer(FC_associative ~ 1 + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+GMM_deli <- glmer(FC_associative ~ Associative_Trial*trt + group*Associative_Trial + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+install.packages("lmtest")
+library(lmtest)
+lrtest(null, GMM_deli)
+anova(GMM_deli)
+plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  
+geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
+  facet_grid(as.factor(deli_associative$group))
+print(plot_deli)
+```
+
 We calculated $R^2$ as follows

### 2023-10-16 .vdoc.r

@@ -71,7 +71,7 @@ pacman::p_load(tidyverse, flextable)
 #| warning: false
  
 # Load packages
-pacman::p_load(tidyverse, flextable, brms, ggplot2)
+pacman::p_load(tidyverse, flextable, brms, ggplot2,lme4, zoo)
 
 # Load data
 	data  <-  read.csv("./data/Learning.csv")
@@ -116,6 +116,21 @@ guich_associative <- data_associative %>% filter (species == "guichenoti")
 #
 #
 #
+#
+#| label: dataclean
+#| echo: false
+#| warning: false
+
+null <- glmer(FC_associative ~ 1 + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+GMM_deli <- glmer(FC_associative ~ Associative_Trial*trt + group*Associative_Trial + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+install.packages("lmtest")
+library(lmtest)
+lrtest(null, GMM_deli)
+anova(GMM_deli)
+plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  geom_line() +  
+geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
+  facet_grid(as.factor(deli_associative$group))
+print(plot_deli)
 #
 #
 #

### 2023-10-17 ms.qmd
Adding some Bayesian code

--- 2023-10-16 ms.qmd
@@
 
-pacman::p_load(tidyverse, flextable)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms)
 ```
@@
 # Load packages
-pacman::p_load(tidyverse, flextable, brms, ggplot2)
+pacman::p_load(tidyverse, flextable, brms, ggplot2,lme4, zoo, lmerTest)
 
@@
   filter(sum(is.na(FC_associative)) <= 15) %>%
-  ungroup()
-data_associative <- as.data.frame(data_associative)
+  ungroup()  %>% data.frame()
 
@@
 filter(trial_associative <= 35) %>%
-ungroup()
-data_associative <- as.data.frame(data_associative)
+ungroup()  %>% mutate(temp = gsub("[AB]_", "", trt),
+                      cort = gsub("_[2][38]", "", trt))  %>% 
+                mutate(group = factor(group, levels = c("R_B", "B_R"))) %>% data.frame()
 
@@
 
+```
+
+```{r, models}
+#| label: dataclean
+#| echo: false
+#| warning: false
+
+    null <- glmer(FC_associative ~ 1 + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+GMM_deli <- glmer(FC_associative ~ Associative_Trial*trt + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+
+GMM_deli2 <- glmer(FC_associative ~temp*cort*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+summary(GMM_deli2)
+
+emmeans(GMM_deli2, pairwise ~ temp*Associative_Trial)
+emmeans(GMM_deli2, pairwise ~ cort*Associative_Trial)
+
+## Bayesian 
+  mod <- brm(FC_associative ~ trt*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
+  summary(mod)
+
+# R2
+bayes_R2(mod)
+
+# Extract posteriors
+posterior <- posterior_samples(mod, pars = "^b")
+plyr::ldply(lapply(posterior, mean))
+plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
+temp23 <- c(posterior[,"b_Intercept"], (posterior[,"b_Intercept"]+ posterior[,"b_trtB_23"]))
+temp28 <- c((posterior[,"b_Intercept"] + posterior[,"b_trtB_28"]), posterior[,"b_trtB_23"])
+
+dharma(GMM_deli2)
+install.packages("lmtest")
+library(lmtest)
+lrtest(null, GMM_deli)
+anova(GMM_deli)
+plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  
+geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
+  facet_grid(as.factor(deli_associative$group)) + labs(y = "Colour Association Task", x = "Trial")
+print(plot_deli)
 ```

### 2023-10-17 .vdoc.r

@@ -1,170 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-
-pacman::p_load(tidyverse, flextable)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: dataload
-#| echo: false
-#| warning: false
- 
-# Load packages
-pacman::p_load(tidyverse, flextable, brms, ggplot2,lme4, zoo)
-
-# Load data
-	data  <-  read.csv("./data/Learning.csv")
-#
-#
-#
-#| label: dataclean
-#| echo: false
-#| warning: false
-
-# Removing individuals who did not participate (more than 15 NAs)
-data_associative <- data %>%
-  group_by(lizard_id) %>%
-  filter(sum(is.na(FC_associative)) <= 15) %>%
-  ungroup()
-data_associative <- as.data.frame(data_associative)
-
-# Removing trials [36-40] (Only in associative)
-data_associative <- data_associative %>%
-group_by(lizard_id) %>%
-filter(trial_associative <= 35) %>%
-ungroup()
-data_associative <- as.data.frame(data_associative)
-
-# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
-
-data_associative <- data_associative %>%
-  group_by(lizard_id) %>%
-  mutate(
-    first_non_na = min(which(!is.na(FC_associative))),
-    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
-    filter(Associative_Trial >= 1) %>%
-   ungroup()
-  
-data_associative <- as.data.frame(data_associative)
-write.csv(data_associative, file= "./output/Checking/data_associative.csv")
-
-# Split data
-deli_associative <- data_associative %>% filter (species == "delicata")
-guich_associative <- data_associative %>% filter (species == "guichenoti")
-
-#
-#
-#
-#
-#| label: dataclean
-#| echo: false
-#| warning: false
-
[…]

### 2023-10-17 ms.qmd
pmcmc function and some exampeles

@@
 
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here)
+
+source(here("R", "func.R"))
 ```
@@
 
+pmcmc(temp23 - temp28)
 dharma(GMM_deli2)

### 2023-10-17 R/func.r

@@ -1,0 +1,12 @@
+
+#' @title pMCMC Function
+ #' @param x The vector for the posterior distribution. Note that this will test the null hypothesis that the parameter of interest is significantly different from 0. 
+ #' @param null A numeric value decsribing what the null hypothesis should be
+ #' @param twotail Whether to conduct a one-tailed hypothesis or a two-tailed hypotheses. Default = true indicating a two-tailed test will be done.
+pmcmc <- function(x, null = 0, twotail = TRUE){
+  if(twotail){
+    2*(1 - max(table(x<=null) / length(x)))
+  } else{
+    (1 - max(table(x<=null) / length(x)))
+  }
+}

### 2023-10-17 ms.qmd
Updates models

--- 2023-10-16 ms.qmd
@@
 
-pacman::p_load(tidyverse, flextable)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest)
+
+source(here("R", "func.R"))
 ```
@@
 
-# Load packages
-pacman::p_load(tidyverse, flextable, brms, ggplot2,lme4, zoo)
-
 # Load data
@@
 
-# Removing individuals who did not participate (more than 15 NAs)
+# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
 data_associative <- data %>%
@@
     filter(sum(is.na(FC_associative)) <= 15) %>%
-  ungroup()
-data_associative <- as.data.frame(data_associative)
-
-# Removing trials [36-40] (Only in associative)
-data_associative <- data_associative %>%
-group_by(lizard_id) %>%
     filter(trial_associative <= 35) %>%
-ungroup()
-data_associative <- as.data.frame(data_associative)
+  ungroup()  %>% 
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(group = factor(group, levels = c("R_B", "B_R"))) %>%
+  data.frame()
 
@@
     filter(Associative_Trial >= 1) %>%
-   ungroup()
+   ungroup() %>% data.frame()
 
-data_associative <- as.data.frame(data_associative)
 write.csv(data_associative, file= "./output/Checking/data_associative.csv")
 
-# Split data
+# Split data by species
 deli_associative <- data_associative %>% filter (species == "delicata")
@@
 
-```{r, models}
-#| label: dataclean
+```{r, models1}
+#| label: models1
 #| echo: false
@@
 
-null <- glmer(FC_associative ~ 1 + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
-GMM_deli <- glmer(FC_associative ~ Associative_Trial*trt + group*Associative_Trial + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
-install.packages("lmtest")
-library(lmtest)
-lrtest(null, GMM_deli)
-anova(GMM_deli)
-plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  
-geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
-  facet_grid(as.factor(deli_associative$group))
+# Generalized Mixed Models delicata
+GMM_deli <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+summary(GMM_deli)
+
+emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
+emmeans(GMM_deli, pairwise ~ cort*Associative_Trial)
+
+# Generalized Mixed Models guichenoti
+GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"))
+summary(GMM_guich)
+
+emmeans(GMM_guich, pairwise ~ temp*Associative_Trial)
+emmeans(GMM_guich, pairwise ~ cort*Associative_Trial)
+emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
+
+```
+
+```{r, models2}
+#| label: models2
+#| echo: false
+#| warning: false
+
+# Bayesian model delicata
+  deli_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
+  summary(deli_mod)
+
+# Bayesian model guichenoti
+  guich_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
+  summary(deli_mod)
+# R2
+bayes_R2(mod)
+
+# Extract posteriors
+posterior <- posterior_samples(mod, pars = "^b")
+plyr::ldply(lapply(posterior, mean))
+plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
+temp23 <- c(posterior[,"b_Intercept"], (posterior[,"b_Intercept"]+ posterior[,"b_trtB_23"]))
+temp28 <- c((posterior[,"b_Intercept"] + posterior[,"b_trtB_28"]), posterior[,"b_trtB_23"])
+
+pmcmc(temp23 - temp28)
+dharma(GMM_deli2)
+
+```
+
+```{r, plots}
+#| label: plots
+#| echo: false
+#| warning: false
+
+# Plot delicata
+plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
+  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
+  facet_grid(as.factor(deli_associative$group)) + 
+  labs(y = "Colour Association Task", x = "Trial")  
 print(plot_deli)
+
+# Plot guichenoti
+plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
+  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
+  facet_grid(as.factor(guich_associative$group)) + 
+  labs(y = "Colour Association Task", x = "Trial") 
+print(plot_guich)
 ```

### 2023-10-17 .vdoc.r

@@ -1,0 +1,220 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest)
+
+source(here("R", "func.R"))
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: dataload
+#| echo: false
+#| warning: false
+ 
+# Load data
+	data  <-  read.csv("./data/Learning.csv")
+#
+#
+#
+#| label: dataclean
+#| echo: false
+#| warning: false
+
+# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
+data_associative <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_associative)) <= 15) %>%
+    filter(trial_associative <= 35) %>%
+  ungroup()  %>% 
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(group = factor(group, levels = c("R_B", "B_R"))) %>%
+  data.frame()
+
+# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
+
+data_associative <- data_associative %>%
+  group_by(lizard_id) %>%
+  mutate(
+    first_non_na = min(which(!is.na(FC_associative))),
+    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
+    filter(Associative_Trial >= 1) %>%
+   ungroup() %>% data.frame()
+  
+write.csv(data_associative, file= "./output/Checking/data_associative.csv")
+
+# Split data by species
+deli_associative <- data_associative %>% filter (species == "delicata")
+guich_associative <- data_associative %>% filter (species == "guichenoti")
+
+#
+#
+#
+#
+#| label: models1
+#| echo: false
+#| warning: false
+
+# Generalized Mixed Models delicata
[…]

### 2023-11-03 ms.qmd
Update ms.qmd

@@
   summary(deli_mod)
+  plot(deli_mod)
 

### 2023-11-18 ms.qmd
Updates

@@
 
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
 
@@
   guich_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
-  summary(deli_mod)
+  summary(guich_mod)
+  plot(guich_mod)
 # R2
-bayes_R2(mod)
+bayes_R2(deli_mod)
+bayes_R2(guich_mod)
 

### 2023-11-18 .vdoc.r

@@ -19,7 +19,7 @@
 #
 #| label: setup
 
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
 
 source(here("R", "func.R"))
 #
@@ -141,12 +141,28 @@ emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
 # Bayesian model delicata
   deli_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
   summary(deli_mod)
-
+  plot(deli_mod)
+flextable_summary <- flextable(deli_mod) %>%
+  set_table_properties(width = .8, layout = "autofit") %>%
+  theme_zebra() %>%
+tidy_summary <- data.frame(term = rownames(fixed_effects),
+                            estimate = fixed_effects,
+                            conf.low = summary_table$ci[,"lower"],
+                            conf.high = summary_table$ci[,"upper"])
+flextable::set_header_labels(
+    term = "Term",
+    estimate = "Estimate",
+    conf.low = "Lower CI",
+    conf.high = "Upper CI"
+  ) %>%
+  flextable::rename(columns = "term" ~ "Fixed Effects")
 # Bayesian model guichenoti
   guich_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
-  summary(deli_mod)
+  summary(guich_mod)
+  plot(guich_mod)
 # R2
-bayes_R2(mod)
+bayes_R2(deli_mod)
+bayes_R2(guich_mod)
 
 # Extract posteriors
 posterior <- posterior_samples(mod, pars = "^b")

### 2023-11-18 ms.qmd
Updates

@@
           cort = gsub("_[2][38]", "", trt))  %>% 
-    mutate(group = factor(group, levels = c("R_B", "B_R"))) %>%
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"), 
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
+    mutate(temp = factor(temp,
+     levels = c("23", "28"), 
+     labels=c("23"="Cold", "28"="Hot"))) %>%
+    mutate(cort = factor(cort,
+     levels = c("A", "B"), 
+     labels=c("A"="Control", "B"="CORT"))) %>%
+  data.frame()
+
+data_reversal <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_reversal)) <= 15) %>%
+   ungroup()  %>% 
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"), 
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
+    mutate(temp = factor(temp,
+     levels = c("23", "28"), 
+     labels=c("23"="Cold", "28"="Hot"))) %>%
+    mutate(cort = factor(cort,
+     levels = c("A", "B"), 
+     labels=c("A"="Control", "B"="CORT"))) %>%
   data.frame()
@@
 # Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
-
 data_associative <- data_associative %>%
@@
 
+# Split data by species
+deli_reversal <- data_reversal %>% filter (species == "delicata")
+guich_reversal <- data_reversal %>% filter (species == "guichenoti")
 ```
@@
 
-```{r, models2}
-#| label: models2
+```{r, modelsasso}
+#| label: modelsasso
 #| echo: false
@@
 
+```{r, modelsrev}
+#| label: modelsrev
+#| echo: false
+#| warning: false
+
+# Bayesian model delicata
+  deli_rev <- brm(FC_reversal ~ cort*temp*trial_reversal + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
+  summary(deli_rev)
+  plot(deli_rev)
+
+# Bayesian model guichenoti
+  guich_rev <- brm(FC_reversal ~ cort*temp*trial_reversal + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
+  summary(guich_rev)
+  plot(guich_rev)
+# R2
+bayes_R2(deli_rev)
+bayes_R2(guich_rev)
+
+# Extract posteriors
+posterior <- posterior_samples(mod, pars = "^b")
+plyr::ldply(lapply(posterior, mean))
+plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
+temp23 <- c(posterior[,"b_Intercept"], (posterior[,"b_Intercept"]+ posterior[,"b_trtB_23"]))
+temp28 <- c((posterior[,"b_Intercept"] + posterior[,"b_trtB_28"]), posterior[,"b_trtB_23"])
+
+pmcmc(temp23 - temp28)
+dharma(GMM_deli2)
+
+```
+
 ```{r, plots}
@@
 
-# Plot delicata
+# Plot delicata associative
 plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
-  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
+  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
   facet_grid(as.factor(deli_associative$group)) + 
-  labs(y = "Colour Association Task", x = "Trial")  
+  labs(y = "Probability of correct choice", x = "Trial")  
 print(plot_deli)
 
-# Plot guichenoti
+# Plot guichenoti associative
 plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
@@
   facet_grid(as.factor(guich_associative$group)) + 
-  labs(y = "Colour Association Task", x = "Trial") 
+  labs(y = "Probability of correct choice", x = "Trial") 
 print(plot_guich)
+
+# Plot delicata reversal
+
+# Plot guichenoti reversal
+
 ```

### 2023-11-18 .vdoc.r

@@ -89,11 +89,36 @@ data_associative <- data %>%
   ungroup()  %>% 
     mutate(temp = gsub("[AB]_", "", trt),
           cort = gsub("_[2][38]", "", trt))  %>% 
-    mutate(group = factor(group, levels = c("R_B", "B_R"))) %>%
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"), 
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
+    mutate(temp = factor(temp,
+     levels = c("23", "28"), 
+     labels=c("23"="Cold", "28"="Hot"))) %>%
+    mutate(cort = factor(cort,
+     levels = c("A", "B"), 
+     labels=c("A"="Control", "B"="CORT"))) %>%
   data.frame()
 
-# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
+data_reversal <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_reversal)) <= 15) %>%
+   ungroup()  %>% 
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"), 
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
+    mutate(temp = factor(temp,
+     levels = c("23", "28"), 
+     labels=c("23"="Cold", "28"="Hot"))) %>%
+    mutate(cort = factor(cort,
+     levels = c("A", "B"), 
+     labels=c("A"="Control", "B"="CORT"))) %>%
+  data.frame() 
 
+
+# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
 data_associative <- data_associative %>%
   group_by(lizard_id) %>%
   mutate(
@@ -108,6 +133,9 @@ write.csv(data_associative, file= "./output/Checking/data_associative.csv")
 deli_associative <- data_associative %>% filter (species == "delicata")
 guich_associative <- data_associative %>% filter (species == "guichenoti")
 
+# Split data by species
+deli_reversal <- data_reversal %>% filter (species == "delicata")
+guich_reversal <- data_reversal %>% filter (species == "guichenoti")
 #
 #
 #
@@ -134,7 +162,7 @@ emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
 #
 #
 #
[…]

### 2023-11-19 ms.qmd
Updates and figures

@@
 plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
-  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
-  facet_grid(as.factor(deli_associative$group)) + 
-  labs(y = "Probability of correct choice", x = "Trial")  
+  stat_smooth(method = "glm", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
+  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
+    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
+  ) +
+  facet_wrap(deli_associative$group, scales = "free_y", ncol = 1) +
+  theme(strip.placement = "outside") +  
+  theme(strip.background = element_blank()) +
+  labs(y = "Probability of correct choice", x = "Trial") +
+  theme_classic() +
+  theme(
+    axis.title = element_text(size = 18, family = "sans"),  
+    axis.text = element_text(size = 10, family = "sans"),  
+    legend.title = element_text(size = 14, family = "sans"), 
+    legend.text = element_text(size = 12, family = "sans")  
+  )
 print(plot_deli)
+ggsave("./output/figures/fig_deli_asso.png", plot=plot_deli, width = 15, height = 12, units = "cm", dpi = 3000)
 
@@
 plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
-  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
-  facet_grid(as.factor(guich_associative$group)) + 
-  labs(y = "Probability of correct choice", x = "Trial") 
+  stat_smooth(method = "glm", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
+  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
+    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
+  ) +
+  facet_wrap(guich_associative$group, scales = "free_y", ncol = 1) +
+  theme(strip.placement = "outside") +  
+  theme(strip.background = element_blank()) +
+  labs(y = "Probability of correct choice", x = "Trial") +
+  theme_classic() +
+  theme(
+    axis.title = element_text(size = 18, family = "sans"),  
+    axis.text = element_text(size = 10, family = "sans"),  
+    legend.title = element_text(size = 14, family = "sans"), 
+    legend.text = element_text(size = 12, family = "sans")  
+  )
 print(plot_guich)
+ggsave("./output/figures/fig_guich_asso.png", plot=plot_guich, width = 15, height = 12, units = "cm", dpi = 3000)
 
 # Plot delicata reversal
+label_mapping <- c("R_B" = "Blue", "B_R" = "Red")
+deli_reversal$group <- factor(deli_reversal$group, levels = levels(deli_reversal$group), labels = label_mapping)
+deli_rev <- ggplot(deli_reversal, aes(x = trial_reversal, y = FC_reversal, color=interaction(cort,temp))) +  
+  stat_smooth(method = "glm", formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
+  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
+    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
+  ) +
+  facet_wrap(~group, scales = "free_y", ncol = 1) +
+  theme(strip.placement = "outside") +  
+  theme(strip.background = element_blank()) +
+  labs(y="", x = "Trial", color="Treatments") +
+  theme_classic() +
+  theme(
+    axis.title = element_text(size = 18, family = "sans"),  
+    axis.text = element_text(size = 10, family = "sans"),  
+    legend.title = element_text(size = 14, family = "sans"), 
+    legend.text = element_text(size = 12, family = "sans")  
+  )
+print(deli_rev)
+ggsave("./output/figures/fig_deli_rev.png", plot=deli_rev, width = 15, height = 12, units = "cm", dpi = 3000)
 
 # Plot guichenoti reversal
+label_mapping <- c("R_B" = "Blue", "B_R" = "Red")
+guich_reversal$group <- factor(guich_reversal$group, levels = levels(deli_reversal$group), labels = label_mapping)
+guich_rev <- ggplot(guich_reversal, aes(x = trial_reversal, y = FC_reversal, color=interaction(cort,temp))) +  
+  stat_smooth(method = "glm", formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
+  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
+    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
+  ) +
+  facet_wrap(~group, scales = "free_y", ncol = 1) +
+  theme(strip.placement = "outside") +  
+  theme(strip.background = element_blank()) +
+  labs(y="", x = "Trial", color="Treatments") +
+  theme_classic() +
+  theme(
+    axis.title = element_text(size = 18, family = "sans"),  
+    axis.text = element_text(size = 10, family = "sans"),  
+    legend.title = element_text(size = 14, family = "sans"), 
+    legend.text = element_text(size = 12, family = "sans")  
+  )
+print(guich_rev)
+ggsave("./output/figures/fig_guich_rev.png", plot=guich_rev, width = 15, height = 12, units = "cm", dpi = 3000)
 

### 2023-11-19 .vdoc.r

@@ -1,288 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
-
-source(here("R", "func.R"))
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: dataload
-#| echo: false
-#| warning: false
- 
-# Load data
-	data  <-  read.csv("./data/Learning.csv")
-#
-#
-#
-#| label: dataclean
-#| echo: false
-#| warning: false
-
-# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
-data_associative <- data %>%
-  group_by(lizard_id) %>%
-    filter(sum(is.na(FC_associative)) <= 15) %>%
-    filter(trial_associative <= 35) %>%
-  ungroup()  %>% 
-    mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>% 
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"), 
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
-    mutate(temp = factor(temp,
-     levels = c("23", "28"), 
-     labels=c("23"="Cold", "28"="Hot"))) %>%
-    mutate(cort = factor(cort,
-     levels = c("A", "B"), 
-     labels=c("A"="Control", "B"="CORT"))) %>%
-  data.frame()
-
-data_reversal <- data %>%
-  group_by(lizard_id) %>%
-    filter(sum(is.na(FC_reversal)) <= 15) %>%
-   ungroup()  %>% 
-    mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>% 
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"), 
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
[…]

### 2023-11-19 .vdoc.r
Create .vdoc.r

@@ -1,0 +1,353 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
+
+source(here("R", "func.R"))
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: dataload
+#| echo: false
+#| warning: false
+ 
+# Load data
+	data  <-  read.csv("./data/Learning.csv")
+#
+#
+#
+#| label: dataclean
+#| echo: false
+#| warning: false
+
+# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
+data_associative <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_associative)) <= 15) %>%
+    filter(trial_associative <= 35) %>%
+  ungroup()  %>% 
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"), 
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
+    mutate(temp = factor(temp,
+     levels = c("23", "28"), 
+     labels=c("23"="Cold", "28"="Hot"))) %>%
+    mutate(cort = factor(cort,
+     levels = c("A", "B"), 
+     labels=c("A"="Control", "B"="CORT"))) %>%
+  data.frame()
+
+data_reversal <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_reversal)) <= 15) %>%
+   ungroup()  %>% 
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"), 
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
[…]

### 2023-11-22 ms.qmd
Updates

@@
 #| warning: false
-
+library(emmeans)
+library(lme4)
 # Generalized Mixed Models delicata
@@
 summary(GMM_deli)
-
 emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
-emmeans(GMM_deli, pairwise ~ cort*Associative_Trial)
+emmeans(GMM_deli, pairwise ~ cort*temp*Associative_Trial)
 
 # Generalized Mixed Models guichenoti
-GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"))
+GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"), control = glmerControl(maxit = 1000))
 summary(GMM_guich)
 
-emmeans(GMM_guich, pairwise ~ temp*Associative_Trial)
-emmeans(GMM_guich, pairwise ~ cort*Associative_Trial)
 emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
 
+# Generalized Mixed Models delicata REVERSAL
+GMM_deli_rev <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = binomial(link = "logit"))
+summary(GMM_deli)
+
+emmeans(GMM_deli_rev, pairwise ~ cort*temp*trial_reversal)
+emmeans(GMM_deli_rev, pairwise ~ temp*trial_reversal)
+
+# Generalized Mixed Models guichenoti REVERSAL
+MM_guich <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = binomial(link = "logit"))
+summary(GMM_guich)
+
+emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
+```
+
+```{r, models2}
 ```

### 2023-11-22 .vdoc.r

@@ -143,22 +143,35 @@ guich_reversal <- data_reversal %>% filter (species == "guichenoti")
 #| label: models1
 #| echo: false
 #| warning: false
-
+library(emmeans)
+library(lme4)
 # Generalized Mixed Models delicata
 GMM_deli <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
 summary(GMM_deli)
-
 emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
-emmeans(GMM_deli, pairwise ~ cort*Associative_Trial)
+emmeans(GMM_deli, pairwise ~ cort*temp*Associative_Trial)
 
 # Generalized Mixed Models guichenoti
-GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"))
+GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"), control = glmerControl(maxit = 1000))
 summary(GMM_guich)
 
-emmeans(GMM_guich, pairwise ~ temp*Associative_Trial)
-emmeans(GMM_guich, pairwise ~ cort*Associative_Trial)
 emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
 
+# Generalized Mixed Models delicata REVERSAL
+GMM_deli_rev <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = binomial(link = "logit"))
+summary(GMM_deli)
+
+emmeans(GMM_deli_rev, pairwise ~ cort*temp*trial_reversal)
+emmeans(GMM_deli_rev, pairwise ~ temp*trial_reversal)
+
+# Generalized Mixed Models guichenoti REVERSAL
+MM_guich <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = binomial(link = "logit"))
+summary(GMM_guich)
+
+emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
+#
+#
+#
 #
 #
 #

### 2023-11-23 .vdoc.r
Updates

@@ -1,366 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
-
-source(here("R", "func.R"))
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: dataload
-#| echo: false
-#| warning: false
- 
-# Load data
-	data  <-  read.csv("./data/Learning.csv")
-#
-#
-#
-#| label: dataclean
-#| echo: false
-#| warning: false
-
-# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
-data_associative <- data %>%
-  group_by(lizard_id) %>%
-    filter(sum(is.na(FC_associative)) <= 15) %>%
-    filter(trial_associative <= 35) %>%
-  ungroup()  %>% 
-    mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>% 
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"), 
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
-    mutate(temp = factor(temp,
-     levels = c("23", "28"), 
-     labels=c("23"="Cold", "28"="Hot"))) %>%
-    mutate(cort = factor(cort,
-     levels = c("A", "B"), 
-     labels=c("A"="Control", "B"="CORT"))) %>%
-  data.frame()
-
-data_reversal <- data %>%
-  group_by(lizard_id) %>%
-    filter(sum(is.na(FC_reversal)) <= 15) %>%
-   ungroup()  %>% 
-    mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>% 
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"), 
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
[…]

### 2023-11-23 R/1_data_process.R

@@ -3,16 +3,47 @@
 ####################################
 
 ## Load packages
-	intstall.packages("pacman")
-	pacman::p_load(tidyverse, readxl)
+	install.packages("pacman")
+	pacman::p_load(tidyverse, readxl, ggplot2, dplyr, magrittr)
 
 ## Load data	
-	              activ_files <- list.files("./data/Activity/")
-	       data_activity_list <- lapply(activ_files, function(x) read_xlsx(paste0("./data/Activity/", x))[-c(1:3),])
-	names(data_activity_list) <- activ_files
+data<-read.csv("./data/learning.csv")
+
+data<- data %>%
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(temp = factor(temp,
+     levels = c("23", "28"), 
+     labels=c("23"="Cold", "28"="Hot"))) %>%
+    mutate(cort = factor(cort,
+     levels = c("A", "B"), 
+     labels=c("A"="Control", "B"="CORT"))) %>%
+	mutate(species = factor(species,
+	 labels=c("delicata"="L. delicata", "guichenoti"="L. guichenoti")))
+  data.frame()
+
+
+## Histogram ages by treatment
+hist<-ggplot(data, aes(x = age.start, y = ..density..)) +  
+  geom_density(alpha = 0.7,
+  aes(fill = interaction(cort, temp))) +
+  scale_fill_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
+    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
+  ) +
+  facet_wrap(~species, scales = "free_y", ncol = 2) +  
+  theme(strip.background = element_blank()) +
+  labs(y="", x = "Age") +
+  theme_classic() +
+  theme(
+    axis.title = element_text(size = 18, family = "sans"),  
+    axis.text = element_text(size = 10, family = "sans"),  
+    legend.title = element_text(size = 14, family = "sans"), 
+    legend.text = element_text(size = 12, family = "sans")  
+  )
+print(hist)
+ggsave("./output/figures/hist.png", plot=hist, width = 30, height = 12, units = "cm", dpi = 3000) 
 
 ## Merge
-	data_activity <- dplyr::bind_rows(data_activity_list, .id = "id")
 
 
 

### 2023-11-23 R/1_data_process.R
Updates

@@ -41,7 +41,7 @@ hist<-ggplot(data, aes(x = age.start, y = ..density..)) +
     legend.text = element_text(size = 12, family = "sans")  
   )
 print(hist)
-ggsave("./output/figures/hist.png", plot=hist, width = 30, height = 12, units = "cm", dpi = 3000) 
+ggsave("./output/figures/hist.png", plot=hist, width = 30, height = 12, units = "cm", dpi = 1000) 
 
 ## Merge
 

### 2023-12-14 ms.qmd
Update ms.qmd

@@
 
-[@ODea2019]
+Cognition can be defined as the mechanisms by which animals acquire, process, and store information from their environment through perception, learning, memory, and decision making (@shettleworth_2009); and it underpins several aspects of animals' ecology such as habitat selection, foraging decisions, mate choice, antipredatory strategies, and/or social behaviours (@dukas_evolutionary_2004).
+Among cognitive traits, learning represents the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) and is, as such, essential for dealing with environmental changes (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
+
+Effects of maternal effects and early environment on learning. Why temperature and GCs?
+
+Cognition it is affected by the conditions in which organisms develop (Burger, 1991; Lemaire et al., 2000; Amiel and Shine, 2012; Amiel et al., 2014; Abayarathna and Webb, 2020).
+
+Among these effects, maternal glucocorticoids (GCs) have been demonstrated to influence offspring phenotype across taxa (Lemaire et al., 2000; Belliure et al., 2004; Haussmann et al., 2012; Monaghan, 2014; Owen et al., 2018; Haq et al., 2021).
+For instance, restraint stress in pregnant rats leads to impairments in neurogenesis and learning (Lemaire et al., 2000; Zhu et al., 2004); and direct experimental elevation of maternal GCs can affect morphology and behaviour of lizards (Belliure et al., 2004; Owen et al., 2018).
+In this vein, the temperature at which embryos develop (also referred as early thermal environment) is a pervasive mechanism of phenotypic variation in ectotherms (Noble et al., 2017); having substantial and unpredictable effects on diverse traits such as growth (Shine et al., 1995), behaviour (Burger, 1989; 1990; 1991; Dayananda and Webb, 2017; Vila-Pouca et al., 2018; 2019), and survival (Burger, 1989; Vila-Pouca et al., 2019).
+
+How are temperature and GCs related to each other?
+Metabolic effects, effects on the brain morphology and function.
+
+Objectives, hypothesis and predictions
+
+Here, we investigated how prenatal Corticosterone (CORT) - the main GCs in reptiles - and incubation temperature interact to shape learning abilities in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+guichenoti_).
+We experimentally increased CORT levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
+Then, we subjected the juveniles to a colour-associative and a reversal task to explore their learning skills.
+We hypothesized that changes in CORT levels and temperature during development will have sustained effects on brain's morphology, physiology, and gene expression, ultimately affecting learning skills.
+We predicted that individuals exposed to high levels of CORT and/or low temperatures will perform worse in the learning tasks than control individuals or individuals exposed to high temperatures.
+We also expected incubation at high temperatures to decrease the impact of CORT on learning, while cold incubation temperatures were expected to increase CORT detrimental effects.
 

### 2023-12-19 ms.qmd
Updates CODE

@@
 
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
 
@@
 
-```{r, dataload}
-#| label: dataload
-#| echo: false
-#| warning: false
-
-# Load data
-	data  <-  read.csv("./data/Learning.csv")
-```
-
-```{r, dataclean}
-#| label: dataclean
-#| echo: false
-#| warning: false
-
-# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
-data_associative <- data %>%
-  group_by(lizard_id) %>%
-    filter(sum(is.na(FC_associative)) <= 15) %>%
-    filter(trial_associative <= 35) %>%
-  ungroup()  %>% 
-    mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>% 
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"), 
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
-    mutate(temp = factor(temp,
-     levels = c("23", "28"), 
-     labels=c("23"="Cold", "28"="Hot"))) %>%
-    mutate(cort = factor(cort,
-     levels = c("A", "B"), 
-     labels=c("A"="Control", "B"="CORT"))) %>%
-  data.frame()
-
-data_reversal <- data %>%
-  group_by(lizard_id) %>%
-    filter(sum(is.na(FC_reversal)) <= 15) %>%
-   ungroup()  %>% 
-    mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>% 
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"), 
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
-    mutate(temp = factor(temp,
-     levels = c("23", "28"), 
-     labels=c("23"="Cold", "28"="Hot"))) %>%
-    mutate(cort = factor(cort,
-     levels = c("A", "B"), 
-     labels=c("A"="Control", "B"="CORT"))) %>%
-  data.frame()
-
-# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
-data_associative <- data_associative %>%
-  group_by(lizard_id) %>%
-  mutate(
-    first_non_na = min(which(!is.na(FC_associative))),
-    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
-    filter(Associative_Trial >= 1) %>%
-   ungroup() %>% data.frame()
-
-write.csv(data_associative, file= "./output/Checking/data_associative.csv")
-
-# Split data by species
-deli_associative <- data_associative %>% filter (species == "delicata")
-guich_associative <- data_associative %>% filter (species == "guichenoti")
-
-# Split data by species
-deli_reversal <- data_reversal %>% filter (species == "delicata")
-guich_reversal <- data_reversal %>% filter (species == "guichenoti")
-```
-
-```{r, models1}
-#| label: models1
-#| echo: false
-#| warning: false
-library(emmeans)
-library(lme4)
-# Generalized Mixed Models delicata
-GMM_deli <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
-summary(GMM_deli)
-emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
-emmeans(GMM_deli, pairwise ~ cort*temp*Associative_Trial)
-
-# Generalized Mixed Models guichenoti
-GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"), control = glmerControl(maxit = 1000))
-summary(GMM_guich)
-
-emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
-
-# Generalized Mixed Models delicata REVERSAL
-GMM_deli_rev <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = binomial(link = "logit"))
-summary(GMM_deli)
-
-emmeans(GMM_deli_rev, pairwise ~ cort*temp*trial_reversal)
-emmeans(GMM_deli_rev, pairwise ~ temp*trial_reversal)
-
-# Generalized Mixed Models guichenoti REVERSAL
-MM_guich <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = binomial(link = "logit"))
-summary(GMM_guich)
-
-emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
-```
-
-```{r, models2}
-```
-
-```{r, modelsasso}
-#| label: modelsasso
-#| echo: false
-#| warning: false
-
-# Bayesian model delicata
-  deli_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
-  summary(deli_mod)
-  plot(deli_mod)
-
-# Bayesian model guichenoti
-  guich_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
-  summary(guich_mod)
-  plot(guich_mod)
-# R2
-bayes_R2(deli_mod)
-bayes_R2(guich_mod)
-
-# Extract posteriors
-posterior <- posterior_samples(mod, pars = "^b")
-plyr::ldply(lapply(posterior, mean))
-plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
-temp23 <- c(posterior[,"b_Intercept"], (posterior[,"b_Intercept"]+ posterior[,"b_trtB_23"]))
-temp28 <- c((posterior[,"b_Intercept"] + posterior[,"b_trtB_28"]), posterior[,"b_trtB_23"])
-
-pmcmc(temp23 - temp28)
-dharma(GMM_deli2)
-
-```
-
-```{r, modelsrev}
-#| label: modelsrev
-#| echo: false
-#| warning: false
-
-# Bayesian model delicata
-  deli_rev <- brm(FC_reversal ~ cort*temp*trial_reversal + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
-  summary(deli_rev)
-  plot(deli_rev)
-
-# Bayesian model guichenoti
-  guich_rev <- brm(FC_reversal ~ cort*temp*trial_reversal + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
-  summary(guich_rev)
-  plot(guich_rev)
-# R2
-bayes_R2(deli_rev)
-bayes_R2(guich_rev)
-
-# Extract posteriors
-posterior <- posterior_samples(mod, pars = "^b")
-plyr::ldply(lapply(posterior, mean))
-plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
-temp23 <- c(posterior[,"b_Intercept"], (posterior[,"b_Intercept"]+ posterior[,"b_trtB_23"]))
-temp28 <- c((posterior[,"b_Intercept"] + posterior[,"b_trtB_28"]), posterior[,"b_trtB_23"])
-
-pmcmc(temp23 - temp28)
-dharma(GMM_deli2)
-
-```
-
-```{r, plots}
-#| label: plots
-#| echo: false
-#| warning: false
-
-# Plot delicata associative
-plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
-  stat_smooth(method = "glm", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
-  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
-    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
-  ) +
-  facet_wrap(deli_associative$group, scales = "free_y", ncol = 1) +
-  theme(strip.placement = "outside") +  
-  theme(strip.background = element_blank()) +
-  labs(y = "Probability of correct choice", x = "Trial") +
-  theme_classic() +
-  theme(
-    axis.title = element_text(size = 18, family = "sans"),  
-    axis.text = element_text(size = 10, family = "sans"),  
-    legend.title = element_text(size = 14, family = "sans"), 
-    legend.text = element_text(size = 12, family = "sans")  
-  )
-print(plot_deli)
-ggsave("./output/figures/fig_deli_asso.png", plot=plot_deli, width = 15, height = 12, units = "cm", dpi = 3000)
-
-# Plot guichenoti associative
-plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
-  stat_smooth(method = "glm", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
-  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
-    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
-  ) +
-  facet_wrap(guich_associative$group, scales = "free_y", ncol = 1) +
-  theme(strip.placement = "outside") +  
-  theme(strip.background = element_blank()) +
-  labs(y = "Probability of correct choice", x = "Trial") +
-  theme_classic() +
-  theme(
-    axis.title = element_text(size = 18, family = "sans"),  
-    axis.text = element_text(size = 10, family = "sans"),  
-    legend.title = element_text(size = 14, family = "sans"), 
-    legend.text = element_text(size = 12, family = "sans")  
-  )
-print(plot_guich)
-ggsave("./output/figures/fig_guich_asso.png", plot=plot_guich, width = 15, height = 12, units = "cm", dpi = 3000)
-
-# Plot delicata reversal
-label_mapping <- c("R_B" = "Blue", "B_R" = "Red")
-deli_reversal$group <- factor(deli_reversal$group, levels = levels(deli_reversal$group), labels = label_mapping)
-deli_rev <- ggplot(deli_reversal, aes(x = trial_reversal, y = FC_reversal, color=interaction(cort,temp))) +  
-  stat_smooth(method = "glm", formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
-  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
-    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
-  ) +
-  facet_wrap(~group, scales = "free_y", ncol = 1) +
-  theme(strip.placement = "outside") +  
-  theme(strip.background = element_blank()) +
-  labs(y="", x = "Trial", color="Treatments") +
-  theme_classic() +
-  theme(
-    axis.title = element_text(size = 18, family = "sans"),  
-    axis.text = element_text(size = 10, family = "sans"),  
-    legend.title = element_text(size = 14, family = "sans"), 
-    legend.text = element_text(size = 12, family = "sans")  
-  )
-print(deli_rev)
-ggsave("./output/figures/fig_deli_rev.png", plot=deli_rev, width = 15, height = 12, units = "cm", dpi = 3000)
-
-# Plot guichenoti reversal
-label_mapping <- c("R_B" = "Blue", "B_R" = "Red")
-guich_reversal$group <- factor(guich_reversal$group, levels = levels(deli_reversal$group), labels = label_mapping)
-guich_rev <- ggplot(guich_reversal, aes(x = trial_reversal, y = FC_reversal, color=interaction(cort,temp))) +  
-  stat_smooth(method = "glm", formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
-  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
-    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
-  ) +
-  facet_wrap(~group, scales = "free_y", ncol = 1) +
-  theme(strip.placement = "outside") +  
-  theme(strip.background = element_blank()) +
-  labs(y="", x = "Trial", color="Treatments") +
-  theme_classic() +
-  theme(
-    axis.title = element_text(size = 18, family = "sans"),  
-    axis.text = element_text(size = 10, family = "sans"),  
-    legend.title = element_text(size = 14, family = "sans"), 
-    legend.text = element_text(size = 12, family = "sans")  
-  )
-print(guich_rev)
-ggsave("./output/figures/fig_guich_rev.png", plot=guich_rev, width = 15, height = 12, units = "cm", dpi = 3000)
-
-```
-
 We calculated $R^2$ as follows

### 2023-12-19 .vdoc.r

@@ -1,0 +1,122 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+
+source(here("R", "func.R"))
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-fig1
+#| fig-cap: "Activity budget of the focal group of chacma baboons (Papio ursinus) at the Cape Peninsula, South Africa, during the study period. The data are presented as the mean percentage of time spent in each activity category per hour (± SE)."
+
+data %>% ggplot(aes(x = Lizard_id))  + geom_histogram()
+
+
+#
+#
+#
+#
+#
+#| label: tbl-tb1
+#| tbl-cap: "Summary of the data"
+
+tab <- data %>% 
+  group_by(Lizard_id) %>% 
+  summarise(
+    n = n()
+  ) 
+flextable(tab[2:3,])
+#
+#
+#
+#
+#

### 2023-12-19 R/1_data_process.R

@@ -2,51 +2,68 @@
 # 1_data_process
 ####################################
 
-## Load packages
-	install.packages("pacman")
-	pacman::p_load(tidyverse, readxl, ggplot2, dplyr, magrittr)
+# Packages
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
+source(here("R", "func.R"))
 
-## Load data	
-data<-read.csv("./data/learning.csv")
+# Load data
+data  <-  read.csv("./data/Learning.csv")
 
-data<- data %>%
+# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
+data_associative <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_associative)) <= 15) %>%
+    filter(trial_associative <= 35) %>%
+  ungroup()  %>% 
     mutate(temp = gsub("[AB]_", "", trt),
           cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"), 
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
     mutate(temp = factor(temp,
      levels = c("23", "28"), 
      labels=c("23"="Cold", "28"="Hot"))) %>%
     mutate(cort = factor(cort,
      levels = c("A", "B"), 
      labels=c("A"="Control", "B"="CORT"))) %>%
-	mutate(species = factor(species,
-	 labels=c("delicata"="L. delicata", "guichenoti"="L. guichenoti"))) %>%
   data.frame()
 
+data_reversal <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_reversal)) <= 15) %>%
+   ungroup()  %>% 
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>% 
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"), 
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
+    mutate(temp = factor(temp,
+     levels = c("23", "28"), 
+     labels=c("23"="Cold", "28"="Hot"))) %>%
+    mutate(cort = factor(cort,
+     levels = c("A", "B"), 
+     labels=c("A"="Control", "B"="CORT"))) %>%
[…]

### 2023-12-19 R/func.r

@@ -1,3 +1,226 @@
+```{r}
+#| label: setup
+
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+
+source(here("R", "func.R"))
+```
+
+
+
+```{r, models1}
+#| label: models1
+#| echo: false
+#| warning: false
+library(emmeans)
+library(lme4)
+# Generalized Mixed Models delicata
+GMM_deli <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
+summary(GMM_deli)
+emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
+emmeans(GMM_deli, pairwise ~ cort*temp*Associative_Trial)
+
+# Generalized Mixed Models guichenoti
+GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"), control = glmerControl(maxit = 1000))
+summary(GMM_guich)
+
+emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
+
+# Generalized Mixed Models delicata REVERSAL
+GMM_deli_rev <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = binomial(link = "logit"))
+summary(GMM_deli)
+
+emmeans(GMM_deli_rev, pairwise ~ cort*temp*trial_reversal)
+emmeans(GMM_deli_rev, pairwise ~ temp*trial_reversal)
+
+# Generalized Mixed Models guichenoti REVERSAL
+MM_guich <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = binomial(link = "logit"))
+summary(GMM_guich)
+
+emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
+```
+
+```{r, models2}
+```
+
+```{r, modelsasso}
+#| label: modelsasso
+#| echo: false
+#| warning: false
+
+# Bayesian model delicata
[…]

### 2023-12-23 ms.qmd
Update ms.qmd

@@
 
-Cognition can be defined as the mechanisms by which animals acquire, process, and store information from their environment through perception, learning, memory, and decision making (@shettleworth_2009); and it underpins several aspects of animals' ecology such as habitat selection, foraging decisions, mate choice, antipredatory strategies, and/or social behaviours (@dukas_evolutionary_2004).
-Among cognitive traits, learning represents the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) and is, as such, essential for dealing with environmental changes (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
+Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shettleworth_2009).
+These mechanisms underpin several aspects of animals' ecology such as habitat selection, foraging decisions, mate choice, antipredatory strategies, and/or social behaviours that are crucial for survival and reproduction (@dukas_evolutionary_2004).
+Particularly, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by allowing individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
+However, the ability of organisms to acquire new information varies accross individuals, with this natural variation usually being influenced by factors like age, sex, social system, gut microbiota, or the environment where animals develop (**REFS**).
+In this regard, the latter can be particularly relevant because the brain is especially sensitive to environmental impacts during early stages of development (**REFS**).
+These differences in neural development caused by prenatal environment can have long-lasting effects on learning skills (**REFS**).
+In this regard, prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa.
+GCs - **hormones related to organisms' response to changes in homeostasis (BEST DEF AND REF**) - can have sustained pysiological effects on neural structure and physiology associated with animals' performance on learning tasks (**Definition and REF**).
+In this sense, there is evidence that high prenatal GC levels impair with learning accross different taxa (**MORE EG.S AND REFS**; @lemaire_prenatal_2000; @zhu_prenatal_2004), but results vary depending on sex, or task (**REFS**).
+Also, some studies have revealed effects of prenatal temperature on learning in ectotherms (**REFS**).
+For instance, ...
+(**REFS**).
+In this vein, the effect of prenatal temperature has been associated with similar changes in neural structure and metabolic activity (**REFS**).
+However, despite both prenatal GCs and thermal environment are known to affect learning through similar mechanisms, the interaction between this two factors is still poorly understood.
+ In this study, we aim to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning using two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+guichenoti_), as our model species.
+We experimentally increased Corticosterone (CORT) - the main GC in reptiles - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
+Then, we subjected the juveniles to a colour-associative and a reversal task to explore their learning abilities.
+We hypothesise that changes in CORT levels and temperature during early development will have sustained effects on brain's morphology and physiology that will ultimately impact learning skills.
+We predicted that individuals exposed to high levels of CORT and/or low temperatures will perform worse in the learning tasks than control individuals or individuals exposed to high temperatures.
+We also expected incubation at high temperatures to decrease the impact of CORT on skink's performance, while cold incubation temperatures were expected to increase CORT detrimental effects on learning.
 
-Effects of maternal effects and early environment on learning. Why temperature and GCs?
-
-Cognition it is affected by the conditions in which organisms develop (Burger, 1991; Lemaire et al., 2000; Amiel and Shine, 2012; Amiel et al., 2014; Abayarathna and Webb, 2020).
-
-Among these effects, maternal glucocorticoids (GCs) have been demonstrated to influence offspring phenotype across taxa (Lemaire et al., 2000; Belliure et al., 2004; Haussmann et al., 2012; Monaghan, 2014; Owen et al., 2018; Haq et al., 2021).
-For instance, restraint stress in pregnant rats leads to impairments in neurogenesis and learning (Lemaire et al., 2000; Zhu et al., 2004); and direct experimental elevation of maternal GCs can affect morphology and behaviour of lizards (Belliure et al., 2004; Owen et al., 2018).
-In this vein, the temperature at which embryos develop (also referred as early thermal environment) is a pervasive mechanism of phenotypic variation in ectotherms (Noble et al., 2017); having substantial and unpredictable effects on diverse traits such as growth (Shine et al., 1995), behaviour (Burger, 1989; 1990; 1991; Dayananda and Webb, 2017; Vila-Pouca et al., 2018; 2019), and survival (Burger, 1989; Vila-Pouca et al., 2019).
-
-How are temperature and GCs related to each other?
-Metabolic effects, effects on the brain morphology and function.
-
-Objectives, hypothesis and predictions
-
-Here, we investigated how prenatal Corticosterone (CORT) - the main GCs in reptiles - and incubation temperature interact to shape learning abilities in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
-guichenoti_).
-We experimentally increased CORT levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
-Then, we subjected the juveniles to a colour-associative and a reversal task to explore their learning skills.
-We hypothesized that changes in CORT levels and temperature during development will have sustained effects on brain's morphology, physiology, and gene expression, ultimately affecting learning skills.
-We predicted that individuals exposed to high levels of CORT and/or low temperatures will perform worse in the learning tasks than control individuals or individuals exposed to high temperatures.
-We also expected incubation at high temperatures to decrease the impact of CORT on learning, while cold incubation temperatures were expected to increase CORT detrimental effects.
+**Cognition it is affected by the conditions in which organisms develop (Burger, 1991; Lemaire et al., 2000; Amiel and Shine, 2012; Amiel et al., 2014; Abayarathna and Webb, 2020).**
 
@@
 
-The subjects in our experiments were juveniles from two species of skinks, the common garden skink (*Lampropholis guichenoti*) and the rainbow skink or delicate skink (*L.
-delicata*).
-These are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia ([@chapple_know_2011]).
+_L.
+guichenoti_ and _L.
+delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia ([@chapple_know_2011]).
 They also have similar breeding periods, but with some differences in reproductive output: while *L.
@@
 guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season ([@chapple_know_2011]; [@chapple_biology_2014]).
-This difference in reproductive output through the breeding season may involve different degree of sensitivity to maternal effects and its interaction with other aspects of early environment.
 
@@
 There is a total of 270 and 180 adults of *L.
-delicata* and *L.* guichenoti respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+delicata* and *L.
+guichenoti* respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
 Enclosures are provided with non-stick matting, shelter, and several small water dishes.

### 2023-12-24 ms.qmd
Updates

@@
 
-source(here("R", "func.R"))
+source("./R/1_data_process.R")
+source("./R/func.r")
 ```
@@
 However, the ability of organisms to acquire new information varies accross individuals, with this natural variation usually being influenced by factors like age, sex, social system, gut microbiota, or the environment where animals develop (**REFS**).
-In this regard, the latter can be particularly relevant because the brain is especially sensitive to environmental impacts during early stages of development (**REFS**).
-These differences in neural development caused by prenatal environment can have long-lasting effects on learning skills (**REFS**).
-In this regard, prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa.
+In this regard, the latter can be particularly relevant because the brain is especially sensitive to environmental impacts during early stages of development (@zhu_prenatal_2004).
+These differences in neural development caused by early environment can have long-lasting effects on learning skills, and prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020).
 GCs - **hormones related to organisms' response to changes in homeostasis (BEST DEF AND REF**) - can have sustained pysiological effects on neural structure and physiology associated with animals' performance on learning tasks (**Definition and REF**).
@@
 
-INSERT Fig 1
+```{r, Fig1}
+#| label: fig-fig1
+#| fig-cap: ""
+knitr::include_graphics("./Others/LEARN_FIG_1.svg") 
+```
 
@@
 
-```{r, fig1}
-#| label: fig-fig1
-#| fig-cap: "Activity budget of the focal group of chacma baboons (Papio ursinus) at the Cape Peninsula, South Africa, during the study period.
-The data are presented as the mean percentage of time spent in each activity category per hour (± SE)."
-
-data %>% ggplot(aes(x = Lizard_id))  + geom_histogram()
-
-```
-
 We have a total of `r length(unique(data$Lizard_id))`

### 2023-12-24 .vdoc.r

@@ -1,122 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
-
-source(here("R", "func.R"))
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-fig1
-#| fig-cap: "Activity budget of the focal group of chacma baboons (Papio ursinus) at the Cape Peninsula, South Africa, during the study period. The data are presented as the mean percentage of time spent in each activity category per hour (± SE)."
-
-data %>% ggplot(aes(x = Lizard_id))  + geom_histogram()
-
-
-#
-#
-#
-#
-#
-#| label: tbl-tb1
-#| tbl-cap: "Summary of the data"
-
-tab <- data %>% 
-  group_by(Lizard_id) %>% 
-  summarise(
-    n = n()
-  ) 
-flextable(tab[2:3,])
-#
-#
-#
-#
-#

### 2023-12-24 R/func.r

@@ -1,11 +1,7 @@
-```{r}
-#| label: setup
 
+
+# Packages
 pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
-
-source(here("R", "func.R"))
-```
-
 
 
 ```{r, models1}

### 2023-12-24 ms.qmd
Updates

@@
 #| label: setup
-
 pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
-
-source("./R/1_data_process.R")
-source("./R/func.r")
 ```
@@
 
-Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shettleworth_2009).
+Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shet).
 These mechanisms underpin several aspects of animals' ecology such as habitat selection, foraging decisions, mate choice, antipredatory strategies, and/or social behaviours that are crucial for survival and reproduction (@dukas_evolutionary_2004).
@@
 
-We calculated $R^2$ as follows
-
-$$
-R^2 = \frac{SS_{reg}}{SS_{tot}}
-$$ {#eq-r2}
-
-@eq-r2
-
-We have a total of `r length(unique(data$Lizard_id))`
-
-```{r,tb1}
-#| label: tbl-tb1
-#| tbl-cap: "Summary of the data"
-
-tab <- data %>% 
-  group_by(Lizard_id) %>% 
-  summarise(
-    n = n()
-  ) 
-flextable(tab[2:3,])
-```
-
 # References

### 2023-12-24 R/func.r

@@ -229,3 +229,30 @@ pmcmc <- function(x, null = 0, twotail = TRUE){
     (1 - max(table(x<=null) / length(x)))
   }
 }
+
+
+
+
+
+We calculated $R^2$ as follows
+
+$$
+R^2 = \frac{SS_{reg}}{SS_{tot}}
+$$ {#eq-r2}
+
+@eq-r2
+
+
+We have a total of `r length(unique(data$Lizard_id))`
+
+```{r,tb1}
+#| label: tbl-tb1
+#| tbl-cap: "Summary of the data"
+
+tab <- data %>% 
+  group_by(Lizard_id) %>% 
+  summarise(
+    n = n()
+  ) 
+flextable(tab[2:3,])
+```

### 2023-12-24 ms.qmd
Update ms.qmd

@@
 
-Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shet).
+Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making ().
 These mechanisms underpin several aspects of animals' ecology such as habitat selection, foraging decisions, mate choice, antipredatory strategies, and/or social behaviours that are crucial for survival and reproduction (@dukas_evolutionary_2004).

### 2023-12-26 ms.qmd
Updates

@@
 
-Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making ().
-These mechanisms underpin several aspects of animals' ecology such as habitat selection, foraging decisions, mate choice, antipredatory strategies, and/or social behaviours that are crucial for survival and reproduction (@dukas_evolutionary_2004).
+Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shettleworth).
+These mechanisms underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours that are crucial for survival and reproduction (@dukas_evolutionary_2004).
 Particularly, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by allowing individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
-However, the ability of organisms to acquire new information varies accross individuals, with this natural variation usually being influenced by factors like age, sex, social system, gut microbiota, or the environment where animals develop (**REFS**).
+However, the ability of organisms to acquire new information varies accross individuals, with this natural variation usually being influenced by factors like age, sex, gut microbiota, or the environment where animals develop (@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014).
 In this regard, the latter can be particularly relevant because the brain is especially sensitive to environmental impacts during early stages of development (@zhu_prenatal_2004).
-These differences in neural development caused by early environment can have long-lasting effects on learning skills, and prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020).
-GCs - **hormones related to organisms' response to changes in homeostasis (BEST DEF AND REF**) - can have sustained pysiological effects on neural structure and physiology associated with animals' performance on learning tasks (**Definition and REF**).
-In this sense, there is evidence that high prenatal GC levels impair with learning accross different taxa (**MORE EG.S AND REFS**; @lemaire_prenatal_2000; @zhu_prenatal_2004), but results vary depending on sex, or task (**REFS**).
-Also, some studies have revealed effects of prenatal temperature on learning in ectotherms (**REFS**).
-For instance, ...
-(**REFS**).
-In this vein, the effect of prenatal temperature has been associated with similar changes in neural structure and metabolic activity (**REFS**).
-However, despite both prenatal GCs and thermal environment are known to affect learning through similar mechanisms, the interaction between this two factors is still poorly understood.
+Prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020).
+GCs - hormones related to organisms' response to stress (@sapolsky_how_2000) - can have sustained effects on neural structure and physiology that are associated with animals' performance on learning tasks (@lemaire_prenatal_2000; @zhu_prenatal_2004; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
+Some studies have demonstrated that prenatal stress and high prenatal GC levels impair with learning (@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn), while others revealed that these effects may vary depending on aspects like sex or learning task (@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
+Similarly, diverse experiments have shown pivotal impacts of prenatal temperature on learning in ectotherms (@amiel_hotter_2012; @amiel_egg_2014;).
+For instance, high incubation temperatures have been linked with faster learning rates in skinks (@amiel_hotter_2012; @amiel_egg_2014), but velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits (@abayarathna_effects_2020).
+In this vein, the effect of prenatal temperature has been linked to alterations in neural structure and metabolic activity (@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021) that are similar to those resulting from prenatal increased stress or GC levels (@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009).
+This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, as such, both may interact to shape individual variation on learning skills (@amiel_effects_2017; @noble_developmental_2018).
+Furthermore, GCs can play an important role in determining vertebrate responses to elevated temperatures (@Crino_2023) potentially driving to natural interactions between temperature and GCs.
+However, despite the similar mechanistic effects of prenatal GCs and temperature and the potential function of GCs in vertebrates response to elevated temperatures, our understanding of how these two factors interplay remains incomplete.
 In this study, we aim to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning using two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_), as our model species.
-We experimentally increased Corticosterone (CORT) - the main GC in reptiles - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
+We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents (@Crino_2023) - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
 Then, we subjected the juveniles to a colour-associative and a reversal task to explore their learning abilities.
-We hypothesise that changes in CORT levels and temperature during early development will have sustained effects on brain's morphology and physiology that will ultimately impact learning skills.
-We predicted that individuals exposed to high levels of CORT and/or low temperatures will perform worse in the learning tasks than control individuals or individuals exposed to high temperatures.
-We also expected incubation at high temperatures to decrease the impact of CORT on skink's performance, while cold incubation temperatures were expected to increase CORT detrimental effects on learning.
-
-**Cognition it is affected by the conditions in which organisms develop (Burger, 1991; Lemaire et al., 2000; Amiel and Shine, 2012; Amiel et al., 2014; Abayarathna and Webb, 2020).**
+We hypothesised that changes in CORT levels and temperature during early development would have sustained effects on brain's morphology and physiology that would ultimately impact learning skills.
+We predicted that individuals exposed to high levels of CORT and/or low temperatures would perform worse in the learning tasks than control individuals or individuals exposed to high temperatures.
+We also expected incubation at high temperatures to decrease the impact of CORT on skink's performance, while cold incubation temperatures are expected to increase CORT detrimental effects on learning.
 
@@
 
-Two weeks before we started the training phase (see below), lizards were moved to the experimental arena (Fig.
-1c) for acclimatation.
+Two weeks before we started the training phase (see below), lizards were moved to the experimental arena  for acclimatation.
 The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
@@
 
-```{r, Fig1}
-#| label: fig-fig1
-#| fig-cap: ""
-knitr::include_graphics("./Others/LEARN_FIG_1.svg") 
-```
-
 ### Learning
@@
 To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (Fig.
-2) (see [@leal_behavioural_2012]; [@clark_colour_2014]).
+1b) (see [@leal_behavioural_2012]; [@clark_colour_2014]).
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
 We divided this training phase into three stages (see Fig.
-2): in the first stage, lizards had to eat a small, frozen cricket (*A.
+1b): in the first stage, lizards had to eat a small, frozen cricket (*A.
 domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure; in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps; and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage.
@@
 In the next phase, we trained lizards to associate between colour and a food reward (colour association task in Fig.
-2).
+1b).
 The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour.
@@
 
-INSERT Fig 2
+```{r, Fig1}
+#| label: fig-fig1
+#| fig-cap: ""
+knitr::include_graphics("./Others/LEARN_FIG_1.svg") 
+```
 

### 2023-12-26 ms.qmd
Updates

@@
 Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shettleworth).
-These mechanisms underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours that are crucial for survival and reproduction (@dukas_evolutionary_2004).
-Particularly, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by allowing individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
-However, the ability of organisms to acquire new information varies accross individuals, with this natural variation usually being influenced by factors like age, sex, gut microbiota, or the environment where animals develop (@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014).
-In this regard, the latter can be particularly relevant because the brain is especially sensitive to environmental impacts during early stages of development (@zhu_prenatal_2004).
+These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, all crucial for the survival and reproduction of animals (@dukas_evolutionary_2004).
+Notably, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
+However, the capacity of individuals to acquire new information exhibits natural variation influenced by factors like age, sex, gut microbiota, or the environment where animals develop (@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning).
+The developmental environment, in particular, plays a pivotal role, as the brain is especially susceptible to environmental influences during early stages of development (@zhu_prenatal_2004).
 Prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020).
-GCs - hormones related to organisms' response to stress (@sapolsky_how_2000) - can have sustained effects on neural structure and physiology that are associated with animals' performance on learning tasks (@lemaire_prenatal_2000; @zhu_prenatal_2004; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
-Some studies have demonstrated that prenatal stress and high prenatal GC levels impair with learning (@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn), while others revealed that these effects may vary depending on aspects like sex or learning task (@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
-Similarly, diverse experiments have shown pivotal impacts of prenatal temperature on learning in ectotherms (@amiel_hotter_2012; @amiel_egg_2014;).
-For instance, high incubation temperatures have been linked with faster learning rates in skinks (@amiel_hotter_2012; @amiel_egg_2014), but velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits (@abayarathna_effects_2020).
-In this vein, the effect of prenatal temperature has been linked to alterations in neural structure and metabolic activity (@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021) that are similar to those resulting from prenatal increased stress or GC levels (@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009).
-This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, as such, both may interact to shape individual variation on learning skills (@amiel_effects_2017; @noble_developmental_2018).
-Furthermore, GCs can play an important role in determining vertebrate responses to elevated temperatures (@Crino_2023) potentially driving to natural interactions between temperature and GCs.
-However, despite the similar mechanistic effects of prenatal GCs and temperature and the potential function of GCs in vertebrates response to elevated temperatures, our understanding of how these two factors interplay remains incomplete.
-In this study, we aim to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning using two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
-guichenoti_), as our model species.
+GCs - hormones related to organisms' response to stress (@sapolsky_how_2000) - exert sustained effects on neural structure and physiology that are associated with animals' performance on learning tasks (@lemaire_prenatal_2000; @zhu_prenatal_2004; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
+Some studies have demonstrated that prenatal stress and high prenatal GC levels impair with learning (@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn), while others showed diverse effects depending on factors such as sex or the nature of the learning task (@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
+Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms (@amiel_hotter_2012; @amiel_egg_2014;).
+For instance, high incubation temperatures have been linked with faster learning rates in skinks (@amiel_hotter_2012; @amiel_egg_2014), while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits (@abayarathna_effects_2020).
+In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity (@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021) that are similar to those resulting from prenatal increased stress or GC levels (@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009).
+This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning skills (@amiel_effects_2017; @noble_developmental_2018).
+Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures (@Crino_2023) potentially fostering natural interactions between temperature and GCs.
+Despite the proximate similarities of prenatal GCs and temperature effects and the potential role of GCs in vertebrates response to elevated temperatures, our understanding of how these two factors interact remains incomplete.
+In this study, our objective is to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning.
+We utilized two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+guichenoti_), as model species.
 We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents (@Crino_2023) - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
-Then, we subjected the juveniles to a colour-associative and a reversal task to explore their learning abilities.
-We hypothesised that changes in CORT levels and temperature during early development would have sustained effects on brain's morphology and physiology that would ultimately impact learning skills.
-We predicted that individuals exposed to high levels of CORT and/or low temperatures would perform worse in the learning tasks than control individuals or individuals exposed to high temperatures.
-We also expected incubation at high temperatures to decrease the impact of CORT on skink's performance, while cold incubation temperatures are expected to increase CORT detrimental effects on learning.
+Post-incubation, the juveniles were subjectd to a colour-associative and a reversal task to comprehensively assess their learning abilities.
+Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's morphology and physiology that will ultimately impact learning skills.
+We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently in the learning tasks compared to control individuals or those exposed to high temperatures.
+Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
 

### 2023-12-27 ms.qmd
Updates

@@
 Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shettleworth).
-These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, all crucial for the survival and reproduction of animals (@dukas_evolutionary_2004).
-Notably, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
+These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, that are crucial for the survival and reproduction of animals (@dukas_evolutionary_2004).
+Particularly, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
 However, the capacity of individuals to acquire new information exhibits natural variation influenced by factors like age, sex, gut microbiota, or the environment where animals develop (@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning).
 The developmental environment, in particular, plays a pivotal role, as the brain is especially susceptible to environmental influences during early stages of development (@zhu_prenatal_2004).
-Prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020).
+Hence, investigating the effects of the developmental environment on learning can be essential to understand the evolution of learning and predict animals' responses towards environmental change.
+In this sense, prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020).
 GCs - hormones related to organisms' response to stress (@sapolsky_how_2000) - exert sustained effects on neural structure and physiology that are associated with animals' performance on learning tasks (@lemaire_prenatal_2000; @zhu_prenatal_2004; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
 Some studies have demonstrated that prenatal stress and high prenatal GC levels impair with learning (@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn), while others showed diverse effects depending on factors such as sex or the nature of the learning task (@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
-Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms (@amiel_hotter_2012; @amiel_egg_2014;).
+Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms (@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020).
 For instance, high incubation temperatures have been linked with faster learning rates in skinks (@amiel_hotter_2012; @amiel_egg_2014), while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits (@abayarathna_effects_2020).
-In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity (@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021) that are similar to those resulting from prenatal increased stress or GC levels (@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009).
-This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning skills (@amiel_effects_2017; @noble_developmental_2018).
+In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity (@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021) that share some similarities with those resulting from prenatal increased stress or GC levels (@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009).
+This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning skills (@noble_developmental_2018).
 Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures (@Crino_2023) potentially fostering natural interactions between temperature and GCs.
@@
 guichenoti_ and _L.
-delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia ([@chapple_know_2011]).
+delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia (@chapple_know_2011).
 They also have similar breeding periods, but with some differences in reproductive output: while *L.
 delicata* lays 1 to 6 eggs in only one clutch per season, *L.
-guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season ([@chapple_know_2011]; [@chapple_biology_2014]).
+guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season (@chapple_know_2011; @chapple_biology_2014).
 
@@
 The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
-During acclimatation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum.* We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
+During acclimatation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
+We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
 The rooms temperature was set to between 22-24 Celsius.
-We tested temperatures with laser temperature guns to ensure such a set up established a thermal gradient and we there were no significant differences between treatments or species (see Supplementary Material).
 
 ### CORT and Temperature manipulation
-
 To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (Fig.
 1a).
-We first allocated eggs to one of two different treatments: in one of the treatments, eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); while eggs in the other group (Control treatment) received an equal volume of the vehicle.
+We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
 CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
@@
 ### Learning
-
 To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (Fig.
-1b) (see [@leal_behavioural_2012]; [@clark_colour_2014]).
+1b) (see @leal_behavioural_2012; @clark_colour_2014).
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
-We divided this training phase into three stages (see Fig.
-1b): in the first stage, lizards had to eat a small, frozen cricket (*A.
-domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure; in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps; and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage.
+We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A.
+domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (Fig.
+1B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (Fig.
+1B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
+1B, Stage 3).
 Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
@@
 Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials.
-This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase (see Supplementary material).
-
-In the next phase, we trained lizards to associate between colour and a food reward (colour association task in Fig.
+This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
+In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig.
 1b).
@@
 We placed the food reward (small, frozen, *A.
-domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in one ramp.
-The food reward was placed in all three wells to avoid the use of chemical cues to determine the correct choice; our lids had a series of small holes on the top for the same reason.
-The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours (REF).
-To control for potential colour preference that could bias our results, we split the subjects in two groups counterbalanced by treatment and species; in one group the correct choice (i.e., the ramp with non-covered cricket) was the blue one in the associative task and red in the reversal, while we did the opposite for the other half.
+domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
+The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals.
+The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours (@Baden_Osorio_2019_Vert_vision).
+To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with non-covered cricket) was the blue one in the associative task and red in the reversal (see below), while we did the opposite for the other group.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
 Lizards were tested in this task once a day for 35 days.
-
-After the colour association phase, we performed a choice reversal task.
+After the colour association phase, we performed a choice reversal task (Reversal task in Fig.
+1B).
 This task was like the colour association test, except that the attainability of prey was indicated by a different colour, requiring the lizards to form a novel association between the new colour and the food reward.
 This test was done once a day for 40 days.
-
 All trials were done daily between the 6^th^ of March until the 26^th^ of June 2023, beginning at 11 am until 12 pm.
@@
 Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not.
+A choice was considered to be made if the head of the lizard was inside the well of one of the ramps.
+PR was blinded to the treatments of the lizards during the analyses of the video.
+We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
 
@@
 #| label: fig-fig1
-#| fig-cap: ""
+#| fig-cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**).
+Stages 1-3 indicate the different phases of the habituation process.
+In the associative and reversal tasks, white lids indicate the ramps where the food reward was not attainable."
 knitr::include_graphics("./Others/LEARN_FIG_1.svg") 

### 2023-12-28 R/1_data_process.R
Updates CODE

@@ -14,36 +14,36 @@ data_associative <- data %>%
   group_by(lizard_id) %>%
     filter(sum(is.na(FC_associative)) <= 15) %>%
     filter(trial_associative <= 35) %>%
-  ungroup()  %>% 
+  ungroup()  %>%
     mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>% 
+          cort = gsub("_[2][38]", "", trt))  %>%
     mutate(group = factor(group,
-     levels = c("R_B", "B_R"), 
+     levels = c("R_B", "B_R"),
      labels=c("R_B"="Red", "B_R"="Blue"))) %>%
     mutate(temp = factor(temp,
-     levels = c("23", "28"), 
+     levels = c("23", "28"),
      labels=c("23"="Cold", "28"="Hot"))) %>%
     mutate(cort = factor(cort,
-     levels = c("A", "B"), 
+     levels = c("A", "B"),
      labels=c("A"="Control", "B"="CORT"))) %>%
   data.frame()
 
 data_reversal <- data %>%
   group_by(lizard_id) %>%
     filter(sum(is.na(FC_reversal)) <= 15) %>%
-   ungroup()  %>% 
+   ungroup()  %>%
     mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>% 
+          cort = gsub("_[2][38]", "", trt))  %>%
     mutate(group = factor(group,
-     levels = c("R_B", "B_R"), 
+     levels = c("R_B", "B_R"),
      labels=c("R_B"="Red", "B_R"="Blue"))) %>%
     mutate(temp = factor(temp,
-     levels = c("23", "28"), 
+     levels = c("23", "28"),
      labels=c("23"="Cold", "28"="Hot"))) %>%
     mutate(cort = factor(cort,
-     levels = c("A", "B"), 
+     levels = c("A", "B"),
      labels=c("A"="Control", "B"="CORT"))) %>%
-  data.frame() 
+  data.frame()
 
 # Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
 data_associative <- data_associative %>%
@@ -52,18 +52,19 @@ data_associative <- data_associative %>%
     first_non_na = min(which(!is.na(FC_associative))),
[…]

### 2023-12-28 R/2_models.R

@@ -1,0 +1,107 @@
+####################################
+# 2_Models
+####################################
+
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
+source(here("R", "func.R"))
+
+######## 2.B) EXTRACT POSTERIORS FOR ALL MODELS
+
+posterior <- posterior_samples(deli_mod, pars = "^b")
+plyr::ldply(lapply(posterior, mean))
+plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
+
+######## 2.C) pmcmc FOR ALL MODELS
+
+# pmcmc for differences between 'Groups'
+
+# Also pmcmc for differences between both species
+
+
+######## 2.D) MAKE TABLE WITH POSTERIORS AND pmcmc
+
+
+######## 2.E) PLOTS MODELS 
+# Plot delicata associative
+plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +
+  stat_smooth(method = "glm", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
+  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
+    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
+  ) +
+  facet_wrap(deli_associative$group, scales = "free_y", ncol = 1) +
+  theme(strip.placement = "outside") +  
+  theme(strip.background = element_blank()) +
+  labs(y = "Probability of correct choice", x = "Trial") +
+  theme_classic() +
+  theme(
+    axis.title = element_text(size = 18, family = "sans"),
+    axis.text = element_text(size = 10, family = "sans"),
+    legend.title = element_text(size = 14, family = "sans"),
+    legend.text = element_text(size = 12, family = "sans")
+  )
+print(plot_deli)
+ggsave("./output/figures/fig_deli_asso.png", plot=plot_deli, width = 15, height = 12, units = "cm", dpi = 3000)
+ 
+# Plot guichenoti associative
+plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +
[…]

### 2023-12-28 R/3_supplementary.R

@@ -1,0 +1,26 @@
+####################################
+# 3_Supplementary material
+####################################
+
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
+source(here("R", "func.R"))
+
+## Histogram ages by treatment
+hist<-ggplot(data, aes(x = age.start, y = after_stat(density))) +  
+  geom_density(alpha = 0.7,
+  aes(fill = interaction(cort, temp))) +
+  scale_fill_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
+    labels=c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
+  ) +
+  facet_wrap(~species, scales = "free_y", ncol = 2) +  
+  theme(strip.background = element_blank()) +
+  labs(y="Density", x = "Age", fill="Treatments") +
+  theme_classic() +
+  theme(
+    axis.title = element_text(size = 18, family = "sans"),  
+    axis.text = element_text(size = 10, family = "sans"),  
+    legend.title = element_text(size = 14, family = "sans"), 
+    legend.text = element_text(size = 12, family = "sans")  
+  )
+print(hist)
+ggsave("./output/figures/hist.png", plot=hist, width = 30, height = 12, units = "cm", dpi = 1000) 

### 2023-12-28 R/func.r

@@ -1,221 +1,62 @@
-
-
-# Packages
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
-
-
-```{r, models1}
-#| label: models1
-#| echo: false
-#| warning: false
-library(emmeans)
-library(lme4)
-# Generalized Mixed Models delicata
-GMM_deli <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
-summary(GMM_deli)
-emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
-emmeans(GMM_deli, pairwise ~ cort*temp*Associative_Trial)
-
-# Generalized Mixed Models guichenoti
-GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"), control = glmerControl(maxit = 1000))
-summary(GMM_guich)
-
-emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
-
-# Generalized Mixed Models delicata REVERSAL
-GMM_deli_rev <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = binomial(link = "logit"))
-summary(GMM_deli)
-
-emmeans(GMM_deli_rev, pairwise ~ cort*temp*trial_reversal)
-emmeans(GMM_deli_rev, pairwise ~ temp*trial_reversal)
-
-# Generalized Mixed Models guichenoti REVERSAL
-MM_guich <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = binomial(link = "logit"))
-summary(GMM_guich)
-
-emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
-```
-
-```{r, models2}
-```
-
-```{r, modelsasso}
-#| label: modelsasso
-#| echo: false
-#| warning: false
-
-# Bayesian model delicata
[…]

### 2023-12-28 .vdoc.r
Updates

@@ -1,0 +1,104 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-fig1
+#| fig-cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids indicate the ramps where the food reward was not attainable."
+knitr::include_graphics("./Others/LEARN_FIG_1.svg") 
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: models
+#### The function here is to fit all the (brm) models for future analyses using the databases from output/clean_databases already processed using the code in "1_data_process.R"
+source(here("R", "func.R"))
+# A) Associative task
+### L. delicata
+deli_asso<-fit_asso(here("output/databases_clean/deli_associative.csv"))
+### L. guichenoti
+guich_asso<-fit_asso(here("output/databases_clean/guich_associative.csv"))
+
+# B) Reversal task
+### L. delicata
+deli_rev<-fit_rev(here("output/databases_clean/deli_reversal.csv"))
+### L. guichenoti
+guich_rev<-fit_rev(here("output/databases_clean/guich_reversal.csv"))
+#
+#
+#
+#| label: posteriors
+#### The function here is to extract the posteriors of the models fitted in the previous chunk
+source(here("R", "func.R"))
+posteriors_deli_asso <- extract_posteriors(deli_asso)
+emm_results <- emmeans(deli_asso, specs = ~trial_associative:temp:cort)
+emm_results <- emmeans(deli_asso, specs = ~trial_associative:group)
+emm_results <- emmeans(deli_asso, specs = ~trial_associative:temp)
+emm_results <- emmeans(deli_asso, specs = ~trial_associative:cort)
+summary(emm_results, infer = TRUE)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#

### 2023-12-28 R/1_data_process.R

@@ -3,7 +3,7 @@
 ####################################
 
 # Packages
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, forcats)
 source(here("R", "func.R"))
 
 # Load data
@@ -43,6 +43,7 @@ data_reversal <- data %>%
     mutate(cort = factor(cort,
      levels = c("A", "B"),
      labels=c("A"="Control", "B"="CORT"))) %>%
+    mutate(trial_reversal = ordered(trial_reversal)) %>%
   data.frame()
 
 # Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
@@ -52,6 +53,7 @@ data_associative <- data_associative %>%
     first_non_na = min(which(!is.na(FC_associative))),
     Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
     filter(Associative_Trial >= 1) %>%
+    mutate(Associative_Trial = fct_inorder(as.factor(Associative_Trial))) %>%
   ungroup() %>% 
   data.frame()
   

### 2023-12-28 R/2_models.R

@@ -1,11 +1,33 @@
 ####################################
-# 2_Models
+# 2_MODELS
 ####################################
-
 pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
+#
+######## 2.A) BUILD ALL MODELS
+#### The function here is to fit all the (brm) models for future analyses using the databases from output/clean_databases already processed using the code in "1_data_process.R"
 source(here("R", "func.R"))
-
+# A) Associative task
+### L. delicata
+deli_asso<-fit_asso(here("output/databases_clean/deli_associative.csv"))
+### L. guichenoti
+guich_asso<-fit_asso(here("output/databases_clean/guich_associative.csv"))
+# B) Reversal task
+### L. delicata
+deli_rev<-fit_rev(here("output/databases_clean/deli_reversal.csv"))
+### L. guichenoti
+guich_rev<-fit_rev(here("output/databases_clean/guich_reversal.csv"))
+#
+#
 ######## 2.B) EXTRACT POSTERIORS FOR ALL MODELS
+source(here("R", "func.R"))
+posteriors_deli_asso <- extract_posteriors(deli_asso)
+posteriors_guich_asso <- extract_posteriors(guich_asso)
+posteriors_deli_rev <- extract_posteriors(deli_rev)
+posteriors_guich_rev <- extract_posteriors(guich_rev)
+#
+emtrends_results <- emtrends(deli_asso, ~ cort * temp * Associative_Trial|group, var = "Associative_Trial", infer = TRUE)
+# Display the results
+summary(emtrends_results)
 
 posterior <- posterior_samples(deli_mod, pars = "^b")
 plyr::ldply(lapply(posterior, mean))

### 2023-12-28 R/func.r

@@ -1,7 +1,7 @@
 #################### 
 # PACKAGES
 ####################
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, pmcmc)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
 #
 #################### 
 # MODELS
@@ -16,7 +16,7 @@ fit_asso <- function(data_asso) {
   # Load the data
   data <- read.csv(data_asso)
   # Fit the model
-  model <- brm(FC_associative ~ cort*temp*trial_associative + group*trial_associative + (1 + trial_associative|lizard_id),
+  model <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id),
               data = data,
               family = bernoulli(link = "logit"),
               chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
@@ -32,29 +32,27 @@ fit_rev <- function(data_rev) {
   # Load the data
   data <- read.csv(data_rev)
   # Fit the model
-  model <- brm(FC_reversal ~ cort*temp*trial_reversal + group*trial_reversal (1 + trial_reversal|lizard_id),
+  model <- brm(FC_reversal ~ cort*temp*trial_reversal + group*trial_reversal + (1 + trial_reversal|lizard_id),
               data = data,
               family = bernoulli(link = "logit"),
               chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
 return(model)
 }
 #
-# Extract posteriors functions:
+# Extract posteriors function:
 #' @title extract_posteriors function
 #' @description Obtain posteriors for all factors from different models
 #' @param model Path to the model
 #' @return Data frame with posteriors
-posteriors <- function(model) {
+extract_posteriors <- function(model) {
   # Extract posteriors
-  extract_posteriors <- posterior_samples(model, pars = "^b")
+  posterior <- posterior_samples(model, pars = "^b")
   # Calculate means
   means <- plyr::ldply(lapply(posterior, mean))
   # Calculate quantiles
   quantiles <- plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
-  # Calculate p-values using pmcmc
[…]

### 2024-01-10 ms.qmd
Updates
Updates models and functions

@@
 
+```{r, cleaning}
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
+write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
+write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
+```
+
+```{r, models}
+#| label: models
+# fitting the model and extraction of posteriors for both types of task and species using fit_m function
+source(here("R", "func.R"))
+# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + Associative_Trial*group + (1 + Associative_Trial|lizard_id)
+## A.1) L. delicata
+deli_asso <- fit_m("asso", "deli")
+write.csv(deli_asso, file= "./output/Checking/deli_asso.csv")
+## A.2) L. guichenoti
+guich_asso <- fit_m("asso", "guich")
+write.csv(guich_asso, file= "./output/Checking/guich_asso.csv")
+# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + trial_reversal*group + (1 + trial_reversal|lizard_id)
+## B.1) L. delicata
+deli_rev <- fit_m("rev", "deli")
+write.csv(deli_rev, file= "./output/Checking/deli_rev.csv")
+## B.2) L. guichenoti
+guich_rev <- fit_m("rev", "guich")
+write.csv(guich_rev, file= "./output/Checking/guich_rev.csv")
+```
+
+```{r, results}
+```
+
+```{r, plots}
+```
+
 ## Results
 
-# References
+## References

### 2024-01-10 .vdoc.r

@@ -1,104 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-fig1
-#| fig-cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids indicate the ramps where the food reward was not attainable."
-knitr::include_graphics("./Others/LEARN_FIG_1.svg") 
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: models
-#### The function here is to fit all the (brm) models for future analyses using the databases from output/clean_databases already processed using the code in "1_data_process.R"
-source(here("R", "func.R"))
-# A) Associative task
-### L. delicata
-deli_asso<-fit_asso(here("output/databases_clean/deli_associative.csv"))
-### L. guichenoti
-guich_asso<-fit_asso(here("output/databases_clean/guich_associative.csv"))
-
-# B) Reversal task
-### L. delicata
-deli_rev<-fit_rev(here("output/databases_clean/deli_reversal.csv"))
-### L. guichenoti
-guich_rev<-fit_rev(here("output/databases_clean/guich_reversal.csv"))
-#
-#
-#
-#| label: posteriors
-#### The function here is to extract the posteriors of the models fitted in the previous chunk
-source(here("R", "func.R"))
-posteriors_deli_asso <- extract_posteriors(deli_asso)
-emm_results <- emmeans(deli_asso, specs = ~trial_associative:temp:cort)
-emm_results <- emmeans(deli_asso, specs = ~trial_associative:group)
-emm_results <- emmeans(deli_asso, specs = ~trial_associative:temp)
-emm_results <- emmeans(deli_asso, specs = ~trial_associative:cort)
-summary(emm_results, infer = TRUE)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#

### 2024-01-10 R/1_data_process.R

@@ -9,7 +9,7 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 data  <-  read.csv("./data/Learning.csv")
 
 # Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
-data_associative <- data %>%
+data_asso <- data %>%
   group_by(lizard_id) %>%
     filter(sum(is.na(FC_associative)) <= 15) %>%
     filter(trial_associative <= 35) %>%
@@ -17,32 +17,36 @@ data_associative <- data %>%
     mutate(group = factor(group,
      levels = c("R_B", "B_R"),
      labels=c("R_B"="Red", "B_R"="Blue"))) %>%
-    mutate(trt = factor(trt,
-     levels = c("B_23", "A_23", "A_23", "B_28"),
-     labels=c("B_23"="CORT Cold",
-              "A_23"="Control Cold",
-              "B_28"="CORT Hot",
-              "A_28"="Control Hot"))) %>%
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>%
+    mutate(temp = factor(temp,
+      levels = c("23", "28"),
+      labels = c("23" = "Cold", "28" = "Hot"))) %>%
+    mutate(cort = factor(cort,
+      levels = c("B", "A"),
+      labels = c("B" = "CORT", "A" = "Control"))) %>%
 data.frame()
 
-data_reversal <- data %>%
+data_rev <- data %>%
   group_by(lizard_id) %>%
     filter(sum(is.na(FC_reversal)) <= 15) %>%
    ungroup()  %>%
     mutate(group = factor(group,
      levels = c("R_B", "B_R"),
      labels=c("R_B"="Red", "B_R"="Blue"))) %>%
-    mutate(trt = factor(trt,
-     levels = c("B_23", "A_23", "A_23", "B_28"),
-     labels=c("B_23"="CORT Cold",
-              "A_23"="Control Cold",
-              "B_28"="CORT Hot",
-              "A_28"="Control Hot"))) %>%
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>%
+    mutate(temp = factor(temp,
+      levels = c("23", "28"),
+      labels = c("23" = "Cold", "28" = "Hot"))) %>%
+    mutate(cort = factor(cort,
+      levels = c("B", "A"),
[…]

### 2024-01-10 R/2_models.R

@@ -2,38 +2,7 @@
 # 2_MODELS
 ####################################
 pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
-#
-######## 2.A) BUILD ALL MODELS AND EXTRACT POSTERIORS
-#### Here we fit all the (brm) models and extract the posteriors per each of the treatments using output/clean_databases already processed using the code in "1_data_process.R"
-#### All this posteriors are processed by fit_asso function and a golbal database with the estimates of Associative_Trial per each treatment level, species, and group is created
-source(here("R", "func.R"))
-## Associative task
-species_levels <- unique(data_associative$species)
-bias_levels <- unique(data_associative$group)
-global_asso <- fit_m(type = "asso", sp = species_levels, bias = bias_levels)
-write.csv(global_asso, here("output/Checking/global_asso.csv"))
-#
-## Reversal task
-species_levels <- unique(data_reversal$species)
-bias_levels <- unique(data_reversal$group)
-global_rev <- fit_m(type = "rev", sp = species_levels, bias = bias_levels)
-write.csv(global_rev, here("output/Checking/global_rev.csv"))
-#
-model <- brm(FC_associative ~ trt*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id),
-              data = deli_associative,
-              family = bernoulli(link = "logit"),
-              chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
-posteriors_model <- as_draws(model)
-posteriors_model_tidy <- tidy_post(posteriors_model)
-#
-data_associative$trt <- relevel(data_associative$trt, ref="Control Cold")
-model <- brm(FC_associative ~ trt*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id),
-              data = deli_associative,
-              family = bernoulli(link = "logit"),
-              chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
-posteriors_model2 <- as_draws(model)
-posteriors_model2_tidy <- tidy_post(posteriors_model2)
-#
+
 ######## 2.B) TIDY POSTERIOR DFs
 source(here("R", "func.R"))
 ## Associative task

### 2024-01-10 R/func.r

@@ -1,83 +1,66 @@
 #################### 
-# PACKAGES
 ####################
 pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
 #
-#################### 
-# MODELS & RAW POSTERIORS
 ####################
-#
+####################
 # Fit models and extract posteriors both per each treatment:
 #' @title fit_m Function
 #' @description Fit brm models for different the associative task
-#' @param type To define if we are analysing the reversal or the associative
+#' @param type To define if we are analysing the associative ("asso) or the reversal ("rev")
 #' @param sp To select the species of interest
-#' @param bias To select the 'group' we want, i.e. to analyse those who learn Red first and Blue second
-#' @return Estimates of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(type, sp, bias, refit = TRUE) {
+#' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
+fit_m <- function(type, sp, refit = TRUE) {
   #Specify the type
   if (type == "asso"){
-    data <- data_associative
-    formula <- FC_associative ~ Associative_Trial + (1 + Associative_Trial|lizard_id)
+    data <- data_asso
+    formula <- FC_associative ~ Associative_Trial*cort*temp + Associative_Trial*group + (1 + Associative_Trial|lizard_id)
   }else{
     if(type == "rev"){
-      data <- data_reversal
-      formula <- FC_reversal ~ trial_reversal + (1 + trial_reversal|lizard_id)
+      data <- data_rev
+      formula <- FC_reversal ~ trial_reversal*cort*temp + trial_reversal*group + (1 + trial_reversal|lizard_id)
     } else {
-      cat("Option not valid\n")
+      stop("Option not valid")
       return(NULL)  # Return NULL in case of an invalid option
     }
   }
-  # Create global database for all the posteriors of all the models
-  global <- data.frame()
-  # Start the loop for all species and groups
-  for(species_level in sp) {
-    for(bias_level in bias) {
-      # Subsample the data
+  #Specify species
+    if (sp == "deli"){
       sub_data <- data %>%
-        group_by(lizard_id) %>%
-          filter(species_level %in% sp, bias_level %in% bias) %>%
-        ungroup()
-      data.frame()
-      #Define levels of treatment
-      treatment_levels <- c("CORT Cold", "Control Cold", "CORT Hot", "Control Hot")
[…]

### 2024-01-11 ms.qmd
Updates

--- 2023-12-27 ms.qmd
@@
 ### Statistical analyses
+- We split by species to analyse them separately. We also saw a significant effect of the colour assigned (blue or red) in the preliminary analises, so we decided to split the data by colour as well.
 
-## Results
+### Results
+```{r, cleaning}
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
+write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
+write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
+```
 
-# References
+```{r, models}
+#| label: models
+# fitting the model and extraction of posteriors for both types of task and species using fit_m function
+source(here("R", "func.R"))
+# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
+## A.1) L. delicata
+deli_asso_red <- fit_m("asso", "deli", "red")
+write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
+deli_asso_blue <- fit_m("asso", "deli", "blue")
+write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
+## A.2) L. guichenoti
+guich_asso_red <- fit_m("asso", "guich", "red")
+write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
+guich_asso_blue <- fit_m("asso", "guich", "blue")
+write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
+# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+## B.1) L. delicata
+deli_rev_red <- fit_m("rev", "deli", "red")
+write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
+deli_rev_blue <- fit_m("rev", "deli", "blue")
+write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
+## B.2) L. guichenoti
+guich_rev_red <- fit_m("rev", "guich", "red")
+write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
+guich_rev_blue <- fit_m("rev", "guich", "blue")
+write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
+```
+
+```{r, resultsAssodeli}
+
+```
+
+```{r, results}
+```
+
+```{r, plots}
+```
+
+## References

### 2024-01-11 .vdoc.r

@@ -1,0 +1,115 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-fig1
+#| fig-cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids indicate the ramps where the food reward was not attainable."
+knitr::include_graphics("./Others/LEARN_FIG_1.svg") 
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
+write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
+write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
+#
+#
+#
+#| label: models
+# fitting the model and extraction of posteriors for both types of task and species using fit_m function
+source(here("R", "func.R"))
+# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
+## A.1) L. delicata
+deli_asso_red <- fit_m("asso", "deli", "red")
+write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
+deli_asso_blue <- fit_m("asso", "deli", "blue")
+write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
+## A.2) L. guichenoti
+guich_asso_red <- fit_m("asso", "guich", "red")
+write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
+guich_asso_blue <- fit_m("asso", "guich", "blue")
[…]

### 2024-01-11 R/func.r

@@ -8,38 +8,58 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #' @title fit_m Function
 #' @description Fit brm models for different the associative task
 #' @param type To define if we are analysing the associative ("asso) or the reversal ("rev")
-#' @param sp To select the species of interest
+#' @param sp To select the species of interest ("deli"/"guich")
+#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
+#' @param refir To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(type, sp, refit = TRUE) {
+fit_m <- function(type, sp, bias, refit = TRUE) {
   #Specify the type
   if (type == "asso"){
     data <- data_asso
-    formula <- FC_associative ~ Associative_Trial*cort*temp + Associative_Trial*group + (1 + Associative_Trial|lizard_id)
+    formula <- FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
   }else{
     if(type == "rev"){
       data <- data_rev
-      formula <- FC_reversal ~ trial_reversal*cort*temp + trial_reversal*group + (1 + trial_reversal|lizard_id)
+      formula <- FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
     } else {
-      stop("Option not valid")
+      stop("Type not valid")
       return(NULL)  # Return NULL in case of an invalid option
     }
   }
   #Specify species
     if (sp == "deli"){
-      sub_data <- data %>%
+      sp_data <- data %>%
             group_by(lizard_id) %>%
             filter(species == "delicata") %>%
             ungroup() %>%
       data.frame() 
     } else {
       if(sp == "guich"){
-        sub_data <- data %>%
+        sp_data <- data %>%
               group_by(lizard_id) %>%
               filter(species == "guichenoti") %>%
               ungroup() %>%
         data.frame()
       } else {
-        stop("Species non valid")
+        stop("Species not valid")
+      }
+    }
+  #Specify bias/group
+    if (bias == "blue"){
+      sub_data <- sp_data %>%
+            group_by(lizard_id) %>%
+            filter(group == "Blue") %>%
+            ungroup() %>%
+      data.frame() 
[…]

### 2024-01-12 ms.qmd
Updates

@@
 
-```{r, resultsAssodeli}
+```{r, resultsAsso}
+# Rename some of the posteriors and make new estimates for the learning rate for the Associative task
+## 1) L. delicata
+### Group = red
+d_a_r_CORTCold <- deli_asso_red$b_Associative_Trial #"Learning estimate" for treatment CORT-Cold for L. delicata, red as the right choice
+d_a_r_ControlCold <- (deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$b_Associative_Trial)
+d_a_r_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
+d_a_r_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial)
+### Group = blue
+d_a_b_CORTCold <- deli_asso_blue$b_Associative_Trial
+d_a_b_ControlCold <- (deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$b_Associative_Trial)
+d_a_b_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
+d_a_b_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial)
+## 2) L. guichenoti
+### Group = red
+g_a_r_CORTCold <- guich_asso_red$b_Associative_Trial
+g_a_r_ControlCold <- (guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$b_Associative_Trial)
+g_a_r_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
+g_a_r_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial)
+### Group = blue
+g_a_b_CORTCold <- guich_asso_blue$b_Associative_Trial
+g_a_b_ControlCold <- (guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$b_Associative_Trial)
+g_a_b_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
+g_a_b_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial)
+```
+
+```{r, resultsRev}
+# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task
+## 1) L. delicata
+### Group = red
+d_r_r_CORTCold <- deli_rev_red$b_trial_reversal
+d_r_r_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
+d_r_r_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
+d_r_r_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal)
+### Group = blue
+d_r_b_CORTCold <- deli_rev_blue$b_trial_reversal
+d_r_b_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
+d_r_b_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
+d_r_b_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal)
+## 2) L. guichenoti
+### Group = red
+g_r_r_CORTCold <- guich_rev_red$b_trial_reversal
+g_r_r_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
+g_r_r_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
+g_r_r_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal)
+### Group = blue
+g_r_b_CORTCold <- guich_rev_blue$b_trial_reversal
+g_r_b_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
+g_r_b_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
+g_r_b_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal)
+```
+
+```{r, results}
+```
+
+```{r, resultsRev}
 

### 2024-01-12 .vdoc.r

@@ -1,115 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-fig1
-#| fig-cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids indicate the ramps where the food reward was not attainable."
-knitr::include_graphics("./Others/LEARN_FIG_1.svg") 
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
-write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
-write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
-#
-#
-#
-#| label: models
-# fitting the model and extraction of posteriors for both types of task and species using fit_m function
-source(here("R", "func.R"))
-# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
-## A.1) L. delicata
-deli_asso_red <- fit_m("asso", "deli", "red")
-write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
-deli_asso_blue <- fit_m("asso", "deli", "blue")
-write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
-## A.2) L. guichenoti
-guich_asso_red <- fit_m("asso", "guich", "red")
-write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
-guich_asso_blue <- fit_m("asso", "guich", "blue")
[…]

### 2024-01-12 R/2_models.R

@@ -2,7 +2,21 @@
 # 2_MODELS
 ####################################
 pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
+data2 <- data_asso %>%
+          mutate(temp = factor(temp,
+                levels = c("Hot", "Cold"))) %>%
+          filter(group == "Red") %>%
+          filter(species == "delicata") %>%
+        data.frame()
 
+model2 <- brm(FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id),
+                data = data2,
+                family = bernoulli(link = "logit"),
+                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
+postm2 <- as_draws_df(model2)
+mean(postm2$b_Associative_Trial)
+write.csv(postm2, here("output/Checking/postm2.csv"))
+mean(postm2$b_Associative_Trial + postm2$'b_Associative_Trial:tempCold')
 ######## 2.B) TIDY POSTERIOR DFs
 source(here("R", "func.R"))
 ## Associative task

### 2024-01-12 ms.qmd
Updates 12/1

--- 2024-01-11 ms.qmd
@@
 ### CORT and Temperature manipulation
-To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (Fig.
-1a).
+To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@FigMethods A).
 We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
@@
 ### Learning
-To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (Fig.
-1b) (see @leal_behavioural_2012; @clark_colour_2014).
+To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@FigMethods B) (see @leal_behavioural_2012; @clark_colour_2014).
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
 We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A.
-domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (Fig.
-1B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (Fig.
-1B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
-1B, Stage 3).
+domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@FigMethods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@FigMethods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (@FigMethods B, Stage 3).
 Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
@@
 This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
-In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig.
-1b).
+In the next phase, we trained lizards to associate between colour and a food reward (Associative task in @FigMethods B).
 The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour.
@@
 Lizards were tested in this task once a day for 35 days.
-After the colour association phase, we performed a choice reversal task (Reversal task in Fig.
-1B).
+After the colour association phase, we performed a choice reversal task (Reversal task in @FigMethods B).
 This task was like the colour association test, except that the attainability of prey was indicated by a different colour, requiring the lizards to form a novel association between the new colour and the food reward.
@@
 
-```{r, Fig1}
-#| label: fig-fig1
+```{r, FigMethods}
+#| label: FigMethods
 #| fig-cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**).
 Stages 1-3 indicate the different phases of the habituation process.
-In the associative and reversal tasks, white lids indicate the ramps where the food reward was not attainable."
+In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
 knitr::include_graphics("./Others/LEARN_FIG_1.svg") 
@@
 
+```{r, sampleSize}
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task.
+We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+      }
+    }
+  }
+}
+```
+
+Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
+However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards.
+Final sample sizes per treatment and species are disclosed on @Tabledata.
+
 ```{r, models}
 #| label: models
-# fitting the model and extraction of posteriors for both types of task and species using fit_m function
+# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder).
+The result everytime the function is used is a df with the posteriors of the model.
+The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
 source(here("R", "func.R"))
@@
 ## A.1) L. delicata
-deli_asso_red <- fit_m("asso", "deli", "red")
+deli_asso_red <- fit_m("asso", "deli", "red", refit = FALSE)
 write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
-deli_asso_blue <- fit_m("asso", "deli", "blue")
+deli_asso_blue <- fit_m("asso", "deli", "blue", refit = FALSE)
 write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
 ## A.2) L. guichenoti
-guich_asso_red <- fit_m("asso", "guich", "red")
+guich_asso_red <- fit_m("asso", "guich", "red", refit = FALSE)
 write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
-guich_asso_blue <- fit_m("asso", "guich", "blue")
+guich_asso_blue <- fit_m("asso", "guich", "blue", refit = FALSE)
 write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
@@
 ## B.1) L. delicata
-deli_rev_red <- fit_m("rev", "deli", "red")
+deli_rev_red <- fit_m("rev", "deli", "red", refit = FALSE)
 write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
-deli_rev_blue <- fit_m("rev", "deli", "blue")
+deli_rev_blue <- fit_m("rev", "deli", "blue", refit = FALSE)
 write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
 ## B.2) L. guichenoti
-guich_rev_red <- fit_m("rev", "guich", "red")
+guich_rev_red <- fit_m("rev", "guich", "red", refit = FALSE)
 write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
-guich_rev_blue <- fit_m("rev", "guich", "blue")
+guich_rev_blue <- fit_m("rev", "guich", "blue", refit = FALSE)
 write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
@@
 
-```{r, resultsAssodeli}
+```{r, resultsAsso}
+# Rename some of the posteriors and make new estimates for the learning rate for the Associative task
+## 1) L. delicata
+### Group = red
+dar_CORTCold <- deli_asso_red$b_Associative_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
+dar_ControlCold <- (deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$b_Associative_Trial)
+dar_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
+dar_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial)
+### Group = blue
+dab_CORTCold <- deli_asso_blue$b_Associative_Trial
+dab_ControlCold <- (deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$b_Associative_Trial)
+dab_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
+dab_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial)
+## 2) L. guichenoti
+### Group = red
+gar_CORTCold <- guich_asso_red$b_Associative_Trial
+gar_ControlCold <- (guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$b_Associative_Trial)
+gar_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
+gar_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial)
+### Group = blue
+gab_CORTCold <- guich_asso_blue$b_Associative_Trial
+gab_ControlCold <- (guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$b_Associative_Trial)
+gab_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
+gab_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial)
+```
+
+```{r, resultsRev}
+# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task
+## 1) L. delicata
+### Group = red
+drr_CORTCold <- deli_rev_red$b_trial_reversal
+drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
+drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
+drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal)
+### Group = blue
+drb_CORTCold <- deli_rev_blue$b_trial_reversal
+drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
+drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
+drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal)
+## 2) L. guichenoti
+### Group = red
+grr_CORTCold <- guich_rev_red$b_trial_reversal
+grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
+grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
+grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal)
+### Group = blue
+grb_CORTCold <- guich_rev_blue$b_trial_reversal
+grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
+grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
+grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal)
+```
+
+```{r, Tabledata}
+#| label: Tabledata
+#| fig-cap: "Data models"
+source(here("R", "func.R"))
+#
+# Building the vectors for titles of rows and columns
+specie <- c("L. delicata", "L. guichenoti")
+groups <- c("Red", "Blue")
+test <- c("Associative", "Reversal")
+treatments <- c("CORT - Cold", "Control - Cold", "CORT - Hot", "Control - Hot")
+values <- c("Mean", "95% CI", "p-value")
+# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors.
+p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
+#First get estimates for both tasks
+estimates_asso <- list(
+  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
+  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot, 
+  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot, 
+  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot
+)
+#
+estimates_rev <- list(
+  drr_CORTCold, drr_ControlCold, drr_CORTHot, drr_ControlHot, 
+  drb_CORTCold, drb_ControlCold, drb_CORTHot, drb_ControlHot, 
+  grr_CORTCold, grr_ControlCold, grr_CORTHot, grr_ControlHot, 
+  grb_CORTCold, grb_ControlCold, grb_CORTHot, grb_ControlHot
+)
+# Then get the mean, co.intervals(95%), and p-values
+asso_mean <- format_dec(sapply(estimates_asso, mean), 4)
+asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
+asso_interval_975 <- format_dec(sapply(estimates_asso, function (x) quantile(x,0.975)), 3)
+asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
+asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 4)
+#
+rev_mean <- format_dec(sapply(estimates_rev, mean), 4)
+rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
+rev_interval_975 <- format_dec(sapply(estimates_rev, function (x) quantile(x,0.975)), 3)
+rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
+rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 4)
+#
+# Building the df for the associative
+asso_df <- data.frame(
+  Specie = rep(specie, each = length(groups) * length(treatments)),
+  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
+  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
+  Mean = rep(asso_mean, each = 1),
+  CI = rep(asso_intervals, each = 1),
+  PValue = rep(asso_pvalue, each = 1),
+  Task = rep("Associative", length(asso_mean))
+)
+# Building the df for the reversal
+rev_df <- data.frame(
+  Specie = rep(specie, each = length(groups) * length(treatments)),
+  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
+  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
+  Mean = rep(rev_mean, each = 1),
+  CI = rep(rev_intervals, each = 1),
+  PValue = rep(rev_pvalue, each = 1),
+  Task = rep("Reversal", length(rev_mean))
+)
+# Joining both dfs
+table_data <- rbind(asso_df, rev_df)
+write.csv(table_data, file= "./output/Checking/Table_data.csv")
+#
+# Making the table
+
+```
+
+```{r, plots}
+```
+
+```{r, results})                   
+```
+
+```{r, resultsRev}
 

### 2024-01-12 R/1_data_process.R

@@ -25,10 +25,17 @@ data_asso <- data %>%
     mutate(cort = factor(cort,
       levels = c("B", "A"),
       labels = c("B" = "CORT", "A" = "Control"))) %>%
+    mutate( # Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
+      first_non_na = min(which(!is.na(FC_associative))),
+      Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>% 
+      filter(Associative_Trial >= 1) %>%
+  ungroup() %>% 
 data.frame()
+
 
 data_rev <- data %>%
   group_by(lizard_id) %>%
+    filter(sum(is.na(FC_associative)) <= 15) %>%
     filter(sum(is.na(FC_reversal)) <= 15) %>%
    ungroup()  %>%
     mutate(group = factor(group,
@@ -45,14 +52,4 @@ data_rev <- data %>%
     mutate(trial_reversal=as.numeric(trial_reversal)) %>%
   data.frame()
 
-# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
-data_asso <- data_asso %>%
-  group_by(lizard_id) %>%
-  mutate(
-    first_non_na = min(which(!is.na(FC_associative))),
-    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
-    filter(Associative_Trial >= 1) %>%
-  ungroup() %>% 
-  data.frame()
-  
 

### 2024-01-12 R/2_models.R

@@ -3,8 +3,8 @@
 ####################################
 pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
 data2 <- data_asso %>%
-          mutate(temp = factor(temp,
-                levels = c("Hot", "Cold"))) %>%
+          mutate(cort = factor(cort,
+                levels = c("Control", "CORT"))) %>%
           filter(group == "Red") %>%
           filter(species == "delicata") %>%
         data.frame()
@@ -16,7 +16,6 @@ model2 <- brm(FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Tr
 postm2 <- as_draws_df(model2)
 mean(postm2$b_Associative_Trial)
 write.csv(postm2, here("output/Checking/postm2.csv"))
-mean(postm2$b_Associative_Trial + postm2$'b_Associative_Trial:tempCold')
 ######## 2.B) TIDY POSTERIOR DFs
 source(here("R", "func.R"))
 ## Associative task

### 2024-01-12 R/func.r

@@ -4,6 +4,27 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #
 ####################
 ####################
+# Extract sample size per group
+#' @title sample
+#' @description Estract sample size per group
+#' @param sp To select the species of interest ("deli"/"guich")
+#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
+#' @param corti To select cort treatment ("CORT"/"Control")
+#' @param therm To select temp treatment ("Cold"/"Hot")
+sample <- function(sp, bias, corti, therm){
+  #Specify database
+  data <- data_asso
+  # Count sample
+  sample_size <- data %>%
+                filter(species == sp, group == bias, cort == corti, temp == therm, Associative_Trial == 1) %>%
+                group_by(lizard_id) %>%
+                summarise(n = n()) %>%
+                summarise(total_count = sum(n)) %>%
+                pull(total_count)
+  return(sample_size)
+}
+####################
+####################
 # Fit models and extract posteriors both per each treatment:
 #' @title fit_m Function
 #' @description Fit brm models for different the associative task
@@ -116,3 +137,11 @@ pmcmc <- function(x, null = 0, twotail = TRUE){
 }
 ####################
 ####################
+# Function to format numbers with 2 decimal places
+#' @title format_dec
+#' @param x The object
+#' @param n The number of decimals
+format_dec <- function(x, n) {
+  z <- sprintf(paste0("%.",n,"f"), x)
+  return(as.numeric(z))
+}

### 2024-01-13 ms.qmd
Updates

@@
 ```{r, resultsAsso}
-# Rename some of the posteriors and make new estimates for the learning rate for the Associative task
+# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment in the Associative task.
+This "learning rate" consists on the slope of the posterior of the Associative_Trial parameter.
+The slope is the rate at which the probability of choosing the correct feeder increases with each trial.
+The slope is obtained by adding the posterior of the Associative_Trial parameter to the posterior of the interaction between Associative_Trial and the treatment (cort and temp).
 ## 1) L. delicata
@@
 ```{r, resultsRev}
-# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task
+# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
 ## 1) L. delicata
@@
 #
+############################## CREATING BIG DF FOR TABLE ##############################
 # Building the vectors for titles of rows and columns
@@
 test <- c("Associative", "Reversal")
-treatments <- c("CORT - Cold", "Control - Cold", "CORT - Hot", "Control - Hot")
+treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
 values <- c("Mean", "95% CI", "p-value")
@@
 # Then get the mean, co.intervals(95%), and p-values
-asso_mean <- format_dec(sapply(estimates_asso, mean), 4)
+asso_mean <- format_dec(sapply(estimates_asso, mean), 3)
 asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
@@
 asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
-asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 4)
+asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 3)
 #
-rev_mean <- format_dec(sapply(estimates_rev, mean), 4)
+rev_mean <- format_dec(sapply(estimates_rev, mean), 3)
 rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
@@
 rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
-rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 4)
+rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 3)
 #
@@
 table_data <- rbind(asso_df, rev_df)
-write.csv(table_data, file= "./output/Checking/Table_data.csv")
+table_data[, sapply(table_data, is.numeric)] <- lapply(table_data[, sapply(table_data, is.numeric)], function(x) format(x, scientific = FALSE))
 #
-# Making the table
+############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
+# Make n_list into a df
+n_df <- as.data.frame(do.call(rbind, n_list)) %>%
+  rename("n" = V1) %>%
+  rownames_to_column("model") %>%
+  separate(model, into = c("Specie", "Group", "cort", "temp"), sep = "_") %>%
+  unite("Treatment", c("cort", "temp"), sep = "-") %>%
+  mutate(Specie = factor(Specie,
+                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
+        Treatment = factor(Treatment,
+                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
+# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
+new_table_data <- merge(table_data, n_df) %>%
+  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
+  pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal
+  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #Tor order the columns in the way I want for the table
+  mutate(Specie = factor(Specie,
+                  levels = c("L. delicata", "L. guichenoti")),
+        Group = factor(Group,
+                  levels = c("Red", "Blue")),
+        Treatment = factor(Treatment, 
+                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
+  arrange(Specie, Group, Treatment) %>% # To arrange the rows the way I want
+  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
+  mutate(Treatment = paste0(Treatment, ")"))
+write.csv(new_table_data, file= "./output/Checking/new_table_data.csv")
+#
+############################## MAKING THE TABLE ##############################
+## Table format
+set_flextable_defaults(
+ font.family = "Arial",
+ fint.size = 10)
+# Split the table_data df by task
+real_table <- flextable(new_table_data) %>%
+    bold(~ `p-value_Associative` < 0.01, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
+    bold(~ `p-value_Reversal` < 0.01, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
+    set_table_properties(width = 1) %>%
+    align(align="center", part="all") %>% 
+    add_header_row(values = c("", "Associative task", "Reversal task"), colwidths = c(3, 3, 3)) %>%
+    set_header_labels(Mean_Associative = "Mean",
+                      `95% CI_Associative` = "95% CI",
+                      `p-value_Associative` = "p-value",
+                      Mean_Reversal = "Mean",
+                      `95% CI_Reversal` = "95% CI",
+                      `p-value_Reversal` = "p-value") %>%
+    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
+    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
+    hline(i = c(4,12), j = c(2:9), part = "body") %>% # To make some horizontal lines
+    hline(i = c(8), j = c(1:9), part = "body") %>% # To make some horizontal lines
+    vline(i = (1:16), j = c(3,6), part = "body") %>% # To make some vertical lines on body
+    vline(j=c(3,6), part = "header") %>% # To make some vertical lines on header
+    autofit()
+
+print(real_table)
 

### 2024-01-13 ms.qmd
Updates

@@
 dar_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
-dar_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial)
+dar_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial+ deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$'b_Associative_Trial:tempHot')
 ### Group = blue
@@
 dab_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
-dab_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial)
+dab_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial + deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$'b_Associative_Trial:tempHot')
 ## 2) L. guichenoti
@@
 gar_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
-gar_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial)
+gar_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial + guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$'b_Associative_Trial:tempHot')
 ### Group = blue
@@
 gab_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
-gab_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial)
+gab_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial + guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$'b_Associative_Trial:tempHot')
 ```
@@
 drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
-drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal)
+drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
 ### Group = blue
@@
 drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
-drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal)
+drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
 ## 2) L. guichenoti
@@
 grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
-grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal)
+grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
 ### Group = blue
@@
 grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
-grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal)
+grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
 ```
@@
 #| label: Tabledata
-#| fig-cap: "Data models"
+#| tbl-cap: 'Data models'
 source(here("R", "func.R"))
@@
     bold(~ `p-value_Associative` < 0.01, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
-    bold(~ `p-value_Reversal` < 0.01, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
+    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
     set_table_properties(width = 1) %>%
@@
     autofit() 
-
-print(real_table)
-
-```
-
-```{r, plots}
-```
-
-```{r, results})                   
-```
-
-```{r, resultsRev}
-
-```
-
-```{r, results}
-```
-
-```{r, plots}
+real_table
 ```

### 2024-01-15 ms.qmd
Updates

@@
 docx: 
+bibliography: "./bib/refs.bib"
+csl: "./bib/animal-cognition.csl"
 reference-doc: "./bib/tmpl.docx"
-bibliography: "./bib/refs.bib"
 execute:
@@
   warning: false
+link-citations: true
 crossref:  
@@
   fig-prefix: Fig.   # (default is "Figure")
-  tbl-prefix: Tab.   # (default is "Table")
+  tbl-prefix: Table  # (default is "Table")
 editor_options: 
@@
 
-Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shettleworth).
-These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, that are crucial for the survival and reproduction of animals (@dukas_evolutionary_2004).
-Particularly, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013).
-However, the capacity of individuals to acquire new information exhibits natural variation influenced by factors like age, sex, gut microbiota, or the environment where animals develop (@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning).
-The developmental environment, in particular, plays a pivotal role, as the brain is especially susceptible to environmental influences during early stages of development (@zhu_prenatal_2004).
+Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
+These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, that are crucial for the survival and reproduction of animals [@dukas_evolutionary_2004].
+Particularly, learning - the acquisition of neuronal representations of new information [@dukas_evolutionary_2004] - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
+However, the capacity of individuals to acquire new information exhibits natural variation influenced by factors like age, sex, gut microbiota, or the environment where animals develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
+The developmental environment, in particular, plays a pivotal role, as the brain is especially susceptible to environmental influences during early stages of development [@zhu_prenatal_2004].
 Hence, investigating the effects of the developmental environment on learning can be essential to understand the evolution of learning and predict animals' responses towards environmental change.
-In this sense, prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020).
-GCs - hormones related to organisms' response to stress (@sapolsky_how_2000) - exert sustained effects on neural structure and physiology that are associated with animals' performance on learning tasks (@lemaire_prenatal_2000; @zhu_prenatal_2004; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
-Some studies have demonstrated that prenatal stress and high prenatal GC levels impair with learning (@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn), while others showed diverse effects depending on factors such as sex or the nature of the learning task (@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016).
-Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms (@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020).
-For instance, high incubation temperatures have been linked with faster learning rates in skinks (@amiel_hotter_2012; @amiel_egg_2014), while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits (@abayarathna_effects_2020).
-In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity (@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021) that share some similarities with those resulting from prenatal increased stress or GC levels (@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009).
-This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning skills (@noble_developmental_2018).
-Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures (@Crino_2023) potentially fostering natural interactions between temperature and GCs.
+In this sense, prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
+GCs - hormones related to organisms' response to stress [@sapolsky_how_2000] - exert sustained effects on neural structure and physiology that are associated with animals' performance on learning tasks [@lemaire_prenatal_2000; @zhu_prenatal_2004; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
+Some studies have demonstrated that prenatal stress and high prenatal GC levels impair with learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors such as sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
+Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020].
+For instance, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@abayarathna_effects_2020].
+In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021] that share some similarities with those resulting from prenatal increased stress or GC levels [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009].
+This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning skills [@noble_developmental_2018].
+Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
 Despite the proximate similarities of prenatal GCs and temperature effects and the potential role of GCs in vertebrates response to elevated temperatures, our understanding of how these two factors interact remains incomplete.
@@
 guichenoti_), as model species.
-We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents (@Crino_2023) - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
+We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
 Post-incubation, the juveniles were subjectd to a colour-associative and a reversal task to comprehensively assess their learning abilities.
@@
 Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
+We also expect the treatments to affect both tasks equally, with those individuals exposed to high levels of CORT and/or low temperatures performing less proficiently in both tasks compared to control individuals or those exposed to high temperatures.
+Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species in learning [@bezzina2014does].
 
@@
 guichenoti_ and _L.
-delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia (@chapple_know_2011).
-They also have similar breeding periods, but with some differences in reproductive output: while *L.
+delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011].
+Both species have similar breeding periods, but with some differences in reproductive output: while *L.
 delicata* lays 1 to 6 eggs in only one clutch per season, *L.
-guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season (@chapple_know_2011; @chapple_biology_2014).
+guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014].
+Also, some sudies have found some behavioural divergence between the two skinks [@chapple_know_2011].
+_L.
+delicata_ is more exploratory and bolder than _L.
+guichenoti_ [@chapple_know_2011] which was related to the former's success as an invassive species [@chapple_know_2011; @bezzina2014does], but not with their ability to learn in an associatve learning task [@bezzina2014does].
 
@@
 ### Learning
-To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@FigMethods B) (see @leal_behavioural_2012; @clark_colour_2014).
+To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@FigMethods B) [see @leal_behavioural_2012; @clark_colour_2014].
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
 We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A.
-domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@FigMethods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@FigMethods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (@FigMethods B, Stage 3).
+domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@FigMethods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@FigMethods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
+@FigMethods B, Stage 3).
 Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
-At the end of the experiment, we recorded whether the cricket has been consumed or not.
+At the end of each trial, we recorded whether the cricket had been consumed or not.
 Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials.
 This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
-In the next phase, we trained lizards to associate between colour and a food reward (Associative task in @FigMethods B).
+In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig.
+@FigMethods B).
 The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour.
@@
 The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals.
-The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours (@Baden_Osorio_2019_Vert_vision).
-To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with non-covered cricket) was the blue one in the associative task and red in the reversal (see below), while we did the opposite for the other group.
+The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
+To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
@@
 This test was done once a day for 40 days.
-All trials were done daily between the 6^th^ of March until the 26^th^ of June 2023, beginning at 11 am until 12 pm.
+The full experiment was done daily between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
 Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.
@@
 We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
+We excluded from our analyses those individuals with more than 15 trials failed (i.e.
+they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.
 
@@
 #| label: FigMethods
-#| fig-cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**).
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**).
 Stages 1-3 indicate the different phases of the habituation process.
 In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
 knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+
 ```
@@
 ### Statistical analyses
-- We split by species to analyse them separately. We also saw a significant effect of the colour assigned (blue or red) in the preliminary analises, so we decided to split the data by colour as well.
+We performed the analyses with species (_L.
+delicata_ or _L.
+guichenoti_) and task ('Associative' or 'Reversal') separately.
+We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour ('Blue' or 'Red') as well.
+As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (**REF brm package**) in Quartos (**REF QUARTOS**).
+Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e.
+whether the individual chose correct (1) or not (0) was used as the response variable, employing a Bernoulli probability distribution (link=‘logit’).
+The fixed effects of the model included a triple interaction between: trial ('Associative trial' or 'Reversal trial') as a numeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors.
+For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the variable trial within each level of lizard identity.
+For all models we
+We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned.
+More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not.
+We used the pmcmc method to test whether those slopes or the comparissons between 'Treatments' (e.g.
+slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests).
+We considered statistical significance if p-value < 0.05.
 
@@
 Final sample sizes per treatment and species are disclosed on @Tabledata.
-
 ```{r, models}
@@
 ```
+```{r, InterceptsRev}
+```
+
+```{r, InterceptsRev}
+```
 
@@
 #| label: Tabledata
-#| tbl-cap: 'Data models'
+#| tbl-cap: "\beta estimates of Associative learning slope for all the different treatments per each task, species and group.
+Mean shows the aritmetic mean of the /beta estimates obtain from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All p-values were obtained using pmcmc and test the hypothesis that the mean /beta estimates is equal to zero.
+In bold those values that are significant (p-value <0.05)"
 source(here("R", "func.R"))
@@
 set_flextable_defaults(
- font.family = "Arial",
+ font.family = "Times New Roman",
  fint.size = 10)
@@
 real_table <- flextable(new_table_data) %>%
-    bold(~ `p-value_Associative` < 0.01, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
+    bold(~ `p-value_Associative` < 0.05, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
     bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
@@
 
+@Tabledata summarizes the estimates of learning slopes for all the treatments in each model (see Statistical analyses).
+On average, we found that learning slopes were lower when the 'Blue' feeders were correct compared to those assigned to the group 'Red'  for _L.
+delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot))`), but not for _L.
+guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`).
+However, because we suspect there may be a bias towards 'Blue' in the initial choice (see Supplementary Material and Figs.
+@Figdeli, @Figguich), we only used those individuals assigned to 'Red' to compare performance in the associative learning task.
+In this regard, we did not find any significant differences between treatments for _L.
+delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figduich).
+When groups were pooled by incubation temperature or hormonal treatment, there was not significant differences in the estimated slopes caused by temperature (_L.
+delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`) or the hormone (_L.
+delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L.
+guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`).
+We also did not find any significant differences when we compared the estimated slopes between species for the associative task (only individuals from 'Red' group: _L.
+delicata_ - _L.
+guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
+
 ## References

### 2024-01-15 R/2_models.R

@@ -5,6 +5,8 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 data2 <- data_asso %>%
           mutate(cort = factor(cort,
                 levels = c("Control", "CORT"))) %>%
+          mutate(temp = factor(temp,
+                levels = c("Hot", "Cold"))) %>%
           filter(group == "Red") %>%
           filter(species == "delicata") %>%
         data.frame()
@@ -117,3 +119,97 @@ guich_rev <- ggplot(guich_reversal, aes(x = trial_reversal, y = FC_reversal, col
   )
 print(guich_rev)
 ggsave("./output/figures/fig_guich_rev.png", plot=guich_rev, width = 15, height = 12, units = "cm", dpi = 3000)
+
+
+
+
+
+```{r, FigResults}
+|# label: FigResults
+|# fig.cap:
+######## 2.E) PLOTS MODELS 
+# Plot delicata associative
+plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +
+  stat_smooth(method = "glm", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
+  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
+    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
+  ) +
+  facet_wrap(deli_associative$group, scales = "free_y", ncol = 1) +
+  theme(strip.placement = "outside") +  
+  theme(strip.background = element_blank()) +
+  labs(y = "Probability of correct choice", x = "Trial") +
+  theme_classic() +
+  theme(
+    axis.title = element_text(size = 18, family = "sans"),
+    axis.text = element_text(size = 10, family = "sans"),
+    legend.title = element_text(size = 14, family = "sans"),
+    legend.text = element_text(size = 12, family = "sans")
+  )
+print(plot_deli)
+ggsave("./output/figures/fig_deli_asso.png", plot=plot_deli, width = 15, height = 12, units = "cm", dpi = 3000)
+ 
+# Plot guichenoti associative
[…]

### 2024-01-16 ms.qmd
Updates

@@
 The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal.
+To control for potential colour preference that could bias our results (see Supplementary Material), we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
@@
 
-```{r, InterceptsRev}
-```
-
 ```{r, Tabledata}
@@
   pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal
-  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #Tor order the columns in the way I want for the table
+  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #To order the columns in the way I want for the table
   mutate(Specie = factor(Specie,
@@
 ## References
+
+## Suplementary Material
+
+### Colour preference in the Associative task
+To test if lizards were biased towards blue as our preliminary analyses indicated, we employed the intercept estimates from our posterior distribution.
+We get this intercepts for each species, group and treatment, and we estimated the probability of choosing right using the formula:
+
+As we used the link=‘logit’ adjustment in our initial models.
+```{r, Tablebias}
+#| label: Tablebias
+#| tbl-cap: "Biases"
+# First we estimate the probability of choosing right in the first trial using the intercepts from the posteriors
+## 1) L. delicata
+### Group = red
+probright_drCORTCold <- 1/(1+exp(-deli_asso_red$b_Intercept))
+probright_drControlCold <- 1/(1+exp(-(deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)))
+probright_drCORTHot <- 1/(1+exp(-(deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
+probright_drControlHot <- 1/(1+exp(-(deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
+### Group = blue
+probright_dbCORTCold <- 1/(1+exp(-(deli_asso_blue$b_Intercept)))
+probright_dbControlCold <- 1/(1+exp(-(deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)))
+probright_dbCORTHot <- 1/(1+exp(-(deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
+probright_dbControlHot <- 1/(1+exp(-(deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
+## 2) L. guichenoti
+### Group = red
+probright_grCORTCold <- 1/(1+exp(-guich_asso_red$b_Intercept))
+probright_grControlCold <- 1/(1+exp(-(guich_asso_red$b_cortControl + guich_asso_red$b_Intercept)))
+probright_grCORTHot <- 1/(1+exp(-(guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
+probright_grControlHot <- 1/(1+exp(-(guich_asso_red$'b_cortControl:tempHot' + guich_asso_red$b_cortControl + guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
+### Group = blue
+probright_gbCORTCold <- 1/(1+exp(-guich_asso_blue$b_Intercept))
+probright_gbControlCold <- 1/(1+exp(-(guich_asso_blue$b_cortControl + guich_asso_blue$b_Intercept)))
+probright_gbCORTHot <- 1/(1+exp(-(guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
+probright_gbControlHot <- 1/(1+exp(-(guich_asso_blue$'b_cortControl:tempHot' + guich_asso_blue$b_cortControl + guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
+# Second we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species
+prob_df <- data.frame(
+  probright_drCORTCold = probright_drCORTCold,
+  probright_drControlCold = probright_drControlCold,
+  probright_drCORTHot = probright_drCORTHot,
+  probright_drControlHot = probright_drControlHot,
+  probright_dbCORTCold = probright_dbCORTCold,
+  probright_dbControlCold = probright_dbControlCold,
+  probright_dbCORTHot = probright_dbCORTHot,
+  probright_dbControlHot = probright_dbControlHot,
+  probright_grCORTCold = probright_grCORTCold,
+  probright_grControlCold = probright_grControlCold,
+  probright_grCORTHot = probright_grCORTHot,
+  probright_grControlHot = probright_grControlHot,
+  probright_gbCORTCold = probright_gbCORTCold,
+  probright_gbControlCold = probright_gbControlCold,
+  probright_gbCORTHot = probright_gbCORTHot,
+  probright_gbControlHot = probright_gbControlHot
+) %>% #This way we get a df with 16 variables
+  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
+  gather(key = "column", value = "value", .) %>% #To transpose the df
+  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
+  mutate(Group = gsub(".*_(dr|db|gr|gb).*", "\\1",column)) %>%
+  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
+  mutate(Treatment = factor(Treatment, 
+                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
+                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
+  mutate(Specie = factor(Specie,
+                levels = c("d", "g"),
+                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
+  mutate(Group = recode(Group, "dr" = "Red", "db" = "Blue", "gr" = "Red", "gb" = "Blue")) %>%
+  pivot_wider(names_from = Group, values_from = c(value, column)) %>% #To split the df in Red and Blue
+data.frame()
+
+write.csv(prob_df, file= "./output/Checking/prob_df.csv")
+
+# Then we build a df with the statistical comparison between probabilities (Blue minus Red) for each treatment and species and p-values for each comparison
+comp_prob <- data.frame(
+  (probright_dbCORTCold - probright_drCORTCold),
+  (probright_dbControlCold - probright_drControlCold),
+  (probright_dbCORTHot - probright_drCORTHot),
+  (probright_dbControlHot - probright_drControlHot),
+  (probright_gbCORTCold - probright_grCORTCold),
+  (probright_gbControlCold - probright_grControlCold),
+  (probright_gbCORTHot - probright_grCORTHot),
+  (probright_gbControlHot - probright_grControlHot)
+) %>% 
+  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
+  gather(key = "column", value = "value", .) %>% #To transpose the df
+  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
+  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
+  mutate(Treatment = factor(Treatment, 
+                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
+                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
+  mutate(Specie = factor(Specie,
+                levels = c("d", "g"),
+                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
+  rename("[Blue - Red]" = "value") %>%
+data.frame()
+#
+comp_pval <- data.frame(
+  pmcmc(probright_dbCORTCold - probright_drCORTCold),
+  pmcmc(probright_dbControlCold - probright_drControlCold),
+  pmcmc(probright_dbCORTHot - probright_drCORTHot),
+  pmcmc(probright_dbControlHot - probright_drControlHot),
+  pmcmc(probright_gbCORTCold - probright_grCORTCold),
+  pmcmc(probright_gbControlCold - probright_grControlCold),
+  pmcmc(probright_gbCORTHot - probright_grCORTHot),
+  pmcmc(probright_gbControlHot - probright_grControlHot)
+) %>% 
+  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
+  gather(key = "column", value = "value", .) %>% #To transpose the df
+  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
+  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
+  mutate(Treatment = factor(Treatment, 
+                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
+                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
+  mutate(Specie = factor(Specie,
+                levels = c("d", "g"),
+                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
+  rename("p-value" = "value") %>%
+data.frame()
+#Create the final database and the table
+table_df <- merge(prob_df, comp_prob, by = c("Specie", "Treatment")) %>%
+  merge(comp_pval, by = c("Specie", "Treatment")) %>%
+  select(Specie, Treatment, value_Blue, value_Red, X.Blue...Red., p.value) %>%
+  mutate(Treatment = factor(Treatment, 
+                    levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
+data.frame()
+table_df <- table_df %>%
+#
+colour_table <- flextable(table_df) %>%
+  bold(~ `p.value` < 0.05, ~ `p.value` + X.Blue...Red.) %>%
+  set_table_properties(width = 1) %>%
+  align(align="center", part="all") %>% 
+  set_header_labels(value_Blue = "Blue",
+                    value_Red = "Red",
+                    p.value = "p-value",
+                    X.Blue...Red. = "[Blue - Red]") %>%
+  italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
+  colformat_num(columns = c("Blue", "Red", "[Blue-Red]", "p-value"), digits = 3) %>% # To set the number of decimals
+  flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+  hline(i = c(4), j = c(1:6), part = "body") %>% # To make some horizontal lines
+autofit()
+colour_table
+```
+
+For _L. delicata_, there was no differences between treatments ('Red' group: 'Control-Cold' - 'CORTCold')
+
+```

### 2024-01-17 ms.qmd
Updates

@@
 
-### Subjects
+#### Subjects
 
@@
 
-### Husbandry
+#### Husbandry
 
@@
 
-### CORT and Temperature manipulation
+#### CORT and Temperature manipulation
 To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@FigMethods A).
@@
 
-### Learning
+#### Learning
 To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@FigMethods B) [see @leal_behavioural_2012; @clark_colour_2014].
@@
 
-### Statistical analyses
+#### Statistical analyses
 We performed the analyses with species (_L.
@@
 
-### Results
+## Results
 ```{r, cleaning}
@@
 ```
-```{r, InterceptsRev}
-```
 
@@
 #| label: Tabledata
-#| tbl-cap: "\beta estimates of Associative learning slope for all the different treatments per each task, species and group.
-Mean shows the aritmetic mean of the /beta estimates obtain from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
-All p-values were obtained using pmcmc and test the hypothesis that the mean /beta estimates is equal to zero.
-In bold those values that are significant (p-value <0.05)"
+#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.
+Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero.
+In bold, those values that are significant (p-value <0.05)"
 source(here("R", "func.R"))
@@
 asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
-asso_interval_975 <- format_dec(sapply(estimates_asso, function (x) quantile(x,0.975)), 3)
+asso_interval_975 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.975)), 3)
 asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
@@
 rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
-rev_interval_975 <- format_dec(sapply(estimates_rev, function (x) quantile(x,0.975)), 3)
+rev_interval_975 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.975)), 3)
 rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
@@
 delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figduich).
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figguich).
 When groups were pooled by incubation temperature or hormonal treatment, there was not significant differences in the estimated slopes caused by temperature (_L.
@@
 
+```{r, Figdeli}
+#| label: Figdeli
+#| fig.cap: "Deli"
+```
+
+```{r, figguich}
+#| label: Figguich
+#| fig.cap: "Guich"
+```
+
+[RESULTS reversal]
+
+## Discussion
+
 ## References
+\printbibliography
 
-## Suplementary Material
+\pagebreak
 
-### Colour preference in the Associative task
-To test if lizards were biased towards blue as our preliminary analyses indicated, we employed the intercept estimates from our posterior distribution.
-We get this intercepts for each species, group and treatment, and we estimated the probability of choosing right using the formula:
+# Suplementary Material
 
+#### Colour preference in the Associative task
+To test if lizards were biased towards blue as our preliminary analyses indicated, we employed the intercept estimates from our posterior distribution to get the predicted probability of choosing the right in the first trial using the formula:
+$$\text{Probability} = \frac{1}{1 + e^{-A}}$$
 As we used the link=‘logit’ adjustment in our initial models.
@@
 #| tbl-cap: "Biases"
+source(here("R", "func.R"))
 # First we estimate the probability of choosing right in the first trial using the intercepts from the posteriors
@@
 prob_df <- data.frame(
-  probright_drCORTCold = probright_drCORTCold,
-  probright_drControlCold = probright_drControlCold,
-  probright_drCORTHot = probright_drCORTHot,
-  probright_drControlHot = probright_drControlHot,
-  probright_dbCORTCold = probright_dbCORTCold,
-  probright_dbControlCold = probright_dbControlCold,
-  probright_dbCORTHot = probright_dbCORTHot,
-  probright_dbControlHot = probright_dbControlHot,
-  probright_grCORTCold = probright_grCORTCold,
-  probright_grControlCold = probright_grControlCold,
-  probright_grCORTHot = probright_grCORTHot,
-  probright_grControlHot = probright_grControlHot,
-  probright_gbCORTCold = probright_gbCORTCold,
-  probright_gbControlCold = probright_gbControlCold,
-  probright_gbCORTHot = probright_gbCORTHot,
-  probright_gbControlHot = probright_gbControlHot
-) %>% #This way we get a df with 16 variables
-  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
-  gather(key = "column", value = "value", .) %>% #To transpose the df
+  probright_drCORTCold_t = format_dec(mean(probright_drCORTCold), 3),
+  probright_drControlCold_t = format_dec(mean(probright_drControlCold), 3),
+  probright_drCORTHot_t = format_dec(mean(probright_drCORTHot), 3),
+  probright_drControlHot_t = format_dec(mean(probright_drControlHot), 3),
+  probright_dbCORTCold_t = format_dec(mean(probright_dbCORTCold), 3),
+  probright_dbControlCold_t = format_dec(mean(probright_dbControlCold), 3),
+  probright_dbCORTHot_t = format_dec(mean(probright_dbCORTHot), 3),
+  probright_dbControlHot_t = format_dec(mean(probright_dbControlHot), 3),
+  probright_grCORTCold_t = format_dec(mean(probright_grCORTCold), 3),
+  probright_grControlCold_t = format_dec(mean(probright_grControlCold), 3),
+  probright_grCORTHot_t = format_dec(mean(probright_grCORTHot), 3),
+  probright_grControlHot_t = format_dec(mean(probright_grControlHot), 3),
+  probright_gbCORTCold_t = format_dec(mean(probright_gbCORTCold), 3),
+  probright_gbControlCold_t = format_dec(mean(probright_gbControlCold), 3),
+  probright_gbCORTHot_t = format_dec(mean(probright_gbCORTHot), 3),
+  probright_gbControlHot_t = format_dec(mean(probright_gbControlHot), 3)) %>%
+gather(key = "column", value = "value", .) %>%
+rename("prob_choice" = "value") %>%
+data.frame()
+write.csv(prob_df, file= "./output/Checking/prob_df.csv")
+# Then we build a df with the statistical test (one-tailed pmcmc) that the probability is >0.33 (the probability of choosing right by chance)
+comp_pval <- data.frame(
+  probright_drCORTCold_t = format_dec(pmcmc(probright_drCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_drControlCold_t = format_dec(pmcmc(probright_drControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_drCORTHot_t = format_dec(pmcmc(probright_drCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_drControlHot_t = format_dec(pmcmc(probright_drControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_dbCORTCold_t = format_dec(pmcmc(probright_dbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_dbControlCold_t = format_dec(pmcmc(probright_dbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_dbCORTHot_t = format_dec(pmcmc(probright_dbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_dbControlHot_t = format_dec(pmcmc(probright_dbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_grCORTCold_t = format_dec(pmcmc(probright_grCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_grControlCold_t = format_dec(pmcmc(probright_grControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_grCORTHot_t = format_dec(pmcmc(probright_grCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_grControlHot_t = format_dec(pmcmc(probright_grControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_gbCORTCold_t = format_dec(pmcmc(probright_gbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_gbControlCold_t = format_dec(pmcmc(probright_gbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_gbCORTHot_t = format_dec(pmcmc(probright_gbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_gbControlHot_t = format_dec(pmcmc(probright_gbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3)) %>%
+gather(key = "column", value = "value", .) %>%
+rename("p_value" = "value") %>%
+data.frame()
+write.csv(comp_pval, file= "./output/Checking/comp_pval.csv")
+# Now we merge them and organise them to have the final dt for the table
+table_df <- merge(prob_df, comp_pval, by ="column") %>%
   mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
@@
                     levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
-                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
+                    labels = c("CORTCold" = "CORT-Cold", "ControlCold" = "Control-Cold", "CORTHot" = "CORT-Hot", "ControlHot" = "Control-Hot"))) %>%
   mutate(Specie = factor(Specie,
@@
   mutate(Group = recode(Group, "dr" = "Red", "db" = "Blue", "gr" = "Red", "gb" = "Blue")) %>%
-  pivot_wider(names_from = Group, values_from = c(value, column)) %>% #To split the df in Red and Blue
+  select(-column) %>%
+  pivot_wider(names_from = Group, values_from = c(prob_choice, p_value)) %>% #To split the df in Red and Blue
+  select(Specie, Treatment, prob_choice_Blue, p_value_Blue, prob_choice_Red, p_value_Red) %>%
+  arrange(Specie, Treatment) %>% # To arrange the rows the way I wantdata.frame()
 data.frame()
-
-write.csv(prob_df, file= "./output/Checking/prob_df.csv")
-
-# Then we build a df with the statistical comparison between probabilities (Blue minus Red) for each treatment and species and p-values for each comparison
-comp_prob <- data.frame(
-  (probright_dbCORTCold - probright_drCORTCold),
-  (probright_dbControlCold - probright_drControlCold),
-  (probright_dbCORTHot - probright_drCORTHot),
-  (probright_dbControlHot - probright_drControlHot),
-  (probright_gbCORTCold - probright_grCORTCold),
-  (probright_gbControlCold - probright_grControlCold),
-  (probright_gbCORTHot - probright_grCORTHot),
-  (probright_gbControlHot - probright_grControlHot)
-) %>% 
-  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
-  gather(key = "column", value = "value", .) %>% #To transpose the df
-  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
-  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
-  mutate(Treatment = factor(Treatment, 
-                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
-                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
-  mutate(Specie = factor(Specie,
-                levels = c("d", "g"),
-                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
-  rename("[Blue - Red]" = "value") %>%
-data.frame()
-#
-comp_pval <- data.frame(
-  pmcmc(probright_dbCORTCold - probright_drCORTCold),
-  pmcmc(probright_dbControlCold - probright_drControlCold),
-  pmcmc(probright_dbCORTHot - probright_drCORTHot),
-  pmcmc(probright_dbControlHot - probright_drControlHot),
-  pmcmc(probright_gbCORTCold - probright_grCORTCold),
-  pmcmc(probright_gbControlCold - probright_grControlCold),
-  pmcmc(probright_gbCORTHot - probright_grCORTHot),
-  pmcmc(probright_gbControlHot - probright_grControlHot)
-) %>% 
-  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
-  gather(key = "column", value = "value", .) %>% #To transpose the df
-  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
-  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
-  mutate(Treatment = factor(Treatment, 
-                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
-                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
-  mutate(Specie = factor(Specie,
-                levels = c("d", "g"),
-                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
-  rename("p-value" = "value") %>%
-data.frame()
-#Create the final database and the table
-table_df <- merge(prob_df, comp_prob, by = c("Specie", "Treatment")) %>%
-  merge(comp_pval, by = c("Specie", "Treatment")) %>%
-  select(Specie, Treatment, value_Blue, value_Red, X.Blue...Red., p.value) %>%
-  mutate(Treatment = factor(Treatment, 
-                    levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
-data.frame()
-table_df <- table_df %>%
-#
+write.csv(table_df, file= "./output/Checking/table_df.csv")
+#################
 colour_table <- flextable(table_df) %>%
-  bold(~ `p.value` < 0.05, ~ `p.value` + X.Blue...Red.) %>%
+  bold(~ `p_value_Blue` < 0.05, ~ `p_value_Blue` + prob_choice_Blue) %>%
+  bold(~ `p_value_Red` < 0.05, ~ `p_value_Red` + prob_choice_Red) %>%
   set_table_properties(width = 1) %>%
   align(align="center", part="all") %>% 
-  set_header_labels(value_Blue = "Blue",
-                    value_Red = "Red",
-                    p.value = "p-value",
-                    X.Blue...Red. = "[Blue - Red]") %>%
-  italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
-  colformat_num(columns = c("Blue", "Red", "[Blue-Red]", "p-value"), digits = 3) %>% # To set the number of decimals
+  set_header_labels(prob_choice_Blue = "Prob Blue", 
+                    p_value_Blue = "p-value Blue", 
+                    prob_choice_Red = "Prob Red", 
+                    p_value_Red = "p-value Red") %>%
+  italic(j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
   flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
   hline(i = c(4), j = c(1:6), part = "body") %>% # To make some horizontal lines
+  vline(j = c(2,4), part = "all") %>% # To make some vertical lines on body
 autofit()

### 2024-01-17 .vdoc.r

@@ -1,0 +1,440 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: FigMethods
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
+write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
+write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+      }
+    }
+  }
+}
+#
+#
+#
+#
+#| label: models
[…]

### 2024-01-17 R/func.r

@@ -128,11 +128,20 @@ return(new_df)
 #' @param x The vector for the posterior distribution. Note that this will test the null hypothesis that the parameter of interest is significantly different from 0. 
 #' @param null A numeric value decsribing what the null hypothesis should be
 #' @param twotail Whether to conduct a one-tailed hypothesis or a two-tailed hypotheses. Default = true indicating a two-tailed test will be done.
-pmcmc <- function(x, null = 0, twotail = TRUE){
+#' @param dir The direction of the one-tail test (<) or (>)
+pmcmc <- function(x, null = 0, twotail = TRUE, dir){
   if(twotail){
     2*(1 - max(table(x<=null) / length(x)))
   } else{
-    (1 - max(table(x<=null) / length(x)))
+    if(dir == "<"){
+    (max(sum(x>=null) / length(x)))
+    } else{
+      if(dir == ">"){
+        (max(sum(x<=null) / length(x)))
+      } else{
+        stop("dir not valid")
+      }
+    }
   }
 }
 ####################

### 2024-01-17 ms.qmd
Updates Suppl

@@
 #### Colour preference in the Associative task
-To test if lizards were biased towards blue as our preliminary analyses indicated, we employed the intercept estimates from our posterior distribution to get the predicted probability of choosing the right in the first trial using the formula:
+To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercept  from our posterior distribution.
+We first estimated the predicted probability of making the right choice in the first trial, by using the formula:
 $$\text{Probability} = \frac{1}{1 + e^{-A}}$$
-As we used the link=‘logit’ adjustment in our initial models.
+Where A was the intercept per each of the treatments, colour and species.
+Secondly, we tested the hypothesis that the estimated probability was higher than 0.33 (the probability expected by chance of making the right choice) using pmcmc.
+If the estimated probability is above 0.33.
+we consider it as an indication that there was a preference towards that colour that could be affecting our learning slopes.
+The results per treatment are summarize in @Tablebias.
 ```{r, Tablebias}
 #| label: Tablebias
-#| tbl-cap: "Biases"
+#| tbl-cap: "Probability of choosing right when the assigned feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment"
 source(here("R", "func.R"))
@@
 
-For _L. delicata_, there was no differences between treatments ('Red' group: 'Control-Cold' - 'CORTCold')
+On average, we found that, for both species, the proportion of right choices was significantly above chance when the assigned feeder was 'Blue' (_L.
+delicata_: mean Prob choice = `r format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
+guichenoti_: mean Prob choice = `r format_dec(mean((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was 'Red' (_L.
+delicata_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
+guichenoti_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`).
+
+#### Checking the models residuals and posterior distributions
+
+```{r, residuals}
 
 ```
+
+#### Checking age per treatment and species
+
+```{r, age}
+
+```

### 2024-01-17 .vdoc.r

@@ -181,7 +181,7 @@ grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich
 #
 #
 #| label: Tabledata
-#| tbl-cap: "\beta estimates of Associative learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the /beta estimates obtain from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean /beta estimates is equal to zero. In bold those values that are significant (p-value <0.05)"
+#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"
 source(here("R", "func.R"))
 #
 ############################## CREATING BIG DF FOR TABLE ##############################
@@ -322,8 +322,13 @@ real_table
 #
 #
 #
+#
+#
+#
+#
+#
 #| label: Tablebias
-#| tbl-cap: "Biases"
+#| tbl-cap: "Probability of choosing right when the assigned feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment"
 source(here("R", "func.R"))
 # First we estimate the probability of choosing right in the first trial using the intercepts from the posteriors
 ## 1) L. delicata
@@ -426,6 +431,7 @@ colour_table <- flextable(table_df) %>%
   vline(j = c(2,4), part = "all") %>% # To make some vertical lines on body
 autofit()
 colour_table
+format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot/4), 3))
 #
 #
 #
@@ -434,6 +440,16 @@ colour_table
 #
 #
 #
+#
+
+
+#
+#
+#
+#
+#
+#
+
 #
 #
 #

### 2024-01-19 .vdoc.r
Updates

@@ -1,456 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: FigMethods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG_1.svg")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
-write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
-write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
-    for(k in 1:length(hormone)){
-      for(l in 1:length(temperature)){
-        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
-      }
-    }
-  }
-}
-#
-#
-#
-#
-#| label: models
[…]

### 2024-01-20 ms.qmd
Updates

--- 2024-01-17 ms.qmd
@@
 crossref:  
-  fig-title: Figure    # (default is "Figure")
+  fig-title: Fig    # (default is "Figure")
   title-delim: —     # (default is ":")
@@
 Particularly, learning - the acquisition of neuronal representations of new information [@dukas_evolutionary_2004] - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
-However, the capacity of individuals to acquire new information exhibits natural variation influenced by factors like age, sex, gut microbiota, or the environment where animals develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
-The developmental environment, in particular, plays a pivotal role, as the brain is especially susceptible to environmental influences during early stages of development [@zhu_prenatal_2004].
-Hence, investigating the effects of the developmental environment on learning can be essential to understand the evolution of learning and predict animals' responses towards environmental change.
-In this sense, prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
-GCs - hormones related to organisms' response to stress [@sapolsky_how_2000] - exert sustained effects on neural structure and physiology that are associated with animals' performance on learning tasks [@lemaire_prenatal_2000; @zhu_prenatal_2004; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
-Some studies have demonstrated that prenatal stress and high prenatal GC levels impair with learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors such as sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
+However, in nature, there is individual variation in the capacity to acquire new information, influenced by factors like age, sex, gut microbiota, or the environment where they develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
+In particular, early life conditions can play a pivotal role since the brain is especially susceptible to environmental influences during early stages of development [@zhu_prenatal_2004].
+Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.
+In this sense, prenatal Glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
+For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like subjects' sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
 Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020].
-For instance, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@abayarathna_effects_2020].
+For example, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@abayarathna_effects_2020].
 In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021] that share some similarities with those resulting from prenatal increased stress or GC levels [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009].
-This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning skills [@noble_developmental_2018].
+This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning abilities [@noble_developmental_2018].
 Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
-Despite the proximate similarities of prenatal GCs and temperature effects and the potential role of GCs in vertebrates response to elevated temperatures, our understanding of how these two factors interact remains incomplete.
+However, despite the proximate similarities of prenatal GCs and temperature effects, and the potential role of GCs in vertebrates' response to elevated temperatures, our understanding of how these two factors interact remains incomplete.
 In this study, our objective is to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning.
@@
 We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
-Post-incubation, the juveniles were subjectd to a colour-associative and a reversal task to comprehensively assess their learning abilities.
-Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's morphology and physiology that will ultimately impact learning skills.
-We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently in the learning tasks compared to control individuals or those exposed to high temperatures.
+Post-incubation, the juveniles were subjectd to a colour-associative and a reversal task to assess their learning abilities.
+Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's physiology that will ultimately impact learning skills.
+We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently in both learning tasks compared to control individuals or those exposed to high temperatures.
 Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
 We also expect the treatments to affect both tasks equally, with those individuals exposed to high levels of CORT and/or low temperatures performing less proficiently in both tasks compared to control individuals or those exposed to high temperatures.
-Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species in learning [@bezzina2014does].
+Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].
 
@@
 #### Subjects  
-
 _L.
@@
 #### Husbandry  
-
 *Breeding colony* -- We tested juveniles coming from a breeding colony established in the lab since 2019.
@@
 Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
-
 *Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
@@
 The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
-
 *Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
@@
 All care otherwise follows similar protocols to adults (see above).
-
 Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation.
@@
 #### CORT and Temperature manipulation  
-To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@FigMethods A).
+To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
 We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
@@
 #### Learning  
-To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@FigMethods B) [see @leal_behavioural_2012; @clark_colour_2014].
+To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@fig-Methods B) [see @leal_behavioural_2012; @clark_colour_2014].
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
 We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A.
-domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@FigMethods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@FigMethods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
-@FigMethods B, Stage 3).
+domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
+@fig-Methods B, Stage 3).
 Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
@@
 In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig.
-@FigMethods B).
+@fig-Methods B).
 The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour.
@@
 Lizards were tested in this task once a day for 35 days.
-After the colour association phase, we performed a choice reversal task (Reversal task in @FigMethods B).
+After the colour association phase, we performed a choice reversal task (Reversal task in @fig-Methods B).
 This task was like the colour association test, except that the attainability of prey was indicated by a different colour, requiring the lizards to form a novel association between the new colour and the food reward.
@@
 
-```{r, FigMethods}
-#| label: FigMethods
+```{r, fig-Methods}
+#| label: fig-Methods
 #| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**).
@@
 Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e.
-whether the individual chose correct (1) or not (0) was used as the response variable, employing a Bernoulli probability distribution (link=‘logit’).
+whether the individual chose correct (1) or not (0) was used as the response variable.
 The fixed effects of the model included a triple interaction between: trial ('Associative trial' or 'Reversal trial') as a numeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors.
-For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the variable trial within each level of lizard identity.
-For all models we
+For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the variable trial ('Associative' or 'Reversal') within each level of lizard identity.
 We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned.
@@
 However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards.
-Final sample sizes per treatment and species are disclosed on @Tabledata.
+Final sample sizes per treatment and species are disclosed on @tbl-data.
 ```{r, models}
@@
 
-```{r, Tabledata}
-#| label: Tabledata
+```{r, tbl-data}
+#| label: tbl-data
 #| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.
@@
 
-@Tabledata summarizes the estimates of learning slopes for all the treatments in each model (see Statistical analyses).
-On average, we found that learning slopes were lower when the 'Blue' feeders were correct compared to those assigned to the group 'Red'  for _L.
-delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot))`), but not for _L.
+Results of the associative task are summarized in @tbl-data and figures @Figdeli, @Figguich.
+On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red'  for _L.
+delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`), but not for _L.
 guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`).
-However, because we suspect there may be a bias towards 'Blue' in the initial choice (see Supplementary Material and Figs.
-@Figdeli, @Figguich), we only used those individuals assigned to 'Red' to compare performance in the associative learning task.
+However, further analyses using the first trial indicated a potential bias towards 'Blue' in the initial choice (see Supplementary Material and Figs.
+@Figdeli, @Figguich); and in consequence, we only used those individuals assigned to 'Red' to compare between-treatment performance in the associative learning task.
 In this regard, we did not find any significant differences between treatments for _L.
@@
 guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`).
-We also did not find any significant differences when we compared the estimated slopes between species for the associative task (only individuals from 'Red' group: _L.
+We also did not find any significant differences when we compared the estimated slopes between species for the associative task (_L.
 delicata_ - _L.
 guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
+In the reversal tesk, we decided to pool both groups 'Blue' and 'Red' to make the between-treatment comparisons for two reasons.
+First, we did not find any significant differences caused group on the learning slopes (_L.
+delicata_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`, p = `r format_dec(pmcmc((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`; _L.
+guichenoti_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`, p = `r format_dec(pmcmc((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`).
+Second, we were expecting an acquired bias towards the colour assigned in the associative task as part of the design.
+Nonetheless, we did not find any significant differences between treatments in _L.
+delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`) (see @Figguich).
+We did not find any effect of incubation temperature (_L.
+delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L.
+delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L.
+guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled.
+Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L.
+delicata_ - _L.
+guichenoti_ = `r format_dec(mean((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).
 
-```{r, Figdeli}
-#| label: Figdeli
+```{r, figdeli}
+#| label: figdeli
 #| fig.cap: "Deli"
+# First step, create the Intercepts for all models
+## 1) Associative task
+### Group = red
+int_dar_CORTCold <- deli_asso_red$b_Intercept
+int_dar_ControlCold <- (deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)
+int_dar_CORTHot <- (deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)
+int_dar_ControlHot <- (deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)
+### Group = blue
+int_dab_CORTCold <- deli_asso_blue$b_Intercept
+int_dab_ControlCold <- (deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)
+int_dab_CORTHot <- (deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)
+int_dab_ControlHot <- (deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)
+## 2) Reversal task
+### Group = red
+int_drr_CORTCold <- deli_rev_red$b_Intercept
+int_drr_ControlCold <- (deli_rev_red$b_cortControl + deli_rev_red$b_Intercept)
+int_drr_CORTHot <- (deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
+int_drr_ControlHot <- (deli_rev_red$'b_cortControl:tempHot' + deli_rev_red$b_cortControl + deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
+### Group = blue
+int_drb_CORTCold <- deli_rev_blue$b_Intercept
+int_drb_ControlCold <- (deli_rev_blue$b_cortControl + deli_rev_blue$b_Intercept)
+int_drb_CORTHot <- (deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
+int_drb_ControlHot <- (deli_rev_blue$'b_cortControl:tempHot' + deli_rev_blue$b_cortControl + deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
+# Second step, create the df for each model with trials as columns and the predicted probability of choosing right as rows under equation: Prob = 1/(1+e^-(Intercept + Slope*trial))??
+## 1) Associative task
+### Group = red
+#### CORT-Cold
+
 ```
@@
 
-[RESULTS reversal]
-
 ## Discussion
@@
 ## References
-\printbibliography
+<div id="refs"></div>
 
-\pagebreak
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
 
@@
 #### Colour preference in the Associative task
-To test if lizards were biased towards blue as our preliminary analyses indicated, we employed the intercept estimates from our posterior distribution to get the predicted probability of choosing the right in the first trial using the formula:
-$$\text{Probability} = \frac{1}{1 + e^{-A}}$$
-As we used the link=‘logit’ adjustment in our initial models.
-```{r, Tablebias}
-#| label: Tablebias
-#| tbl-cap: "Biases"
+To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercepts  from our posterior distributions.
+We first estimated the predicted probability of choosing the correct feeder first in the first trial, by using the formula:
+$$\text{Probability} = \frac{1}{1 + e^{-Intercept}}$$
+
+Second, we tested the hypothesis that the estimated probability was higher than 0.33 (the probability expected by chance of choosing the correct feeder) using pmcmc.
+If the estimated probability is above 0.33.
+we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes.
+The results per treatment are summarized in @tbl-bias.
+```{r, tbl-bias}
+#| label: tbl-bias
+#| tbl-cap: "Probability of choosing the correct feeder in the first trial when the correct feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
+p-values were obtained using pmcmc and test the hypothesis that the probability is >0.33.
+In bold, those values that are significant (p-value <0.05)"
 source(here("R", "func.R"))
@@
 
-For _L. delicata_, there was no differences between treatments ('Red' group: 'Control-Cold' - 'CORTCold')
+On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue (_L.
+delicata_: mean Prob choice = `r format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
+guichenoti_: mean Prob choice = `r format_dec(mean((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L.
+delicata_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
+guichenoti_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`).
 
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
 ```
+
+#### Checking the models plots  
+```{r, residuals}
+# Chunk for calling all the models and making the residuals
+# Associative task
+## L. delicata
+### Red
+mod_dar <- readRDS(here("output/models/asso_deli_red.rds"))
+resid_dar <- residuals(mod_dar)
+### Blue
+mod_dab <- readRDS(here("output/models/asso_deli_blue.rds"))
+resid_dab <- residuals(mod_dab)
+## L. guichenoti
+### Red
+mod_gar <- readRDS(here("output/models/asso_guich_red.rds"))
+resid_gar <- residuals(mod_gar)
+### Blue
+mod_gab <- readRDS(here("output/models/asso_guich_blue.rds"))
+resid_gab <- residuals(mod_gab)
+# Reversal task
+## L. delicata
+### Red
+mod_drr <- readRDS(here("output/models/rev_deli_red.rds"))
+resid_drr <- residuals(mod_drr)
+### Blue
+mod_drb <- readRDS(here("output/models/rev_deli_blue.rds"))
+resid_drb <- residuals(mod_drb)
+## L. guichenoti
+### Red
+mod_grr <- readRDS(here("output/models/rev_guich_red.rds"))
+resid_grr <- residuals(mod_grr)
+### Blue
+mod_grb <- readRDS(here("output/models/rev_guich_blue.rds"))
+resid_grb <- residuals(mod_grb)
+```
+
+Model formula for the associative task is:  
+Choice  ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)  
+Plots for the different models of the associative task:  
+1.- _L. delicata_  
+  1.a.- Red  
+```{r , plotmod_dar, out.width="70%", fig.align="center"}
+plot(mod_dar)
+```
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+  1.b.- Blue  
+```{r , plotmod_dab, out.width="70%", fig.align="center"}
+plot(mod_dab)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+2.- _L. guichenoti_  
+  2.a.- Red  
+```{r , plotmod_gar, out.width="70%", fig.align="center"}
+plot(mod_gar)
+```
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+  2.b.- Blue  
+```{r , plotmod_gab, out.width="70%", fig.align="center"}
+plot(mod_gab)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+Model formula for the reversal task is:  
+Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)  
+Plots for the different models of the associative task:  
+1.- _L. delicata_  
+  1.a.- Red  
+```{r , plotmod_drr, out.width="70%", fig.align="center"}
+plot(mod_drr)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+  1.b.- Blue  
+```{r , plotmod_drb, out.width="70%", fig.align="center"}  
+plot(mod_drb)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+2.- _L. guichenoti_  
+  2.a.- Red  
+```{r , plotmod_grr, out.width="70%", fig.align="center"}
+plot(mod_grr)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+  2.b.- Blue  
+```{r , plotmod_grb, out.width="70%", fig.align="center"}
+plot(mod_grb)
+```

### 2024-01-26 ms.qmd
Updates

@@
 Particularly, learning - the acquisition of neuronal representations of new information [@dukas_evolutionary_2004] - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
-However, in nature, there is individual variation in the capacity to acquire new information, influenced by factors like age, sex, gut microbiota, or the environment where they develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
-In particular, early life conditions can play a pivotal role since the brain is especially susceptible to environmental influences during early stages of development [@zhu_prenatal_2004].
+However, in nature, there is individual variation in the capacity to acquire new information, depending on factors like age, sex, gut microbiota, or the environment where organisms develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
+The latter can be particularly relevant since the brain is especially susceptible to environmental conditions during early stages of development [@zhu_prenatal_2004].
 Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.
@@
 Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
-However, despite the proximate similarities of prenatal GCs and temperature effects, and the potential role of GCs in vertebrates' response to elevated temperatures, our understanding of how these two factors interact remains incomplete.
+However, despite the proximate similarities of prenatal GCs and temperature effects, and the potential role of GCs in vertebrates' response to temperature, our understanding of how these two factors interact remains incomplete.
 In this study, our objective is to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning.
@@
 We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
-Post-incubation, the juveniles were subjectd to a colour-associative and a reversal task to assess their learning abilities.
+Post-incubation, the juveniles were subjectd to a colour-associative task to assess their learning abilities.
 Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's physiology that will ultimately impact learning skills.
-We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently in both learning tasks compared to control individuals or those exposed to high temperatures.
+We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently compared to control individuals or those exposed to high temperatures.
 Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
-We also expect the treatments to affect both tasks equally, with those individuals exposed to high levels of CORT and/or low temperatures performing less proficiently in both tasks compared to control individuals or those exposed to high temperatures.
 Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].
@@
 This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
-In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig.
+For the learning phase, we trained lizards to associate between colour and a food reward (Associative task in Fig.
 @fig-Methods B).
@@
 Lizards were tested in this task once a day for 35 days.
-After the colour association phase, we performed a choice reversal task (Reversal task in @fig-Methods B).
-This task was like the colour association test, except that the attainability of prey was indicated by a different colour, requiring the lizards to form a novel association between the new colour and the food reward.
-This test was done once a day for 40 days.
-The full experiment was done daily between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
-Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.
+The full experiment was done daily between the 6^th^ of March until the 17^th^ of June 2023, between 11 to 12 am, when the lizards were active.
+Trials in the learning phases (colour associative task and reversal tasks) were recorded with CCTV systems always using the same camera per individual.
 Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not.
@@
 delicata_ or _L.
-guichenoti_) and task ('Associative' or 'Reversal') separately.
+guichenoti_) separately.
 We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour ('Blue' or 'Red') as well.
-As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (**REF brm package**) in Quartos (**REF QUARTOS**).
+As such, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
 Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e.
-whether the individual chose correct (1) or not (0) was used as the response variable.
-The fixed effects of the model included a triple interaction between: trial ('Associative trial' or 'Reversal trial') as a numeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors.
-For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the variable trial ('Associative' or 'Reversal') within each level of lizard identity.
+whether the feeder visited first was the correct one (1) or not (0) was used as the response variable.
+The fixed effects of the model included a triple interaction between: 'Trial' as a nummeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors.
+For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the 'Trial' within each level of lizard identity.
 We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned.
@@
 source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
-write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
-write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
 ```
@@
 #| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task.
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task.
 We used function sample (see func.R) to estimate the sample size per treatment and species.
@@
 #| label: models
-# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder).
+# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder).
 The result everytime the function is used is a df with the posteriors of the model.
@@
 source(here("R", "func.R"))
-# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
+# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
 ## A.1) L. delicata
-deli_asso_red <- fit_m("asso", "deli", "red", refit = FALSE)
-write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
-deli_asso_blue <- fit_m("asso", "deli", "blue", refit = FALSE)
-write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
+deli_red <- fit_m("deli", "red", refit = TRUE)
+write.csv(deli_red, file= "./output/Checking/deli_red.csv")
+deli_blue <- fit_m("deli", "blue", refit = TRUE)
+write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
 ## A.2) L. guichenoti
-guich_asso_red <- fit_m("asso", "guich", "red", refit = FALSE)
-write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
-guich_asso_blue <- fit_m("asso", "guich", "blue", refit = FALSE)
-write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
-# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-## B.1) L. delicata
-deli_rev_red <- fit_m("rev", "deli", "red", refit = FALSE)
-write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
-deli_rev_blue <- fit_m("rev", "deli", "blue", refit = FALSE)
-write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
-## B.2) L. guichenoti
-guich_rev_red <- fit_m("rev", "guich", "red", refit = FALSE)
-write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
-guich_rev_blue <- fit_m("rev", "guich", "blue", refit = FALSE)
-write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
+guich_red <- fit_m("guich", "red", refit = TRUE)
+write.csv(guich_red, file= "./output/Checking/guich_red.csv")
+guich_blue <- fit_m("guich", "blue", refit = TRUE)
+write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
 ```
 
-```{r, resultsAsso}
-# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment in the Associative task.
-This "learning rate" consists on the slope of the posterior of the Associative_Trial parameter.
+```{r, results}
+# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment.
+This "learning rate" consists on the slope of the posterior of the Trial parameter.
 The slope is the rate at which the probability of choosing the correct feeder increases with each trial.
-The slope is obtained by adding the posterior of the Associative_Trial parameter to the posterior of the interaction between Associative_Trial and the treatment (cort and temp).
+The slope is obtained by adding the posterior of the Trial parameter to the posterior of the interaction between Trial and the treatment (cort and temp).
 ## 1) L. delicata
 ### Group = red
-dar_CORTCold <- deli_asso_red$b_Associative_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
-dar_ControlCold <- (deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$b_Associative_Trial)
-dar_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
-dar_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial+ deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$'b_Associative_Trial:tempHot')
+dar_CORTCold <- deli_red$b_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
+dar_ControlCold <- (deli_red$'b_Trial:cortControl' + deli_red$b_Trial)
+dar_CORTHot <- (deli_red$'b_Trial:tempHot' + deli_red$b_Trial)
+dar_ControlHot <- (deli_red$'b_Trial:cortControl:tempHot' + deli_red$b_Trial+ deli_red$'b_Trial:cortControl' + deli_red$'b_Trial:tempHot')
 ### Group = blue
-dab_CORTCold <- deli_asso_blue$b_Associative_Trial
-dab_ControlCold <- (deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$b_Associative_Trial)
-dab_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
-dab_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial + deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$'b_Associative_Trial:tempHot')
+dab_CORTCold <- deli_blue$b_Trial
+dab_ControlCold <- (deli_blue$'b_Trial:cortControl' + deli_blue$b_Trial)
+dab_CORTHot <- (deli_blue$'b_Trial:tempHot' + deli_blue$b_Trial)
+dab_ControlHot <- (deli_blue$'b_Trial:cortControl:tempHot' + deli_blue$b_Trial + deli_blue$'b_Trial:cortControl' + deli_blue$'b_Trial:tempHot')
 ## 2) L. guichenoti
 ### Group = red
-gar_CORTCold <- guich_asso_red$b_Associative_Trial
-gar_ControlCold <- (guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$b_Associative_Trial)
-gar_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
-gar_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial + guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$'b_Associative_Trial:tempHot')
+gar_CORTCold <- guich_red$b_Trial
+gar_ControlCold <- (guich_red$'b_Trial:cortControl' + guich_red$b_Trial)
+gar_CORTHot <- (guich_red$'b_Trial:tempHot' + guich_red$b_Trial)
+gar_ControlHot <- (guich_red$'b_Trial:cortControl:tempHot' + guich_red$b_Trial + guich_red$'b_Trial:cortControl' + guich_red$'b_Trial:tempHot')
 ### Group = blue
-gab_CORTCold <- guich_asso_blue$b_Associative_Trial
-gab_ControlCold <- (guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$b_Associative_Trial)
-gab_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
-gab_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial + guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$'b_Associative_Trial:tempHot')
-```
-
-```{r, resultsRev}
-# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
-## 1) L. delicata
-### Group = red
-drr_CORTCold <- deli_rev_red$b_trial_reversal
-drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
-drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
-drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
-### Group = blue
-drb_CORTCold <- deli_rev_blue$b_trial_reversal
-drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
-drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
-drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
-## 2) L. guichenoti
-### Group = red
-grr_CORTCold <- guich_rev_red$b_trial_reversal
-grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
-grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
-grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
-### Group = blue
-grb_CORTCold <- guich_rev_blue$b_trial_reversal
-grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
-grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
-grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
+gab_CORTCold <- guich_blue$b_Trial
+gab_ControlCold <- (guich_blue$'b_Trial:cortControl' + guich_blue$b_Trial)
+gab_CORTHot <- (guich_blue$'b_Trial:tempHot' + guich_blue$b_Trial)
+gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial + guich_blue$'b_Trial:cortControl' + guich_blue$'b_Trial:tempHot')
 ```
@@
 #| label: tbl-data
-#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.
+#| tbl-cap: "Estimates of learning slope for all the different treatments per each task, species and group.
 Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
@@
 groups <- c("Red", "Blue")
-test <- c("Associative", "Reversal")
 treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
@@
 p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
-#First get estimates for both tasks
-estimates_asso <- list(
+# First call the estimates
+estimates <- list(
   dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
@@
 #
-estimates_rev <- list(
-  drr_CORTCold, drr_ControlCold, drr_CORTHot, drr_ControlHot, 
-  drb_CORTCold, drb_ControlCold, drb_CORTHot, drb_ControlHot, 
-  grr_CORTCold, grr_ControlCold, grr_CORTHot, grr_ControlHot, 
-  grb_CORTCold, grb_ControlCold, grb_CORTHot, grb_ControlHot
-)
 # Then get the mean, co.intervals(95%), and p-values
-asso_mean <- format_dec(sapply(estimates_asso, mean), 3)
-asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
-asso_interval_975 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.975)), 3)
-asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
-asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 3)
+l_mean <- format_dec(sapply(estimates, mean), 3)
+l_interval_025 <- format_dec(sapply(estimates, function(x) quantile(x,0.025)), 3)
+l_interval_975 <- format_dec(sapply(estimates, function(x) quantile(x,0.975)), 3)
+l_intervals <- paste(l_interval_025, l_interval_975, sep = " , ")
+l_pvalue <- format_dec(sapply(estimates, pmcmc), 3)
 #
-rev_mean <- format_dec(sapply(estimates_rev, mean), 3)
-rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
-rev_interval_975 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.975)), 3)
-rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
-rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 3)
-#
-# Building the df for the associative
-asso_df <- data.frame(
+# Building the df
+df <- data.frame(
   Specie = rep(specie, each = length(groups) * length(treatments)),
@@
   Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
-  Mean = rep(asso_mean, each = 1),
-  CI = rep(asso_intervals, each = 1),
-  PValue = rep(asso_pvalue, each = 1),
-  Task = rep("Associative", length(asso_mean))
+  Mean = rep(l_mean, each = 1),
+  CI = rep(l_intervals, each = 1),
+  PValue = rep(l_pvalue, each = 1)
 )
-# Building the df for the reversal
-rev_df <- data.frame(
-  Specie = rep(specie, each = length(groups) * length(treatments)),
-  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
-  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
-  Mean = rep(rev_mean, each = 1),
-  CI = rep(rev_intervals, each = 1),
-  PValue = rep(rev_pvalue, each = 1),
-  Task = rep("Reversal", length(rev_mean))
-)
-# Joining both dfs
-table_data <- rbind(asso_df, rev_df)
-table_data[, sapply(table_data, is.numeric)] <- lapply(table_data[, sapply(table_data, is.numeric)], function(x) format(x, scientific = FALSE))
+write.csv(df, file= "./output/Checking/df.csv")
 #
@@
 # Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
-new_table_data <- merge(table_data, n_df) %>%
+table_data <- merge(df, n_df) %>%
   rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
-  pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal
-  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #To order the columns in the way I want for the table
+  select(Specie, Group, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table
   mutate(Specie = factor(Specie,
@@
   mutate(Treatment = paste0(Treatment, ")"))
-write.csv(new_table_data, file= "./output/Checking/new_table_data.csv")
+write.csv(table_data, file= "./output/Checking/table_data.csv")
 #
@@
 # Split the table_data df by task
-real_table <- flextable(new_table_data) %>%
-    bold(~ `p-value_Associative` < 0.05, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
-    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
+real_table <- flextable(table_data) %>%
+    bold(~ `p-value` < 0.05, ~ `p-value` + Mean + `95% CI`) %>%
     set_table_properties(width = 1) %>%
     align(align="center", part="all") %>% 
-    add_header_row(values = c("", "Associative task", "Reversal task"), colwidths = c(3, 3, 3)) %>%
-    set_header_labels(Mean_Associative = "Mean",
-                      `95% CI_Associative` = "95% CI",
-                      `p-value_Associative` = "p-value",
+    set_header_labels(Mean = "Mean",
+                      `95% CI` = "95% CI",
+                      `p-value` = "p-value",
                       Mean_Reversal = "Mean",
@@
     flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
-    hline(i = c(4,12), j = c(2:9), part = "body") %>% # To make some horizontal lines
-    hline(i = c(8), j = c(1:9), part = "body") %>% # To make some horizontal lines
-    vline(i = (1:16), j = c(3,6), part = "body") %>% # To make some vertical lines on body
-    vline(j=c(3,6), part = "header") %>% # To make some vertical lines on header
+    hline(i = c(4,12), j = c(2:6), part = "body") %>% # To make some horizontal lines
+    hline(i = c(8), j = c(1:6), part = "body") %>% # To make some horizontal lines
     autofit() 
@@
 
-Results of the associative task are summarized in @tbl-data and figures @Figdeli, @Figguich.
+Results of the are summarized in @tbl-data and figures @Figdeli, @Figguich.
 On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red'  for _L.
@@
 However, further analyses using the first trial indicated a potential bias towards 'Blue' in the initial choice (see Supplementary Material and Figs.
-@Figdeli, @Figguich); and in consequence, we only used those individuals assigned to 'Red' to compare between-treatment performance in the associative learning task.
+@Figdeli, @Figguich); and in consequence, we only used those individuals assigned to 'Red' to compare between-treatment performance.
 In this regard, we did not find any significant differences between treatments for _L.
@@
 guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`).
-We also did not find any significant differences when we compared the estimated slopes between species for the associative task (_L.
+We also did not find any significant differences when we compared the estimated slopes between species (_L.
 delicata_ - _L.
 guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
-In the reversal tesk, we decided to pool both groups 'Blue' and 'Red' to make the between-treatment comparisons for two reasons.
-First, we did not find any significant differences caused group on the learning slopes (_L.
-delicata_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`, p = `r format_dec(pmcmc((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`; _L.
-guichenoti_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`, p = `r format_dec(pmcmc((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`).
-Second, we were expecting an acquired bias towards the colour assigned in the associative task as part of the design.
-Nonetheless, we did not find any significant differences between treatments in _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`) (see @Figguich).
-We did not find any effect of incubation temperature (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled.
-Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L.
-delicata_ - _L.
-guichenoti_ = `r format_dec(mean((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).
 
@@
 ### Group = red
-int_dar_CORTCold <- deli_asso_red$b_Intercept
-int_dar_ControlCold <- (deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)
-int_dar_CORTHot <- (deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)
-int_dar_ControlHot <- (deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)
+int_dar_CORTCold <- deli_red$b_Intercept
+int_dar_ControlCold <- (deli_red$b_cortControl + deli_red$b_Intercept)
+int_dar_CORTHot <- (deli_red$b_tempHot + deli_red$b_Intercept)
+int_dar_ControlHot <- (deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)
 ### Group = blue
-int_dab_CORTCold <- deli_asso_blue$b_Intercept
-int_dab_ControlCold <- (deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)
-int_dab_CORTHot <- (deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)
-int_dab_ControlHot <- (deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)
+int_dab_CORTCold <- deli_blue$b_Intercept
+int_dab_ControlCold <- (deli_blue$b_cortControl + deli_blue$b_Intercept)
+int_dab_CORTHot <- (deli_blue$b_tempHot + deli_blue$b_Intercept)
+int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)
 ## 2) Reversal task
@@
 
-#### Colour preference in the Associative task
+#### Colour preference
 To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercepts  from our posterior distributions.
@@
 ### Group = red
-probright_drCORTCold <- 1/(1+exp(-deli_asso_red$b_Intercept))
-probright_drControlCold <- 1/(1+exp(-(deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)))
-probright_drCORTHot <- 1/(1+exp(-(deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
-probright_drControlHot <- 1/(1+exp(-(deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
+probright_drCORTCold <- 1/(1+exp(-deli_red$b_Intercept))
+probright_drControlCold <- 1/(1+exp(-(deli_red$b_cortControl + deli_red$b_Intercept)))
+probright_drCORTHot <- 1/(1+exp(-(deli_red$b_tempHot + deli_red$b_Intercept)))
+probright_drControlHot <- 1/(1+exp(-(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)))
 ### Group = blue
-probright_dbCORTCold <- 1/(1+exp(-(deli_asso_blue$b_Intercept)))
-probright_dbControlCold <- 1/(1+exp(-(deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)))
-probright_dbCORTHot <- 1/(1+exp(-(deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
-probright_dbControlHot <- 1/(1+exp(-(deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
+probright_dbCORTCold <- 1/(1+exp(-(deli_blue$b_Intercept)))
+probright_dbControlCold <- 1/(1+exp(-(deli_blue$b_cortControl + deli_blue$b_Intercept)))
+probright_dbCORTHot <- 1/(1+exp(-(deli_blue$b_tempHot + deli_blue$b_Intercept)))
+probright_dbControlHot <- 1/(1+exp(-(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)))
 ## 2) L. guichenoti
 ### Group = red
-probright_grCORTCold <- 1/(1+exp(-guich_asso_red$b_Intercept))
-probright_grControlCold <- 1/(1+exp(-(guich_asso_red$b_cortControl + guich_asso_red$b_Intercept)))
-probright_grCORTHot <- 1/(1+exp(-(guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
-probright_grControlHot <- 1/(1+exp(-(guich_asso_red$'b_cortControl:tempHot' + guich_asso_red$b_cortControl + guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
+probright_grCORTCold <- 1/(1+exp(-guich_red$b_Intercept))
+probright_grControlCold <- 1/(1+exp(-(guich_red$b_cortControl + guich_red$b_Intercept)))
+probright_grCORTHot <- 1/(1+exp(-(guich_red$b_tempHot + guich_red$b_Intercept)))
+probright_grControlHot <- 1/(1+exp(-(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept)))
 ### Group = blue
-probright_gbCORTCold <- 1/(1+exp(-guich_asso_blue$b_Intercept))
-probright_gbControlCold <- 1/(1+exp(-(guich_asso_blue$b_cortControl + guich_asso_blue$b_Intercept)))
-probright_gbCORTHot <- 1/(1+exp(-(guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
-probright_gbControlHot <- 1/(1+exp(-(guich_asso_blue$'b_cortControl:tempHot' + guich_asso_blue$b_cortControl + guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
+probright_gbCORTCold <- 1/(1+exp(-guich_blue$b_Intercept))
+probright_gbControlCold <- 1/(1+exp(-(guich_blue$b_cortControl + guich_blue$b_Intercept)))
+probright_gbCORTHot <- 1/(1+exp(-(guich_blue$b_tempHot + guich_blue$b_Intercept)))
+probright_gbControlHot <- 1/(1+exp(-(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept)))
 # Second we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species
@@
 # Chunk for calling all the models and making the residuals
-# Associative task
 ## L. delicata
 ### Red
-mod_dar <- readRDS(here("output/models/asso_deli_red.rds"))
+mod_dar <- readRDS(here("output/models/deli_red.rds"))
 resid_dar <- residuals(mod_dar)
 ### Blue
-mod_dab <- readRDS(here("output/models/asso_deli_blue.rds"))
+mod_dab <- readRDS(here("output/models/deli_blue.rds"))
 resid_dab <- residuals(mod_dab)
@@
 ### Red
-mod_gar <- readRDS(here("output/models/asso_guich_red.rds"))
+mod_gar <- readRDS(here("output/models/guich_red.rds"))
 resid_gar <- residuals(mod_gar)
 ### Blue
-mod_gab <- readRDS(here("output/models/asso_guich_blue.rds"))
+mod_gab <- readRDS(here("output/models/guich_blue.rds"))
 resid_gab <- residuals(mod_gab)
-# Reversal task
-## L. delicata
-### Red
-mod_drr <- readRDS(here("output/models/rev_deli_red.rds"))
-resid_drr <- residuals(mod_drr)
-### Blue
-mod_drb <- readRDS(here("output/models/rev_deli_blue.rds"))
-resid_drb <- residuals(mod_drb)
-## L. guichenoti
-### Red
-mod_grr <- readRDS(here("output/models/rev_guich_red.rds"))
-resid_grr <- residuals(mod_grr)
-### Blue
-mod_grb <- readRDS(here("output/models/rev_guich_blue.rds"))
-resid_grb <- residuals(mod_grb)
 ```
 
-Model formula for the associative task is:  
-Choice  ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)  
+Model formula for task is:  
+Choice  ~ Trial*cort*temp + (1 + Trial|lizard_id)  
 Plots for the different models of the associative task:  
@@
 ```
-
-Model formula for the reversal task is:  
-Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)  
-Plots for the different models of the associative task:  
-1.- _L. delicata_  
-  1.a.- Red  
-```{r , plotmod_drr, out.width="70%", fig.align="center"}
-plot(mod_drr)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-  1.b.- Blue  
-```{r , plotmod_drb, out.width="70%", fig.align="center"}  
-plot(mod_drb)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-2.- _L. guichenoti_  
-  2.a.- Red  
-```{r , plotmod_grr, out.width="70%", fig.align="center"}
-plot(mod_grr)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-  2.b.- Blue  
-```{r , plotmod_grb, out.width="70%", fig.align="center"}
-plot(mod_grb)
-```

### 2024-01-26 R/1_data_process.R

@@ -8,8 +8,8 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 # Load data
 data  <-  read.csv("./data/Learning.csv")
 
-# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
-data_asso <- data %>%
+# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] and split treatment into Temp and Cort
+data_clean <- data %>%
   group_by(lizard_id) %>%
     filter(sum(is.na(FC_associative)) <= 15) %>%
     filter(trial_associative <= 35) %>%
@@ -27,29 +27,7 @@ data_asso <- data %>%
       labels = c("B" = "CORT", "A" = "Control"))) %>%
     mutate( # Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
       first_non_na = min(which(!is.na(FC_associative))),
-      Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>% 
-      filter(Associative_Trial >= 1) %>%
+      Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>% 
+      filter(Trial >= 1) %>%
   ungroup() %>% 
 data.frame()
-
-
-data_rev <- data %>%
-  group_by(lizard_id) %>%
-    filter(sum(is.na(FC_associative)) <= 15) %>%
-    filter(sum(is.na(FC_reversal)) <= 15) %>%
-   ungroup()  %>%
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"),
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
-    mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>%
-    mutate(temp = factor(temp,
-      levels = c("23", "28"),
-      labels = c("23" = "Cold", "28" = "Hot"))) %>%
-    mutate(cort = factor(cort,
-      levels = c("B", "A"),
-      labels = c("B" = "CORT", "A" = "Control"))) %>%
-    mutate(trial_reversal=as.numeric(trial_reversal)) %>%
-  data.frame()
-
-

### 2024-01-26 R/func.r

@@ -13,10 +13,10 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #' @param therm To select temp treatment ("Cold"/"Hot")
 sample <- function(sp, bias, corti, therm){
   #Specify database
-  data <- data_asso
+  data <- data_clean
   # Count sample
   sample_size <- data %>%
-                filter(species == sp, group == bias, cort == corti, temp == therm, Associative_Trial == 1) %>%
+                filter(species == sp, group == bias, cort == corti, temp == therm, Trial == 1) %>%
                 group_by(lizard_id) %>%
                 summarise(n = n()) %>%
                 summarise(total_count = sum(n)) %>%
@@ -27,26 +27,14 @@ sample <- function(sp, bias, corti, therm){
 ####################
 # Fit models and extract posteriors both per each treatment:
 #' @title fit_m Function
-#' @description Fit brm models for different the associative task
-#' @param type To define if we are analysing the associative ("asso) or the reversal ("rev")
+#' @description Fit brm models for the associative task
 #' @param sp To select the species of interest ("deli"/"guich")
 #' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
 #' @param refir To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(type, sp, bias, refit = TRUE) {
-  #Specify the type
-  if (type == "asso"){
-    data <- data_asso
-    formula <- FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
-  }else{
-    if(type == "rev"){
-      data <- data_rev
-      formula <- FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-    } else {
-      stop("Type not valid")
-      return(NULL)  # Return NULL in case of an invalid option
-    }
-  }
+fit_m <- function(sp, bias, refit = TRUE) {
+  data <- data_clean
+  formula <- FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
   #Specify species
     if (sp == "deli"){
       sp_data <- data %>%
@@ -91,10 +79,10 @@ fit_m <- function(type, sp, bias, refit = TRUE) {
                 family = bernoulli(link = "logit"),
[…]

### 2024-01-26 ms.qmd
Updates

@@
 This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
-For the learning phase, we trained lizards to associate between colour and a food reward (Associative task in Fig.
+For the learning phase, we trained lizards to associate between colour and a food reward ('Associative task' in Fig.
 @fig-Methods B).
@@
 The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-To control for potential colour preference that could bias our results (see Supplementary Material), we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal.
+To control for potential colour preference that could bias our results we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one, while for the other group we assigned red as correct.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
@@
 The full experiment was done daily between the 6^th^ of March until the 17^th^ of June 2023, between 11 to 12 am, when the lizards were active.
-Trials in the learning phases (colour associative task and reversal tasks) were recorded with CCTV systems always using the same camera per individual.
+Trials in the learning phase were recorded with CCTV systems always using the same camera per individual.
 Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not.
@@
 guichenoti_) separately.
-We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour ('Blue' or 'Red') as well.
+We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour (blue or red) as well.
 As such, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
-Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e.
+Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.
+'Choice', i.e.
 whether the feeder visited first was the correct one (1) or not (0) was used as the response variable.
@@
 More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not.
-We used the pmcmc method to test whether those slopes or the comparissons between 'Treatments' (e.g.
+We used the pmcmc method to test whether those slopes or the comparissons between treatments (e.g.
 slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests).
@@
 Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
-However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards.
+However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards.
 Final sample sizes per treatment and species are disclosed on @tbl-data.
@@
 ## A.1) L. delicata
-deli_red <- fit_m("deli", "red", refit = TRUE)
+deli_red <- fit_m("deli", "red", refit = FALSE)
 write.csv(deli_red, file= "./output/Checking/deli_red.csv")
-deli_blue <- fit_m("deli", "blue", refit = TRUE)
+deli_blue <- fit_m("deli", "blue", refit = FALSE)
 write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
 ## A.2) L. guichenoti
-guich_red <- fit_m("guich", "red", refit = TRUE)
+guich_red <- fit_m("guich", "red", refit = FALSE)
 write.csv(guich_red, file= "./output/Checking/guich_red.csv")
-guich_blue <- fit_m("guich", "blue", refit = TRUE)
+guich_blue <- fit_m("guich", "blue", refit = FALSE)
 write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
@@
 guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`).
-However, further analyses using the first trial indicated a potential bias towards 'Blue' in the initial choice (see Supplementary Material and Figs.
-@Figdeli, @Figguich); and in consequence, we only used those individuals assigned to 'Red' to compare between-treatment performance.
-In this regard, we did not find any significant differences between treatments for _L.
+However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and Figs.
+@Figdeli, @Figguich) that could be affecting the estimated slopes.
+As such, we analysed the between treatments differences for each group separately.
+For those individuals assigned to group 'Red', we did not find any significant differences between treatments neither for _L.
 delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L.
 guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figguich).
-When groups were pooled by incubation temperature or hormonal treatment, there was not significant differences in the estimated slopes caused by temperature (_L.
+However, in both species the slope in the 'CORTCold' treatments seems bigger than the rest for group 'Red'.
+When groups were pooled by incubation temperature, slopes from individuals incubated at 23ºC were on average bigger in both species, but the difference was not significant (_L.
 delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`) or the hormone (_L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`).
+CORT also lead to higher slopes in both species, but the differences were not significant (_L.
 delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L.
@@
 guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
+The results for 'Blue' individuals were similar.
+We did not find significant differences between treatments in _L.delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dab_ControlCold - dab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dab_ControlCold - dab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dab_ControlHot- dab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dab_ControlHot - dab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dab_ControlHot - dab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dab_ControlHot - dab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dab_CORTHot - dab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dab_CORTHot - dab_CORTCold), 3)`) (see @Figdeli), or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gab_ControlCold - gab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gab_ControlCold - gab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gab_ControlHot- gab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gab_ControlHot - gab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gab_ControlHot - gab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gab_ControlHot - gab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gab_CORTHot - gab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gab_CORTHot - gab_CORTCold), 3)`) (see @Figguich).
+However, here the estimated slopes from those incubated at higher temperatures seem to be bigger on average, although the difference was not significant (_L.
+delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`; _L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`).
+Also, 'Control' _L.
+delicata_ seem to have slightly higher estimated slopes than on average ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)` ) while in _L.
+guichenoti_ is the opposite ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`); nevertheless, the differences found were not significant in any case.
+Finally, we found that learning slopes estimated for _L.
+guichenoti_ assigned to group 'Blue' were marginally higher than those from _L.
+delicata_ (_L.
+delicata_ - _L.
+guichenoti_ = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`).
 
@@
 int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)
-## 2) Reversal task
-### Group = red
-int_drr_CORTCold <- deli_rev_red$b_Intercept
-int_drr_ControlCold <- (deli_rev_red$b_cortControl + deli_rev_red$b_Intercept)
-int_drr_CORTHot <- (deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
-int_drr_ControlHot <- (deli_rev_red$'b_cortControl:tempHot' + deli_rev_red$b_cortControl + deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
-### Group = blue
-int_drb_CORTCold <- deli_rev_blue$b_Intercept
-int_drb_ControlCold <- (deli_rev_blue$b_cortControl + deli_rev_blue$b_Intercept)
-int_drb_CORTHot <- (deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
-int_drb_ControlHot <- (deli_rev_blue$'b_cortControl:tempHot' + deli_rev_blue$b_cortControl + deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
-# Second step, create the df for each model with trials as columns and the predicted probability of choosing right as rows under equation: Prob = 1/(1+e^-(Intercept + Slope*trial))??
-## 1) Associative task
-### Group = red
-#### CORT-Cold
 

### 2024-01-28 ms.qmd
bayes_R2

@@
 deli_red <- fit_m("deli", "red", refit = FALSE)
+bayes_R2(deli_red)
+
 write.csv(deli_red, file= "./output/Checking/deli_red.csv")

### 2024-01-28 ms.qmd
Fix priobability

@@
 ```{r, results}
+#| label: results
 # Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment.
@@
 ### Group = red
-probright_drCORTCold <- 1/(1+exp(-deli_red$b_Intercept))
+probright_drCORTCold <- exp(deli_red$b_Intercept)/(1+exp(deli_red$b_Intercept))
 probright_drControlCold <- 1/(1+exp(-(deli_red$b_cortControl + deli_red$b_Intercept)))

### 2024-01-28 ms.qmd
Update MS

@@
 ## A.1) L. delicata
-deli_red <- fit_m("deli", "red", refit = FALSE)
+deli_red <- fit_m("deli", "red", refit = TRUE)
 bayes_R2(deli_red)
@@
 write.csv(deli_red, file= "./output/Checking/deli_red.csv")
-deli_blue <- fit_m("deli", "blue", refit = FALSE)
+deli_blue <- fit_m("deli", "blue", refit = TRUE)
 write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
 ## A.2) L. guichenoti
-guich_red <- fit_m("guich", "red", refit = FALSE)
+guich_red <- fit_m("guich", "red", refit = TRUE)
 write.csv(guich_red, file= "./output/Checking/guich_red.csv")
-guich_blue <- fit_m("guich", "blue", refit = FALSE)
+guich_blue <- fit_m("guich", "blue", refit = TRUE)
 write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")

### 2024-01-29 ms.qmd
Updates

--- 2024-01-28 ms.qmd
@@
 deli_red <- fit_m("deli", "red", refit = FALSE)
-bayes_R2(deli_red)
-
 write.csv(deli_red, file= "./output/Checking/deli_red.csv")
@@
 
-```{r, figdeli}
+```{r, fig-results}
 #| label: figdeli
@@
 
-```{r, figguich}
-#| label: Figguich
-#| fig.cap: "Guich"
-```
-
 ## Discussion
@@
 We first estimated the predicted probability of choosing the correct feeder first in the first trial, by using the formula:
-$$\text{Probability} = \frac{1}{1 + e^{-Intercept}}$$
+$$\text{Probability} = \frac{e^{Intercept}}{1 + e^{Intercept}}$$
 
@@
 probright_drCORTCold <- exp(deli_red$b_Intercept)/(1+exp(deli_red$b_Intercept))
-probright_drControlCold <- 1/(1+exp(-(deli_red$b_cortControl + deli_red$b_Intercept)))
-probright_drCORTHot <- 1/(1+exp(-(deli_red$b_tempHot + deli_red$b_Intercept)))
-probright_drControlHot <- 1/(1+exp(-(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)))
+probright_drControlCold <- exp(deli_red$b_cortControl + deli_red$b_Intercept)/(1+exp(deli_red$b_cortControl + deli_red$b_Intercept))
+probright_drCORTHot <- exp(deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$b_tempHot + deli_red$b_Intercept))
+probright_drControlHot <- exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept))
 ### Group = blue
-probright_dbCORTCold <- 1/(1+exp(-(deli_blue$b_Intercept)))
-probright_dbControlCold <- 1/(1+exp(-(deli_blue$b_cortControl + deli_blue$b_Intercept)))
-probright_dbCORTHot <- 1/(1+exp(-(deli_blue$b_tempHot + deli_blue$b_Intercept)))
-probright_dbControlHot <- 1/(1+exp(-(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)))
+probright_dbCORTCold <- exp(deli_blue$b_Intercept)/(1+exp(deli_blue$b_Intercept))
+probright_dbControlCold <- exp(deli_blue$b_cortControl + deli_blue$b_Intercept)/(1+exp(deli_blue$b_cortControl + deli_blue$b_Intercept))
+probright_dbCORTHot <- exp(deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$b_tempHot + deli_blue$b_Intercept))
+probright_dbControlHot <- exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept))
 ## 2) L. guichenoti
 ### Group = red
-probright_grCORTCold <- 1/(1+exp(-guich_red$b_Intercept))
-probright_grControlCold <- 1/(1+exp(-(guich_red$b_cortControl + guich_red$b_Intercept)))
-probright_grCORTHot <- 1/(1+exp(-(guich_red$b_tempHot + guich_red$b_Intercept)))
-probright_grControlHot <- 1/(1+exp(-(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept)))
+probright_grCORTCold <- exp(guich_red$b_Intercept)/(1+exp(guich_red$b_Intercept))
+probright_grControlCold <- exp(guich_red$b_cortControl + guich_red$b_Intercept)/(1+exp(guich_red$b_cortControl + guich_red$b_Intercept))
+probright_grCORTHot <- exp(guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$b_tempHot + guich_red$b_Intercept))
+probright_grControlHot <- exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept))
 ### Group = blue
-probright_gbCORTCold <- 1/(1+exp(-guich_blue$b_Intercept))
-probright_gbControlCold <- 1/(1+exp(-(guich_blue$b_cortControl + guich_blue$b_Intercept)))
-probright_gbCORTHot <- 1/(1+exp(-(guich_blue$b_tempHot + guich_blue$b_Intercept)))
-probright_gbControlHot <- 1/(1+exp(-(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept)))
+probright_gbCORTCold <- exp(guich_blue$b_Intercept)/(1+exp(guich_blue$b_Intercept))
+probright_gbControlCold <- exp(guich_blue$b_cortControl + guich_blue$b_Intercept)/(1+exp(guich_blue$b_cortControl + guich_blue$b_Intercept))
+probright_gbCORTHot <- exp(guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$b_tempHot + guich_blue$b_Intercept))
+probright_gbControlHot <- exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept))
+#
 # Second we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species
@@
 plot(mod_dar)
+bayes_R2(mod_dar)
 ```

### 2024-01-29 .vdoc.r

@@ -1,0 +1,444 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+      }
+    }
+  }
+}
+#
+#
+#
+#
+#| label: models
[…]

### 2024-01-29 R/2_models.R

@@ -1,40 +1,3 @@
-####################################
-# 2_MODELS
-####################################
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
-data2 <- data_asso %>%
-          mutate(cort = factor(cort,
-                levels = c("Control", "CORT"))) %>%
-          mutate(temp = factor(temp,
-                levels = c("Hot", "Cold"))) %>%
-          filter(group == "Red") %>%
-          filter(species == "delicata") %>%
-        data.frame()
-
-model2 <- brm(FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id),
-                data = data2,
-                family = bernoulli(link = "logit"),
-                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
-postm2 <- as_draws_df(model2)
-mean(postm2$b_Associative_Trial)
-write.csv(postm2, here("output/Checking/postm2.csv"))
-######## 2.B) TIDY POSTERIOR DFs
-source(here("R", "func.R"))
-## Associative task
-tidy_posts_asso <- tidy_post(global_asso)
-write.csv(tidy_posts_asso, here("output/Checking/tidy_posts_asso.csv"))
-## Reversal task
-tidy_posts_rev <- tidy_post(global_rev)
-write.csv(tidy_posts_rev, here("output/Checking/tidy_posts_rev.csv"))
-#
-# pmcmc for specific comparisons
-
-# pmcmc for differences between 'Groups'
-
-# pmcmc for differences between both species
-
-######## 2.C) MAKE TABLE WITH POSTERIORS AND pmcmc
-
 ######## 2.E) PLOTS MODELS 
 # Plot delicata associative
 plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +

### 2024-01-29 R/func.r

@@ -142,3 +142,24 @@ format_dec <- function(x, n) {
   z <- sprintf(paste0("%.",n,"f"), x)
   return(as.numeric(z))
 }
+####################
+####################
+# Function to create each df for the figure
+#' @title df_fig
+#' @param df
+  # Select the original df
+  data_fig <- df
+  # Create new matrix
+  fig_matrix <- matrix(NA, nrow = 8000, ncol = 35)
+  # Loop
+  for(x in 0:34){
+    for(j in 1:8000){
+      value <- exp(u[j] + m[j] * x) / (1 + exp(u[j] + m[j] * x))
+      fig_matrix[j, x] <- value
+    }
+  fig_df <- as.data.frame(fig_matrix)
+  }
+data_fig <- deli_red
+u <- deli_red$b_Intercept
+m <- deli_red$b_Trial
+write.csv(fig_df, here("output/Checking/fig_df.csv"))

### 2024-01-30 ms.qmd
Updates

@@
 guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
+
+```{r, fig-results}
+#| label: figdeli
+#| fig.cap: "Deli"
+source(here("R", "func.R"))
+# First step, create the dfs for all models
+## 1) L. delicata
+### Red
+df_del_red <- df_fig(as.data.frame(deli_red), "L. delicata", "Red")
+### Blue
+df_del_blue <- df_fig(as.data.frame(deli_blue), "L. delicata", "Blue")
+## 2) L. guichenoti
+### Red
+df_gui_red <- df_fig(as.data.frame(guich_red), "L. guichenoti", "Red")
+### Blue
+df_gui_blue <- df_fig(as.data.frame(guich_blue), "L. guichenoti", "Blue")
+#
+# Second step, merge the df into a big Fig_df
+Fig_df <- rbind(df_del_red, df_del_blue, df_gui_red, df_gui_blue) %>%
+  mutate(Trial = gsub("X", "", Trial)) %>%
+  mutate(Trial = as.numeric(Trial)) %>%
+  rename("Predicted_prob" = "Value") %>%
+data.frame()
+write.csv(Fig_df, file= "./output/Checking/Fig_df.csv")
+# Make the plot
+figure_results <- plotting(Fig_df)
+ggsave("./output/figures/figure_results.png", plot=figure_results, width = 18, height = 20, units = "cm", dpi = 3000)
+print(figure_results)
+```
+
 The results for 'Blue' individuals were similar.
@@
 guichenoti_ = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`).
-
-```{r, fig-results}
-#| label: figdeli
-#| fig.cap: "Deli"
-# First step, create the Intercepts for all models
-## 1) Associative task
-### Group = red
-int_dar_CORTCold <- deli_red$b_Intercept
-int_dar_ControlCold <- (deli_red$b_cortControl + deli_red$b_Intercept)
-int_dar_CORTHot <- (deli_red$b_tempHot + deli_red$b_Intercept)
-int_dar_ControlHot <- (deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)
-### Group = blue
-int_dab_CORTCold <- deli_blue$b_Intercept
-int_dab_ControlCold <- (deli_blue$b_cortControl + deli_blue$b_Intercept)
-int_dab_CORTHot <- (deli_blue$b_tempHot + deli_blue$b_Intercept)
-int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)
-
-```
 
@@
 ```{r , plotmod_dar, out.width="70%", fig.align="center"}
+bayes_R2(mod_dar)
 plot(mod_dar)
-bayes_R2(mod_dar)
 ```
@@
 ```{r , plotmod_dab, out.width="70%", fig.align="center"}
+bayes_R2(mod_dab)
 plot(mod_dab)
@@
 ```{r , plotmod_gar, out.width="70%", fig.align="center"}
+bayes_R2(mod_gar)
 plot(mod_gar)
@@
 ```{r , plotmod_gab, out.width="70%", fig.align="center"}
+bayes_R2(mod_gab)
 plot(mod_gab)

### 2024-01-30 .vdoc.r

@@ -229,23 +229,33 @@ real_table
 #
 #
 #
-#
-#
 #| label: figdeli
 #| fig.cap: "Deli"
-# First step, create the Intercepts for all models
-## 1) Associative task
-### Group = red
-int_dar_CORTCold <- deli_red$b_Intercept
-int_dar_ControlCold <- (deli_red$b_cortControl + deli_red$b_Intercept)
-int_dar_CORTHot <- (deli_red$b_tempHot + deli_red$b_Intercept)
-int_dar_ControlHot <- (deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)
-### Group = blue
-int_dab_CORTCold <- deli_blue$b_Intercept
-int_dab_ControlCold <- (deli_blue$b_cortControl + deli_blue$b_Intercept)
-int_dab_CORTHot <- (deli_blue$b_tempHot + deli_blue$b_Intercept)
-int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)
-
+source(here("R", "func.R"))
+# First step, create the dfs for all models
+## 1) L. delicata
+### Red
+df_del_red <- df_fig(as.data.frame(deli_red), "L. delicata", "Red")
+### Blue
+df_del_blue <- df_fig(as.data.frame(deli_blue), "L. delicata", "Blue")
+## 2) L. guichenoti
+### Red
+df_gui_red <- df_fig(as.data.frame(guich_red), "L. guichenoti", "Red")
+### Blue
+df_gui_blue <- df_fig(as.data.frame(guich_blue), "L. guichenoti", "Blue")
+#
+# Second step, merge the df into a big Fig_df
+Fig_df <- rbind(df_del_red, df_del_blue, df_gui_red, df_gui_blue) %>%
+  mutate(Trial = gsub("X", "", Trial)) %>%
+  mutate(Trial = as.numeric(Trial)) %>%
+  rename("Predicted_prob" = "Value") %>%
+data.frame()
+write.csv(Fig_df, file= "./output/Checking/Fig_df.csv")
+# Make the plot
+figure_results <- plotting(Fig_df)
[…]

### 2024-01-30 R/2_models.R

@@ -1,178 +1,0 @@
-######## 2.E) PLOTS MODELS 
-# Plot delicata associative
-plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +
-  stat_smooth(method = "glm", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
-  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
-    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
-  ) +
-  facet_wrap(deli_associative$group, scales = "free_y", ncol = 1) +
-  theme(strip.placement = "outside") +  
-  theme(strip.background = element_blank()) +
-  labs(y = "Probability of correct choice", x = "Trial") +
-  theme_classic() +
-  theme(
-    axis.title = element_text(size = 18, family = "sans"),
-    axis.text = element_text(size = 10, family = "sans"),
-    legend.title = element_text(size = 14, family = "sans"),
-    legend.text = element_text(size = 12, family = "sans")
-  )
-print(plot_deli)
-ggsave("./output/figures/fig_deli_asso.png", plot=plot_deli, width = 15, height = 12, units = "cm", dpi = 3000)
- 
-# Plot guichenoti associative
-plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +
-  stat_smooth(method = "glm", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
-  scale_color_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
-    labels=c("CORT-Cold (n=11)", "Control-Cold (n=12)", "CORT-Hot (n=11)", "Control-Hot (n=10)")
-  ) +
-  facet_wrap(guich_associative$group, scales = "free_y", ncol = 1) +
-  theme(strip.placement = "outside") +
-  theme(strip.background = element_blank()) +
-  labs(y = "Probability of correct choice", x = "Trial") +
-  theme_classic() +
-  theme(
-    axis.title = element_text(size = 18, family = "sans"),
[…]

### 2024-01-30 R/3_supplementary.R

@@ -1,26 +1,0 @@
-####################################
-# 3_Supplementary material
-####################################
-
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom)
-source(here("R", "func.R"))
-
-## Histogram ages by treatment
-hist<-ggplot(data, aes(x = age.start, y = after_stat(density))) +  
-  geom_density(alpha = 0.7,
-  aes(fill = interaction(cort, temp))) +
-  scale_fill_manual(values = c("CORT.Cold"="darkblue", "Control.Cold"="cyan", "CORT.Hot"="black", "Control.Hot"="grey"),
-    labels=c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
-  ) +
-  facet_wrap(~species, scales = "free_y", ncol = 2) +  
-  theme(strip.background = element_blank()) +
-  labs(y="Density", x = "Age", fill="Treatments") +
-  theme_classic() +
-  theme(
-    axis.title = element_text(size = 18, family = "sans"),  
-    axis.text = element_text(size = 10, family = "sans"),  
-    legend.title = element_text(size = 14, family = "sans"), 
-    legend.text = element_text(size = 12, family = "sans")  
-  )
-print(hist)
-ggsave("./output/figures/hist.png", plot=hist, width = 30, height = 12, units = "cm", dpi = 1000) 

### 2024-01-30 R/func.r

@@ -146,20 +146,71 @@ format_dec <- function(x, n) {
 ####################
 # Function to create each df for the figure
 #' @title df_fig
-#' @param df
+#' @param df to select the df
+#' @param specie to add data of the specie
+#' @param group to add data of group
+df_fig <- function(data_fig, specie, group){
   # Select the original df
-  data_fig <- df
-  # Create new matrix
-  fig_matrix <- matrix(NA, nrow = 8000, ncol = 35)
-  # Loop
-  for(x in 0:34){
-    for(j in 1:8000){
-      value <- exp(u[j] + m[j] * x) / (1 + exp(u[j] + m[j] * x))
-      fig_matrix[j, x] <- value
+  df <- data_fig
+  # Create a vector with treatments
+  treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
+  # Create new matrix and new dfs
+  treat_matrix <- matrix(NA, nrow = 8000, ncol = 35)
+  fig_df <- data.frame()
+  # Loop through treatments
+  for(t in treatments){
+    if(t == "CORT-Cold"){
+      m <- df$b_Trial
+      u <- df$b_Intercept
+    } else if(t == "Control-Cold"){
+        m <- (df$'b_Trial:cortControl' + df$b_Trial)
+        u <- (df$b_cortControl + df$b_Intercept)
+    } else if(t == "CORT-Hot"){
+        m <- (df$'b_Trial:tempHot' + df$b_Trial)
+        u <- (df$b_tempHot + df$b_Intercept)
+    } else if(t == "Control-Hot"){
+        m <- (df$'b_Trial:cortControl:tempHot' + df$b_Trial+ df$'b_Trial:cortControl' + df$'b_Trial:tempHot')
+        u <- (df$'b_cortControl:tempHot' + df$b_cortControl + df$b_tempHot + df$b_Intercept)
+    } else {
+    stop("loop wrong")
     }
-  fig_df <- as.data.frame(fig_matrix)
+    # Loop per treatment
+    for(x in 0:35){
+      for(j in 1:8000){
+        value <- exp(u[j] + m[j] * x) / (1 + exp(u[j] + m[j] * x))
+        treat_matrix[j, x] <- value
+      }
+    }
+    treat_df <- as.data.frame(treat_matrix)
+    colnames(treat_df) <- paste0("X", 1:35)  # Adjust column names
+    treat_df <- gather(treat_df, key = "Trial", value = "Value")  # Reshape data frame
[…]

### 2024-01-30 ms.qmd
Updates

@@
 #| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
 ```
@@
 
-Results of the are summarized in @tbl-data and figures @Figdeli, @Figguich.
+Results of the are summarized in @tbl-data and @fig-results.
 On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red' for _L.
@@
 guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`).
-However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and Figs.
-@Figdeli, @Figguich) that could be affecting the estimated slopes.
+However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and @fig-results) that could be affecting the estimated slopes.
 As such, we analysed the between treatments differences for each group separately.
 For those individuals assigned to group 'Red', we did not find any significant differences between treatments neither for _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figguich).
+delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @fig-results), or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @fig-results).
 However, in both species the slope in the 'CORTCold' treatments seems bigger than the rest for group 'Red'.
@@
 ```{r, fig-results}
-#| label: figdeli
-#| fig.cap: "Deli"
+#| label: fig-results
+#| fig.cap: "Predicted probability of choosing the correct feeder first over trials.
+The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean both obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours represent the different treatments.
+The different panels represent the different species and groups."
 source(here("R", "func.R"))
@@
   mutate(Trial = as.numeric(Trial)) %>%
-  rename("Predicted_prob" = "Value") %>%
+  group_by(Trial, Treatment, Group, Species) %>%
+  summarize(
+    Mean_Predicted_prob = mean(Value),
+    SE_Predicted_prob = sd(Value)
+    ) %>%
+  ungroup() %>%
+  mutate(
+    Treatment = factor(Treatment,
+                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
+    Group = factor(Group,
+                        levels = c("Red", "Blue")),
+    ) %>%
 data.frame()
@@
 ggsave("./output/figures/figure_results.png", plot=figure_results, width = 18, height = 20, units = "cm", dpi = 3000)
-print(figure_results)
+knitr::include_graphics("./output/figures/figure_results.png")
 ```
@@
 The results for 'Blue' individuals were similar.
-We did not find significant differences between treatments in _L.delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dab_ControlCold - dab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dab_ControlCold - dab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dab_ControlHot- dab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dab_ControlHot - dab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dab_ControlHot - dab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dab_ControlHot - dab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dab_CORTHot - dab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dab_CORTHot - dab_CORTCold), 3)`) (see @Figdeli), or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gab_ControlCold - gab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gab_ControlCold - gab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gab_ControlHot- gab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gab_ControlHot - gab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gab_ControlHot - gab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gab_ControlHot - gab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gab_CORTHot - gab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gab_CORTHot - gab_CORTCold), 3)`) (see @Figguich).
+We did not find significant differences between treatments in _L.delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dab_ControlCold - dab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dab_ControlCold - dab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dab_ControlHot- dab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dab_ControlHot - dab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dab_ControlHot - dab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dab_ControlHot - dab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dab_CORTHot - dab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dab_CORTHot - dab_CORTCold), 3)`) (see @fig-results), or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gab_ControlCold - gab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gab_ControlCold - gab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gab_ControlHot- gab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gab_ControlHot - gab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gab_ControlHot - gab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gab_ControlHot - gab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gab_CORTHot - gab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gab_CORTHot - gab_CORTCold), 3)`) (see @fig-results).
 However, here the estimated slopes from those incubated at higher temperatures seem to be bigger on average, although the difference was not significant (_L.

### 2024-01-30 .vdoc.r

@@ -20,7 +20,7 @@
 #
 #
 #| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
 #
 #
 #
@@ -229,8 +229,8 @@ real_table
 #
 #
 #
-#| label: figdeli
-#| fig.cap: "Deli"
+#| label: fig-results
+#| fig.cap: "Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. The different panels represent the different species and groups."
 source(here("R", "func.R"))
 # First step, create the dfs for all models
 ## 1) L. delicata
@@ -248,13 +248,24 @@ df_gui_blue <- df_fig(as.data.frame(guich_blue), "L. guichenoti", "Blue")
 Fig_df <- rbind(df_del_red, df_del_blue, df_gui_red, df_gui_blue) %>%
   mutate(Trial = gsub("X", "", Trial)) %>%
   mutate(Trial = as.numeric(Trial)) %>%
-  rename("Predicted_prob" = "Value") %>%
+  group_by(Trial, Treatment, Group, Species) %>%
+  summarize(
+    Mean_Predicted_prob = mean(Value),
+    SE_Predicted_prob = sd(Value)
+    ) %>%
+  ungroup() %>%
+  mutate(
+    Treatment = factor(Treatment,
+                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
+    Group = factor(Group,
+                        levels = c("Red", "Blue")),
+    ) %>%
 data.frame()
 write.csv(Fig_df, file= "./output/Checking/Fig_df.csv")
 # Make the plot
 figure_results <- plotting(Fig_df)
 ggsave("./output/figures/figure_results.png", plot=figure_results, width = 18, height = 20, units = "cm", dpi = 3000)
-print(figure_results)
+knitr::include_graphics("./output/figures/figure_results.png")
 #
 #
 #

### 2024-01-30 R/func.r

@@ -1,6 +1,6 @@
 #################### 
 ####################
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
 #
 ####################
 ####################
@@ -198,19 +198,23 @@ df_fig <- function(data_fig, specie, group){
 #' @title plotting
 #' @param df to select the df
 plotting <- function(df){
-  a <- ggplot(df, aes(x = Trial, y = Predicted_prob, color = Treatment)) +
-  stat_smooth(method = "loess", span=3, formula = y ~ x, se = TRUE, linewidth=1, alpha = 0.1) +
-  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="grey")) +
-  facet_grid(Species ~ Group, scales = "free_y") +
+  plot <- ggplot(df, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +
+  geom_line(linewidth = 1.75) +
+  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#616161")) +
+  geom_ribbon(aes(ymin = Mean_Predicted_prob - SE_Predicted_prob, ymax = Mean_Predicted_prob + SE_Predicted_prob, fill = Treatment), color = NA, alpha = 0.075) + 
+  scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#616161")) +
+  theme_classic() +
+  facet_grid2(Species ~ Group, scale = "free_x", space = "free_x", axes = "all") +
   theme(strip.placement = "outside") +  
   theme(strip.background = element_blank()) +
-  labs(y = "Probability of correct choice", x = "Trial") +
-  theme_classic() +
+  labs(y = "Predicted probability of correct choice", x = "Trial") +
+  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) + 
   theme(
-    axis.title = element_text(size = 18, family = "sans"),
-    axis.text = element_text(size = 10, family = "sans"),
-    legend.title = element_text(size = 14, family = "sans"),
[…]

### 2024-01-31 R/func.r
Updates

@@ -199,7 +199,7 @@ df_fig <- function(data_fig, specie, group){
 #' @param df to select the df
 plotting <- function(df){
   plot <- ggplot(df, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +
-  geom_line(linewidth = 1.75) +
+  geom_line(linewidth = 1) +
   scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#616161")) +
   geom_ribbon(aes(ymin = Mean_Predicted_prob - SE_Predicted_prob, ymax = Mean_Predicted_prob + SE_Predicted_prob, fill = Treatment), color = NA, alpha = 0.075) + 
   scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#616161")) +

### 2024-01-31 .vdoc.r
Updates

@@ -1,469 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG_1.svg")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be the main data base used (data_clean).
-write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
-    for(k in 1:length(hormone)){
-      for(l in 1:length(temperature)){
-        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
-      }
-    }
-  }
-}
-#
-#
-#
-#
-#| label: models
[…]

### 2024-01-31 .vdoc.r
Updates

@@ -1,0 +1,469 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+      }
+    }
+  }
+}
+#
+#
+#
+#
+#| label: models
[…]

### 2024-02-06 ms.qmd
Updates

@@
 
+Our results suggest that the early environment manipulation did not affect learning in both skinks; we found that the estimated learning slopes were not different between treatments or species.
+However, learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red' for _L.
+delicata_, but not for _L.
+guichenoti_.
+This difference could be due to a potential bias towards blue in the initial choice, as we found that the estimated probability of choosing the correct feeder in the first trial was higher than expected by chance when the correct feeder was blue (see Supplementary Material).
+[**EXAMPLES WITH BIASES TOWARDS BLUE**]
+Nevertheless, when lizards assigned to blue or red were analysed separately, the between treatments comparissons remain the same in both species.
+Furthermore, the non-significant trends we observed were not consistent between species or colour assigned.
+As such, we conclude that, overall, lizards learned at the same rate regardless of the early environment manipulation.
+
+- Effect of CORT: what do others study say? Effect of sex, effect of task (brain region), effect of dose and time of exposure (discuss).
+- Effects of temperature: what do others study say? Effect of tasks and region
+
+Finally, we did not see any significant difference in learning rates when both species were compared.
+This result is in line with previous studies that found no differences in learning abilities between _L.
+delicata_ and _L.
+guichenoti_ [@bezzina2014does].
+However, in the experiment conducted by @bezzina2014does the authors did not find any evidence of learning in neither _L.
+delicata_ or _L.
+guichenoti_.
+In this regard, both learning tasks were conducted in a similar way and using the same cognitive domain, so the differences in the results could be due to the different experimental designs or the complexity of stimuli discrimination.
+Nevertheless, to test cognitive difference between these two species, further studies should be conducted using different cognitive domains.
+In conclusion,
+
 ## References

### 2024-02-07 ms.qmd
Updates

@@
 Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020].
-For example, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@abayarathna_effects_2020].
+For example, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@dayananda_incubation_2017; @abayarathna_effects_2020].
 In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021] that share some similarities with those resulting from prenatal increased stress or GC levels [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009].
@@
 
-Our results suggest that the early environment manipulation did not affect learning in both skinks; we found that the estimated learning slopes were not different between treatments or species.
-However, learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red' for _L.
+Our results suggest that the early environment manipulation did not affect learning; we found that the estimated learning slopes were not different between treatments or species.
+However, learning slopes were lower when the blue feeders were the correct choice compared to those lizards assigned to the group 'Red' for _L.
 delicata_, but not for _L.
@@
 This difference could be due to a potential bias towards blue in the initial choice, as we found that the estimated probability of choosing the correct feeder in the first trial was higher than expected by chance when the correct feeder was blue (see Supplementary Material).
-[**EXAMPLES WITH BIASES TOWARDS BLUE**]
+Moreover, those treatments and species whose learning slopes do not differ significantly from zero (see Table 1), are associated to highest bias (see Supplementary Material).
+Because there was a possibility that the bias towards the blue feeder was something acquired during training, we compared the light spectrum of the ramps used in the associative task and the white ones used during habituation, but we did no see any relevant similarity between the white and blue ramps (see Supplementary Material).
+As such, we consider this bias to not be a derivate from our experimental design.
+The species confidence hypothesis posits that animals should bias their attention toward colours they are familiar with, and empirical studies show that, for instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
+However, to the best of our knowledge, noone has reported a colour bias in _L.
+delicata_ or _L.
+guichenoti_ before; and it is not considered to be involved in intraspecific communication [@torr1996patterns, @chapple_biology_2014].
+Still, we recommend to select carefully the colours employed in associative tasks with these species, especially _L.
+delicata_, for future cognitive tasks employing visual stimuli.
 Nevertheless, when lizards assigned to blue or red were analysed separately, the between treatments comparissons remain the same in both species.
@@
 As such, we conclude that, overall, lizards learned at the same rate regardless of the early environment manipulation.
-
-- Effect of CORT: what do others study say? Effect of sex, effect of task (brain region), effect of dose and time of exposure (discuss).
-- Effects of temperature: what do others study say? Effect of tasks and region
-
+As part of our predictions, we expected prenatal CORT to impair learning, as other studies have shown [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn; @bebus_associative_2016].
+However, in other experiments early-life increases in GCs or induced stress did not affect learning abilities or even improve them [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
+In this veins, GCs are known to show an inverted 'U-shaped' relationship with performance on some learning task, with low levels of GCs being beneficial for learning and memory, and high levels being detrimental [@du_dynamic_2009; @mcewen_brain_2012].
+It can be arguable whether the absence of differences in learning slopes between treatments could be due to the fact that the levels of CORT we used were not high or sustained through time enough to impair learning, or that the dose did not reach the embryo.
+However, we believe this to be unlikely since we found that the levels of CORT we used affected other morphological and physiological traits (non-published data).
+In contrast, testing only one cognitive domain could have masked potential differences in learning abilities between treatments.
+For instance, European starlings males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn]; while Scrub-jays that had lower CORT levels as nestlings performed better on an associative learning test as adults, but not on a reversal learning task [@bebus_associative_2016].
+GCs action involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed unevenly in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
+As such, we consider that studying different cognitive domains could provide a more comprehensive understanding of the effects of early-life stress on learning abilities in these species.
+Regarding incubation temperature, we predicted hot-incubated lizards to perform better in our task then those incubated at 23ºC, since most of the studies show enhanced learning abilities with higher incubation temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Furthermore, those studies that found the opposite pattern, were only when the hot treatment was above the natural thermal range of the species [@dayananda_incubation_2017; @abayarathna_effects_2020].
+However, our results do not align with these previous experiments and our predictions.
+In contrast, we did not find any effect of temperature in _L.
+delicata_ or _L.
+guichenoti_.
+In general, the incubation temperature effects observed on learning performance are associated with higher neural density in certain areas [@amiel_effects_2017], but these effects can be region-dependent [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017].
+Hence, as ocurred with CORT, further studies using different cognitive domains should be used to understand the effects of incubation temperature on learning abilities in these species.
 Finally, we did not see any significant difference in learning rates when both species were compared.
@@
 Nevertheless, to test cognitive difference between these two species, further studies should be conducted using different cognitive domains.
-In conclusion,
+In conclusion, we found that neither prenatal CORT, temperature, or their interaction affected learning abilities when _L.
+delicata_ and _L.
+guichenoti_ were subjected to a colour-associative task.
+However, we believe studying different cognitive domains is necessary to understand the effects of early-life stress and incubation temperature on learning abilities in these species.
+In addition, we found a bias towards blue that could affect the results found in cognitive tests, and we therefore recommend to select carefully the colours employed when employing visual stimuli in these two species, particularly _L.
+delicata_.
 

### 2024-02-09 .vdoc.r
Updates

@@ -1,0 +1,566 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+      }
+    }
+  }
+}
+#
+#
+#
+#
+#| label: models
[…]

### 2024-02-09 ms.qmd
Updates

@@
 Moreover, those treatments and species whose learning slopes do not differ significantly from zero (see Table 1), are associated to highest bias (see Supplementary Material).
-Because there was a possibility that the bias towards the blue feeder was something acquired during training, we compared the light spectrum of the ramps used in the associative task and the white ones used during habituation, but we did no see any relevant similarity between the white and blue ramps (see Supplementary Material).
+Because there was a possibility that the bias towards the blue feeder was something acquired during training, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the white ones used during habituation, but we did no see any relevant similarity between the white and blue ramps (see Supplementary Material).
 As such, we consider this bias to not be a derivate from our experimental design.
@@
 
+#### Light spectrum
+To test if the bias towards blue was something acquired during training, we compared the light spectrum of the ramps used in the associative task and the white ones used during habituation.
+We took three measurements of ten feeders per colour with a spectophotometer, and then analysed the spectrum and the perceived differences in colour using the package pavo.
+The spetrum of each type of feeder are shown in @fig-spectrum; the perceived chromatic constrasts between feeders are shown in @fig-perceived1 and @fig-perceived2.
+```{r, fig-spectrum}
+#| label: fig-spectrum
+#| fig.cap: "Light spectrum of the ramps used in the associative task and the white ones used during habituation. The different colours represent the different ramps."
+#
+# Load required packages
+pacman::p_load(pavo,plotrix,plyr,MCMCglmm,Hmisc,DIZutils)
+#
+# For importing the files, change the extension of the .jaz files to .txt files!  
+# Import spec data for pablos feeders - CHNAGE TO WHERE YOUR FILES ARE LOCATED
+specs <- getspec("./Others/Feeders", lim = c(300,700), ext = 'txt') %>%
+  procspec(specs, opt = "smooth" , span = 0.2, fixneg = "addmin") 
+# Plot smoothed raw data as reflectance curve with approximate rgb colours
+plot(specs, type = "o", col = spec2rgb(specs))
+```
+
+```{r, fig-perceived1}
+#| label: fig-perceived1
+#| fig.cap: "Perceived chromatic contrasts between feeders."
+#
+## Processing the data with the lizard visual model 
+# Processing using lizard vision model provided for Dan and Martin's Phyrnocephalus mystaceus paper
+liz_vis <- sensmodel(c(360, 440, 493, 571)) 
+#
+# Apply this over the feeder data visual as the visual system, achromatic is the receptor sensitivity, illum is the illuminate (here using an ideal white illuminate preset), bkg is the background against which we are measuring (here using an ideal background with no influence).
+Other conditions are applied as used in the P mystaceus paper.
+# Does produce an error about luminance but this is noted on the original P mystaceus paper code and should be okay
+# summary(feeders_lizardview) can be used to check what conditions were applied in the visual model
+feeders_lizardview <- vismodel(specs, visual = liz_vis, achromatic = "l", illum = "ideal", bkg = "ideal", vonkries = TRUE,   relative = FALSE, qcatch = "fi")
+#                             
+# Calculate colour distances between all feeder measurements
+coldistance_feeders <- coldist(feeders_lizardview,achro = TRUE, noise = "neural", n = c(1, 1, 3.5, 6),  weber = 0.1)
+#
+# Name all contrasts e.g white/green to categorise them
+annotated_coldistance_feeders <- coldistance_feeders %>%
+  separate(patch1, into = c("color1", "number1"), sep = "_") %>%
+  separate(patch2, into = c("color2", "number2"), sep = "_") %>%
+  mutate(color_comparison = paste0(color1, "/", color2)) %>%
+  mutate(color_comparison = paste0(pmin(color1, color2), "/", pmax(color1, color2))) %>% # Remove duplicate categories(e.g white/green is the same as green/white and all are called green/white)
+  subset(!(color_comparison %in% c("B/B", "G/G", "R/R", "W/W")))
+#
+# Plot the colour differences between the feeders: 
+# Note - above 1 is expected to be visually different under the selected visual system (here, lizard view)
+# dS, or chromatic contrast
+dScomparisons <- ggplot(annotated_coldistance_feeders, aes(x = color_comparison, y = dS, fill = color_comparison)) + 
+  geom_boxplot() + 
+  theme_classic() +
+  ylab("Chromatic Contrast (dS)") +
+  xlab("Feeder Colours Comparison") +
+ scale_fill_manual(values =c("B/G" = 'steelblue',  "B/R" = 'purple', "B/W" = 'lightblue', "G/R" = 'brown', "G/W" = 'lightgreen', "R/W" = 'red')) +
+ theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) + 
+  theme(
+    axis.title = element_text(size = 15, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"),
+    legend.title = element_text(size = 12, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    strip.text = element_text(size = 13, family = "Times New Roman")
+  ) 
+print(dScomparisons)
+```
+
+```{r, fig-perceived2}
+#| label: fig-perceived2
+#| fig.cap: "Perceived achromatic contrasts between feeders."
+#dL, or achromatic contrast
+dLcomparisons <- ggplot(annotated_coldistance_feeders, aes(x = color_comparison, y = dL, fill = color_comparison)) + 
+  geom_boxplot() + 
+  theme_classic() +
+  ylab("Achromatic Contrast (dL") +
+  xlab("Feeder Colours Comparison") +
+ scale_fill_manual(values =c("B/G" = 'steelblue',  "B/R" = 'purple', "B/W" = 'lightblue', "G/R" = 'brown', "G/W" = 'lightgreen', "R/W" = 'red')) +
+ theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) + 
+  theme(
+    axis.title = element_text(size = 15, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"),
+    legend.title = element_text(size = 12, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    strip.text = element_text(size = 13, family = "Times New Roman")
+  )
+print(dLcomparisons)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
 #### Checking the models plots  

### 2024-02-09 .vdoc.r

@@ -1,566 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG_1.svg")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be the main data base used (data_clean).
-write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
-    for(k in 1:length(hormone)){
-      for(l in 1:length(temperature)){
-        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
-      }
-    }
-  }
-}
-#
-#
-#
-#
-#| label: models
[…]

### 2024-02-09 ms.qmd
Updates

@@
 ### Red
-mod_dar <- readRDS(here("output/models/deli_red.rds"))
+mod_dar <- readRDS("./output/models/deli_red.rds")
 resid_dar <- residuals(mod_dar)
 ### Blue
-mod_dab <- readRDS(here("output/models/deli_blue.rds"))
+mod_dab <- readRDS("./output/models/deli_blue.rds")
 resid_dab <- residuals(mod_dab)
@@
 ### Red
-mod_gar <- readRDS(here("output/models/guich_red.rds"))
+mod_gar <- readRDS("./output/models/guich_red.rds")
 resid_gar <- residuals(mod_gar)
 ### Blue
-mod_gab <- readRDS(here("output/models/guich_blue.rds"))
+mod_gab <- readRDS("./output/models/guich_blue.rds")
 resid_gab <- residuals(mod_gab)

### 2024-02-22 ms.qmd
Update ms.qmd

@@
 Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.
-In this sense, prenatal Glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
-For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like subjects' sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
+In this sense, prenatal glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
+For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
 Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020].
-For example, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@dayananda_incubation_2017; @abayarathna_effects_2020].
-In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021] that share some similarities with those resulting from prenatal increased stress or GC levels [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009].
-This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning abilities [@noble_developmental_2018].
+In fact, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@dayananda_incubation_2017; @abayarathna_effects_2020].
+In this vein, the effects of prenatal temperature and GCs are linked to similar alterations in neural structure and metabolic activity [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021], which suggests that bot factors may interact to shape learning [@noble_developmental_2018].
 Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
-However, despite the proximate similarities of prenatal GCs and temperature effects, and the potential role of GCs in vertebrates' response to temperature, our understanding of how these two factors interact remains incomplete.
-In this study, our objective is to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning.
+However, our understanding of how these two factors interact remains incomplete.
+In this study, we aim to explore the interactive effects between prenatal GCs and the prenatal thermal environment on learning.
 We utilized two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_), as model species.
-We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
+We experimentally increased corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
 Post-incubation, the juveniles were subjectd to a colour-associative task to assess their learning abilities.
@@
 Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
+This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time.
 Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].
@@
 
-Our results suggest that the early environment manipulation did not affect learning; we found that the estimated learning slopes were not different between treatments or species.
+Our results suggest that the early environment manipulation did not affect learning, as we found that the estimated learning slopes were not different between treatments.
 However, learning slopes were lower when the blue feeders were the correct choice compared to those lizards assigned to the group 'Red' for _L.
@@
 As such, we consider this bias to not be a derivate from our experimental design.
-The species confidence hypothesis posits that animals should bias their attention toward colours they are familiar with, and empirical studies show that, for instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
+In this regard, the species confidence hypothesis posits that animals should bias their attention towards colours they are familiar with, and empirical studies show that, for instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
 However, to the best of our knowledge, noone has reported a colour bias in _L.
@@
 However, in other experiments early-life increases in GCs or induced stress did not affect learning abilities or even improve them [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
-In this veins, GCs are known to show an inverted 'U-shaped' relationship with performance on some learning task, with low levels of GCs being beneficial for learning and memory, and high levels being detrimental [@du_dynamic_2009; @mcewen_brain_2012].
-It can be arguable whether the absence of differences in learning slopes between treatments could be due to the fact that the levels of CORT we used were not high or sustained through time enough to impair learning, or that the dose did not reach the embryo.
-However, we believe this to be unlikely since we found that the levels of CORT we used affected other morphological and physiological traits (non-published data).
-In contrast, testing only one cognitive domain could have masked potential differences in learning abilities between treatments.
+In this vein, GCs are known to have hermetic effects, with low levels of GCs being beneficial for learning and memory, and high levels being detrimental [@du_dynamic_2009; @mcewen_brain_2012].
+When we measured other traits of lizards coming from the same treatments, we found that the levels of CORT we used affected size and mitochondrial activity in other organs (non-published data), so the CORT dose was enough to affect some aspects of _L.
+delicata_ and _L.
+guichenoti_ biology.
+**However,**  In adition, testing only one cognitive domain could have masked potential differences in learning abilities between treatments.
 For instance, European starlings males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn]; while Scrub-jays that had lower CORT levels as nestlings performed better on an associative learning test as adults, but not on a reversal learning task [@bebus_associative_2016].

### 2024-02-28 ms.qmd
Updates

@@
 l_intervals <- paste(l_interval_025, l_interval_975, sep = " , ")
-l_pvalue <- format_dec(sapply(estimates, pmcmc), 3)
+l_pvalue <- format_p(sapply(estimates, pmcmc), 3)
 #
@@
 For those individuals assigned to group 'Red', we did not find any significant differences between treatments neither for _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @fig-results), or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @fig-results).
+delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_p(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_p(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_p(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_p(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @fig-results), or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_p(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_p(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_p(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_p(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @fig-results).
 However, in both species the slope in the 'CORTCold' treatments seems bigger than the rest for group 'Red'.
 When groups were pooled by incubation temperature, slopes from individuals incubated at 23ºC were on average bigger in both species, but the difference was not significant (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`).
+delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_p(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_p(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`).
 CORT also lead to higher slopes in both species, but the differences were not significant (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`).
+delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_p(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L.
+guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_p(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`).
 We also did not find any significant differences when we compared the estimated slopes between species (_L.
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_p(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
 
@@
 The results for 'Blue' individuals were similar.
-We did not find significant differences between treatments in _L.delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dab_ControlCold - dab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dab_ControlCold - dab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dab_ControlHot- dab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dab_ControlHot - dab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dab_ControlHot - dab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dab_ControlHot - dab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dab_CORTHot - dab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dab_CORTHot - dab_CORTCold), 3)`) (see @fig-results), or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gab_ControlCold - gab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gab_ControlCold - gab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gab_ControlHot- gab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gab_ControlHot - gab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gab_ControlHot - gab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gab_ControlHot - gab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gab_CORTHot - gab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gab_CORTHot - gab_CORTCold), 3)`) (see @fig-results).
+We did not find significant differences between treatments in _L.delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dab_ControlCold - dab_CORTCold), 3)`, p- value = `r format_p(pmcmc(dab_ControlCold - dab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dab_ControlHot- dab_CORTHot), 3)`, p- value = `r format_p(pmcmc(dab_ControlHot - dab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dab_ControlHot - dab_ControlCold), 3)`, p-value = `r format_p(pmcmc(dab_ControlHot - dab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dab_CORTHot - dab_CORTCold), 3)`, p-value = `r format_p(pmcmc(dab_CORTHot - dab_CORTCold), 3)`) (see @fig-results), or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gab_ControlCold - gab_CORTCold), 3)`, p- value = `r format_p(pmcmc(gab_ControlCold - gab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gab_ControlHot- gab_CORTHot), 3)`, p- value = `r format_p(pmcmc(gab_ControlHot - gab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gab_ControlHot - gab_ControlCold), 3)`, p-value = `r format_p(pmcmc(gab_ControlHot - gab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gab_CORTHot - gab_CORTCold), 3)`, p-value = `r format_p(pmcmc(gab_CORTHot - gab_CORTCold), 3)`) (see @fig-results).
 However, here the estimated slopes from those incubated at higher temperatures seem to be bigger on average, although the difference was not significant (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`).
+delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`, p-value = `r format_p(pmcmc((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`; _L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`, p-value = `r format_p(pmcmc((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`).
 Also, 'Control' _L.
-delicata_ seem to have slightly higher estimated slopes than on average ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)` ) while in _L.
-guichenoti_ is the opposite ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`); nevertheless, the differences found were not significant in any case.
+delicata_ seem to have slightly higher estimated slopes than on average ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)`, p-value = `r format_p(pmcmc((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)` ) while in _L.
+guichenoti_ is the opposite ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`, p-value = `r format_p(pmcmc((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`); nevertheless, the differences found were not significant in any case.
 Finally, we found that learning slopes estimated for _L.
@@
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`, p-value = `r format_p(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`).
 
@@
 comp_pval <- data.frame(
-  probright_drCORTCold_t = format_dec(pmcmc(probright_drCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_drControlCold_t = format_dec(pmcmc(probright_drControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_drCORTHot_t = format_dec(pmcmc(probright_drCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_drControlHot_t = format_dec(pmcmc(probright_drControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_dbCORTCold_t = format_dec(pmcmc(probright_dbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_dbControlCold_t = format_dec(pmcmc(probright_dbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_dbCORTHot_t = format_dec(pmcmc(probright_dbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_dbControlHot_t = format_dec(pmcmc(probright_dbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_grCORTCold_t = format_dec(pmcmc(probright_grCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_grControlCold_t = format_dec(pmcmc(probright_grControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_grCORTHot_t = format_dec(pmcmc(probright_grCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_grControlHot_t = format_dec(pmcmc(probright_grControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_gbCORTCold_t = format_dec(pmcmc(probright_gbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_gbControlCold_t = format_dec(pmcmc(probright_gbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_gbCORTHot_t = format_dec(pmcmc(probright_gbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_gbControlHot_t = format_dec(pmcmc(probright_gbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3)) %>%
+  probright_drCORTCold_t = format_p(pmcmc(probright_drCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_drControlCold_t = format_p(pmcmc(probright_drControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_drCORTHot_t = format_p(pmcmc(probright_drCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_drControlHot_t = format_p(pmcmc(probright_drControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_dbCORTCold_t = format_p(pmcmc(probright_dbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_dbControlCold_t = format_p(pmcmc(probright_dbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_dbCORTHot_t = format_p(pmcmc(probright_dbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_dbControlHot_t = format_p(pmcmc(probright_dbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_grCORTCold_t = format_p(pmcmc(probright_grCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_grControlCold_t = format_p(pmcmc(probright_grControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_grCORTHot_t = format_p(pmcmc(probright_grCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_grControlHot_t = format_p(pmcmc(probright_grControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_gbCORTCold_t = format_p(pmcmc(probright_gbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_gbControlCold_t = format_p(pmcmc(probright_gbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_gbCORTHot_t = format_p(pmcmc(probright_gbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
+  probright_gbControlHot_t = format_p(pmcmc(probright_gbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3)) %>%
 gather(key = "column", value = "value", .) %>%
@@
 On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue (_L.
-delicata_: mean Prob choice = `r format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
-guichenoti_: mean Prob choice = `r format_dec(mean((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L.
-delicata_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
-guichenoti_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`).
+delicata_: mean Prob choice = `r format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
+guichenoti_: mean Prob choice = `r format_dec(mean((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L.
+delicata_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
+guichenoti_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`).
 

### 2024-02-28 R/func.r

@@ -140,7 +140,20 @@ pmcmc <- function(x, null = 0, twotail = TRUE, dir){
 #' @param n The number of decimals
 format_dec <- function(x, n) {
   z <- sprintf(paste0("%.",n,"f"), x)
-  return(as.numeric(z))
+  return(z)
+}
+####################
+####################
+# Function to format p_values
+#' @title format_dec
+#' @param x The object
+#' @param n The number of decimals
+format_p <- function(x, n) {
+  z <- sprintf(paste0("%.",n,"f"), x)
+  tmp <- ifelse(as.numeric(z) <= 0.001, "< 0.001",
+         ifelse(as.numeric(z) <= 0.05 & as.numeric(z) > 0.001, "< 0.05",
+                as.character(z)))
+  return(tmp)
 }
 ####################
 ####################

### 2024-03-15 .vdoc.r
Create .vdoc.r

@@ -1,0 +1,562 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+      }
+    }
+  }
+}
+#
+#
+#
+#
+#| label: models
[…]

### 2024-03-15 ms.qmd
Seems like wrong MS, but did some editing

@@
 Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
-These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, that are crucial for the survival and reproduction of animals [@dukas_evolutionary_2004].
-Particularly, learning - the acquisition of neuronal representations of new information [@dukas_evolutionary_2004] - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
+These cognitive processes underpin animal foraging, mate choice, antipredatory strategies and social behaviours that are crucial for the survival and reproduction [@dukas_evolutionary_2004].
+Learning - the acquisition of new information [@dukas_evolutionary_2004] - is fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
 However, in nature, there is individual variation in the capacity to acquire new information, depending on factors like age, sex, gut microbiota, or the environment where organisms develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
@@
 Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.
+
 In this sense, prenatal glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
@@
 However, our understanding of how these two factors interact remains incomplete.
+
 In this study, we aim to explore the interactive effects between prenatal GCs and the prenatal thermal environment on learning.
@@
 As such, we conclude that, overall, lizards learned at the same rate regardless of the early environment manipulation.
+
 As part of our predictions, we expected prenatal CORT to impair learning, as other studies have shown [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn; @bebus_associative_2016].
@@
 As such, we consider that studying different cognitive domains could provide a more comprehensive understanding of the effects of early-life stress on learning abilities in these species.
+
 Regarding incubation temperature, we predicted hot-incubated lizards to perform better in our task then those incubated at 23ºC, since most of the studies show enhanced learning abilities with higher incubation temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].

### 2024-03-18 ms.qmd
Updates

@@
 However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards.
-Final sample sizes per treatment and species are disclosed on @tbl-data.
+Final sample sizes per treatment and species are disclosed on @fig_deli and @fig-guich.
 ```{r, models}
@@
 
-```{r, tbl-data}
-#| label: tbl-data
-#| tbl-cap: "Estimates of learning slope for all the different treatments per each task, species and group.
-Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
-All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero.
-In bold, those values that are significant (p-value <0.05)"
-source(here("R", "func.R"))
-#
-############################## CREATING BIG DF FOR TABLE ##############################
-# Building the vectors for titles of rows and columns
-specie <- c("L. delicata", "L. guichenoti")
-groups <- c("Red", "Blue")
-treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
-values <- c("Mean", "95% CI", "p-value")
-# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors.
-p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
-# First call the estimates
-estimates <- list(
-  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
-  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot, 
-  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot, 
-  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot
-)
-#
-# Then get the mean, co.intervals(95%), and p-values
-l_mean <- format_dec(sapply(estimates, mean), 3)
-l_interval_025 <- format_dec(sapply(estimates, function(x) quantile(x,0.025)), 3)
-l_interval_975 <- format_dec(sapply(estimates, function(x) quantile(x,0.975)), 3)
-l_intervals <- paste(l_interval_025, l_interval_975, sep = " , ")
-l_pvalue <- format_p(sapply(estimates, pmcmc), 3)
-#
-# Building the df
-df <- data.frame(
-  Specie = rep(specie, each = length(groups) * length(treatments)),
-  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
-  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
-  Mean = rep(l_mean, each = 1),
-  CI = rep(l_intervals, each = 1),
-  PValue = rep(l_pvalue, each = 1)
-)
-write.csv(df, file= "./output/Checking/df.csv")
-#
-############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
-# Make n_list into a df
-n_df <- as.data.frame(do.call(rbind, n_list)) %>%
-  rename("n" = V1) %>%
-  rownames_to_column("model") %>%
-  separate(model, into = c("Specie", "Group", "cort", "temp"), sep = "_") %>%
-  unite("Treatment", c("cort", "temp"), sep = "-") %>%
-  mutate(Specie = factor(Specie,
-                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
-        Treatment = factor(Treatment,
-                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
-# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
-table_data <- merge(df, n_df) %>%
-  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
-  select(Specie, Group, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table
-  mutate(Specie = factor(Specie,
-                  levels = c("L. delicata", "L. guichenoti")),
-        Group = factor(Group,
-                  levels = c("Red", "Blue")),
-        Treatment = factor(Treatment, 
-                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
-  arrange(Specie, Group, Treatment) %>% # To arrange the rows the way I want
-  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
-  mutate(Treatment = paste0(Treatment, ")"))
-write.csv(table_data, file= "./output/Checking/table_data.csv")
-#
-############################## MAKING THE TABLE ##############################
-## Table format
-set_flextable_defaults(
- font.family = "Times New Roman",
- fint.size = 10)
-# Split the table_data df by task
-real_table <- flextable(table_data) %>%
-    bold(~ `p-value` < 0.05, ~ `p-value` + Mean + `95% CI`) %>%
-    set_table_properties(width = 1) %>%
-    align(align="center", part="all") %>% 
-    set_header_labels(Mean = "Mean",
-                      `95% CI` = "95% CI",
-                      `p-value` = "p-value",
-                      Mean_Reversal = "Mean",
-                      `95% CI_Reversal` = "95% CI",
-                      `p-value_Reversal` = "p-value") %>%
-    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
-    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
-    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
-    hline(i = c(4,12), j = c(2:6), part = "body") %>% # To make some horizontal lines
-    hline(i = c(8), j = c(1:6), part = "body") %>% # To make some horizontal lines
-    autofit() 
-real_table
+We found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to slopes of individuals assigned to the group 'Red' for _L.
+delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`), but not for _L.
+guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`).
+However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and @fig-results) that could be affecting the estimated slopes.
+As such, we analysed the between treatments differences for each group separately.
+
+For those _L.
+delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (**FIG**).
+Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (**FIG**).
+
+```{r, fig-deli}
 ```
 
-Results of the are summarized in @tbl-data and @fig-results.
-On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red' for _L.
-delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`), but not for _L.
-guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`).
-However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and @fig-results) that could be affecting the estimated slopes.
-As such, we analysed the between treatments differences for each group separately.
-For those individuals assigned to group 'Red', we did not find any significant differences between treatments neither for _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_p(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_p(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_p(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_p(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @fig-results), or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_p(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_p(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_p(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_p(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @fig-results).
-However, in both species the slope in the 'CORTCold' treatments seems bigger than the rest for group 'Red'.
-When groups were pooled by incubation temperature, slopes from individuals incubated at 23ºC were on average bigger in both species, but the difference was not significant (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_p(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_p(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`).
-CORT also lead to higher slopes in both species, but the differences were not significant (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_p(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_p(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`).
-We also did not find any significant differences when we compared the estimated slopes between species (_L.
+In _L.
+guichenoti_, we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the 'Red' group (**FIG**); and we did not find any significant effect of hormone (Control - CORT = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to 'Blue' (**FIG**).
+
+```{r, fig-guich}
+```
+
+Finally, we also did not find any significant differences when we compared the estimated slopes between species for 'Red' group(_L.
+delicata_ mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot), 0.975), 3)`]; _L.
+guichenoti_ mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.975), 3)`]; _L.
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_p(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot))), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the 'Blue' one (_L.
+delicata_ mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; _L.
+guichenoti_ mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; _L.
+delicata_ - _L.
+guichenoti_ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot))), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`).
 
@@
 ```
-
-The results for 'Blue' individuals were similar.
-We did not find significant differences between treatments in _L.delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dab_ControlCold - dab_CORTCold), 3)`, p- value = `r format_p(pmcmc(dab_ControlCold - dab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dab_ControlHot- dab_CORTHot), 3)`, p- value = `r format_p(pmcmc(dab_ControlHot - dab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dab_ControlHot - dab_ControlCold), 3)`, p-value = `r format_p(pmcmc(dab_ControlHot - dab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dab_CORTHot - dab_CORTCold), 3)`, p-value = `r format_p(pmcmc(dab_CORTHot - dab_CORTCold), 3)`) (see @fig-results), or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gab_ControlCold - gab_CORTCold), 3)`, p- value = `r format_p(pmcmc(gab_ControlCold - gab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gab_ControlHot- gab_CORTHot), 3)`, p- value = `r format_p(pmcmc(gab_ControlHot - gab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gab_ControlHot - gab_ControlCold), 3)`, p-value = `r format_p(pmcmc(gab_ControlHot - gab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gab_CORTHot - gab_CORTCold), 3)`, p-value = `r format_p(pmcmc(gab_CORTHot - gab_CORTCold), 3)`) (see @fig-results).
-However, here the estimated slopes from those incubated at higher temperatures seem to be bigger on average, although the difference was not significant (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`, p-value = `r format_p(pmcmc((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`, p-value = `r format_p(pmcmc((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`).
-Also, 'Control' _L.
-delicata_ seem to have slightly higher estimated slopes than on average ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)`, p-value = `r format_p(pmcmc((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)` ) while in _L.
-guichenoti_ is the opposite ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`, p-value = `r format_p(pmcmc((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`); nevertheless, the differences found were not significant in any case.
-Finally, we found that learning slopes estimated for _L.
-guichenoti_ assigned to group 'Blue' were marginally higher than those from _L.
-delicata_ (_L.
-delicata_ - _L.
-guichenoti_ = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`, p-value = `r format_p(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`).
 
@@
 On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue (_L.
-delicata_: mean Prob choice = `r format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
-guichenoti_: mean Prob choice = `r format_dec(mean((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L.
-delicata_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
-guichenoti_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`).
+delicata_: mean Prob choice = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
+guichenoti_: mean Prob choice = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L.
+delicata_: mean Prob choice = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
+guichenoti_: mean Prob choice = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`).
 

### 2024-03-18 R/func.r

@@ -145,14 +145,14 @@ format_dec <- function(x, n) {
 ####################
 ####################
 # Function to format p_values
-#' @title format_dec
+#' @title format_p
 #' @param x The object
 #' @param n The number of decimals
 format_p <- function(x, n) {
   z <- sprintf(paste0("%.",n,"f"), x)
   tmp <- ifelse(as.numeric(z) <= 0.001, "< 0.001",
          ifelse(as.numeric(z) <= 0.05 & as.numeric(z) > 0.001, "< 0.05",
-                as.character(z)))
+                paste0("= ", as.character(z))))
   return(tmp)
 }
 ####################
@@ -229,5 +229,209 @@ plotting <- function(df){
     legend.text = element_text(size = 10, family = "Times New Roman"),
     strip.text = element_text(size = 13, family = "Times New Roman")
   )  
+  return(plot)
+}
+####################
+####################
+# Function to create each df for the probability figure (plots A, C Fig-results)
+#' @title df_plotAC
+#' @param sp to select the df, levels are deli or guich
+df_plotAC <- function(sp){
+  if (sp == "deli"){
+      df <- as.data.frame(deli)
+    } else {
+      if(sp == "guich"){
+        df <- as.data.frame(guich)
+      } else {
+        stop("Species not valid")
+      }
+    }
+  # Create a vector with treatments
+  treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
+  # Create new matrix and new dfs
+  treat_matrix <- matrix(NA, nrow = 8000, ncol = 40)
+  fig_df <- data.frame()
+  # Loop through treatments
+  for(t in treatments){
+    if(t == "CORT-Cold"){
+      m <- df$b_trial_reversal
+      u <- df$b_Intercept
+    } else if(t == "Control-Cold"){
+        m <- (df$'b_trial_reversal:cortControl' + df$b_trial_reversal)
+        u <- (df$b_cortControl + df$b_Intercept)
+    } else if(t == "CORT-Hot"){
+        m <- (df$'b_trial_reversal:tempHot' + df$b_trial_reversal)
+        u <- (df$b_tempHot + df$b_Intercept)
+    } else if(t == "Control-Hot"){
[…]

### 2024-04-12 R/func.r
Update functions

@@ -7,16 +7,13 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 # Extract sample size per group
 #' @title sample
 #' @description Estract sample size per group
+#' @param df To select the df
 #' @param sp To select the species of interest ("deli"/"guich")
-#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
 #' @param corti To select cort treatment ("CORT"/"Control")
 #' @param therm To select temp treatment ("Cold"/"Hot")
-sample <- function(sp, bias, corti, therm){
-  #Specify database
-  data <- data_clean
-  # Count sample
-  sample_size <- data %>%
-                filter(species == sp, group == bias, cort == corti, temp == therm, Trial == 1) %>%
+sample <- function(df, sp, corti, therm){
+  sample_size <- df %>%
+                filter(species == sp, cort == corti, temp == therm, trial_reversal == 1) %>%
                 group_by(lizard_id) %>%
                 summarise(n = n()) %>%
                 summarise(total_count = sum(n)) %>%
@@ -27,24 +24,25 @@ sample <- function(sp, bias, corti, therm){
 ####################
 # Fit models and extract posteriors both per each treatment:
 #' @title fit_m Function
-#' @description Fit brm models for the associative task
+#' @description Fit brm models for different the associative task
+#' @param df To select the df
 #' @param sp To select the species of interest ("deli"/"guich")
-#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
-#' @param refir To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
+#' @param com To select whether the analyses are done for the full dataset ("complete") or for only those lizards 
+# that met the learning criterion ("suppl")
+#' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(sp, bias, refit = TRUE) {
-  data <- data_clean
-  formula <- FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
+fit_m <- function(df, sp, com, refit = TRUE) {
[…]

### 2024-04-12 R/func.r
Revert "Update functions"
This reverts commit 183d613dc6dac8b1113663f2594b08a318f0dbe4.

@@ -7,13 +7,16 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 # Extract sample size per group
 #' @title sample
 #' @description Estract sample size per group
-#' @param df To select the df
 #' @param sp To select the species of interest ("deli"/"guich")
+#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
 #' @param corti To select cort treatment ("CORT"/"Control")
 #' @param therm To select temp treatment ("Cold"/"Hot")
-sample <- function(df, sp, corti, therm){
-  sample_size <- df %>%
-                filter(species == sp, cort == corti, temp == therm, trial_reversal == 1) %>%
+sample <- function(sp, bias, corti, therm){
+  #Specify database
+  data <- data_clean
+  # Count sample
+  sample_size <- data %>%
+                filter(species == sp, group == bias, cort == corti, temp == therm, Trial == 1) %>%
                 group_by(lizard_id) %>%
                 summarise(n = n()) %>%
                 summarise(total_count = sum(n)) %>%
@@ -24,25 +27,24 @@ sample <- function(df, sp, corti, therm){
 ####################
 # Fit models and extract posteriors both per each treatment:
 #' @title fit_m Function
-#' @description Fit brm models for different the associative task
-#' @param df To select the df
+#' @description Fit brm models for the associative task
 #' @param sp To select the species of interest ("deli"/"guich")
-#' @param com To select whether the analyses are done for the full dataset ("complete") or for only those lizards 
-# that met the learning criterion ("suppl")
-#' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
+#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
+#' @param refir To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(df, sp, com, refit = TRUE) {
-  formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)) 
+fit_m <- function(sp, bias, refit = TRUE) {
+  data <- data_clean
[…]

### 2024-04-12 func2.r
Create func2.r

@@ -1,0 +1,341 @@
+#################### 
+####################
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+#
+####################
+####################
+# Extract sample size per group
+#' @title sample
+#' @description Estract sample size per group
+#' @param df To select the df
+#' @param sp To select the species of interest ("deli"/"guich")
+#' @param corti To select cort treatment ("CORT"/"Control")
+#' @param therm To select temp treatment ("Cold"/"Hot")
+sample <- function(df, sp, corti, therm){
+  sample_size <- df %>%
+                filter(species == sp, cort == corti, temp == therm, trial_reversal == 1) %>%
+                group_by(lizard_id) %>%
+                summarise(n = n()) %>%
+                summarise(total_count = sum(n)) %>%
+                pull(total_count)
+  return(sample_size)
+}
+####################
+####################
+# Fit models and extract posteriors both per each treatment:
+#' @title fit_m Function
+#' @description Fit brm models for different the associative task
+#' @param df To select the df
+#' @param sp To select the species of interest ("deli"/"guich")
+#' @param com To select whether the analyses are done for the full dataset ("complete") or for only those lizards 
+# that met the learning criterion ("suppl")
+#' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
+#' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
+fit_m <- function(df, sp, com, refit = TRUE) {
+  formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)) 
+  #Specify species
+    if (sp == "deli"){
+      sp_data <- df %>%
+            group_by(lizard_id) %>%
+            filter(species == "delicata") %>%
+            ungroup() %>%
+      data.frame() 
+    } else {
+      if(sp == "guich"){
+        sp_data <- df %>%
+              group_by(lizard_id) %>%
+              filter(species == "guichenoti") %>%
+              ungroup() %>%
+        data.frame()
+      } else {
+        stop("Species not valid")
[…]

### 2024-04-12 func2.r
Delete func2.r

@@ -1,341 +1,0 @@
-#################### 
-####################
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
-#
-####################
-####################
-# Extract sample size per group
-#' @title sample
-#' @description Estract sample size per group
-#' @param df To select the df
-#' @param sp To select the species of interest ("deli"/"guich")
-#' @param corti To select cort treatment ("CORT"/"Control")
-#' @param therm To select temp treatment ("Cold"/"Hot")
-sample <- function(df, sp, corti, therm){
-  sample_size <- df %>%
-                filter(species == sp, cort == corti, temp == therm, trial_reversal == 1) %>%
-                group_by(lizard_id) %>%
-                summarise(n = n()) %>%
-                summarise(total_count = sum(n)) %>%
-                pull(total_count)
-  return(sample_size)
-}
-####################
-####################
-# Fit models and extract posteriors both per each treatment:
-#' @title fit_m Function
-#' @description Fit brm models for different the associative task
-#' @param df To select the df
-#' @param sp To select the species of interest ("deli"/"guich")
-#' @param com To select whether the analyses are done for the full dataset ("complete") or for only those lizards 
-# that met the learning criterion ("suppl")
-#' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
-#' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(df, sp, com, refit = TRUE) {
-  formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)) 
-  #Specify species
-    if (sp == "deli"){
-      sp_data <- df %>%
-            group_by(lizard_id) %>%
-            filter(species == "delicata") %>%
-            ungroup() %>%
-      data.frame() 
-    } else {
-      if(sp == "guich"){
-        sp_data <- df %>%
-              group_by(lizard_id) %>%
-              filter(species == "guichenoti") %>%
-              ungroup() %>%
-        data.frame()
-      } else {
-        stop("Species not valid")
[…]

### 2024-04-12 ms.qmd
Updates

@@
 #| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
 ```
@@
 
-knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+knitr::include_graphics("./Others/LEARN_FIG_1.png")
 
@@
 ```{r, fig-deli}
+#| label: fig-deli
+#| fig.cap: "Results for Lampropholis delicata for both colour groups "red" (A,B) and "blue" (C, D).
+Panels A and C show the predicted probability of choosing the correct feeder first over trials.
+The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours indicate the different treatments.
+Panels B and D show the distribution of the estimates of slopes per each treatment.
+The x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
+The different colours indicate the different treatments.
+Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
+source(here("R", "func.R"))
+# First step, create the dfs for all models
+## Red
+fig_dar_AC_df <- df_plotAC("deli_red")
+fig_dar_BD1_df <- df_plotBD1("deli_red")
+fig_dar_BD2_df <- df_plotBD2("deli_red")
+## Blue
+fig_dab_AC_df <- df_plotAC("deli_blue")
+fig_dab_BD1_df <- df_plotBD1("deli_blue")
+fig_dab_BD2_df <- df_plotBD2("deli_blue")
+#
+# Second step, create the plots
+fig_dar <- plotting(sp = "deli", col = "red", df_prob = fig_dar_AC_df, df_violin = fig_dar_BD1_df, df_points = fig_dar_BD2_df)
+fig_dab <- plotting(sp = "deli", col = "blue", df_prob = fig_dab_AC_df, df_violin = fig_dab_BD1_df, df_points = fig_dab_BD2_df)
+#
+# Third step, merge plots
+fig_deli <- plot_grid(fig_dar, fig_dab, ncol = 1) +
+  theme(plot.margin = margin(1, 1, 1.25, 1, "cm")) +
+  annotate("text", x = 0.5, y = 1.01, label = "Lampropholis delicata", size = 6, color = "black", fontface = "italic")
 ```
@@
 ```{r, fig-guich}
+#| label: fig-guich
+#| fig.cap: "Results for Lampropholis guichenoti for both colour groups "red" (A,B) and "blue" (C, D).
+Panels A and C show the predicted probability of choosing the correct feeder first over trials.
+The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours indicate the different treatments.
+Panels B and D show the distribution of the estimates of slopes per each treatment.
+The x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
+The different colours indicate the different treatments.
+Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
+source(here("R", "func.R"))
+# First step, create the dfs for all models
+## Red
+fig_gar_AC_df <- df_plotAC("guich_red")
+fig_gar_BD1_df <- df_plotBD1("guich_red")
+fig_gar_BD2_df <- df_plotBD2("guich_red")
+## Blue
+fig_gab_AC_df <- df_plotAC("guich_blue")
+fig_gab_BD1_df <- df_plotBD1("guich_blue")
+write.csv(fig_gab_BD1_df, file= "./output/Checking/fig_gab_BD1_df.csv")
+fig_gab_BD2_df <- df_plotBD2("guich_blue")
+#
+# Second step, create the plots
+fig_gar <- plotting(sp = "guich", col = "red", df_prob = fig_gar_AC_df, df_violin = fig_gar_BD1_df, df_points = fig_gar_BD2_df)
+fig_gab <- plotting(sp = "guich", col = "blue", df_prob = fig_gab_AC_df, df_violin = fig_gab_BD1_df, df_points = fig_gab_BD2_df)
+#
+# Third step, merge plots
+fig_guich <- plot_grid(fig_gar, fig_gab, ncol = 1) +
+  theme(plot.margin = margin(1, 1, 1.25, 1, "cm")) +
+  annotate("text", x = 0.5, y = 1.01, label = "Lampropholis guichenoti", size = 6, color = "black", fontface = "italic")
 ```
@@
 guichenoti_ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot))), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`).
-
-```{r, fig-results}
-#| label: fig-results
-#| fig.cap: "Predicted probability of choosing the correct feeder first over trials.
-The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean both obtained by using the slope and intercept estimates from the posterior distributions.
-The different colours represent the different treatments.
-The different panels represent the different species and groups."
-source(here("R", "func.R"))
-# First step, create the dfs for all models
-## 1) L. delicata
-### Red
-df_del_red <- df_fig(as.data.frame(deli_red), "L. delicata", "Red")
-### Blue
-df_del_blue <- df_fig(as.data.frame(deli_blue), "L. delicata", "Blue")
-## 2) L. guichenoti
-### Red
-df_gui_red <- df_fig(as.data.frame(guich_red), "L. guichenoti", "Red")
-### Blue
-df_gui_blue <- df_fig(as.data.frame(guich_blue), "L. guichenoti", "Blue")
-#
-# Second step, merge the df into a big Fig_df
-Fig_df <- rbind(df_del_red, df_del_blue, df_gui_red, df_gui_blue) %>%
-  mutate(Trial = gsub("X", "", Trial)) %>%
-  mutate(Trial = as.numeric(Trial)) %>%
-  group_by(Trial, Treatment, Group, Species) %>%
-  summarize(
-    Mean_Predicted_prob = mean(Value),
-    SE_Predicted_prob = sd(Value)
-    ) %>%
-  ungroup() %>%
-  mutate(
-    Treatment = factor(Treatment,
-                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
-    Group = factor(Group,
-                        levels = c("Red", "Blue")),
-    ) %>%
-data.frame()
-write.csv(Fig_df, file= "./output/Checking/Fig_df.csv")
-# Make the plot
-figure_results <- plotting(Fig_df)
-ggsave("./output/figures/figure_results.png", plot=figure_results, width = 18, height = 20, units = "cm", dpi = 3000)
-knitr::include_graphics("./output/figures/figure_results.png")
-```
 

### 2024-04-12 .vdoc.r

@@ -20,7 +20,9 @@
 #
 #
 #| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
 #
 #
 #
@@ -52,7 +54,7 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #| label: fig-Methods
 #| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
 
-knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+knitr::include_graphics("./Others/LEARN_FIG_1.png")
 
 #
 #
@@ -137,135 +139,60 @@ gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial
 #
 #
 #
-#| label: tbl-data
-#| tbl-cap: "Estimates of learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"
-source(here("R", "func.R"))
-#
-############################## CREATING BIG DF FOR TABLE ##############################
-# Building the vectors for titles of rows and columns
-specie <- c("L. delicata", "L. guichenoti")
-groups <- c("Red", "Blue")
-treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
-values <- c("Mean", "95% CI", "p-value")
-# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors. p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
-# First call the estimates
-estimates <- list(
[…]

### 2024-04-12 R/func.r

@@ -30,7 +30,7 @@ sample <- function(sp, bias, corti, therm){
 #' @description Fit brm models for the associative task
 #' @param sp To select the species of interest ("deli"/"guich")
 #' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
-#' @param refir To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
+#' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
 fit_m <- function(sp, bias, refit = TRUE) {
   data <- data_clean
@@ -157,14 +157,21 @@ format_p <- function(x, n) {
 }
 ####################
 ####################
-# Function to create each df for the figure
-#' @title df_fig
-#' @param df to select the df
-#' @param specie to add data of the specie
-#' @param group to add data of group
-df_fig <- function(data_fig, specie, group){
-  # Select the original df
-  df <- data_fig
+# Function to create each df for the probability figure (plots A, C fig-deli and fig-guich)
+#' @title df_plotAC
+#' @param data to select the df, levels are: "deli_red", "deli_blue", "guich_red", "guich_blue" 
+df_plotAC <- function(data){
+  if (data == "deli_red"){
+    df <- as.data.frame(deli_red)
+  } else if (data == "deli_blue"){
+    df <- as.data.frame(deli_blue)
+  } else if(data == "guich_red"){
+    df <- as.data.frame(guich_red)
+  } else if(data == "guich_blue"){
+    df <- as.data.frame(guich_blue)
+  } else {
+    stop("Data not valid")
+  }
   # Create a vector with treatments
   treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
   # Create new matrix and new dfs
@@ -200,87 +207,6 @@ df_fig <- function(data_fig, specie, group){
     treat_df$Treatment <- t
     fig_df <- rbind(fig_df, treat_df)
   }
-  # Add species and group information
-  fig_df$Species <- specie
-  fig_df$Group <- group
-  return(fig_df)
-}
-####################
-####################
-# Function to create the plot
[…]

### 2024-04-12 ms.qmd
Updates figures

@@
 fig_deli <- plot_grid(fig_dar, fig_dab, ncol = 1) +
-  theme(plot.margin = margin(1, 1, 1.25, 1, "cm")) +
-  annotate("text", x = 0.5, y = 1.01, label = "Lampropholis delicata", size = 6, color = "black", fontface = "italic")
+  theme(plot.margin = margin(1, 1, 1.5, 1, "cm")) +
+  annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 4.5, color = "black", fontface = "italic")
+ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/fig_deli.png")
 ```
@@
 fig_gab_BD1_df <- df_plotBD1("guich_blue")
-write.csv(fig_gab_BD1_df, file= "./output/Checking/fig_gab_BD1_df.csv")
 fig_gab_BD2_df <- df_plotBD2("guich_blue")
@@
 fig_guich <- plot_grid(fig_gar, fig_gab, ncol = 1) +
-  theme(plot.margin = margin(1, 1, 1.25, 1, "cm")) +
-  annotate("text", x = 0.5, y = 1.01, label = "Lampropholis guichenoti", size = 6, color = "black", fontface = "italic")
+  theme(plot.margin = margin(1, 1, 1.5, 1, "cm")) +
+  annotate("text", x = 0.5, y = 0.985, label = "Lampropholis guichenoti", size = 4.5, color = "black", fontface = "italic")
+ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/fig_guich.png")
 ```

### 2024-04-12 .vdoc.r

@@ -162,8 +162,10 @@ fig_dab <- plotting(sp = "deli", col = "blue", df_prob = fig_dab_AC_df, df_violi
 #
 # Third step, merge plots
 fig_deli <- plot_grid(fig_dar, fig_dab, ncol = 1) +
-  theme(plot.margin = margin(1, 1, 1.25, 1, "cm")) +
-  annotate("text", x = 0.5, y = 1.01, label = "Lampropholis delicata", size = 6, color = "black", fontface = "italic")
+  theme(plot.margin = margin(1, 1, 1.5, 1, "cm")) +
+  annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 5, color = "black", fontface = "italic")
+ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/fig_deli.png")
 #
 #
 #
@@ -180,7 +182,6 @@ fig_gar_BD2_df <- df_plotBD2("guich_red")
 ## Blue
 fig_gab_AC_df <- df_plotAC("guich_blue")
 fig_gab_BD1_df <- df_plotBD1("guich_blue")
-write.csv(fig_gab_BD1_df, file= "./output/Checking/fig_gab_BD1_df.csv")
 fig_gab_BD2_df <- df_plotBD2("guich_blue")
 #
 # Second step, create the plots
@@ -189,8 +190,10 @@ fig_gab <- plotting(sp = "guich", col = "blue", df_prob = fig_gab_AC_df, df_viol
 #
 # Third step, merge plots
 fig_guich <- plot_grid(fig_gar, fig_gab, ncol = 1) +
-  theme(plot.margin = margin(1, 1, 1.25, 1, "cm")) +
-  annotate("text", x = 0.5, y = 1.01, label = "Lampropholis guichenoti", size = 6, color = "black", fontface = "italic")
+  theme(plot.margin = margin(1, 1, 1.5, 1, "cm")) +
+  annotate("text", x = 0.5, y = 0.985, label = "Lampropholis guichenoti", size = 5, color = "black", fontface = "italic")
+ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/fig_guich.png")
 #
 #
 #

### 2024-04-12 R/func.r

@@ -343,25 +343,26 @@ plotting <- function(sp, col, df_prob, df_violin, df_points){
       lab <- c("A", "B")
       df_violin$Treatment <- factor(df_violin$Treatment,
         levels = c("Control-Hot (n =  5 )", "CORT-Hot (n =  5 )", "Control-Cold (n = 6 )", "CORT-Cold (n = 5 )"))
-      img <- readPNG("./Others/Deli.png")
+      img <- readPNG("./Others/Red.png")
     } else if (col == "blue"){
       lab <- c("C", "D")
       df_violin$Treatment <- factor(df_violin$Treatment,
         levels = c("Control-Hot (n =  5 )", "CORT-Hot (n =  6 )", "Control-Cold (n = 6 )", "CORT-Cold (n = 6 )"))
-      img <- readPNG("./Others/Deli.png")
+      img <- readPNG("./Others/Blue.png")
     } else {
       stop("Colour not valid")
     }
   } else if (sp == "guich"){
-    img <- readPNG("./Others/Guich.png")
       if (col == "red"){
       lab <- c("A", "B")
       df_violin$Treatment <- factor(df_violin$Treatment,
         levels = c("Control-Hot (n =  5 )", "CORT-Hot (n =  5 )", "Control-Cold (n = 4 )", "CORT-Cold (n = 5 )"))
+      img <- readPNG("./Others/Red.png")
     } else if (col == "blue"){
       lab <- c("C", "D")
       df_violin$Treatment <- factor(df_violin$Treatment,
         levels = c("Control-Hot (n =  5 )", "CORT-Hot (n =  5 )", "Control-Cold (n = 3 )", "CORT-Cold (n = 5 )"))
+      img <- readPNG("./Others/Blue.png")
     } else {
       stop("Colour not valid")
     }
@@ -375,11 +376,11 @@ plotting <- function(sp, col, df_prob, df_violin, df_points){
   geom_ribbon(aes(ymin = Mean_Predicted_prob - SE_Predicted_prob, ymax = Mean_Predicted_prob + SE_Predicted_prob, fill = Treatment), color = NA, alpha = 0.075) + 
   scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +
   theme_classic() +
-  labs(y = "Predicted probability of correct choice", x = "Trial") +
+  labs(y = "Probability of correct choice", x = "Trial") +
   theme(
[…]

### 2024-04-12 output/Checking/.vdoc.r

@@ -1,0 +1,667 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
[…]

### 2024-04-13 .vdoc.r
Updates

@@ -1,492 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG_1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be the main data base used (data_clean).
-write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
-    for(k in 1:length(hormone)){
-      for(l in 1:length(temperature)){
-        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
-      }
-    }
-  }
-}
-#
-#
-#
-#
-#| label: models
[…]

### 2024-06-03 ms.qmd
Updates

@@
 source(here("R", "func.R"))
-# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
+# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id) + (1| clutch)
 ## A.1) L. delicata
@@
 we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes.
-The results per treatment are summarized in @tbl-bias.
+The results per treatment are summarized in Table 1.
+
+Table 1.
+Probability of choosing the correct feeder in the first trial when the correct feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
+p~mcmc~ tested the hypothesis that the probability is >0.33.
+In bold, those values that are significant (p~mcmc~ <0.05)
 ```{r, tbl-bias}
@@
 #| tbl-cap: "Probability of choosing the correct feeder in the first trial when the correct feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
-p-values were obtained using pmcmc and test the hypothesis that the probability is >0.33.
-In bold, those values that are significant (p-value <0.05)"
+p~mcmc~ tested the hypothesis that the probability is >0.33.
+In bold, those values that are significant (p~mcmc~ <0.05)"
 source(here("R", "func.R"))
@@
 ```
+
 ```{r, results='asis', echo=FALSE}
@@
 ```
+
+#### Models with age included
+
+```{r, modelsage}
+#| label: modelsage
+# Fitting the models for L. delicata and L. guichenoti including age as a covariate
+#
+data_age <- data_clean %>%
+  mutate(age.start = as.numeric(age.start)-mean(as.numeric(age.start)))
+refit2 = FALSE
+formula <- FC_associative ~ age.start + trial_associative*cort*temp + (1 + trial_associative|lizard_id) + (1|clutch)
+species <- c("delicata", "guichenoti")
+group <- c("Red", "Blue")
+#
+models <- list() # Create an empty list to store the models
+for(s in species){
+    # Subset the data for the species
+    data_species <- data_age %>%
+    filter(species == s)
+  for(g in group){
+  # Subset the data for the group
+  data_group <- data_species %>%
+  filter(group == g)
+  # Define model file name
+  model_file <- paste0("output/models/model_age_", s, "_", g,".rds")
+# Fit the model only if it has not been fit yet (if refit2 = TRUE)
+  if(refit2 == TRUE){
+    # Fit the model
+    model <- brm(formula,
+                data = data_group,
+                family = bernoulli(link = "logit"),
+                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
+    # Write the model to a file
+    saveRDS(model, file = model_file)
+  } else {
+      # Read the model from a file
+      model <- readRDS(file = model_file)
+  }
+  # Save the model to the list
+  models[[paste0(s, "_", g)]] <- model
+  }
+}
+#
+model_age_deli_red <- models[["delicata_Red"]]
+model_age_deli_blue <- models[["delicata_Blue"]]
+model_age_guich_red <- models[["guichenoti_Red"]]
+model_age_guich_blue <- models[["guichenoti_Blue"]]
+```
+
+Table 3. Results for _L. delicata_ assigned to red feeders when the model included the age:
+```{r, tbl-agedeli_red, results='asis', out.widht = "26cm"}
+#| label: tbl-agedeli_red
+#| tbl-cap: "Summary model_age_deli_red"
+deli_age_red <- summary(model_age_deli_red)
+# Extract fixed effects names and their corresponding estimates, CIs, etc.
+fixed_effects <- deli_age_red$fixed %>%
+  mutate_all(~ format_dec(., 2))
+Predictors <- rownames(fixed_effects)
+deli_age_red_tbl_df <- cbind(Predictors, fixed_effects)
+# Convert the fixed effects data frame to a flextable
+flextable(deli_age_red_tbl_df) %>%
+  set_table_properties(., width = 1) %>%
+  fontsize(size = 10, part = "all")
+```
+
+Table 4. Results for _L. delicata_ assigned to blue feeders when the model included the age:
+```{r, tbl-agedeli_blue, results='asis', out.widht = "26cm"}
+#| label: tbl-agedeli_blue
+#| tbl-cap: "Summary model_age_deli_blue"
+deli_age_blue <- summary(model_age_deli_blue)
+# Extract fixed effects names and their corresponding estimates, CIs, etc.
+fixed_effects <- deli_age_blue$fixed %>%
+  mutate_all(~ format_dec(., 2))
+Predictors <- rownames(fixed_effects)
+deli_age_blue_tbl_df <- cbind(Predictors, fixed_effects)
+# Convert the fixed effects data frame to a flextable
+flextable(deli_age_blue_tbl_df) %>%
+  set_table_properties(., width = 1) %>%
+  fontsize(size = 10, part = "all")
+```
+
+Table 5. Results for _L. guichenoti_ assigned to red feeders when the model included the age:
+```{r, tbl-ageguich_red, results='asis', out.widht = "26cm"}
+#| label: tbl-ageguich_red
+#| tbl-cap: "Summary model_age_guich_red"
+guich_age_red <- summary(model_age_guich_red)
+# Extract fixed effects names and their corresponding estimates, CIs, etc.
+fixed_effects <- guich_age_red$fixed %>%
+  mutate_all(~ format_dec(., 2))
+Predictors <- rownames(fixed_effects)
+guich_age_red_tbl_df <- cbind(Predictors, fixed_effects)
+# Convert the fixed effects data frame to a flextable
+flextable(guich_age_red_tbl_df) %>%
+  set_table_properties(., width = 1) %>%
+  fontsize(size = 10, part = "all")
+```
+
+Table 6. Results for _L. guichenoti_ assigned to blue feeders when the model included the age:
+```{r, tbl-ageguich_blue, results='asis', out.widht = "26cm"}
+#| label: tbl-ageguich_blue
+#| tbl-cap: "Summary model_age_guich_blue"
+guich_age_blue <- summary(model_age_guich_blue)
+# Extract fixed effects names and their corresponding estimates, CIs, etc.
+fixed_effects <- guich_age_blue$fixed %>%
+  mutate_all(~ format_dec(., 2))
+Predictors <- rownames(fixed_effects)
+guich_age_blue_tbl_df <- cbind(Predictors, fixed_effects)
+# Convert the fixed effects data frame to a flextable
+flextable(guich_age_blue_tbl_df) %>%
+  set_table_properties(., width = 1) %>%
+  fontsize(size = 10, part = "all")
+```

### 2024-06-03 .vdoc.r

@@ -1,0 +1,607 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG_1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+      }
+    }
+  }
+}
+#
+#
+#
+#
+#| label: models
[…]

### 2024-06-03 R/func.r

@@ -34,7 +34,7 @@ sample <- function(sp, bias, corti, therm){
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
 fit_m <- function(sp, bias, refit = TRUE) {
   data <- data_clean
-  formula <- FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
+  formula <- FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id) + (1|clutch)
   #Specify species
     if (sp == "deli"){
       sp_data <- data %>%

### 2024-06-03 ms.qmd
Updates

@@
 ---
-docx: 
+docx: "Early environmental conditions do not impact associative learning in two species of skink"
 bibliography: "./bib/refs.bib"
@@
 Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
-These cognitive processes underpin animal foraging, mate choice, antipredatory strategies and social behaviours that are crucial for the survival and reproduction [@dukas_evolutionary_2004].
+These cognitive processes underpin animal foraging, mate choice, antipredatory strategies and social behaviours that are crucial for survival and reproduction [@dukas_evolutionary_2004].
 Learning - the acquisition of new information [@dukas_evolutionary_2004] - is fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
 However, in nature, there is individual variation in the capacity to acquire new information, depending on factors like age, sex, gut microbiota, or the environment where organisms develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
-The latter can be particularly relevant since the brain is especially susceptible to environmental conditions during early stages of development [@zhu_prenatal_2004].
-Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.
+The latter can be particularly relevant since the brain is especially susceptible to environmental conditions during early stages of development [@zhu_prenatal_2004].Understanding how the environment shapes learning processes is essential due to its profound impact on animals' fitness and adaptability to environmental changes.
 
-In this sense, prenatal glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
+In this context, the prenatal environment emerges as a relevant key of animals' cognitive skills, shaping their capacity for learning and adaptation.
+Prenatal glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
 For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
@@
 guichenoti_), as model species.
-We experimentally increased corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
+We experimentally increased corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - in the eggs and then incubated them at two different temperatures in a 2X2 factorial design.
 Post-incubation, the juveniles were subjectd to a colour-associative task to assess their learning abilities.
 Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's physiology that will ultimately impact learning skills.
-We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently compared to control individuals or those exposed to high temperatures.
-Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
-This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time.
+We predicted that individuals exposed to high levels of CORT or low temperatures will perform less proficiently compared to control individuals or those incubated at higher temperatures.
+Additionally, we predicted that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
+This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
 Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].
@@
 delicata* lays 1 to 6 eggs in only one clutch per season, *L.
-guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014].
-Also, some sudies have found some behavioural divergence between the two skinks [@chapple_know_2011].
-_L.
-delicata_ is more exploratory and bolder than _L.
-guichenoti_ [@chapple_know_2011] which was related to the former's success as an invassive species [@chapple_know_2011; @bezzina2014does], but not with their ability to learn in an associatve learning task [@bezzina2014does].
+guichenoti* clutches are smaller (1-5 eggs per clutch) and they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014].
+Also, some sudies show behavioural differences between both skinks; _L.
+delicata_ is bolder and tends to explore more than _L.
+guichenoti_ [@chapple_know_2011].
+These differences have been associated with _L.
+delicata_'s success as an invassive species [@chapple_know_2011; @bezzina2014does], but not with their ability to perform an associatve learning task [@bezzina2014does].
 
@@
 #### Statistical analyses  
-We performed the analyses with species (_L.
-delicata_ or _L.
-guichenoti_) separately.
-We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour (blue or red) as well.
+We performed the analyses for species separately.
+Because preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red).
 As such, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
-Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.
-'Choice', i.e.
-whether the feeder visited first was the correct one (1) or not (0) was used as the response variable.
-The fixed effects of the model included a triple interaction between: 'Trial' as a nummeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors.
-For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the 'Trial' within each level of lizard identity.
-We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned.
-More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not.
-We used the pmcmc method to test whether those slopes or the comparissons between treatments (e.g.
-slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests).
-We considered statistical significance if p-value < 0.05.
+We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
+We employed correct choice [correct (1) or not (0)] as the response variable, and trial, incubation temperature (Cold versus Hot), hormone (CORT versus Control), and their interaction as fixed factors.
+We included a random intercept and slope (trial) for each lizard in our models.
+We also incorporated the clutch identity as a random factor.
+Since learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature can affect hatching time, we explored the effects of age on learning.
+Lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L.
+delicata_ and 48 to 132 in _L.
+guichenoti_.
+However, when this variable was included in the models we did not find any significant effect of age (see Supplementary material).
+As such, we present models without age as a fixed effect.
+We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
+Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
+Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
+We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions.
+We considered statistical significance if p~mcmc~ < 0.05.
 
@@
 However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards.
-Final sample sizes per treatment and species are disclosed on @fig_deli and @fig-guich.
+Final sample sizes per treatment and species are listed in @fig_deli and @fig-guich.
 ```{r, models}
@@
 guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`).
-However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and @fig-results) that could be affecting the estimated slopes.
+However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material) that could be affecting the estimated slopes.
 As such, we analysed the between treatments differences for each group separately.
@@
 For those _L.
-delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (**FIG**).
-Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (**FIG**).
+delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
+Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
 
@@
 #| label: fig-deli
-#| fig.cap: "Results for Lampropholis delicata for both colour groups "red" (A,B) and "blue" (C, D).
+#| fig.cap: "Results for _Lampropholis delicata_ for both colour groups "red" (A,B) and "blue" (C, D).
 Panels A and C show the predicted probability of choosing the correct feeder first over trials.
@@
 In _L.
-guichenoti_, we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the 'Red' group (**FIG**); and we did not find any significant effect of hormone (Control - CORT = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to 'Blue' (**FIG**).
+guichenoti_, we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the 'Red' group (@fig-guich A, B); and we did not find any significant effect of hormone (Control - CORT = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to 'Blue' (@fig-guich C, D).
 
@@
 
-Our results suggest that the early environment manipulation did not affect learning, as we found that the estimated learning slopes were not different between treatments.
-However, learning slopes were lower when the blue feeders were the correct choice compared to those lizards assigned to the group 'Red' for _L.
-delicata_, but not for _L.
-guichenoti_.
-This difference could be due to a potential bias towards blue in the initial choice, as we found that the estimated probability of choosing the correct feeder in the first trial was higher than expected by chance when the correct feeder was blue (see Supplementary Material).
-Moreover, those treatments and species whose learning slopes do not differ significantly from zero (see Table 1), are associated to highest bias (see Supplementary Material).
-Because there was a possibility that the bias towards the blue feeder was something acquired during training, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the white ones used during habituation, but we did no see any relevant similarity between the white and blue ramps (see Supplementary Material).
-As such, we consider this bias to not be a derivate from our experimental design.
-In this regard, the species confidence hypothesis posits that animals should bias their attention towards colours they are familiar with, and empirical studies show that, for instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
+The scope of the present study was to investigate the effects of early environment on lizards' cognition using two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+guichenoti_).
+We expected early environment to influence cognition in both skinks.
+However, we did not find any significant effects of the experimental conditions on lizards' performance in an associative learning task.
+We found that both _L.
+delicata_ and _L.
+guichenoti_ learned to associate a colour with a food reward, at least for those assigned to the red feeders, and that the learning process ocurred at the same rate regardless of the early environment manipulation.
+These results suggest that learning abilities in these species are robust to prenatal CORT and thermal environment.
+
+The colour of the correct choice had a significant effect on the estimated learning slopes.
+When the correct choice was red lizards learned faster.
+Furthermore, the learning slope in some of the 'Blue' assigned lizards did not differ from zero.
+This could indicate that lizards did not learn to associate the blue ramp with the reward.
+However, the analyses presented in the supplemenatry material show that there was an initial preference towards blue feeders that can be masking our results.
+Indeed, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance when the correct choice was blue.
+Moreover, in those groups where we found that the learning slopes did not differ significantly from zero (see @fig-deli and @fig-guich), we also observed the highest probability to select blue ramps in the first trial (see Supplementary Material).
+Because there was a possibility that this bias towards blue feeders was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see Supplementary Material).
+Given that but we did no see any relevant similarity between the white and blue ramps, we consider the preference towards blue to not be a derivate from our experimental design.
+Rather, it seems likely that lizards innately prefer the blue feeders.
+The species confidence hypothesis posits that animals should bias their attention towards colours they are familiar with, and empirical studies show that, for instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
 However, to the best of our knowledge, noone has reported a colour bias in _L.
 delicata_ or _L.
-guichenoti_ before; and it is not considered to be involved in intraspecific communication [@torr1996patterns, @chapple_biology_2014].
-Still, we recommend to select carefully the colours employed in associative tasks with these species, especially _L.
-delicata_, for future cognitive tasks employing visual stimuli.
-Nevertheless, when lizards assigned to blue or red were analysed separately, the between treatments comparissons remain the same in both species.
-Furthermore, the non-significant trends we observed were not consistent between species or colour assigned.
+guichenoti_ before; and blue colouration is not considered to be involved in intraspecific communication in these species [@torr1996patterns, @chapple_biology_2014].
+Still, we recommend to select carefully the colours employed in associative tasks when employing visual stimuli.
+Despite this, when lizards assigned to blue or red were analysed separately, the between treatments comparissons remain the same in both species.
+Furthermore, the trends we observed were consistent between species or colour assigned.
 As such, we conclude that, overall, lizards learned at the same rate regardless of the early environment manipulation.
 
-As part of our predictions, we expected prenatal CORT to impair learning, as other studies have shown [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn; @bebus_associative_2016].
-However, in other experiments early-life increases in GCs or induced stress did not affect learning abilities or even improve them [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
-In this vein, GCs are known to have hermetic effects, with low levels of GCs being beneficial for learning and memory, and high levels being detrimental [@du_dynamic_2009; @mcewen_brain_2012].
-When we measured other traits of lizards coming from the same treatments, we found that the levels of CORT we used affected size and mitochondrial activity in other organs (non-published data), so the CORT dose was enough to affect some aspects of _L.
+We predicted prenatal CORT to have a negative effect on learning, as previous studies have shown [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn; @bebus_associative_2016].
+However, our results are consistent with other experiments that revealed no effect of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016].
+GCs are known to have hormetic effects, with low levels of GCs being beneficial for learning and memory, and high levels being detrimental [@du_dynamic_2009; @mcewen_brain_2012].
+In a previous study, we found that the same dose of CORT affected mortality and hatch size in both species [**WAIT FOR REFERENCE**].
+However, since dose effects can differ between tissues [@lemaire_prenatal_2000], we cannot dismiss the possibility that our concentrations failed to elicit changes to the brain that would result in impaired learning.
+Conversely, the absence of significant effects of prenatal CORT on learning could be due to the cognitive task employed, as some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
+GCs action involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed unevenly in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
+For instance, in European starlings, males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn].
+Similarly, while Scrub-jays that had lower CORT levels as nestlings performed better on an associative learning test as adults, but not on a reversal learning task [@bebus_associative_2016].
+We must acknowledge the possibility that prenatal CORT does not affect the brain regions involved in coding associative learning in these species.
+Future studies should focus on examining the effect of early-life stress on different cognitive domains.
+
+We also expected hot-incubated lizards to perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Furthermore, those authors that found the opposite pattern [@dayananda_incubation_2017; @abayarathna_effects_2020] employed temperatures far above the natural thermal range of the species in their hot treatments and it is unclear how such conditions relate to wild environments.
+In lizards, higher incubation temperatures are associated with higher neural density in the dorsal and the medial cortex [@amiel_effects_2017].
+Both brain regions have been linked to learning in reptiles [@day2001effects; @lopez2003spatial; @amiel_effects_2017], and, in consequence, we predicted performance in the task to be affected by the prenatal thermal environment.
+However, the effect of prenatal temperature in cognition, and brain physiology and structure has been investigated in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how thermal early environment can affect cognitive abilities.
+In _L.
 delicata_ and _L.
-guichenoti_ biology.
-**However,**  In adition, testing only one cognitive domain could have masked potential differences in learning abilities between treatments.
-For instance, European starlings males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn]; while Scrub-jays that had lower CORT levels as nestlings performed better on an associative learning test as adults, but not on a reversal learning task [@bebus_associative_2016].
-GCs action involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed unevenly in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
-As such, we consider that studying different cognitive domains could provide a more comprehensive understanding of the effects of early-life stress on learning abilities in these species.
+guichenoti_, associative learning appears to be robust to incubation temperature.
+In our analyses, we did not include sex as a factor for several reasons: first, lizads were tested before sexual maduration; and second, previous studies have found weak evidence for sex-dependent learning [@szabo_sex_meta].
+In fact, incubation temperature was not sex-depedent when learning abilities were tested in the Eastern three-lined skink (_Bassiana dupeyerri_) [@amiel_hotter_2012; @clark_colour_2014].
+However, there is previous evidence for interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
+Furthermore, in _B.
+dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal - developing male phenotypes while retaining female genotype [@dissanayake2021effects].
+Such effects were not easily accounted for in these experiments making it challenging to understand whether sex or temperature was the cause of learning differences [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Future investigations should investigate the potential interactive impacts of sex and incubation temperature on cognitive abilities.
+Nevertheless, conducting such studies poses challenges due to the substantial sample sizes necessary.
 
-Regarding incubation temperature, we predicted hot-incubated lizards to perform better in our task then those incubated at 23ºC, since most of the studies show enhanced learning abilities with higher incubation temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Furthermore, those studies that found the opposite pattern, were only when the hot treatment was above the natural thermal range of the species [@dayananda_incubation_2017; @abayarathna_effects_2020].
-However, our results do not align with these previous experiments and our predictions.
-In contrast, we did not find any effect of temperature in _L.
-delicata_ or _L.
-guichenoti_.
-In general, the incubation temperature effects observed on learning performance are associated with higher neural density in certain areas [@amiel_effects_2017], but these effects can be region-dependent [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017].
-Hence, as ocurred with CORT, further studies using different cognitive domains should be used to understand the effects of incubation temperature on learning abilities in these species.
 Finally, we did not see any significant difference in learning rates when both species were compared.
@@
 guichenoti_ [@bezzina2014does].
-However, in the experiment conducted by @bezzina2014does the authors did not find any evidence of learning in neither _L.
+In the experiment conducted by @bezzina2014does the authors did not find any evidence of learning in neither _L.
 delicata_ or _L.
 guichenoti_.
-In this regard, both learning tasks were conducted in a similar way and using the same cognitive domain, so the differences in the results could be due to the different experimental designs or the complexity of stimuli discrimination.
-Nevertheless, to test cognitive difference between these two species, further studies should be conducted using different cognitive domains.
-In conclusion, we found that neither prenatal CORT, temperature, or their interaction affected learning abilities when _L.
-delicata_ and _L.
-guichenoti_ were subjected to a colour-associative task.
-However, we believe studying different cognitive domains is necessary to understand the effects of early-life stress and incubation temperature on learning abilities in these species.
-In addition, we found a bias towards blue that could affect the results found in cognitive tests, and we therefore recommend to select carefully the colours employed when employing visual stimuli in these two species, particularly _L.
-delicata_.
+The learning task conducted in the present experiment was very similar, but we found a different outcome, since both species learned at the same rate.
+The differences between studies could be due to the different experimental designs or the complexity of stimuli discrimination.
+
+In conclusion, our results indicate that lizards completed the associative learning task at similar rates, with no significant differences between species or treatments.
+This outcome contrasts with our predictions and suggest that learning skills in both species are robust to the impact of early environment (at least for temperature and GCs).
+Future research should examine the possible impact of prenatal CORT and temperature on cognitive function, taking into account variables such as the early environment-sex interaction, or the nature of the cognitive task.
+Additionally, it is essential to assess the effects of these treatments on brain function.
+Exploring these areas will enhance our comprehension of the cognitive and physiological mechanisms involved in the adaptability of both species.
 

### 2024-06-03 .vdoc.r

@@ -1,607 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG_1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be the main data base used (data_clean).
-write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
-    for(k in 1:length(hormone)){
-      for(l in 1:length(temperature)){
-        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
-      }
-    }
-  }
-}
-#
-#
-#
-#
-#| label: models
[…]

### 2024-06-03 ms.qmd
updates

@@
 ---
-docx: "Early environmental conditions do not impact associative learning in two species of skink"
+title: "Early environmental conditions do not impact associative learning in two species of skink"
+docx: 
 bibliography: "./bib/refs.bib"
@@
 
-knitr::include_graphics("./Others/LEARN_FIG_1.png")
+knitr::include_graphics("./Others/LEARN_FIG1.png")
 
@@
 #| label: fig-deli
-#| fig.cap: "Results for _Lampropholis delicata_ for both colour groups "red" (A,B) and "blue" (C, D).
+#| fig.cap: "Results for Lampropholis delicata for both colour groups 'Red' (A,B) and 'Blue' (C, D).
 Panels A and C show the predicted probability of choosing the correct feeder first over trials.
@@
 #| label: fig-guich
-#| fig.cap: "Results for Lampropholis guichenoti for both colour groups "red" (A,B) and "blue" (C, D).
+#| fig.cap: "Results for Lampropholis guichenoti for both colour groups 'Red' (A,B) and 'Blue' (C, D).
 Panels A and C show the predicted probability of choosing the correct feeder first over trials.
@@
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot))), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the 'Blue' one (_L.
+guichenoti_ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the 'Blue' one (_L.
 delicata_ mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; _L.
@@
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot))), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`).
 
@@
 
-The colour of the correct choice had a significant effect on the estimated learning slopes.
+The colour of the correct choice had a significant effect on the estimated learning slopes in _L.
+delicata_.
 When the correct choice was red lizards learned faster.
 Furthermore, the learning slope in some of the 'Blue' assigned lizards did not differ from zero.
-This could indicate that lizards did not learn to associate the blue ramp with the reward.
+This could indicate that _L.
+delicata_ did not learn to associate the blue ramp with the reward.
 However, the analyses presented in the supplemenatry material show that there was an initial preference towards blue feeders that can be masking our results.
 Indeed, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance when the correct choice was blue.
-Moreover, in those groups where we found that the learning slopes did not differ significantly from zero (see @fig-deli and @fig-guich), we also observed the highest probability to select blue ramps in the first trial (see Supplementary Material).
+Moreover, in those groups where we found that the learning slopes did not differ significantly from zero (see @fig-deli), we also observed the highest probability to select blue ramps in the first trial (see Supplementary Material).
 Because there was a possibility that this bias towards blue feeders was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see Supplementary Material).
@@
 
-On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue (_L.
-delicata_: mean Prob choice = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
-guichenoti_: mean Prob choice = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L.
+On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue for _L.
+delicata_ (mean Prob choice = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`) but not for _L.
+guichenoti_ (mean Prob choice = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`).
+When the correct choice was red, it was not significant for neither species (_L.
 delicata_: mean Prob choice = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
@@
 
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
 Table 4. Results for _L. delicata_ assigned to blue feeders when the model included the age:
@@
   fontsize(size = 10, part = "all")
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
 ```
@@
 
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
 Table 6. Results for _L. guichenoti_ assigned to blue feeders when the model included the age:

### 2024-08-30 ms.qmd
Updates

@@
 
+Pablo Recio^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^
+
+^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2601, Australia  
+^2^ Flinder's University, College of Science and Engineering, Bedford Park, SA 5042, Australia  
+^3^ Melbourne University, Melbourne, VIC 3000, Australia  
+^4^ University of Wollongong, Wollongong, NSW 2500, Australia  
+^5^ Université de Lille, Lille 59000, France  
+$\ddagger$ Corresponding author: pablo.reciosantiago@anu.edu.au
+
+ORCID:
+
+Pablo Recio ORCID: 0000-0002-5890-0218  
+Dalton C. Leibold ORCID: 0000-0001-9645-2033  
+Ondi L. Crino ORCID: 0000-0001-5700-1387  
+Kristoffer H. Wild ORCID: 0000-0001-6714-3311  
+Chris Friesen ORCID: 0000-0001-5338-7454  
+Basile Mauclaire ORCID:  
+Amelia Y. Peardon ORCID: 0009-0005-6227-8379  
+Daniel W.A. Noble ORCID: 0000-0001-9460-8743
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+## Abstract
+**Behavioural flexibility is expected to be crucial for animals adapting to environmental changes.
+However, the conditions experienced during early development can profoundly impact behavioural flexibility making it unclear how populations will respond to novel circumstances.
+Stressful situations faced by the parents can have a direct impact on offspring cognition through the transmission of glucocorticoids - stress-related hormones that affect offspring cognition.
+At the same time, stressful conditions can influence parental behaviour during nesting and consequently the thermal developmental conditions offspring experience.
+Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
+guichenoti_.
+We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then assessed behavioural flexibility through a reversal learning task.
+We hypothesized prenatal CORT and cold temperatures to impair with lizards' performance in the reversal task.
+Given _L.
+delicata_'s success as an invassive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
+Contrary to our expectations, behavioural flexibility appears to be robust to prenatal temperature and CORT in both species.
+The lack of difference in reversal learning between _L.
+delicata_ and _L.
+guichenoti_ suggests that novel environments are unlikely to influence flexible behavioural learning and that behavioural flexibility itself is unlikely to explain differences in invasion success between these species.**
+
 ## Introduction
+Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
+These cognitive processes are fundamental to foraging, mate selection, antipredatory strategies, and social behaviours, all of which are crucial for survival and reproduction [@dukas_evolutionary_2004].
+Particularly, learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
+Allowing animals to adequate their behavior to their conditions implies that learning can have cascading effects on population dynamics by influencing survival rates or reproductive success.
+However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, gut microbiota, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
+These variations can further affect population dynamics, as differences in learning ability may lead to unequal responses to environmental pressures.
+Therefore, understanding the factors that shape learning is crucial to predict how populations will respond to novel circumstances.
 
-Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
-These cognitive processes underpin animal foraging, mate choice, antipredatory strategies and social behaviours that are crucial for survival and reproduction [@dukas_evolutionary_2004].
-Learning - the acquisition of new information [@dukas_evolutionary_2004] - is fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
-However, in nature, there is individual variation in the capacity to acquire new information, depending on factors like age, sex, gut microbiota, or the environment where organisms develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
-The latter can be particularly relevant since the brain is especially susceptible to environmental conditions during early stages of development [@zhu_prenatal_2004].Understanding how the environment shapes learning processes is essential due to its profound impact on animals' fitness and adaptability to environmental changes.
+Developing conditions are especially relevant in shaping learning abilities because the brain is highly susceptible to environmental inputs during early stages of development [@zhu_prenatal_2004].
+Impacts on brain development can have long-lasting effects on cognitive abilities, potentially influencing an individual's ability to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
+For instance, prenatal glucocorticoids (GCs) - hormones related to organisms' response to allostasis [@sapolsky_how_2000] - and prenatal thermal environment are predicted to be important factors shaping learning abilities [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
+Elevating GCs during early stages of develoment is tipically associated to learning impairments in different taxa [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn]; but factors like sex or the nature of the learning task can affect the direction and magnitud of these effects [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
+In ectotherms, temperature is a pervasive mechanisms of phenotypic plasticity, influencing a suite broad spectrum of traits including growth, metabolism, or learning abilities [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
+High incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while for velvet geckos, being incubated at temperatures beyond their natural thermal range reduce their performance in learning tasks compared to those incubated at colder temperatures [@dayananda_incubation_2017; @abayarathna_effects_2020].
+Learning effects of prenatal GCs and temperature are both related to alterations in neurogenesis, neural structure, and brain metabolic activity [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021], suggesting that both factors could be impacting similar neurological mechanisms to influence learning abilities.
+Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
+This implies that the effects of GCs and temperature on learning could be interdependent, with the impact of one factor being modulated by the other.
+Nevertheless, the interactive effects of GCs and temperature on learning abilities remain unexplored.
 
-In this context, the prenatal environment emerges as a relevant key of animals' cognitive skills, shaping their capacity for learning and adaptation.
-Prenatal glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
-For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
-Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020].
-In fact, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@dayananda_incubation_2017; @abayarathna_effects_2020].
-In this vein, the effects of prenatal temperature and GCs are linked to similar alterations in neural structure and metabolic activity [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021], which suggests that bot factors may interact to shape learning [@noble_developmental_2018].
-Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
-However, our understanding of how these two factors interact remains incomplete.
-
-In this study, we aim to explore the interactive effects between prenatal GCs and the prenatal thermal environment on learning.
-We utilized two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
-guichenoti_), as model species.
-We experimentally increased corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - in the eggs and then incubated them at two different temperatures in a 2X2 factorial design.
-Post-incubation, the juveniles were subjectd to a colour-associative task to assess their learning abilities.
-Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's physiology that will ultimately impact learning skills.
+In this study, we investigated the combined effects of prenatal GCs and thermal environment on learning in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+guichenoti_).
+We manipulated corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - levels in the eggs and then incubated them at two different temperatures in a 2X2 factorial design.
+Post-incubation, juveniles were subjectd to a colour-associative task to assess their learning abilities.
+Our hypothesis posits that prenatal CORT levels and thermal environment will induce sustained effects on brain's physiology that will ultimately impact learning skills [@zhu_prenatal_2004; @amiel_hotter_2012; @eaton2015mild; @amiel_effects_2017].
 We predicted that individuals exposed to high levels of CORT or low temperatures will perform less proficiently compared to control individuals or those incubated at higher temperatures.
 Additionally, we predicted that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
-This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
-Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].
+This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
 
@@
 guichenoti* clutches are smaller (1-5 eggs per clutch) and they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014].
-Also, some sudies show behavioural differences between both skinks; _L.
-delicata_ is bolder and tends to explore more than _L.
-guichenoti_ [@chapple_know_2011].
-These differences have been associated with _L.
-delicata_'s success as an invassive species [@chapple_know_2011; @bezzina2014does], but not with their ability to perform an associatve learning task [@bezzina2014does].
+Besides, previous studies exploring behavioral differences between the two species have found _L.
+delicata_ to be more exploratory than _L.
+guichenoti_ [@chapple_know_2011] but no differences in learning were observed between the skinks in an associative learning task [@bezzina2014does].
 
@@
 To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
-Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
+Room temperatures are set to 22-24 Celsius, and the warm side of enclosures is usually at 32 Celsius.
+
 *Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
 We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm, weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error, and assigned identities to the clutch and each egg.
 Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
 The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
+
 *Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
 After hatchling, we measured juveniles' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
-We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
+We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting, shelter, and a small water dish.
 During this period, they were sprayed water every day and received 3-6 small *A.
@@
 All care otherwise follows similar protocols to adults (see above).
-Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation.
-The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
-These new enclosures were placed in two rooms in 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
-The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
-During acclimatation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
+Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatisation.
+The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the sides and a water dish on the other.
+These new enclosures were placed in two rooms in 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
+Although the conditions in the new room were identical to the main room, the number of lizards per species and treatment in each rack was counterbalanced to control for any potential effect of the room or the position of the lizard in the rack.
+During acclimatisation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
-The rooms temperature was set to between 22-24 Celsius.
 
 #### CORT and Temperature manipulation  
-To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
+To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' - 23ºC ± 3ºC or 'Hot' - 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
 We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
-CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
-Then, eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching.
+We selected these doses based on previous studies publishing yolk CORT concentrations in other ovipaorus reptiles [@lovern2008effects; @hanover2019corticosterone] and our own unpublished data.
+CORT concentration represents 2 standard deviations above the mean natural concentration.
+After the treatment, the eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching.
 The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
@@
 #### Learning  
-To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@fig-Methods B) [see @leal_behavioural_2012; @clark_colour_2014].
+To estimate learning skills, we tested skinks' ability to locate a food reward in an colour-associative learning task (@fig-Methods C, D).
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
 We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A.
-domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
-@fig-Methods B, Stage 3).
+domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods C, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods C, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
+@fig-Methods C, Stage 3).
 Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
 At the end of each trial, we recorded whether the cricket had been consumed or not.
-Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials.
+Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials to ensure lizards' consistency.
 This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
-For the learning phase, we trained lizards to associate between colour and a food reward ('Associative task' in Fig.
-@fig-Methods B).
-The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour.
+
+In the associative learning phase, we trained lizards to associate between colour and a food reward (Fig.
+@fig-Methods D).
+The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in colour.
 We placed the food reward (small, frozen, *A.
 domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
-The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals.
+The food reward was placed insidde all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals.
 The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
@@
 Lizards were tested in this task once a day for 35 days.
-The full experiment was done daily between the 6^th^ of March until the 17^th^ of June 2023, between 11 to 12 am, when the lizards were active.
+
+The full task took place between the 6^th^ of March until the 17^th^ of May 2023, and tests were performed between 11 to 12 am when the lizards were active.
 Trials in the learning phase were recorded with CCTV systems always using the same camera per individual.
-Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not.
-A choice was considered to be made if the head of the lizard was inside the well of one of the ramps.
-PR was blinded to the treatments of the lizards during the analyses of the video.
-We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
+We recorded whether the animal chose the correct ramp first or not.
+We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
+We considered a trial failed if there was no choice in one hour of recordingcored those trials as NA.
 We excluded from our analyses those individuals with more than 15 trials failed (i.e.
-they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.
+they did not make a choice), and we considered the first trial for each individual to be the first one where the a choice was made.
 
@@
 Because preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red).
-As such, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
+Therefore, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
 We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
-We employed correct choice [correct (1) or not (0)] as the response variable, and trial, incubation temperature (Cold versus Hot), hormone (CORT versus Control), and their interaction as fixed factors.
+
+We employed correct choice [correct (1) or not (0)] as the response variable, and trial, incubation temperature (Cold versus Hot), hormone (CORT versus Control), and the three-way interaction as fixed factors.
+The error structure was modeled using a Bernoulli distribution with a logit link function (family = Bernoulli(link = 'logit')).
 We included a random intercept and slope (trial) for each lizard in our models.
-We also incorporated the clutch identity as a random factor.
-Since learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature can affect hatching time, we explored the effects of age on learning.
+Furthermore, even if our split clutch design should control for potential effects of paternity, we also incorporated the clutch identity as a random factor.
+Because eggs were collected during half of the breeding season and both species do not lay more than two clutches [@chapple_know_2011; @chapple_biology_2014], each clutch likely come from a unique mother, and so, clutch identity captures potential maternal effects.
+Learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature can affect hatching time, we explored the effects of age on learning.
 Lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L.
@@
 As such, we present models without age as a fixed effect.
+
 We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
-Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
+Learning reates were estiamated as the choice-trial slope, obtained for each treatment by using the ‘trial’ estimates and its interaction with hormone and temperature.
 Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
-We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions.
+We employed the posterior predictive Markov chain Monte Carlo (p~mcmc~) to test the hypothesis that slopes and slopes contrasts were different from zero.
 We considered statistical significance if p~mcmc~ < 0.05.
@@
 However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards.
-Final sample sizes per treatment and species are listed in @fig_deli and @fig-guich.
+Final sample sizes per treatment and species are listed in @fig_deli and @fig-guich (figures for both species with the raw data are included in the Supplementary Material).
+Mean slopes per treatment for both species are provided in Table 1 in Supplementary Material.
 ```{r, models}
@@
 We found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to slopes of individuals assigned to the group 'Red' for _L.
-delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`), but not for _L.
+delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; slope contrast: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`), but not for _L.
 guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`).
@@
 
-The scope of the present study was to investigate the effects of early environment on lizards' cognition using two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+The scope of the present study was to investigate the effects of early environment on lizards' learning using two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
-We expected early environment to influence cognition in both skinks.
-However, we did not find any significant effects of the experimental conditions on lizards' performance in an associative learning task.
-We found that both _L.
-delicata_ and _L.
-guichenoti_ learned to associate a colour with a food reward, at least for those assigned to the red feeders, and that the learning process ocurred at the same rate regardless of the early environment manipulation.
-These results suggest that learning abilities in these species are robust to prenatal CORT and thermal environment.
+In our experiment, we manipulated CORT levels and temperature during incubation, and we then subjected hatched animals to a colour-associative learning task using food as a reward.
+We expected prenatal CORT and thermal environment to have combined effects on lizards' performance in the test.
+However, we did not find any significant effects of the experimental conditions.
+We found that most individuals from both species learned to associate a colour with a food reward and that the learning process ocurred at the same rate regardless of the early environment, suggesting that learning abilities in these skinks are robust to prenatal CORT and temperature.
+In adition, we found that the learning rates varied depending on the colour assigned to the correct choice, at least for _L.
+delicata_, with lizards assigned to blue feeders performing worse compared to the red group.
 
-The colour of the correct choice had a significant effect on the estimated learning slopes in _L.
-delicata_.
-When the correct choice was red lizards learned faster.
-Furthermore, the learning slope in some of the 'Blue' assigned lizards did not differ from zero.
-This could indicate that _L.
-delicata_ did not learn to associate the blue ramp with the reward.
-However, the analyses presented in the supplemenatry material show that there was an initial preference towards blue feeders that can be masking our results.
-Indeed, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance when the correct choice was blue.
+#### Effect of colour on learning
+The colour of the ramp associated with the attainable cricket (i.e.
+the correct choice) influences learning slopes in _L.
+delicata_, but not _L.
+guichenoti_.
+For _L.
+delicata_, performance was proficient when the reward was linked to red feeders, but learning slopes for lizards assigned to the blue condition did not differ from zero.
+In contrast, _L.
+guichenoti_ showed similar results in both colour scenarios.
+This indicates that _L.
+delicata_ were not able to associate the blue ramp with the reward.
+However, our results could be consequence of an initial bias in lizards' choice.
+The analyses presented in the supplemenatry material show that, overall, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue condition.
 Moreover, in those groups where we found that the learning slopes did not differ significantly from zero (see @fig-deli), we also observed the highest probability to select blue ramps in the first trial (see Supplementary Material).
+
 Because there was a possibility that this bias towards blue feeders was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see Supplementary Material).
-Given that but we did no see any relevant similarity between the white and blue ramps, we consider the preference towards blue to not be a derivate from our experimental design.
+Since these results show no similarities between the white and blue ramps, we consider the preference towards blue to not be a derivate from our experimental design.
 Rather, it seems likely that lizards innately prefer the blue feeders.
-The species confidence hypothesis posits that animals should bias their attention towards colours they are familiar with, and empirical studies show that, for instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
+The species confidence hypothesis posits that animals should bias their attention towards colours they are familiar with [@putman2017fear].
+For instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
 However, to the best of our knowledge, noone has reported a colour bias in _L.
@@
 guichenoti_ before; and blue colouration is not considered to be involved in intraspecific communication in these species [@torr1996patterns, @chapple_biology_2014].
-Still, we recommend to select carefully the colours employed in associative tasks when employing visual stimuli.
-Despite this, when lizards assigned to blue or red were analysed separately, the between treatments comparissons remain the same in both species.
-Furthermore, the trends we observed were consistent between species or colour assigned.
-As such, we conclude that, overall, lizards learned at the same rate regardless of the early environment manipulation.
+Still, we recommend to select carefully the colours employed in associative tasks when relying on visual stimuli.
+Despite this, when lizards assigned to blue or red were analysed separately, the between treatments comparissons remain the same in both conditions and species.
 
-We predicted prenatal CORT to have a negative effect on learning, as previous studies have shown [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn; @bebus_associative_2016].
-However, our results are consistent with other experiments that revealed no effect of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016].
-GCs are known to have hormetic effects, with low levels of GCs being beneficial for learning and memory, and high levels being detrimental [@du_dynamic_2009; @mcewen_brain_2012].
-In a previous study, we found that the same dose of CORT affected mortality and hatch size in both species [**WAIT FOR REFERENCE**].
+#### Effect of prenatal CORT on learning
+Prenatal CORT was expected to have a negative effect on learning, declining CORT-treated lizards performance in the learning task [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn; @bebus_associative_2016].
+However, we did not find any significant difference between hormone treatments in none of the two species.
+Our results are consistent with other experiments that showed no effect of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016].
+In this sense, GCs are known to have hormetic effects, with low or short exposure to GCs improving performance in learning tasks, and high levels impairing proficiency [@du_dynamic_2009; @mcewen_brain_2012].
+When using the same dose and application methods in eggs of _L.
+delicata_, @crino2024eggs found CORT treatment had sustained effects on growth, mitochondrial activity, and baseline CORT levels; and their findings also aligned with the predictions expected under high GCs elevations.
+This suggests that the absence of effects on learning abilities are not due to methodological caveats, but rather to _L.
+delicata_ and _L.
+guichenoti_'s brain being robust to CORT elevations during development.
 However, since dose effects can differ between tissues [@lemaire_prenatal_2000], we cannot dismiss the possibility that our concentrations failed to elicit changes to the brain that would result in impaired learning.
+
 Conversely, the absence of significant effects of prenatal CORT on learning could be due to the cognitive task employed, as some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
@@
 Similarly, while Scrub-jays that had lower CORT levels as nestlings performed better on an associative learning test as adults, but not on a reversal learning task [@bebus_associative_2016].
-We must acknowledge the possibility that prenatal CORT does not affect the brain regions involved in coding associative learning in these species.
-Future studies should focus on examining the effect of early-life stress on different cognitive domains.
+We must acknowledge the possibility that prenatal CORT does not affect the brain regions involved in coding associative learning in these species, and future studies should focus on examining the effect of early-life stress on different cognitive domains.
 
+#### Effect of incubation temperature on learning
 We also expected hot-incubated lizards to perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Furthermore, those authors that found the opposite pattern [@dayananda_incubation_2017; @abayarathna_effects_2020] employed temperatures far above the natural thermal range of the species in their hot treatments and it is unclear how such conditions relate to wild environments.
-In lizards, higher incubation temperatures are associated with higher neural density in the dorsal and the medial cortex [@amiel_effects_2017].
-Both brain regions have been linked to learning in reptiles [@day2001effects; @lopez2003spatial; @amiel_effects_2017], and, in consequence, we predicted performance in the task to be affected by the prenatal thermal environment.
-However, the effect of prenatal temperature in cognition, and brain physiology and structure has been investigated in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how thermal early environment can affect cognitive abilities.
+Furthermore, the opposite pattern was found only in studies that employed temperatures far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020], and it is unclear how such conditions relate to wild environments.
 In _L.
@@
 guichenoti_, associative learning appears to be robust to incubation temperature.
-In our analyses, we did not include sex as a factor for several reasons: first, lizads were tested before sexual maduration; and second, previous studies have found weak evidence for sex-dependent learning [@szabo_sex_meta].
+Our results, therefore, do not align with the outcome observed in previous experiment.
+However, the effect of prenatal temperature in cognition, and brain physiology and structure has been investigated only in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how thermal early environment can affect cognitive abilities.
+
+In our analyses, we did not include sex as a factor for several reasons: first, lizads were tested before sexual maduration; and second, previous studies have found weak evidence for sex-dependent learning in reptiles [@szabo_sex_meta].
 In fact, incubation temperature was not sex-depedent when learning abilities were tested in the Eastern three-lined skink (_Bassiana dupeyerri_) [@amiel_hotter_2012; @clark_colour_2014].
@@
 Furthermore, in _B.
-dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal - developing male phenotypes while retaining female genotype [@dissanayake2021effects].
+dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal, where individuals under cold incubation temepratures develop male phenotypes while retaining female genotypes [@dissanayake2021effects].
 Such effects were not easily accounted for in these experiments making it challenging to understand whether sex or temperature was the cause of learning differences [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Future investigations should investigate the potential interactive impacts of sex and incubation temperature on cognitive abilities.
+Similarly, not accounting for sex in our analyses could be masking potential interactions between temperature and sex in shaping learning abilities.
+Future research should investigate the potential interactive impacts of sex and incubation temperature on cognitive abilities.
 Nevertheless, conducting such studies poses challenges due to the substantial sample sizes necessary.
 
-Finally, we did not see any significant difference in learning rates when both species were compared.
-This result is in line with previous studies that found no differences in learning abilities between _L.
+#### Learning rates between species
+We did not see any significant difference in learning rates when both species were compared.
+This result is in line with previous studies that found similar learning abilities in _L.
 delicata_ and _L.
 guichenoti_ [@bezzina2014does].
-In the experiment conducted by @bezzina2014does the authors did not find any evidence of learning in neither _L.
-delicata_ or _L.
+In the experiment conducted by @bezzina2014does, both species failed to complete the associative learning task under the authors' criterion, while in our experiment both species completed the task, exhibiting similar learning rates.
+Complexity, experimental design, or the criterion employed to define learning could be tha major cause of the discrepancies between ours and @bezzina2014does's findings.
+Developing common strategies and approaches to assess learning in animals could help understand how learning abilities are shaped in different taxa or under different environments.
+
+#### Conclusion
+Our results revealed that lizards completed the associative learning task at similar rates, with no significant differences observed between species or treatments.
+This outcome contrasts with our initial predictions, suggesting that the learning abilities of both species are resilient to the early environmental influences examined.
+Our findings indicate that the learning skills of these lizards may be more robust than anticipated under varying early life conditions.
+We also found significant effects of the colour employed in the task on learning rates in _L.
+delicata_, but not in _L.
 guichenoti_.
-The learning task conducted in the present experiment was very similar, but we found a different outcome, since both species learned at the same rate.
-The differences between studies could be due to the different experimental designs or the complexity of stimuli discrimination.
+These results seem to be consequence of an innate colour bias, and highlights the importance of carefully selecting the colour employed when testing cognition using visual stimuli.
 
-In conclusion, our results indicate that lizards completed the associative learning task at similar rates, with no significant differences between species or treatments.
-This outcome contrasts with our predictions and suggest that learning skills in both species are robust to the impact of early environment (at least for temperature and GCs).
-Future research should examine the possible impact of prenatal CORT and temperature on cognitive function, taking into account variables such as the early environment-sex interaction, or the nature of the cognitive task.
-Additionally, it is essential to assess the effects of these treatments on brain function.
-Exploring these areas will enhance our comprehension of the cognitive and physiological mechanisms involved in the adaptability of both species.
+Future research should continue exploring the potential effects of prenatal corticosterone (CORT) and temperature on cognitive function, but with a focus on interactions between early environmental factors and sex, as well as the specific nature of the cognitive tasks employed.
+Furthermore, it is crucial to explore how these treatments influence brain function at a neurological level.
+Investigating these aspects will help us understand the cognitive and physiological mechanisms underpinning adaptability in these species and offer insights into how early developmental factors shape long-term cognitive outcomes.
 
@@
 
+#### Estimates of reversal learning slopes for all the different treatments per each task, specie, and group.
+Table 1.
+Estimates of learning slopes for all the different treatments per each task, specie, and group.
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All p~mcmc~ tested the hypothesis that the mean equals zero.
+In bold, those values that are significant (p~mcmc~ <0.05).
+```{r, tbl-data, results='asis'}
+#| label: tbl-data
+#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All pmcmc tested the hypothesis that the mean equals zero.
+In bold, those values that are significant (pmcmc <0.05)"
+source(here("R", "func.R"))
+#
+############################## CREATING BIG DF FOR TABLE ##############################
+# Building the vectors for titles of rows and columns
+specie <- c("L. delicata", "L. guichenoti")
+group <- c("Red", "Blue")
+treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
+values <- c("Mean", "95% CI", "pmcmc")
+# Building the vectors for estimated means, co.intervals(95%), and pmcmc for the slopes obtained from posteriors, assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
+#First get estimates for both tasks
+estimates <- list(
+  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot,
+  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot,
+  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot,
+  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot
+)
+#
+# Then get the mean, co.intervals(95%), and pmcmc
+mean <- format_dec(sapply(estimates, mean), 3)
+interval_025 <- format_dec(sapply(estimates, function(x) quantile(x,0.025)), 3)
+interval_975 <- format_dec(sapply(estimates, function(x) quantile(x,0.975)), 3)
+intervals <- paste0("[", interval_025, " , ", interval_975, "]")
+Pmcmc <- format_p(sapply(estimates, pmcmc), 4)
+#
+# Building the df
+table_df <- data.frame(
+  Specie = rep(specie, each = length(group) * length(treatments)),
+  Group = rep(rep(group, each = length(treatments)), times = length(specie)),
+  Treatment = rep(treatments, times = length(specie) * length(group)),
+  Mean = mean,          # 'mean' vector directly
+  CI = intervals,       # 'intervals' vector directly
+  pmcmc = Pmcmc         # 'Pmcmc' vector directly
+) %>%
+  pivot_wider(names_from = Group, values_from = c(Mean, CI, pmcmc)) %>% #To divide by colour
+  select(Specie, Treatment, Mean_Red, CI_Red, pmcmc_Red, Mean_Blue, CI_Blue, pmcmc_Blue) %>% #To order the columns in the way I want for the table
+data.frame()
+#
+############################## MAKING THE TABLE ##############################
+## Table format
+set_flextable_defaults(
+ font.family = "Times New Roman",
+ font.size = 10)
+# Create some objects to use in the table
+bold_red <- table_df$pmcmc_Red == "< 0.05" | table_df$pmcmc_Red == "< 0.001"
+bold_blue <- table_df$pmcmc_Blue == "< 0.05" | table_df$pmcmc_Blue == "< 0.001" 
+# Make table
+real_table <- flextable(table_df) %>%
+    bold(i = which(bold_red), j = c("pmcmc_Red", "Mean_Red", "CI_Red"), part = "body") %>%
+    bold(i = which(bold_blue), j = c("pmcmc_Blue", "Mean_Blue", "CI_Blue"), part = "body") %>%
+    set_table_properties(width = 1) %>%
+    align(align="center", part="all") %>% 
+    add_header_row(values = c("", "Red", "Blue"), colwidths = c(2, 3, 3)) %>%
+    set_header_labels(Mean_Red = "Mean",
+                      CI_Red = "95% CI",
+                      pmcmc_Red = "pmcmc",
+                      Mean_Blue = "Mean",
+                      CI_Blue = "95% CI",
+                      pmcmc_Blue = "pmcmc") %>%
+    italic(i= c(1, 5), j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
+    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    hline(i = 4, j = c(1:8), part = "body") %>% # To make some horizontal lines
+    vline(j = c(2,5), part = "all") %>% # To make some vertical lines
+    autofit() 
+real_table
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
 #### Colour preference
@@
 we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes.
-The results per treatment are summarized in Table 1.
+The results per treatment are summarized in Table 2.
 
-Table 1.
+Table 2.
 Probability of choosing the correct feeder in the first trial when the correct feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment.

### 2024-08-30 R/func.r

@@ -152,7 +152,7 @@ format_p <- function(x, n) {
   z <- sprintf(paste0("%.",n,"f"), x)
   tmp <- ifelse(as.numeric(z) <= 0.001, "< 0.001",
          ifelse(as.numeric(z) <= 0.05 & as.numeric(z) > 0.001, "< 0.05",
-                paste0("= ", as.character(z))))
+                format_dec(as.numeric(z), 2)))
   return(tmp)
 }
 ####################
@@ -341,13 +341,13 @@ plotting <- function(sp, col, df_prob, df_violin, df_points){
   if(sp == "deli"){
     if (col == "red"){
       lab <- c("A", "B")
-      df_violin$Treatment <- factor(df_violin$Treatment,
-        levels = c("Control-Hot (n =  5 )", "CORT-Hot (n =  5 )", "Control-Cold (n = 6 )", "CORT-Cold (n = 5 )"))
+      Treatment <- factor(df_violin$Treatment,
+        levels = c("Control-Hot (n =  5)", "CORT-Hot (n =  5)", "Control-Cold (n = 6)", "CORT-Cold (n = 5)"))
       img <- readPNG("./Others/Red.png")
     } else if (col == "blue"){
       lab <- c("C", "D")
-      df_violin$Treatment <- factor(df_violin$Treatment,
-        levels = c("Control-Hot (n =  5 )", "CORT-Hot (n =  6 )", "Control-Cold (n = 6 )", "CORT-Cold (n = 6 )"))
+      Treatment <- factor(df_violin$Treatment,
+        levels = c("Control-Hot (n =  5)", "CORT-Hot (n =  6)", "Control-Cold (n = 6)", "CORT-Cold (n = 6)"))
       img <- readPNG("./Others/Blue.png")
     } else {
       stop("Colour not valid")
@@ -355,13 +355,13 @@ plotting <- function(sp, col, df_prob, df_violin, df_points){
   } else if (sp == "guich"){
       if (col == "red"){
       lab <- c("A", "B")
-      df_violin$Treatment <- factor(df_violin$Treatment,
-        levels = c("Control-Hot (n =  5 )", "CORT-Hot (n =  5 )", "Control-Cold (n = 4 )", "CORT-Cold (n = 5 )"))
+      Treatment <- factor(df_violin$Treatment,
+        levels = c("Control-Hot (n =  5)", "CORT-Hot (n =  5)", "Control-Cold (n = 4)", "CORT-Cold (n = 5)"))
[…]

### 2024-08-30 ms.qmd
Updates

@@
 title: "Early environmental conditions do not impact associative learning in two species of skink"
+format:
   docx: 
+    reference-doc: "./bib/tmpl.docx"
+    number_sections: true
+    linestretch: 2
+    fontsize: 12pt
+    mainfont: Times New Roman
     bibliography: "./bib/refs.bib"
     csl: "./bib/animal-cognition.csl"
-reference-doc: "./bib/tmpl.docx"
 execute:
@@
 ## Abstract
-**Behavioural flexibility is expected to be crucial for animals adapting to environmental changes.
-However, the conditions experienced during early development can profoundly impact behavioural flexibility making it unclear how populations will respond to novel circumstances.
-Stressful situations faced by the parents can have a direct impact on offspring cognition through the transmission of glucocorticoids - stress-related hormones that affect offspring cognition.
-At the same time, stressful conditions can influence parental behaviour during nesting and consequently the thermal developmental conditions offspring experience.
-Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
+Acquiring new information through learning is essential for animals to adjust their behaviour adaptively.
+However, animals' abilities to learn can be constrained by the conditions experienced during early stages of development, when the brain is especially susceptible to environmental inputs.
+Temperature is a pervasive mechanism of phenotypic plasticity in ectotherms, exerting direct effects on growth, metabolism, or learning.
+In vertebrates, abrupt thermal changes can trigger an allostatic response, which is mediated by glucocorticoids - stress-related hormones - that can be transmitted to the offspring, potentially impacting their learning abilities.
+Thus, glucocorticoids and the thermal environment are predicted to have interactive effects on the development of learning functions in animals.
+Here, we investigated the combined consequences of corticosterone (CORT) and temperature elevations on learning in two species of lizards, _Lampropholis delicata_ and _L.
 guichenoti_.
-We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then assessed behavioural flexibility through a reversal learning task.
-We hypothesized prenatal CORT and cold temperatures to impair with lizards' performance in the reversal task.
-Given _L.
-delicata_'s success as an invassive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
-Contrary to our expectations, behavioural flexibility appears to be robust to prenatal temperature and CORT in both species.
-The lack of difference in reversal learning between _L.
-delicata_ and _L.
-guichenoti_ suggests that novel environments are unlikely to influence flexible behavioural learning and that behavioural flexibility itself is unlikely to explain differences in invasion success between these species.**
+We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then subjected juveniles to a colour-associative learning task.
+In the learning task lizards had to associate the attainability of a food item with the colour of the feeder.
+We perfomed 35 trials per individual and recorded whether lizards made the correct choice or not.
+In our analyses, we compared the rate of behavioural change over time (learning slopes) between treatments.
+We anticipated that elevated CORT and low temperatures would impair lizards' performance.
+However, our results show that associative learning skills in these two species is robust to prenatal temperature and CORT.
+We also found a significant effect of the colour employed as the correct choice in our tests for _L.
+delicata_, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
 
@@
 #| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**).
-Stages 1-3 indicate the different phases of the habituation process.
-In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+#| fig.cap: "Experimental design of the experiment.
+Panel **A** shows the early environment manipulation.
+In panel **B**, the measurements of the 3D-printed ramps employed in the habituation and learning tasks.
+Panel **C** shows the habituation process with the three different stages.
+And in panel **D**, the associative task.
+White lids in **D** show the ramps where the food reward was not attainable."
 
@@
 Because preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red).
-Therefore, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
+Therefore, we run a total of four different Bayesian multilevel models using the brm function from the brms package [@burkner2017brms] in Quarto [@Allaire_Quarto_2022].
 We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
@@
 However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards.
-Final sample sizes per treatment and species are listed in @fig_deli and @fig-guich (figures for both species with the raw data are included in the Supplementary Material).
+Final sample sizes per treatment and species are listed in @fig-deli and @fig-guich (figures for both species with the raw data are included in the Supplementary Material).
 Mean slopes per treatment for both species are provided in Table 1 in Supplementary Material.
@@
 delicata_ or _L.
-guichenoti_ before; and blue colouration is not considered to be involved in intraspecific communication in these species [@torr1996patterns, @chapple_biology_2014].
+guichenoti_ before; and blue colouration is not considered to be involved in intraspecific communication in these species [@torr1996patterns; @chapple_biology_2014].
 Still, we recommend to select carefully the colours employed in associative tasks when relying on visual stimuli.
@@
 Investigating these aspects will help us understand the cognitive and physiological mechanisms underpinning adaptability in these species and offer insights into how early developmental factors shape long-term cognitive outcomes.
+
+## Data accessibility
+All data, data description, and R code are available in public repository [https://github.com/Pablo-Recio/CORT_Temp_learning](https://github.com/Pablo-Recio/CORT_Temp_learning).
+
+## Satements and declarations 
+#### Competing Interests
+We declare we have no competing interests
+#### Conflict of Interest
+We declare we have no conflict of interest
+#### Ethical Approval
+All experimental procedures and laboratory housing complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33).
+
+## Authors’ contributions
+P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.H.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, funding acquisition, writing—review and editing; B.M: data collection, writing—review and editing; A.Y.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
+All authors gave final approval for publication and agreed to be held accountable for the work performed therein.
+
+## Funding
+This work was supported by a National Australian University fellowship (P.R.), the Australian Research Council (grant no.
+DP210101152) to D.N.
+and C.F., and the ACT Herpetological Association grant to P.R.
+
+## Acknowledgements
+We thank the help and assistance of our lab technicians Benjamin Durant and Michelle Stephens for taking care of the lizards.
+We are also grateful to ACTHA for the grant for the 3D printed feeders, and we also thank ANU MakerSpace, where we designed and built the prototypes of the 3D printed feeders.
+Finally, we wish to acknowledge the anonymous reviewers for their valuable feedback on the manuscript.
 

### 2024-09-14 ms.qmd
Updates

@@
 ## Abstract
-Acquiring new information through learning is essential for animals to adjust their behaviour adaptively.
+Animals must acquire new information through learning to adjust their behaviour adaptively.
 However, animals' abilities to learn can be constrained by the conditions experienced during early stages of development, when the brain is especially susceptible to environmental inputs.
@@
 Thus, glucocorticoids and the thermal environment are predicted to have interactive effects on the development of learning functions in animals.
-Here, we investigated the combined consequences of corticosterone (CORT) and temperature elevations on learning in two species of lizards, _Lampropholis delicata_ and _L.
+Here, we investigated the combined effects of corticosterone (CORT) and elevated temperature during development on learning in juveniles of two species of lizards, _Lampropholis delicata_ and _L.
 guichenoti_.
 We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then subjected juveniles to a colour-associative learning task.
-In the learning task lizards had to associate the attainability of a food item with the colour of the feeder.
-We perfomed 35 trials per individual and recorded whether lizards made the correct choice or not.
-In our analyses, we compared the rate of behavioural change over time (learning slopes) between treatments.
-We anticipated that elevated CORT and low temperatures would impair lizards' performance.
-However, our results show that associative learning skills in these two species is robust to prenatal temperature and CORT.
-We also found a significant effect of the colour employed as the correct choice in our tests for _L.
-delicata_, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
+We predicted that elevated CORT and low temperatures would impair associative learning.
+However, both species learned the task at the same rate independently of treatment.
+This suggests that associative learning skills in these two species is robust to prenatal temperature and CORT.
+We also found that lizards learned slower if food rewards were associated with blue coloured feeders compared to red and green feeders, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
 
@@
 Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
-However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards.
+However, due to natural mortality (n = 11), incompletion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we had a final total of 81 lizards.
 Final sample sizes per treatment and species are listed in @fig-deli and @fig-guich (figures for both species with the raw data are included in the Supplementary Material).
-Mean slopes per treatment for both species are provided in Table 1 in Supplementary Material.
+Mean slopes per treatment for both species are provided in Table 1 in the Supplementary Material.
 ```{r, models}
@@
 We found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to slopes of individuals assigned to the group 'Red' for _L.
-delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; slope contrast: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`), but not for _L.
-guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`).
+delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; slope contrast: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
+guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
 However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material) that could be affecting the estimated slopes.
@@
 For those _L.
-delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
-Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
+delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
+Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
 
@@
 In _L.
-guichenoti_, we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the 'Red' group (@fig-guich A, B); and we did not find any significant effect of hormone (Control - CORT = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to 'Blue' (@fig-guich C, D).
+guichenoti_, we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the 'Red' group (@fig-guich A, B); and we did not find any significant effect of hormone (Control - CORT = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to 'Blue' (@fig-guich C, D).
 
@@
 real_table
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
 ```
@@
   theme(
-    axis.title = element_text(size = 15, family = "Times New Roman"),
+    axis.title = element_text(size = 13, family = "Times New Roman"),
     axis.text = element_text(size = 10, family = "Times New Roman"),
@@
 ```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+```{r, fig-age} 
+#| label: fig-age
+#| fig.cap: "Distribution of the age of the lizards by treatment and species"
+# Plotting the distribution of the age of the lizards by treatment and species
+# Load the data
+data_age <- data_clean
+# Plot the distribution of the age of the lizards by treatment and species
+img_deli <- readPNG("./Others/Deli.png")
+plot_age_deli <- data_age %>%
+  filter(species == "delicata") %>%
+  mutate(trt = factor(trt, 
+          levels = c("A_23", "B_23", "A_28", "B_28"), 
+          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot"))) %>%
+  ggplot(aes(x = age.start, color = trt)) +
+  geom_density(linewidth = 1.5) +
+  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +  
+  labs(title = "L. delicata", x = "Age (days)", color = "Treatments") +
+  theme_classic() +
+  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm"),
+    plot.title = element_text(size = 14, family = "Times", face = "italic"),
+    axis.text.y = element_blank(),   # Remove y-axis labels
+    axis.title = element_text(size = 12, family = "Times"),
+    axis.text = element_text(size = 10, family = "Times"),
+    legend.position = "right",
+    legend.title = element_text(size = 12, family = "Times"),
+    legend.text = element_text(size = 11, family = "Times")
+    ) +
+  annotation_custom(rasterGrob(img_deli), xmin = 0.73, xmax = 0.98, ymin = 0.73, ymax = 0.98)
+#
+img_guich <- readPNG("./Others/Guich.png")
+plot_age_guich <- data_age %>%
+  filter(species == "guichenoti") %>%
+  mutate(trt = factor(trt, 
+          levels = c("A_23", "B_23", "A_28", "B_28"), 
+          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot"))) %>%
+  ggplot(aes(x = age.start, color = trt)) +
+  geom_density(linewidth = 1.5) +
+  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +  
+  labs(title = "L. guichenoti", x = "Age (days)", color = "Treatments") +
+  theme_classic() +
+  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm"),
+    plot.title = element_text(size = 14, family = "Times", face = "italic"),
+    axis.text.y = element_blank(),   # Remove y-axis labels
+    axis.title = element_text(size = 12, family = "Times"),
+    axis.text = element_text(size = 10, family = "Times"),
+    legend.position = "right",
+    legend.title = element_text(size = 12, family = "Times"),
+    legend.text = element_text(size = 11, family = "Times")
+    ) +
+  annotation_custom(rasterGrob(img_guich), xmin = 0.73, xmax = 0.98, ymin = 0.73, ymax = 0.98)
+#
+plot_age <- plot_grid(plot_age_deli, plot_age_guich, ncol = 1)
+ggsave("./output/figures/plot_age.png", plot=plot_age, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/plot_age.png")
+```

### 2024-09-14 .vdoc.r

@@ -1,0 +1,835 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the experiment. Panel **A** shows the early environment manipulation. In panel **B**, the measurements of the 3D-printed ramps employed in the habituation and learning tasks. Panel **C** shows the habituation process with the three different stages. And in panel **D**, the associative task. White lids in **D** show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2024-09-14 R/func.r

@@ -239,10 +239,10 @@ df_plotBD1 <- function(data){
         Treatment = factor(rep(names(lst), each = length(dar_CORTCold)))) %>%
         mutate(Treatment = factor(Treatment, 
           levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"),
-          labels = c("CORT-Cold" = paste("CORT-Cold (n =", n_list$delicata_Red_CORT_Cold , ")"),
-                    "Control-Cold" = paste("Control-Cold (n =", n_list$delicata_Red_Control_Cold , ")"),
-                    "CORT-Hot" = paste("CORT-Hot (n = ", n_list$delicata_Red_CORT_Hot , ")"),
-                    "Control-Hot" = paste("Control-Hot (n = ", n_list$delicata_Red_Control_Hot , ")"))
+          labels = c("CORT-Cold" = paste0("CORT-Cold (n = ", n_list$delicata_Red_CORT_Cold, ")"),
+                    "Control-Cold" = paste0("Control-Cold (n = ", n_list$delicata_Red_Control_Cold, ")"),
+                    "CORT-Hot" = paste0("CORT-Hot (n = ", n_list$delicata_Red_CORT_Hot, ")"),
+                    "Control-Hot" = paste0("Control-Hot (n = ", n_list$delicata_Red_Control_Hot, ")"))
           )
         ) %>%
       data.frame()
@@ -255,10 +255,10 @@ df_plotBD1 <- function(data){
         Treatment = factor(rep(names(lst), each = length(dab_CORTCold)))) %>%
         mutate(Treatment = factor(Treatment, 
           levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"),
-          labels = c("CORT-Cold" = paste("CORT-Cold (n =", n_list$delicata_Blue_CORT_Cold , ")"),
-                    "Control-Cold" = paste("Control-Cold (n =", n_list$delicata_Blue_Control_Cold , ")"),
-                    "CORT-Hot" = paste("CORT-Hot (n = ", n_list$delicata_Blue_CORT_Hot , ")"),
-                    "Control-Hot" = paste("Control-Hot (n = ", n_list$delicata_Blue_Control_Hot , ")"))
+          labels = c("CORT-Cold" = paste0("CORT-Cold (n = ", n_list$delicata_Blue_CORT_Cold, ")"),
+                    "Control-Cold" = paste0("Control-Cold (n = ", n_list$delicata_Blue_Control_Cold, ")"),
[…]

### 2024-09-14 ms.qmd
Updates

@@
 This suggests that associative learning skills in these two species is robust to prenatal temperature and CORT.
-We also found that lizards learned slower if food rewards were associated with blue coloured feeders compared to red and green feeders, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
+We also found that lizards learned slower if food rewards were associated with blue coloured ramps compared to red and green, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
 
 ## Introduction
-Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
+Cognition is the set of processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
 These cognitive processes are fundamental to foraging, mate selection, antipredatory strategies, and social behaviours, all of which are crucial for survival and reproduction [@dukas_evolutionary_2004].
 Particularly, learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
-Allowing animals to adequate their behavior to their conditions implies that learning can have cascading effects on population dynamics by influencing survival rates or reproductive success.
+Learning enables animals to adapt their behavior to environmental conditions and thus can have cascading effects on population dynamics by influencing survival rates or reproductive success [@ward2016ecological; @welklin2024spatial].
+
 However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, gut microbiota, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
-These variations can further affect population dynamics, as differences in learning ability may lead to unequal responses to environmental pressures.
+These variations can further affect population dynamics, as differences in learning ability may lead to unequal responses to environmental pressures [@ward2016ecological; @welklin2024spatial].
+For example, fast learners may better exploit resources or avoid dangerous stimuli while those with lower learning capabilities might struggle to adapt.
+This could affect their survival and reproductive output, ultimately influencing population growth rates and stability [@ward2016ecological; @welklin2024spatial].
 Therefore, understanding the factors that shape learning is crucial to predict how populations will respond to novel circumstances.
@@
 Developing conditions are especially relevant in shaping learning abilities because the brain is highly susceptible to environmental inputs during early stages of development [@zhu_prenatal_2004].
-Impacts on brain development can have long-lasting effects on cognitive abilities, potentially influencing an individual's ability to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
-For instance, prenatal glucocorticoids (GCs) - hormones related to organisms' response to allostasis [@sapolsky_how_2000] - and prenatal thermal environment are predicted to be important factors shaping learning abilities [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
-Elevating GCs during early stages of develoment is tipically associated to learning impairments in different taxa [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn]; but factors like sex or the nature of the learning task can affect the direction and magnitud of these effects [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
-In ectotherms, temperature is a pervasive mechanisms of phenotypic plasticity, influencing a suite broad spectrum of traits including growth, metabolism, or learning abilities [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
-High incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while for velvet geckos, being incubated at temperatures beyond their natural thermal range reduce their performance in learning tasks compared to those incubated at colder temperatures [@dayananda_incubation_2017; @abayarathna_effects_2020].
-Learning effects of prenatal GCs and temperature are both related to alterations in neurogenesis, neural structure, and brain metabolic activity [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021], suggesting that both factors could be impacting similar neurological mechanisms to influence learning abilities.
-Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
+Impacts on brain development can have long-lasting effects on cognition, potentially influencing an individual's ability to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
+For example, maternal condition during gestation or pre-oviposition can influence offspring's phenotype through the transmission of hormones, nutrients, or other molecules [@moore_mothers_2019].
+
+Glucocorticoids (GCs) are a class of steroid hormones that are particularly relevant in this context.
+In vertebrates, GCs regulate metabolism and maintain homeostasis in response to disturbances [i.e., ‘the stress response’ @sapolsky_how_2000].
+Under stressful situations, animals respond by instigating adaptive physiological and behavioural adjustments mediated by GCs.
+These GCs can be
+transmitted directly from the parents to their offspring with different effects on offspring phenotype [@Crino_2023].
+Elevations in GCs during early stages of development typically result in altered neurogenesis, brain structure, and metabolic activity that in most cases are related to decreased learning abilities [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009; @eaton2015mild; @farrell_developmental_2015-learn; @farrell_developmental_2016].
+For instance, prenatal stress in Rats (_Rattus norvegicus_) induced reduction of neurogenesis in the dentate gyrus associated to impairments in hippocampal-related spatial tasks[@lemaire_prenatal_2000].
+However, factors like sex or the nature of the learning task can affect the direction and magnitude of the effects of prenatal exposure to elevated GCs [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016; @farrell_developmental_2016].
+Because the effects of prenatal GCs on learning can be context-dependent, it is crutial to conduct studies across diverse taxa and experimental conditions to fully understand these effects.
+
+In addition to the environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
+In ectotherms, early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits including growth, metabolism, or learning abilities [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
+For instante, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while velvet geckos incubated at temperatures beyond their natural thermal range are worse learners than those incubated at colder temperatures [@dayananda_incubation_2017; @abayarathna_effects_2020].
+These effects are likely mediated by changes in neural structure and function, as high temperatures can increase neural density and metabolic activity in the brain [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021].
+
+GCs can play a pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
 This implies that the effects of GCs and temperature on learning could be interdependent, with the impact of one factor being modulated by the other.
-Nevertheless, the interactive effects of GCs and temperature on learning abilities remain unexplored.
-
-In this study, we investigated the combined effects of prenatal GCs and thermal environment on learning in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+However, the interactive effects of GCs and temperature on learning abilities remain unexplored.
+
+In this study, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - and incubation temperature on learning in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
-We manipulated corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - levels in the eggs and then incubated them at two different temperatures in a 2X2 factorial design.
-Post-incubation, juveniles were subjectd to a colour-associative task to assess their learning abilities.
-Our hypothesis posits that prenatal CORT levels and thermal environment will induce sustained effects on brain's physiology that will ultimately impact learning skills [@zhu_prenatal_2004; @amiel_hotter_2012; @eaton2015mild; @amiel_effects_2017].
-We predicted that individuals exposed to high levels of CORT or low temperatures will perform less proficiently compared to control individuals or those incubated at higher temperatures.
-Additionally, we predicted that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
+We manipulated CORT levels in the eggs and then incubated them at two different temperatures in a 2X2 factorial design.
+Post-incubation, juveniles were subjected to a colour-associative task to assess their learning abilities.
+We hypothesized that prenatal CORT levels and thermal environment will induce sustained effects on brain's physiology, ultimately impacting learning skills.
+We predicted that individuals exposed to high levels of CORT or low temperatures will learn slower than control individuals or those incubated at higher temperatures [@zhu_prenatal_2004; @amiel_hotter_2012; @eaton2015mild; @amiel_effects_2017].
+Additionally, we predicted that incubation at high temperatures will mitigate the impact of CORT on skinks' performance, while cold incubation temperatures were expected to enhance the effects of CORT.
 This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
@@
 #### Subjects  
-_L.
-guichenoti_ and _L.
-delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011].
+_Lampropholis delicata and _L.
+guichenoti_ are small (∼35-55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011].
 Both species have similar breeding periods, but with some differences in reproductive output: while *L.
 delicata* lays 1 to 6 eggs in only one clutch per season, *L.
-guichenoti* clutches are smaller (1-5 eggs per clutch) and they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014].
-Besides, previous studies exploring behavioral differences between the two species have found _L.
+guichenoti* clutches are smaller (1-5 eggs per clutch) and they usually lay two clutches per season [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014].
+Previous studies exploring behavioral differences between the two species have found _L.
 delicata_ to be more exploratory than _L.
-guichenoti_ [@chapple_know_2011] but no differences in learning were observed between the skinks in an associative learning task [@bezzina2014does].
+guichenoti_ [@chapple_know_2011].
+However, no differences in learning were observed between the skinks in an associative learning task [@bezzina2014does].
 
 #### Husbandry  
-*Breeding colony* -- We tested juveniles coming from a breeding colony established in the lab since 2019.
-There is a total of 270 and 180 adults of *L.
+*Breeding colony* -- We tested juveniles from a 2019-established lab breeding colony.
+A a total of 270 and 180 adults of *L.
 delicata* and *L.
-guichenoti* respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+guichenoti* respectively, are housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
 Enclosures are provided with non-stick matting, shelter, and several small water dishes.
-Water is given daily, and they are fed approx.
-40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
+Water is given daily, and they are fed approximately 40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
 Crickets are dusted with calcium weekly and multivitamin and calcium biweekly.
 To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
-Room temperatures are set to 22-24 Celsius, and the warm side of enclosures is usually at 32 Celsius.
+Room temperatures are set to 22-24 ºC, and the warm side of enclosures is usually at 32 ºC.
 
@@
 We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm, weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error, and assigned identities to the clutch and each egg.
-Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
+After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm, mass using a digital scale (OHAUS, Model spx123; ± 0.001g error), and assigned individual IDs to the clutch and each egg.
+Eggs were treated with CORT or vehicle (see CORT and Temperature Manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
 The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
-
-*Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
-After hatchling, we measured juveniles' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
-We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting, shelter, and a small water dish.
-During this period, they were sprayed water every day and received 3-6 small *A.
-domestica* crickets three times a week.
+Eggs were then checked three times a week for hatchlings.
+
+*Hatchlings* -- After hatching, we measured juveniles' SVL and Tail Length (TL) with a ruler to the nearest mm and mass using a digital scale (OHAUS, Model spx123; ± 0.001g error).
+Hatchlings were then housed individually in small enclosures (18.7L x 13.2W x 6.3H cm) provided with non-stick matting, shelter, and a water dish.
 All care otherwise follows similar protocols to adults (see above).
-Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatisation.
+
+Two weeks prior to the training phase (see details below), lizards were moved to the experimental arena for acclimatisation.
 The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the sides and a water dish on the other.
-These new enclosures were placed in two rooms in 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
-Although the conditions in the new room were identical to the main room, the number of lizards per species and treatment in each rack was counterbalanced to control for any potential effect of the room or the position of the lizard in the rack.
-During acclimatisation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
+These arenas were placed in two rooms in 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
+Although the conditions in the experimental rooms were identical to the colony room, the number of lizards per species and treatment in each rack was counterbalanced to control for any potential effect of the room or the position of the lizard in the rack.
+During acclimatisation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
 
-#### CORT and Temperature manipulation  
-To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' - 23ºC ± 3ºC or 'Hot' - 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
-We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
-We selected these doses based on previous studies publishing yolk CORT concentrations in other ovipaorus reptiles [@lovern2008effects; @hanover2019corticosterone] and our own unpublished data.
-CORT concentration represents 2 standard deviations above the mean natural concentration.
-After the treatment, the eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching.
+#### CORT and Temperature Manipulation  
+To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (‘Cold’ - 23ºC ± 3ºC or ‘Hot’ - 28ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
+We topically dosed eggs with a CORT solution (10pg/mL) or a control treatment (100% ethanol).
+Corticosterone treatments were made by dissolving crystalline corticosterone (Sigma, Cat.
+No.
+C2505) in 100% ethanol.
+To dose eggs, we applied 5µl of solutions to eggshells using a micropipette.
+We selected these doses based on previous studies publishing yolk CORT concentrations in other ovipaorus reptiles [@lovern2008effects; @hanover2019corticosterone].
+CORT treatment increased mean yolk CORT levels ~3.7x higher than control eggs [@crino2024eggs].
+After the treatment, the eggs were incubated in one of the two previously mentioned temperature regimes (‘Cold’ or ‘Hot’) until hatching.
 The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
@@
 #### Learning  
-To estimate learning skills, we tested skinks' ability to locate a food reward in an colour-associative learning task (@fig-Methods C, D).
+To estimate learning skills, we tested skinks' ability to locate a food reward in a colour-associative learning task (@fig-Methods C, D).
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
-We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A.
-domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods C, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods C, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
+We divided this training phase into three stages: the first stage where lizards had to eat a small, frozen cricket (*A.
+domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods C, Stage 1); the second stage where the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods C, Stage 2); and the third where the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp (Fig.
 @fig-Methods C, Stage 3).
@@
 At the end of each trial, we recorded whether the cricket had been consumed or not.
-Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials to ensure lizards' consistency.
-This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
-
-In the associative learning phase, we trained lizards to associate between colour and a food reward (Fig.
-@fig-Methods D).
-The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in colour.
+A trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials to ensure lizards' consistency.
+This phase lasted 38 days until all the lizards learned to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
+
+During the associative learning phase, we trained lizards to associate colour with a food reward (@fig-Methods D).
+This test was similar to the third stage of the training phase, but here lizards were presented with three 3D printed ramps that differed in colour.
 We placed the food reward (small, frozen, *A.
-domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
-The food reward was placed insidde all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals.
-The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-To control for potential colour preference that could bias our results we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one, while for the other group we assigned red as correct.
-In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
+domestica* crickets) inside the wells of the three ramps, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
+The food reward was placed inside all three wells to avoid lizards using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals.
+The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
+To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was blue, while other group was assigned red as correct.
+In all trials, the position of the ramps was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
 Lizards were tested in this task once a day for 35 days.
 
-The full task took place between the 6^th^ of March until the 17^th^ of May 2023, and tests were performed between 11 to 12 am when the lizards were active.
+```{r, fig-Methods}
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the experiment.
+Panel A shows the early environment manipulation.
+In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks.
+Panel C shows the habituation process with the three different stages.
+And in panel D, the associative task with the three different 3D printed ramps.
+White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+```
+
+The experiment took place between the 6^th^ of March until the 17^th^ of May 2023, and tests were performed between 11 AM to 12 PM when the lizards were active.
 Trials in the learning phase were recorded with CCTV systems always using the same camera per individual.
@@
 We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
-We considered a trial failed if there was no choice in one hour of recordingcored those trials as NA.
-We excluded from our analyses those individuals with more than 15 trials failed (i.e.
-they did not make a choice), and we considered the first trial for each individual to be the first one where the a choice was made.
-
-```{r, fig-Methods}
-#| label: fig-Methods
-#| fig.cap: "Experimental design of the experiment.
-Panel **A** shows the early environment manipulation.
-In panel **B**, the measurements of the 3D-printed ramps employed in the habituation and learning tasks.
-Panel **C** shows the habituation process with the three different stages.
-And in panel **D**, the associative task.
-White lids in **D** show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG1.png")
-
-```
+We considered a trial failed if there was no choice after one hour of recording and scored those trials as NA.
+We excluded from our analyses those individuals that scored 15 trials out of the 35 trials as NA.
+For each individual, we considered their first trial to be the first one where a choice was made.
 
@@
 We performed the analyses for species separately.
-Because preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red).
-Therefore, we run a total of four different Bayesian multilevel models using the brm function from the brms package [@burkner2017brms] in Quarto [@Allaire_Quarto_2022].
+As preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red).
+Therefore, we run a total of four different Bayesian multilevel models using the brm function from the brms package [@burkner2017brms] in R (version 2.8.2) [@R].
 We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
@@
 We included a random intercept and slope (trial) for each lizard in our models.
-Furthermore, even if our split clutch design should control for potential effects of paternity, we also incorporated the clutch identity as a random factor.
-Because eggs were collected during half of the breeding season and both species do not lay more than two clutches [@chapple_know_2011; @chapple_biology_2014], each clutch likely come from a unique mother, and so, clutch identity captures potential maternal effects.
-Learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature can affect hatching time, we explored the effects of age on learning.
+We also incorporated the clutch identity as a random factor.
+_L.
+delicata_ lays one clutch per breeding season while _L.
+guichenoti_ lays up to two [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014] Since egg collection was done during half of the breeding season, each clutch likely come from a unique mother, and so, clutch identity captures potential maternal effects.
+In adition, previous studies indicate that clutches are typically fertilized by a single male, although sperm storage can occur [@kar2024heritability].
+Considering our partial split-clutch design and the expectation that maternal effects are likely to be more pronounced than paternal effects in these species, incorporating clutch as a random factor should effectively account for parental condition.
+Learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature will affect hatching time [@zhang2023developmental], we explored the effects of age on learning.
 Lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L.
@@
 We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
-Learning reates were estiamated as the choice-trial slope, obtained for each treatment by using the ‘trial’ estimates and its interaction with hormone and temperature.
+slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
 Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
-We employed the posterior predictive Markov chain Monte Carlo (p~mcmc~) to test the hypothesis that slopes and slopes contrasts were different from zero.
+p~mcmc~ test the hypothesis that slopes and slopes contrasts are different from zero.
 We considered statistical significance if p~mcmc~ < 0.05.
@@
 Final sample sizes per treatment and species are listed in @fig-deli and @fig-guich (figures for both species with the raw data are included in the Supplementary Material).
-Mean slopes per treatment for both species are provided in Table 1 in the Supplementary Material.
+Mean slopes (denoted as β throughout) per treatment for both species are provided in Table 1 in the Supplementary Material.
 ```{r, models}
@@
 This "learning rate" consists on the slope of the posterior of the Trial parameter.
-The slope is the rate at which the probability of choosing the correct feeder increases with each trial.
+The slope is the rate at which the probability of choosing the correct ramp increases with each trial.
 The slope is obtained by adding the posterior of the Trial parameter to the posterior of the interaction between Trial and the treatment (cort and temp).
@@
 
-We found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to slopes of individuals assigned to the group 'Red' for _L.
-delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; slope contrast: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
-guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
+We found that learning slopes were lower when the blue ramps were the correct choice compared to slopes of individuals assigned to the red group for _L.
+delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
+guichenoti_ (mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
 However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material) that could be affecting the estimated slopes.
-As such, we analysed the between treatments differences for each group separately.
+As such, we analyzed the differences between treatments for each group separately.
 
 For those _L.
-delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
-Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
+delicata_ assigned to group red, we did not find any significant differences between hormones (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
+Similarly, those assigned to blue were not afected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
 
@@
 #| label: fig-deli
-#| fig.cap: "Results for Lampropholis delicata for both colour groups 'Red' (A,B) and 'Blue' (C, D).
-Panels A and C show the predicted probability of choosing the correct feeder first over trials.
-The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+#| fig.cap: "Results for Lampropholis delicata for both colour groups red (A,B) and blue (C, D).
+Panels A and C show the predicted probability of choosing the correct ramp first over trials.
+The lines represent the mean predicted probability of choosing the correct ramp first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
 The different colours indicate the different treatments.
@@
 In _L.
-guichenoti_, we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the 'Red' group (@fig-guich A, B); and we did not find any significant effect of hormone (Control - CORT = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to 'Blue' (@fig-guich C, D).
+guichenoti_, we did not find any significant differences between hormone treatments (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the red group (@fig-guich A, B); and we did not find any significant effect of hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to blue either (@fig-guich C, D).
 
@@
 #| label: fig-guich
-#| fig.cap: "Results for Lampropholis guichenoti for both colour groups 'Red' (A,B) and 'Blue' (C, D).
-Panels A and C show the predicted probability of choosing the correct feeder first over trials.
-The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+#| fig.cap: "Results for Lampropholis guichenoti for both colour groups red (A,B) and blue (C, D).
+Panels A and C show the predicted probability of choosing the correct ramp first over trials.
+The lines represent the mean predicted probability of choosing the correct ramp first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
 The different colours indicate the different treatments.
@@
 
-Finally, we also did not find any significant differences when we compared the estimated slopes between species for 'Red' group(_L.
-delicata_ mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot), 0.975), 3)`]; _L.
-guichenoti_ mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.975), 3)`]; _L.
-delicata_ - _L.
-guichenoti_ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the 'Blue' one (_L.
-delicata_ mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; _L.
-guichenoti_ mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; _L.
-delicata_ - _L.
-guichenoti_ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`).
+Finally, we also did not find any significant differences when we compared the estimated slopes between species for red group (mean β~_L.
+delicata_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)), 3)`, 95% CI β~_L.
+delicata_~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot), 0.975), 3)`]; mean β~_L.
+guichenoti_~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, 95% CI β~_L.
+guichenoti_~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.975), 3)`]; β~_L.
+delicata_~ - β~_L.
+guichenoti_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the blue group (mean β~_L.
+delicata_~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~_L.
+delicata_~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~_L.
+guichenoti_~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~_L.
+guichenoti_~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; β~_L.
+delicata_~ - β~_L.
+guichenoti_~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`).
 
@@
 
-The scope of the present study was to investigate the effects of early environment on lizards' learning using two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+The aim of the present study was to investigate the effects of early environment on lizards' learning using two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 In adition, we found that the learning rates varied depending on the colour assigned to the correct choice, at least for _L.
-delicata_, with lizards assigned to blue feeders performing worse compared to the red group.
+delicata_, with lizards assigned to blue ramps performing worse compared to the red group.
 
@@
 For _L.
-delicata_, performance was proficient when the reward was linked to red feeders, but learning slopes for lizards assigned to the blue condition did not differ from zero.
+delicata_, performance was proficient when the reward was linked to red ramps, but learning slopes for lizards assigned to the blue condition did not differ from zero.
 In contrast, _L.
@@
 delicata_ were not able to associate the blue ramp with the reward.
-However, our results could be consequence of an initial bias in lizards' choice.
+However, our results could be a consequence of an initial bias in lizards' choice.
 The analyses presented in the supplemenatry material show that, overall, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue condition.
@@
 
-Because there was a possibility that this bias towards blue feeders was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see Supplementary Material).
+Because there was a possibility that this bias towards blue ramps was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see Supplementary Material).
 Since these results show no similarities between the white and blue ramps, we consider the preference towards blue to not be a derivate from our experimental design.
-Rather, it seems likely that lizards innately prefer the blue feeders.
+Rather, it seems likely that lizards innately prefer the blue ramps.
 The species confidence hypothesis posits that animals should bias their attention towards colours they are familiar with [@putman2017fear].
 For instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
-However, to the best of our knowledge, noone has reported a colour bias in _L.
+Nevertheless, to the best of our knowledge, there has been no reported colour bias in _L.
 delicata_ or _L.
 guichenoti_ before; and blue colouration is not considered to be involved in intraspecific communication in these species [@torr1996patterns; @chapple_biology_2014].
-Still, we recommend to select carefully the colours employed in associative tasks when relying on visual stimuli.
+Still, we recommend to carefully select the colours employed in associative tasks when relying on visual stimuli.
 Despite this, when lizards assigned to blue or red were analysed separately, the between treatments comparissons remain the same in both conditions and species.
@@
 #### Effect of prenatal CORT on learning
-Prenatal CORT was expected to have a negative effect on learning, declining CORT-treated lizards performance in the learning task [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn; @bebus_associative_2016].
-However, we did not find any significant difference between hormone treatments in none of the two species.
+Prenatal CORT was expected to have a negative effect on learning, declining CORT-treated lizards' performance in the learning task [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn; @bebus_associative_2016].
+However, we did not find any significant difference between hormone treatments in either of the two species.
 Our results are consistent with other experiments that showed no effect of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016].
@@
 For instance, in European starlings, males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn].
-Similarly, while Scrub-jays that had lower CORT levels as nestlings performed better on an associative learning test as adults, but not on a reversal learning task [@bebus_associative_2016].
+Similarly, Scrub-jays that had lower CORT levels as nestlings performed better on an associative learning test as adults, but not on a reversal learning task [@bebus_associative_2016].
 We must acknowledge the possibility that prenatal CORT does not affect the brain regions involved in coding associative learning in these species, and future studies should focus on examining the effect of early-life stress on different cognitive domains.
@@
 guichenoti_, associative learning appears to be robust to incubation temperature.
-Our results, therefore, do not align with the outcome observed in previous experiment.
+Our results, therefore, do not align with the outcome observed in previous experiments.
 However, the effect of prenatal temperature in cognition, and brain physiology and structure has been investigated only in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how thermal early environment can affect cognitive abilities.
 
-In our analyses, we did not include sex as a factor for several reasons: first, lizads were tested before sexual maduration; and second, previous studies have found weak evidence for sex-dependent learning in reptiles [@szabo_sex_meta].
-In fact, incubation temperature was not sex-depedent when learning abilities were tested in the Eastern three-lined skink (_Bassiana dupeyerri_) [@amiel_hotter_2012; @clark_colour_2014].
+In our analyses, we did not include sex as a factor for several reasons: first, lizards were tested before sexual maturation; and second, previous studies have found weak evidence for sex-dependent learning in reptiles [@szabo_sex_meta].
+In fact, in the Eastern three-lined skink (_Bassiana dupeyerri_) the effect of incubation temperature on learning is not sex-dependent [@amiel_hotter_2012; @clark_colour_2014].
 However, there is previous evidence for interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
-Furthermore, in _B.
-dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal, where individuals under cold incubation temepratures develop male phenotypes while retaining female genotypes [@dissanayake2021effects].
-Such effects were not easily accounted for in these experiments making it challenging to understand whether sex or temperature was the cause of learning differences [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Similarly, not accounting for sex in our analyses could be masking potential interactions between temperature and sex in shaping learning abilities.
+Notably, in _B.
+dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal, where individuals under cold incubation temperatures develop male phenotypes while retaining female genotypes [@dissanayake2021effects].
+As a result, even when examining the interactive effects of sex and temperature [@amiel_hotter_2012; @clark_colour_2014], the results could be confounded by the mismatch between genotype and phenotype in _B.
+dupeyerri_ [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Although sex-reversal does not occur in _L.
+delicata_ or _L.
+guichenoti_, not accounting for sex in our analyses could be masking potential interactions between temperature and sex in shaping learning abilities.
 Future research should investigate the potential interactive impacts of sex and incubation temperature on cognitive abilities.
@@
 In the experiment conducted by @bezzina2014does, both species failed to complete the associative learning task under the authors' criterion, while in our experiment both species completed the task, exhibiting similar learning rates.
-Complexity, experimental design, or the criterion employed to define learning could be tha major cause of the discrepancies between ours and @bezzina2014does's findings.
+Complexity, experimental design, or the criterion employed to define learning could be the major cause of the discrepancies between ours and @bezzina2014does's findings.
 Developing common strategies and approaches to assess learning in animals could help understand how learning abilities are shaped in different taxa or under different environments.
@@
 
-Future research should continue exploring the potential effects of prenatal corticosterone (CORT) and temperature on cognitive function, but with a focus on interactions between early environmental factors and sex, as well as the specific nature of the cognitive tasks employed.
+Future research should continue exploring the potential effects of prenatal corticosterone (CORT) and temperature on cognitive function, but with a focus on interactions between early environmental factors and sex, as well as the type of cognitive tasks employed.
 Furthermore, it is crucial to explore how these treatments influence brain function at a neurological level.
@@
 We thank the help and assistance of our lab technicians Benjamin Durant and Michelle Stephens for taking care of the lizards.
-We are also grateful to ACTHA for the grant for the 3D printed feeders, and we also thank ANU MakerSpace, where we designed and built the prototypes of the 3D printed feeders.
+We are also grateful to ACTHA for the grant for the 3D printed ramps, and we also thank ANU MakerSpace, where we designed and built the prototypes of the 3D printed ramps.
 Finally, we wish to acknowledge the anonymous reviewers for their valuable feedback on the manuscript.
@@
 To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercepts  from our posterior distributions.
-We first estimated the predicted probability of choosing the correct feeder first in the first trial, by using the formula:
+We first estimated the predicted probability of choosing the correct ramp first in the first trial, by using the formula:
 $$\text{Probability} = \frac{e^{Intercept}}{1 + e^{Intercept}}$$
 
-Second, we tested the hypothesis that the estimated probability was higher than 0.33 (the probability expected by chance of choosing the correct feeder) using pmcmc.
-If the estimated probability is above 0.33.
-we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes.
+Second, we tested the hypothesis that the estimated probability was higher than 0.33 (the probability expected by chance of choosing the correct ramp) using pmcmc.
+If the estimated probability is above 0.33 we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes.
 The results per treatment are summarized in Table 2.
@@
 Table 2.
-Probability of choosing the correct feeder in the first trial when the correct feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
+Probability of choosing the correct ramp in the first trial when the correct ramp was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
 p~mcmc~ tested the hypothesis that the probability is >0.33.
@@
 #| label: tbl-bias
-#| tbl-cap: "Probability of choosing the correct feeder in the first trial when the correct feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
+#| tbl-cap: "Probability of choosing the correct ramp in the first trial when the correct ramp was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
 p~mcmc~ tested the hypothesis that the probability is >0.33.
@@
   pivot_wider(names_from = Group, values_from = c(prob_choice, p_value)) %>% #To split the df in Red and Blue
-  select(Specie, Treatment, prob_choice_Blue, p_value_Blue, prob_choice_Red, p_value_Red) %>%
+  select(Specie, Treatment, prob_choice_Red, p_value_Red, prob_choice_Blue, p_value_Blue) %>%
   arrange(Specie, Treatment) %>% # To arrange the rows the way I wantdata.frame()
@@
 
-On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue for _L.
+On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct ramp was blue for _L.
 delicata_ (mean Prob choice = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`) but not for _L.
@@
 To test if the bias towards blue was something acquired during training, we compared the light spectrum of the ramps used in the associative task and the white ones used during habituation.
-We took three measurements of ten feeders per colour with a spectophotometer, and then analysed the spectrum and the perceived differences in colour using the package pavo.
-The spetrum of each type of feeder are shown in @fig-spectrum; the perceived chromatic constrasts between feeders are shown in @fig-perceived1 and @fig-perceived2.
+We took three measurements of ten ramps per colour with a spectophotometer, and then analysed the spectrum and the perceived differences in colour using the package pavo.
+The spetrum of each type of ramp are shown in @fig-spectrum; the perceived chromatic constrasts between ramps are shown in @fig-perceived1 and @fig-perceived2.
 ```{r, fig-spectrum}
@@
 # For importing the files, change the extension of the .jaz files to .txt files!  
-# Import spec data for pablos feeders - CHNAGE TO WHERE YOUR FILES ARE LOCATED
+# Import spec data for pablos ramps - CHNAGE TO WHERE YOUR FILES ARE LOCATED
 specs <- getspec("./Others/Feeders", lim = c(300,700), ext = 'txt') %>%
@@
 #| label: fig-perceived1
-#| fig.cap: "Perceived chromatic contrasts between feeders."
+#| fig.cap: "Perceived chromatic contrasts between ramps."
 #
@@
 #
-# Apply this over the feeder data visual as the visual system, achromatic is the receptor sensitivity, illum is the illuminate (here using an ideal white illuminate preset), bkg is the background against which we are measuring (here using an ideal background with no influence).
+# Apply this over the ramp data visual as the visual system, achromatic is the receptor sensitivity, illum is the illuminate (here using an ideal white illuminate preset), bkg is the background against which we are measuring (here using an ideal background with no influence).
 Other conditions are applied as used in the P mystaceus paper.
 # Does produce an error about luminance but this is noted on the original P mystaceus paper code and should be okay
-# summary(feeders_lizardview) can be used to check what conditions were applied in the visual model
+# summary(ramps_lizardview) can be used to check what conditions were applied in the visual model
 feeders_lizardview <- vismodel(specs, visual = liz_vis, achromatic = "l", illum = "ideal", bkg = "ideal", vonkries = TRUE,   relative = FALSE, qcatch = "fi")
 #                             
-# Calculate colour distances between all feeder measurements
+# Calculate colour distances between all ramp measurements
 coldistance_feeders <- coldist(feeders_lizardview,achro = TRUE, noise = "neural", n = c(1, 1, 3.5, 6),  weber = 0.1)
@@
 #
-# Plot the colour differences between the feeders: 
+# Plot the colour differences between the ramps: 
 # Note - above 1 is expected to be visually different under the selected visual system (here, lizard view)
@@
   ylab("Chromatic Contrast (dS)") +
-  xlab("Feeder Colours Comparison") +
+  xlab("ramp Colours Comparison") +
  scale_fill_manual(values =c("B/G" = 'steelblue',  "B/R" = 'purple', "B/W" = 'lightblue', "G/R" = 'brown', "G/W" = 'lightgreen', "R/W" = 'red')) +
@@
   ylab("Achromatic Contrast (dL") +
-  xlab("Feeder Colours Comparison") +
+  xlab("ramp Colours Comparison") +
  scale_fill_manual(values =c("B/G" = 'steelblue',  "B/R" = 'purple', "B/W" = 'lightblue', "G/R" = 'brown', "G/W" = 'lightgreen', "R/W" = 'red')) +
@@
 
-Table 3. Results for _L. delicata_ assigned to red feeders when the model included the age:
+Table 3. Results for _L. delicata_ assigned to red ramps when the model included the age:
 ```{r, tbl-agedeli_red, results='asis', out.widht = "26cm"}
@@
 
-Table 4. Results for _L. delicata_ assigned to blue feeders when the model included the age:
+Table 4. Results for _L. delicata_ assigned to blue ramps when the model included the age:
 ```{r, tbl-agedeli_blue, results='asis', out.widht = "26cm"}
@@
 
-Table 5. Results for _L. guichenoti_ assigned to red feeders when the model included the age:
+Table 5. Results for _L. guichenoti_ assigned to red ramps when the model included the age:
 ```{r, tbl-ageguich_red, results='asis', out.widht = "26cm"}
@@
 
-Table 6. Results for _L. guichenoti_ assigned to blue feeders when the model included the age:
+Table 6. Results for _L. guichenoti_ assigned to blue ramps when the model included the age:
 ```{r, tbl-ageguich_blue, results='asis', out.widht = "26cm"}

### 2024-09-14 .vdoc.r

@@ -87,11 +87,21 @@ cat("\\newpage")
 #
 #
 #
+#
+#
+#
+#
+#
+#
+#
+#
 #| label: fig-Methods
-#| fig.cap: "Experimental design of the experiment. Panel **A** shows the early environment manipulation. In panel **B**, the measurements of the 3D-printed ramps employed in the habituation and learning tasks. Panel **C** shows the habituation process with the three different stages. And in panel **D**, the associative task. White lids in **D** show the ramps where the food reward was not attainable."
+#| fig.cap: "Experimental design of the experiment. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks. Panel C shows the habituation process with the three different stages. And in panel D, the associative task with the three different 3D printed ramps. White lids in D show the ramps where the food reward was not attainable."
 
 knitr::include_graphics("./Others/LEARN_FIG1.png")
 
+#
+#
 #
 #
 #
@@ -153,7 +163,7 @@ write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
 #
 #
 #| label: results
-# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment. This "learning rate" consists on the slope of the posterior of the Trial parameter. The slope is the rate at which the probability of choosing the correct feeder increases with each trial. The slope is obtained by adding the posterior of the Trial parameter to the posterior of the interaction between Trial and the treatment (cort and temp). 
+# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment. This "learning rate" consists on the slope of the posterior of the Trial parameter. The slope is the rate at which the probability of choosing the correct ramp increases with each trial. The slope is obtained by adding the posterior of the Trial parameter to the posterior of the interaction between Trial and the treatment (cort and temp). 
 ## 1) L. delicata
 ### Group = red
 dar_CORTCold <- deli_red$b_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
@@ -184,7 +194,7 @@ gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial
 #
 #
 #| label: fig-deli
[…]

### 2024-09-15 ms.qmd
Update ms.qmd

@@
   docx: 
-    reference-doc: "./bib/tmpl.docx"
     number_sections: true
@@
 Thus, glucocorticoids and the thermal environment are predicted to have interactive effects on the development of learning functions in animals.
-Here, we investigated the combined effects of corticosterone (CORT) and elevated temperature during development on learning in juveniles of two species of lizards, _Lampropholis delicata_ and _L.
+Here, we investigated the combined effects of corticosterone (CORT) - the main GC in reptiles - and elevated temperature during development on learning in juveniles of two species of lizards, _Lampropholis delicata_ and _L.
 guichenoti_.
@@
 However, both species learned the task at the same rate independently of treatment.
-This suggests that associative learning skills in these two species is robust to prenatal temperature and CORT.
-We also found that lizards learned slower if food rewards were associated with blue coloured ramps compared to red and green, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
+This suggests these two species may have evolved mechanisms to maintain learning abilities despite prenatal challegnes.
+We also found that lizards did not learn when food rewards were associated with blue-coloured ramps, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
 
 ## Introduction
-Cognition is the set of processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
-These cognitive processes are fundamental to foraging, mate selection, antipredatory strategies, and social behaviours, all of which are crucial for survival and reproduction [@dukas_evolutionary_2004].
+Cognition is a set of processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
+These processes are fundamental to foraging, mate selection, antipredatory strategies, and social behaviours, all of which are crucial for survival and reproduction [@dukas_evolutionary_2004].
 Particularly, learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
-Learning enables animals to adapt their behavior to environmental conditions and thus can have cascading effects on population dynamics by influencing survival rates or reproductive success [@ward2016ecological; @welklin2024spatial].
-
+Learning allows animals to adapt their behavior to environmental conditions and thus can have cascading effects on population dynamics by influencing survival rates or reproductive success [@ward2016ecological; @welklin2024spatial].
 However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, gut microbiota, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
 These variations can further affect population dynamics, as differences in learning ability may lead to unequal responses to environmental pressures [@ward2016ecological; @welklin2024spatial].
-For example, fast learners may better exploit resources or avoid dangerous stimuli while those with lower learning capabilities might struggle to adapt.
+For example, fast learners may better exploit novel resources or avoid new dangerous stimuli, while those with lower learning capabilities might struggle to adapt to environmental changes.
 This could affect their survival and reproductive output, ultimately influencing population growth rates and stability [@ward2016ecological; @welklin2024spatial].
@@
 
-Developing conditions are especially relevant in shaping learning abilities because the brain is highly susceptible to environmental inputs during early stages of development [@zhu_prenatal_2004].
+Developing conditions are especially relevant in shaping learning abilities because the brain is highly susceptible to environmental inputs during early stages of life [@zhu_prenatal_2004].
 Impacts on brain development can have long-lasting effects on cognition, potentially influencing an individual's ability to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
-For example, maternal condition during gestation or pre-oviposition can influence offspring's phenotype through the transmission of hormones, nutrients, or other molecules [@moore_mothers_2019].
+For example, the state of the mother can influence offspring's phenotype beyond genetic transmission through nest-site selection, provisioning, or the transmission of hormones or nutrients [i.e., 'maternal effects' @moore_mothers_2019]; and the developing brain is not exent of these effects.
 
@@
 In vertebrates, GCs regulate metabolism and maintain homeostasis in response to disturbances [i.e., ‘the stress response’ @sapolsky_how_2000].
-Under stressful situations, animals respond by instigating adaptive physiological and behavioural adjustments mediated by GCs.
-These GCs can be
-transmitted directly from the parents to their offspring with different effects on offspring phenotype [@Crino_2023].
+Under stressful situations, animals react by instigating adaptive physiological and behavioural adjustments mediated by GCs.
+These GCs can be transmitted directly from the parents to their offspring with different effects on offsprings' phenotype [@Crino_2023].
 Elevations in GCs during early stages of development typically result in altered neurogenesis, brain structure, and metabolic activity that in most cases are related to decreased learning abilities [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009; @eaton2015mild; @farrell_developmental_2015-learn; @farrell_developmental_2016].
-For instance, prenatal stress in Rats (_Rattus norvegicus_) induced reduction of neurogenesis in the dentate gyrus associated to impairments in hippocampal-related spatial tasks[@lemaire_prenatal_2000].
+For instance, prenatal stress in rats (_Rattus norvegicus_) induced reduction of neurogenesis in the dentate gyrus associated to impairments in hippocampal-related spatial tasks [@lemaire_prenatal_2000].
 However, factors like sex or the nature of the learning task can affect the direction and magnitude of the effects of prenatal exposure to elevated GCs [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016; @farrell_developmental_2016].
@@
 In ectotherms, early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits including growth, metabolism, or learning abilities [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
-For instante, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while velvet geckos incubated at temperatures beyond their natural thermal range are worse learners than those incubated at colder temperatures [@dayananda_incubation_2017; @abayarathna_effects_2020].
-These effects are likely mediated by changes in neural structure and function, as high temperatures can increase neural density and metabolic activity in the brain [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021].
+For instance, Port Jackson sharks (_Heterodontus portusjacksoni_) incubated at 23.6ºC took fewer days to reach a learning criterion in a numerical learning task than those incubated at 20.6ºC [@vila_pouca_quantity_2019].
+In skinks, high incubation temperatures are generally associated with faster learning rates [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]; but velvet geckos (_Amalosia lesueurii_) incubated at temperatures beyond their natural thermal range are worse learners than those incubated at colder temperatures [@dayananda_incubation_2017; @abayarathna_effects_2020].
+The effects of incubation temperature in reptiles are likely mediated by changes in neural structure and function, as high temperatures increase neural density and metabolic activity in the brain [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021].
 
 GCs can play a pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
-This implies that the effects of GCs and temperature on learning could be interdependent, with the impact of one factor being modulated by the other.
+Additionally, GCs and temperatures can act upon similar physiological mechanisms [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021].
+This implies that the effects of GCs and temperature could be interdependent, with the impact of one factor being modulated by the other.
 However, the interactive effects of GCs and temperature on learning abilities remain unexplored.
@@
 delicata* and *L.
-guichenoti* respectively, are housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
-Enclosures are provided with non-stick matting, shelter, and several small water dishes.
-Water is given daily, and they are fed approximately 40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
-Crickets are dusted with calcium weekly and multivitamin and calcium biweekly.
-To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
-Room temperatures are set to 22-24 ºC, and the warm side of enclosures is usually at 32 ºC.
-
-*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
+guichenoti* respectively, were housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+Enclosures were provided with non-stick matting, shelter, and several small water dishes.
+Water is given daily, and they were fed approximately 40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
+Crickets were dusted with calcium weekly and multivitamin and calcium biweekly.
+To ensure a temperature gradient, we employed a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
+Room temperatures were set to 22-24 ºC, and the warm side of enclosures was usually at 32 ºC.
+
+*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside.
+These boxes were placed in one side of the communal enclosures (see above).
 We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm, mass using a digital scale (OHAUS, Model spx123; ± 0.001g error), and assigned individual IDs to the clutch and each egg.
+After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001g error).
+Then we assigned individual IDs to the clutch and each egg.
 Eggs were treated with CORT or vehicle (see CORT and Temperature Manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
@@
 
-*Hatchlings* -- After hatching, we measured juveniles' SVL and Tail Length (TL) with a ruler to the nearest mm and mass using a digital scale (OHAUS, Model spx123; ± 0.001g error).
+*Hatchlings* -- After hatching, we measured juveniles' SVL and Tail Length (TL) with a ruler to the nearest mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001g error).
 Hatchlings were then housed individually in small enclosures (18.7L x 13.2W x 6.3H cm) provided with non-stick matting, shelter, and a water dish.
@@
 Although the conditions in the experimental rooms were identical to the colony room, the number of lizards per species and treatment in each rack was counterbalanced to control for any potential effect of the room or the position of the lizard in the rack.
-During acclimatisation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
+During acclimatisation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin, and water was supplied *ad libitum*.
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
@@
 To estimate learning skills, we tested skinks' ability to locate a food reward in a colour-associative learning task (@fig-Methods C, D).
-First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
-We divided this training phase into three stages: the first stage where lizards had to eat a small, frozen cricket (*A.
-domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods C, Stage 1); the second stage where the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods C, Stage 2); and the third where the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp (Fig.
-@fig-Methods C, Stage 3).
-Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
+First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical in size and shape to the ones used during the associative task.
+We divided the training phase into three stages: the first stage where lizards had to eat a small, frozen cricket (*A.
+domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods C, Stage 1); the second stage where the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods C, Stage 2); and the third where the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp (@fig-Methods C, Stage 3).
+Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later, when we took it away.
 At the end of each trial, we recorded whether the cricket had been consumed or not.
@@
 During the associative learning phase, we trained lizards to associate colour with a food reward (@fig-Methods D).
-This test was similar to the third stage of the training phase, but here lizards were presented with three 3D printed ramps that differed in colour.
-We placed the food reward (small, frozen, *A.
-domestica* crickets) inside the wells of the three ramps, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
-The food reward was placed inside all three wells to avoid lizards using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals.
-The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was blue, while other group was assigned red as correct.
+This test was like the third stage of the training phase, but here lizards were presented with three 3D printed ramps that differed in colour.
+Ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
+The food reward (small, frozen, *A.
+domestica* crickets) was placed inside the wells of the three ramps, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
+This way, we controlled for the use of prey chemical cues, as the lids had a series of small holes on the top to allow the release of those chemicals.
+To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was blue, while the other group was assigned the red ramp as correct.
 In all trials, the position of the ramps was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
@@
 We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
-We considered a trial failed if there was no choice after one hour of recording and scored those trials as NA.
+We considered a trial failed if there was no choice after one hour of recording, and scored those trials as NA.
 We excluded from our analyses those individuals that scored 15 trials out of the 35 trials as NA.
@@
 We performed the analyses for species separately.
-As preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red).
+Also, as preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red).
 Therefore, we run a total of four different Bayesian multilevel models using the brm function from the brms package [@burkner2017brms] in R (version 2.8.2) [@R].
@@
 delicata_ lays one clutch per breeding season while _L.
-guichenoti_ lays up to two [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014] Since egg collection was done during half of the breeding season, each clutch likely come from a unique mother, and so, clutch identity captures potential maternal effects.
-In adition, previous studies indicate that clutches are typically fertilized by a single male, although sperm storage can occur [@kar2024heritability].
+guichenoti_ lays up to two [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014].
+Since egg collection was done during half of the breeding season, each clutch likely come from a unique mother, and so, clutch identity captures potential maternal effects.
+In addition, previous studies indicate that clutches are typically fertilized by a single male, although sperm storage can occur [@kar2024heritability].
 Considering our partial split-clutch design and the expectation that maternal effects are likely to be more pronounced than paternal effects in these species, incorporating clutch as a random factor should effectively account for parental condition.
-Learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature will affect hatching time [@zhang2023developmental], we explored the effects of age on learning.
+
+Learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature will affect hatching time [@zhang2023developmental], we explored the effects of age on learning by including it as a predictor.
 Lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L.
@@
 guichenoti_.
-However, when this variable was included in the models we did not find any significant effect of age (see Supplementary material).
+However, when this variable was included in the models, we did not find any significant effect of age (see Supplementary material).
 As such, we present models without age as a fixed effect.
 
-We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
+We used the posterior distributions of parameters to test for differences in learning rate between treatments and species.
 slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
@@
 
-The aim of the present study was to investigate the effects of early environment on lizards' learning using two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
-guichenoti_).
-In our experiment, we manipulated CORT levels and temperature during incubation, and we then subjected hatched animals to a colour-associative learning task using food as a reward.
-We expected prenatal CORT and thermal environment to have combined effects on lizards' performance in the test.
-However, we did not find any significant effects of the experimental conditions.
-We found that most individuals from both species learned to associate a colour with a food reward and that the learning process ocurred at the same rate regardless of the early environment, suggesting that learning abilities in these skinks are robust to prenatal CORT and temperature.
-In adition, we found that the learning rates varied depending on the colour assigned to the correct choice, at least for _L.
-delicata_, with lizards assigned to blue ramps performing worse compared to the red group.
+Associative learning in _L.
+delicata_ and _L.
+guichenoti_ is robust to elevations in prenatal CORT and incubation temperature.
+We predicted that elevating CORT levels in eggs or incubating them at colder temperatures would decrease learning slopes, and that warmer incubation temperatures would relax the effects of CORT elevations.
+In contrast to our predictions, both species learned to associate a colour with a food reward at the same rate regardless of the experimental treatments.
+This suggests that these species may have evolved mechanisms to buffer against early environmental stressors and maintain learning performance despite prenatal challenges.
+
+In addition, we found that the learning rates varied depending on the colour assigned to the correct choice, at least for _L.
+delicata_, with lizards assigned to blue ramps showing lower learning slopes than in the red group.
+This outcome manifests the need to consider the potential effects of colour biases in the design of cognitive tasks.
+
+#### Effect of prenatal CORT on learning
+Prenatal CORT was predicted to have a negative effect on learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn; @bebus_associative_2016].
+However, we did not find any significant difference between hormone treatments in either of the two species.
+Our results are consistent with other experiments that showed no influence of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016; @farrell_developmental_2016] and suggest that _L.
+delicata_ and _L.
+guichenoti_ may have evolved some strategies to buffer the impacts of prenatal stress.
+
+Alternatively, our observations could be obscured by other variables that are known to influence the extent and direction of these outcomes.
+[@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016; @farrell_developmental_2016].
+GCs are known to have hormetic effects.
+Generally, low elevations or short exposure to GCs improve the rate at which animals learn while high concentrations or exposure to GCs during long periods have the opposite effects [@du_dynamic_2009; @mcewen_brain_2012].
+When using the same dose and application methods in eggs of _L.
+delicata_, @crino2024eggs found CORT treatment had sustained effects on mass and mitochondrial activity, but not baseline CORT.
+In contrast, lower CORT concentration did not affect mass or mitochondrial activity, but increased CORT baseline levels [@crino2024eggs].
+This suggests that high elevations in CORT could affect learning through permanent changes in brain function (programmatic effects) while lower doses can result in lifelong elevation of baseline CORT, affecting learning through activational effects.
+Our findings indicate that associative learning in _L.
+delicata_ and _L.
+guichenoti_ is robust to the programmatic effects of high CORT elevations, but we cannot exclude the possibility that lower concentrations may affect learning abilities.
+
+Conversely, the absence of significant effects of prenatal CORT on learning could be due to the cognitive task employed, as some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
+GCs action involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed unevenly in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
+For instance, in european starlings (_Sturnus vulgaris_), males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn].
+Similarly, scrub-jays (_Aphelocoma coerulescens_) that have lower CORT levels as nestlings performed better on an associative learning test as adults but not on a reversal-learning task [@bebus_associative_2016].
+We must acknowledge the possibility that prenatal CORT does not affect the brain regions involved in coding associative learning in _L.
+delicata_ and _L.
+guichenoti_, and future studies should focus on examining the effect of early-life stress on different cognitive domains.
+
+#### Effect of incubation temperature on learning
+We also predicted hot-incubated lizards to perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Furthermore, the opposite pattern was found only in studies that employed temperatures far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020], and it is unclear how such conditions relate to wild environments.
+In _L.
+delicata_ and _L.
+guichenoti_, associative learning appears to be robust to incubation temperature.
+Our results, therefore, do not align with the outcome observed in previous experiments.
+However, the effect of prenatal temperature on cognition, and brain physiology and structure has been investigated only in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how thermal early environment can affect cognitive abilities.
+According to our observations, the impact of incubation temperature on learning may not be as widespread across reptiles as we may think.
+
+Alternatively, other factors, such as sex-dependent effects, could be affecting our findings.
+We did not include sex as a predictor for several reasons: first, lizards were tested before sexual maturation [@joss1985reproductive]; and second, previous studies have found weak evidence for sex-dependent learning in reptiles [@szabo_sex_meta].
+In fact, in the eastern three-lined skink (_Bassiana dupeyerri_) the effect of incubation temperature on learning is not sex-dependent [@amiel_hotter_2012; @clark_colour_2014].
+However, there is previous evidence for interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
+Notably, in _B.
+dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal, where individuals under cold incubation temperatures develop male phenotypes while retaining female genotypes [@quinn2009isolation].
+As a result, even when examining the interactive effects of sex and temperature in this species, the results could be confounded by the mismatch between genotype and phenotype [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Although sex-reversal does not occur in _L.
+delicata_ or _L.
+guichenoti_, not accounting for sex in our analyses could be masking potential interactions between temperature and sex in shaping learning abilities [see @coomber_independent_1997; @sakata_neural_2000].
+Future research should investigate the potential interactive impacts of sex and incubation temperature on cognitive abilities.
+Nevertheless, conducting such studies poses challenges due to the substantial sample sizes necessary.
 
@@
 guichenoti_.
-For _L.
-delicata_, performance was proficient when the reward was linked to red ramps, but learning slopes for lizards assigned to the blue condition did not differ from zero.
+_L.
+delicata_ learned the task when the reward was associated to the red ramp but not when the ramp was blue.
 In contrast, _L.
-guichenoti_ showed similar results in both colour scenarios.
+guichenoti_ showed similar results despite the colour of the correct ramp.
 This indicates that _L.
@@
 However, our results could be a consequence of an initial bias in lizards' choice.
-The analyses presented in the supplemenatry material show that, overall, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue condition.
-Moreover, in those groups where we found that the learning slopes did not differ significantly from zero (see @fig-deli), we also observed the highest probability to select blue ramps in the first trial (see Supplementary Material).
+The analyses presented in the supplemenatry material show that, overall, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue ramp.
+These lizards show learning slopes not different from zero, but high probabilities of choosing the correct ramp also in the first trials (see @fig-deli).
 
 Because there was a possibility that this bias towards blue ramps was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see Supplementary Material).
-Since these results show no similarities between the white and blue ramps, we consider the preference towards blue to not be a derivate from our experimental design.
+We found no similarities between the white and blue ramps, so we consider that preference towards blue ramps did not arise as a derivate from trining the lizards with the white ramps.
 Rather, it seems likely that lizards innately prefer the blue ramps.
-The species confidence hypothesis posits that animals should bias their attention towards colours they are familiar with [@putman2017fear].
+Some animals bias their attention towards colours they are familiar with [@putman2017fear - the 'species confidence hypothesis'].
 For instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
@@
 guichenoti_ before; and blue colouration is not considered to be involved in intraspecific communication in these species [@torr1996patterns; @chapple_biology_2014].
-Still, we recommend to carefully select the colours employed in associative tasks when relying on visual stimuli.
-Despite this, when lizards assigned to blue or red were analysed separately, the between treatments comparissons remain the same in both conditions and species.
-
-#### Effect of prenatal CORT on learning
-Prenatal CORT was expected to have a negative effect on learning, declining CORT-treated lizards' performance in the learning task [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn; @bebus_associative_2016].
-However, we did not find any significant difference between hormone treatments in either of the two species.
-Our results are consistent with other experiments that showed no effect of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016].
-In this sense, GCs are known to have hormetic effects, with low or short exposure to GCs improving performance in learning tasks, and high levels impairing proficiency [@du_dynamic_2009; @mcewen_brain_2012].
-When using the same dose and application methods in eggs of _L.
-delicata_, @crino2024eggs found CORT treatment had sustained effects on growth, mitochondrial activity, and baseline CORT levels; and their findings also aligned with the predictions expected under high GCs elevations.
-This suggests that the absence of effects on learning abilities are not due to methodological caveats, but rather to _L.
-delicata_ and _L.
-guichenoti_'s brain being robust to CORT elevations during development.
-However, since dose effects can differ between tissues [@lemaire_prenatal_2000], we cannot dismiss the possibility that our concentrations failed to elicit changes to the brain that would result in impaired learning.
-
-Conversely, the absence of significant effects of prenatal CORT on learning could be due to the cognitive task employed, as some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
-GCs action involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed unevenly in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
-For instance, in European starlings, males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn].
-Similarly, Scrub-jays that had lower CORT levels as nestlings performed better on an associative learning test as adults, but not on a reversal learning task [@bebus_associative_2016].
-We must acknowledge the possibility that prenatal CORT does not affect the brain regions involved in coding associative learning in these species, and future studies should focus on examining the effect of early-life stress on different cognitive domains.
-
-#### Effect of incubation temperature on learning
-We also expected hot-incubated lizards to perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Furthermore, the opposite pattern was found only in studies that employed temperatures far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020], and it is unclear how such conditions relate to wild environments.
-In _L.
-delicata_ and _L.
-guichenoti_, associative learning appears to be robust to incubation temperature.
-Our results, therefore, do not align with the outcome observed in previous experiments.
-However, the effect of prenatal temperature in cognition, and brain physiology and structure has been investigated only in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how thermal early environment can affect cognitive abilities.
-
-In our analyses, we did not include sex as a factor for several reasons: first, lizards were tested before sexual maturation; and second, previous studies have found weak evidence for sex-dependent learning in reptiles [@szabo_sex_meta].
-In fact, in the Eastern three-lined skink (_Bassiana dupeyerri_) the effect of incubation temperature on learning is not sex-dependent [@amiel_hotter_2012; @clark_colour_2014].
-However, there is previous evidence for interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
-Notably, in _B.
-dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal, where individuals under cold incubation temperatures develop male phenotypes while retaining female genotypes [@dissanayake2021effects].
-As a result, even when examining the interactive effects of sex and temperature [@amiel_hotter_2012; @clark_colour_2014], the results could be confounded by the mismatch between genotype and phenotype in _B.
-dupeyerri_ [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Although sex-reversal does not occur in _L.
-delicata_ or _L.
-guichenoti_, not accounting for sex in our analyses could be masking potential interactions between temperature and sex in shaping learning abilities.
-Future research should investigate the potential interactive impacts of sex and incubation temperature on cognitive abilities.
-Nevertheless, conducting such studies poses challenges due to the substantial sample sizes necessary.
+Regardless, our results demonstrate that _L.
+delicata_ has a bias toward blue colours and highlights the need to consider the colours used in associative learning paradigms.
 
@@
 We did not see any significant difference in learning rates when both species were compared.
-This result is in line with previous studies that found similar learning abilities in _L.
+This result supports previous studies that found similar learning abilities in _L.
 delicata_ and _L.
@@
 In the experiment conducted by @bezzina2014does, both species failed to complete the associative learning task under the authors' criterion, while in our experiment both species completed the task, exhibiting similar learning rates.
-Complexity, experimental design, or the criterion employed to define learning could be the major cause of the discrepancies between ours and @bezzina2014does's findings.
+Complexity, experimental design, or the criterion employed to define learning could be the major cause of the discrepancies between ours and @bezzina2014does.
 Developing common strategies and approaches to assess learning in animals could help understand how learning abilities are shaped in different taxa or under different environments.
@@
 #### Conclusion
-Our results revealed that lizards completed the associative learning task at similar rates, with no significant differences observed between species or treatments.
-This outcome contrasts with our initial predictions, suggesting that the learning abilities of both species are resilient to the early environmental influences examined.
-Our findings indicate that the learning skills of these lizards may be more robust than anticipated under varying early life conditions.
+Our results revealed that associative learning abilities in _L.
+delicata_ and _L.
+guichenoti_ are resilient to prenatal CORT and temperature.
+This outcome contrasts with our initial predictions, indicating that the learning skills of these lizards may be more robust than anticipated under varying early life conditions.
 We also found significant effects of the colour employed in the task on learning rates in _L.
@@
 guichenoti_.
-These results seem to be consequence of an innate colour bias, and highlights the importance of carefully selecting the colour employed when testing cognition using visual stimuli.
+These results seem to be a consequence of an innate colour bias and highlights the importance of carefully selecting the colour employed when testing cognition using visual stimuli.
 
@@
 Furthermore, it is crucial to explore how these treatments influence brain function at a neurological level.
-Investigating these aspects will help us understand the cognitive and physiological mechanisms underpinning adaptability in these species and offer insights into how early developmental factors shape long-term cognitive outcomes.
+Investigating these aspects will help us understand these species' cognitive and physiological mechanisms underpinning adaptability and offer insights into how early developmental factors shape long-term cognitive outcomes.
 
@@
 We declare we have no competing interests
+
 #### Conflict of Interest  
 We declare we have no conflict of interest
+
 #### Ethical Approval  

### 2024-09-22 ms.qmd
Updates

@@
 ---
-title: "Early environmental conditions do not impact associative learning in two species of skink"
+title: "Early environmental conditions do not impact associative learning in two lizard species"
 format:
@@
 Animals must acquire new information through learning to adjust their behaviour adaptively.
-However, animals' abilities to learn can be constrained by the conditions experienced during early stages of development, when the brain is especially susceptible to environmental inputs.
+However, learning ability can be constrained by the conditions experienced during early stages of development, when the brain is especially susceptible to environmental inputs.
 Temperature is a pervasive mechanism of phenotypic plasticity in ectotherms, exerting direct effects on growth, metabolism, or learning.
-In vertebrates, abrupt thermal changes can trigger an allostatic response, which is mediated by glucocorticoids - stress-related hormones - that can be transmitted to the offspring, potentially impacting their learning abilities.
-Thus, glucocorticoids and the thermal environment are predicted to have interactive effects on the development of learning functions in animals.
+In vertebrates, abrupt thermal changes can trigger a chronic stress, which is mediated by glucocorticoids that can be transmitted to the offspring, potentially impacting their learning abilities.
+Glucocorticoids and the thermal environments are therefore predicted to have interactive effects on the development of learning functions in animals.
 Here, we investigated the combined effects of corticosterone (CORT) - the main GC in reptiles - and elevated temperature during development on learning in juveniles of two species of lizards, _Lampropholis delicata_ and _L.
@@
 We predicted that elevated CORT and low temperatures would impair associative learning.
-However, both species learned the task at the same rate independently of treatment.
+**However, both species learned the task at the same rate independently of treatment.
 This suggests these two species may have evolved mechanisms to maintain learning abilities despite prenatal challegnes.
-We also found that lizards did not learn when food rewards were associated with blue-coloured ramps, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
+We also found that lizards did not learn when food rewards were associated with blue-coloured ramps, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.**
 
@@
 Particularly, learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
-Learning allows animals to adapt their behavior to environmental conditions and thus can have cascading effects on population dynamics by influencing survival rates or reproductive success [@ward2016ecological; @welklin2024spatial].
-However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, gut microbiota, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
+However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014].
 These variations can further affect population dynamics, as differences in learning ability may lead to unequal responses to environmental pressures [@ward2016ecological; @welklin2024spatial].
@@
 
-Developing conditions are especially relevant in shaping learning abilities because the brain is highly susceptible to environmental inputs during early stages of life [@zhu_prenatal_2004].
+Developmental conditions are especially relevant in shaping learning abilities because the brain is highly susceptible to environmental inputs during early stages of life [@zhu_prenatal_2004].
 Impacts on brain development can have long-lasting effects on cognition, potentially influencing an individual's ability to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
-For example, the state of the mother can influence offspring's phenotype beyond genetic transmission through nest-site selection, provisioning, or the transmission of hormones or nutrients [i.e., 'maternal effects' @moore_mothers_2019]; and the developing brain is not exent of these effects.
-
-Glucocorticoids (GCs) are a class of steroid hormones that are particularly relevant in this context.
+For example, the state of the mother can influence offspring phenotype beyond genetic transmission through nest-site selection, provisioning, or the transmission of hormones or nutrients [i.e., 'maternal effects' @moore_mothers_2019]; and the developing brain is not exempt of these effects.
+
+Glucocorticoids (GCs) are a class of steroid hormone that are particularly relevant in this context.
 In vertebrates, GCs regulate metabolism and maintain homeostasis in response to disturbances [i.e., ‘the stress response’ @sapolsky_how_2000].
 Under stressful situations, animals react by instigating adaptive physiological and behavioural adjustments mediated by GCs.
-These GCs can be transmitted directly from the parents to their offspring with different effects on offsprings' phenotype [@Crino_2023].
+These GCs can be transmitted directly from the parents to their offspring with different effects on offspring phenotype [@Crino_2023].
 Elevations in GCs during early stages of development typically result in altered neurogenesis, brain structure, and metabolic activity that in most cases are related to decreased learning abilities [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009; @eaton2015mild; @farrell_developmental_2015-learn; @farrell_developmental_2016].
@@
 
-In this study, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - and incubation temperature on learning in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - and incubation temperature on learning in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 Post-incubation, juveniles were subjected to a colour-associative task to assess their learning abilities.
-We hypothesized that prenatal CORT levels and thermal environment will induce sustained effects on brain's physiology, ultimately impacting learning skills.
+We hypothesized that prenatal CORT levels and thermal environment will induce sustained effects on brain's physiology, ultimately impacting learning of the association task.
 We predicted that individuals exposed to high levels of CORT or low temperatures will learn slower than control individuals or those incubated at higher temperatures [@zhu_prenatal_2004; @amiel_hotter_2012; @eaton2015mild; @amiel_effects_2017].
@@
 _Lampropholis delicata and _L.
-guichenoti_ are small (∼35-55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011].
+guichenoti_ are small [∼35-55 mm snout-vent length (SVL)], oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011].
 Both species have similar breeding periods, but with some differences in reproductive output: while *L.
-delicata* lays 1 to 6 eggs in only one clutch per season, *L.
+delicata* lays 1-6 eggs in only one clutch per season, *L.
 guichenoti* clutches are smaller (1-5 eggs per clutch) and they usually lay two clutches per season [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014].
@@
 delicata* and *L.
-guichenoti* respectively, were housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
-Enclosures were provided with non-stick matting, shelter, and several small water dishes.
+guichenoti* respectively, were housed in plastic containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+Enclosures were lined with non-stick matting, shelter, and several small water dishes.
 Water is given daily, and they were fed approximately 40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
 Crickets were dusted with calcium weekly and multivitamin and calcium biweekly.
-To ensure a temperature gradient, we employed a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
-Room temperatures were set to 22-24 ºC, and the warm side of enclosures was usually at 32 ºC.
-
-*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside.
+To ensure a temperature gradient, we used a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
+Room temperatures were set to 22-24 ºC, and the warm side of enclosures was usually at 32-34 ºC.
+
+*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) containing moist vermiculite.
 These boxes were placed in one side of the communal enclosures (see above).
-We checked for the presence of eggs in the boxes three days a week.
+We checked for the presence of eggs in the boxes three days a week (Monday, Wednesday, and Friday).
 After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001g error).
@@
 To dose eggs, we applied 5µl of solutions to eggshells using a micropipette.
-We selected these doses based on previous studies publishing yolk CORT concentrations in other ovipaorus reptiles [@lovern2008effects; @hanover2019corticosterone].
+We selected these doses based on previous studies publishing yolk CORT concentrations in other oviparous reptiles [@lovern2008effects; @hanover2019corticosterone], while also validating that it fell within the range of CORT concentrations in eggs within our population [@crino2024eggs].
 CORT treatment increased mean yolk CORT levels ~3.7x higher than control eggs [@crino2024eggs].
@@
 #### Learning  
-To estimate learning skills, we tested skinks' ability to locate a food reward in a colour-associative learning task (@fig-Methods C, D).
+To estimate learning skills, we tested each lizard's ability to locate a food reward in a colour-associative learning task (@fig-Methods C, D).
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical in size and shape to the ones used during the associative task.
@@
 At the end of each trial, we recorded whether the cricket had been consumed or not.
-A trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials to ensure lizards' consistency.
-This phase lasted 38 days until all the lizards learned to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
+A trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials to ensure lizards were feeding consistently.
+This phase lasted 38 days until all the lizards learned to eat from the ramp; only in one case did we decide not to use the lizard because its behaviour was not consistent over the course of the training phase.
 
@@
 #| fig.cap: "Experimental design of the experiment.
-Panel A shows the early environment manipulation.
+Panel A shows the early environment manipulation (see methods for ).
 In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks.
@@
 
-The experiment took place between the 6^th^ of March until the 17^th^ of May 2023, and tests were performed between 11 AM to 12 PM when the lizards were active.
+The experiment took place between the 6^th^ of March to the 17^th^ of May 2023, and tests were performed between 11 AM to 12 PM when the lizards were active.
 Trials in the learning phase were recorded with CCTV systems always using the same camera per individual.
@@
 We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
-We considered a trial failed if there was no choice after one hour of recording, and scored those trials as NA.
-We excluded from our analyses those individuals that scored 15 trials out of the 35 trials as NA.
-For each individual, we considered their first trial to be the first one where a choice was made.
+We considered a trial to have failed if there was no choice after one hour of recording.
+These trials were scored as NA.
+We excluded from our analyses those individuals that did not perform consistently as defined as not choosing in less than 20 out of 35 trials (~57%).
+For each lizard, we considered their first trial to be the first one where a choice was made.
 
 #### Statistical analyses  
-We performed the analyses for species separately.
-Also, as preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red).
-Therefore, we run a total of four different Bayesian multilevel models using the brm function from the brms package [@burkner2017brms] in R (version 2.8.2) [@R].
+We performed analyses for species separately.
+Preliminary analyses showed a significant effect of the colour.
+As such, we decided to split the data by colour (blue or red).
+Therefore, we ran a total of four different Bayesian multilevel models using the _brm_ function from the brms package [@burkner2017brms] in R (version 2.8.2) [@R].
 We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
-
-We employed correct choice [correct (1) or not (0)] as the response variable, and trial, incubation temperature (Cold versus Hot), hormone (CORT versus Control), and the three-way interaction as fixed factors.
-The error structure was modeled using a Bernoulli distribution with a logit link function (family = Bernoulli(link = 'logit')).
+We checked that all MCMC chains converged (R~hat~ < 1.2) and were mixing effectively to ensure we had >1000 effective samples from the posterior distribution.
+
+We modelled correct choice [correct (1) or not (0)] as the response variable, and trial, incubation temperature (Cold versus Hot), hormone (CORT versus Control), and the three-way interaction as fixed factors.
+The error structure was modeled using a Bernoulli distribution with a logit link function [family = Bernoulli(link = 'logit')].
 We included a random intercept and slope (trial) for each lizard in our models.
@@
 guichenoti_ lays up to two [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014].
-Since egg collection was done during half of the breeding season, each clutch likely come from a unique mother, and so, clutch identity captures potential maternal effects.
+Since egg collection was done during half of the breeding season, each clutch likely came from a unique mother, and so, clutch identity captures potential maternal effects.
 In addition, previous studies indicate that clutches are typically fertilized by a single male, although sperm storage can occur [@kar2024heritability].
@@
 Learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature will affect hatching time [@zhang2023developmental], we explored the effects of age on learning by including it as a predictor.
-Lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L.
+Lizard ages at the beginning of the experiment ranged from 41 to 148 days old in _L.
 delicata_ and 48 to 132 in _L.
 guichenoti_.
-However, when this variable was included in the models, we did not find any significant effect of age (see Supplementary material).
+However, when this variable was included in the models, we did not find any significant effect of age (see _Supplementary Material_).
 As such, we present models without age as a fixed effect.
@@
 We used the posterior distributions of parameters to test for differences in learning rate between treatments and species.
-slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
+Slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
 Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
 p~mcmc~ test the hypothesis that slopes and slopes contrasts are different from zero.
-We considered statistical significance if p~mcmc~ < 0.05.
+We considered statistical significant if p~mcmc~ < 0.05.
 
@@
 Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
-However, due to natural mortality (n = 11), incompletion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we had a final total of 81 lizards.
-Final sample sizes per treatment and species are listed in @fig-deli and @fig-guich (figures for both species with the raw data are included in the Supplementary Material).
-Mean slopes (denoted as β throughout) per treatment for both species are provided in Table 1 in the Supplementary Material.
+However, due to natural mortality (n = 11), incompletion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we had a final sample size of 81 lizards.
+Final sample sizes per treatment and species are listed in @fig-deli and @fig-guich (figures for both species with the raw data are included in the _Supplementary Material_).
+Mean slopes (denoted as β throughout) per treatment for both species are provided in Table 1 in the _Supplementary Material_.
 ```{r, models}
@@
 
-We found that learning slopes were lower when the blue ramps were the correct choice compared to slopes of individuals assigned to the red group for _L.
-delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
+We found that the rate of learning was lower when the blue ramps were the correct choice compared to the red ramps, for _L.
+delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc = `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
 guichenoti_ (mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
-However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material) that could be affecting the estimated slopes.
+However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see _Supplementary Material_) that could be affecting the estimated slopes.
 As such, we analyzed the differences between treatments for each group separately.
@@
 However, our results could be a consequence of an initial bias in lizards' choice.
-The analyses presented in the supplemenatry material show that, overall, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue ramp.
+The analyses presented in the Supplemenatry Material show that, overall, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue ramp.
 These lizards show learning slopes not different from zero, but high probabilities of choosing the correct ramp also in the first trials (see @fig-deli).
 
-Because there was a possibility that this bias towards blue ramps was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see Supplementary Material).
+Because there was a possibility that this bias towards blue ramps was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see _Supplementary Material_).
 We found no similarities between the white and blue ramps, so we consider that preference towards blue ramps did not arise as a derivate from trining the lizards with the white ramps.
@@
 
+#### Preliminary analyses
+```{r, modelsage}
+#| label: modelsage
+# Fitting the models for L. delicata and L. guichenoti including age as a covariate
+#
+data_prel <- data_clean %>%
+  mutate(age.start = as.numeric(age.start)-mean(as.numeric(age.start)))
+#
+refit2 = FALSE
+formula <- FC_associative ~ age.start + group*trial_associative + trial_associative*cort*temp + 
+                            (1 + trial_associative|lizard_id) + (1|clutch)
+species <- c("delicata", "guichenoti")
+#
+models <- list() # Create an empty list to store the models
+for(s in species){
+    # Subset the data for the species
+    data_species <- data_prel %>%
+    filter(species == s)
+    model_file <- paste0("output/models/model_prel_", s, ".rds")
+# Fit the model only if it has not been fit yet (if refit2 = TRUE)
+  if(refit2 == TRUE){
+    # Fit the model
+    model <- brm(formula,
+                data = data_species,
+                family = bernoulli(link = "logit"),
+                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
+    # Write the model to a file
+    saveRDS(model, file = model_file)
+  } else {
+      # Read the model from a file
+      model <- readRDS(file = model_file)
+  }
+  # Save the model to the list
+  models[[paste0(s)]] <- model
+}
+#
+model_prel_deli <- models[["delicata"]]
+model_prel_guich <- models[["guichenoti"]]
+#
+summary(model_prel_deli)
+summary(model_prel_guich)
+```
+
 #### Models with age included

### 2024-09-22 .vdoc.r

@@ -1,841 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-cat("\\newpage")
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of the experiment. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks. Panel C shows the habituation process with the three different stages. And in panel D, the associative task with the three different 3D printed ramps. White lids in D show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be the main data base used (data_clean).
-write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
-    for(k in 1:length(hormone)){
-      for(l in 1:length(temperature)){
[…]

### 2024-09-22 R/func.r

@@ -149,10 +149,15 @@ format_dec <- function(x, n) {
 #' @param x The object
 #' @param n The number of decimals
 format_p <- function(x, n) {
+  if(equal == TRUE){
+    e <- "="
+  } else if(equal == FALSE){
+    e <- ""  
+  }
   z <- sprintf(paste0("%.",n,"f"), x)
   tmp <- ifelse(as.numeric(z) <= 0.001, "< 0.001",
          ifelse(as.numeric(z) <= 0.05 & as.numeric(z) > 0.001, "< 0.05",
-                format_dec(as.numeric(z), 2)))
+                paste0(e, format_dec(as.numeric(z), 2))))
   return(tmp)
 }
 ####################

### 2024-09-23 Others/ms_choice.qmd
Updates

--- 2024-09-22 ms.qmd
@@
 #| label: results
+# Rename some of the posteriors and obtain estimates for the "decision making" for each group and treatment.
+This "decision making" consists of the probability of choosing right using the Intercept for each treatment.
+## 1) L. delicata
+## 1) L. delicata
+### Group = red
+probright_drCORTCold <- exp(deli_red$b_Intercept)/(1+exp(deli_red$b_Intercept))
+probright_drControlCold <- exp(deli_red$b_cortControl + deli_red$b_Intercept)/(1+exp(deli_red$b_cortControl + deli_red$b_Intercept))
+probright_drCORTHot <- exp(deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$b_tempHot + deli_red$b_Intercept))
+probright_drControlHot <- exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept))
+### Group = blue
+probright_dbCORTCold <- exp(deli_blue$b_Intercept)/(1+exp(deli_blue$b_Intercept))
+probright_dbControlCold <- exp(deli_blue$b_cortControl + deli_blue$b_Intercept)/(1+exp(deli_blue$b_cortControl + deli_blue$b_Intercept))
+probright_dbCORTHot <- exp(deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$b_tempHot + deli_blue$b_Intercept))
+probright_dbControlHot <- exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept))
+## 2) L. guichenoti
+### Group = red
+probright_grCORTCold <- exp(guich_red$b_Intercept)/(1+exp(guich_red$b_Intercept))
+probright_grControlCold <- exp(guich_red$b_cortControl + guich_red$b_Intercept)/(1+exp(guich_red$b_cortControl + guich_red$b_Intercept))
+probright_grCORTHot <- exp(guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$b_tempHot + guich_red$b_Intercept))
+probright_grControlHot <- exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept))
+### Group = blue
+probright_gbCORTCold <- exp(guich_blue$b_Intercept)/(1+exp(guich_blue$b_Intercept))
+probright_gbControlCold <- exp(guich_blue$b_cortControl + guich_blue$b_Intercept)/(1+exp(guich_blue$b_cortControl + guich_blue$b_Intercept))
+probright_gbCORTHot <- exp(guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$b_tempHot + guich_blue$b_Intercept))
+probright_gbControlHot <- exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept))
+#
 # Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment.
@@
 gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial + guich_blue$'b_Trial:cortControl' + guich_blue$'b_Trial:tempHot')
-```
-
-We found that the rate of learning was lower when the blue ramps were the correct choice compared to the red ramps, for _L.
-delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc = `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
+#
+# Modyfying a parameter for the results later (see p_format function in func.R)
+equal <- TRUE
+```
+
+Decision making in the associative task was affected by the colour of the ramps in _L.
+delicata_.
+The probability of choosing correctly when the correct ramp was blue was higher than when the correct ramp was red (mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc = `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, see @fig-deli).
+For _L.
+guichenoti_, the probability of choosing correctly was similar between blue or red ramps (mean P~Blue~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc = `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, see @fig-guich).
+
+The learning rate, overall, did not differ between colours in _L.
+delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc = `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), nor in _L.
 guichenoti_ (mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
-However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see _Supplementary Material_) that could be affecting the estimated slopes.
-As such, we analyzed the differences between treatments for each group separately.
-
-For those _L.
-delicata_ assigned to group red, we did not find any significant differences between hormones (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
-Similarly, those assigned to blue were not afected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
+However, because of the potential bias towards blue in the initial choice that could be affecting the estimated slopes we analyzed the differences between treatments for each ramp colour separately.
+
+Decision making in _L.
+delicata_ was not impacted by the hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_drControlCold, probright_drControlHot)) - mean(c(probright_drCORTCold, probright_drCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlCold, probright_drControlHot) - c(probright_drCORTCold, probright_drCORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_drControlHot, probright_drCORTHot)) - mean(c(probright_drControlCold, probright_drCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlHot, probright_drCORTHot) - c(probright_drControlCold, probright_drCORTCold)), 3)`) or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(probright_drControlHot - probright_drCORTHot) - mean(probright_drControlCold - probright_drCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_drControlHot - probright_drCORTHot - (probright_drControlCold - probright_drCORTCold)), 3)`) when red ramps were the correct choice (see @fig-deli **A, B**).
+There was no significant effect of hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_dbControlCold, probright_dbControlHot)) - mean(c(probright_dbCORTCold, probright_dbCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbControlCold, probright_dbControlHot) - c(probright_dbCORTCold, probright_dbCORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_dbControlHot, probright_dbCORTHot)) - mean(c(probright_dbControlCold, probright_dbCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbControlHot, probright_dbCORTHot) - c(probright_dbControlCold, probright_dbCORTCold)), 3)`) or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(probright_dbControlHot - probright_dbCORTHot) - mean(probright_dbControlCold - probright_dbCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_dbControlHot - probright_dbCORTHot - (probright_dbControlCold - probright_dbCORTCold)), 3)`) when blue ramps were the correct choice (see @fig-deli **C, D**).
+
+Learning slopes in _L.
+delicata_ assigned to red ramps did not show significant effects of the hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli **A, B**).
+Similarly, those assigned to blue were not afected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli **C, D**).
 
@@
 #| label: fig-deli
-#| fig.cap: "Results for Lampropholis delicata for both colour groups red (A,B) and blue (C, D).
-Panels A and C show the predicted probability of choosing the correct ramp first over trials.
-The lines represent the mean predicted probability of choosing the correct ramp first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+#| fig.cap: "Results for Lampropholis delicata for both colour groups red (A, B, C) and blue (D, E , F).
+Panels A and D show the predicted probability of choosing the correct ramp in the first trial (Decision first trial).
+In panels B and E, the distribution of the estimates of slopes per each treatment.
+In all A, B, D, and E the x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
 The different colours indicate the different treatments.
-Panels B and D show the distribution of the estimates of slopes per each treatment.
-The x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
-The different colours indicate the different treatments.
-Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
+Points and bars represent the mean and standard deviation of the mean of the estimates, respectively.
+Dashed lines indicate value 0.33 (the probability of choosing correctly by chance) in panesl A, D, and 0 in panels B, E.
+Panels C and F show the predicted probability of choosing the correct ramp first over trials.
+The lines represent the mean predicted probability of choosing the correct ramp for each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours indicate the different treatments."
 source(here("R", "func.R"))
@@
 ## Red
-fig_dar_AC_df <- df_plotAC("deli_red")
-fig_dar_BD1_df <- df_plotBD1("deli_red")
-fig_dar_BD2_df <- df_plotBD2("deli_red")
+fig_dar_choiceviol_df <- df_plotviol("deli_red", "choice")
+fig_dar_choicepoints_df <- df_plotpoints("deli_red", "choice")
+fig_dar_sloviol_df <- df_plotviol("deli_red", "slope")
+fig_dar_slopoints_df <- df_plotpoints("deli_red", "slope")
+fig_dar_prob_df <- df_plotprob("deli_red")
 ## Blue
-fig_dab_AC_df <- df_plotAC("deli_blue")
-fig_dab_BD1_df <- df_plotBD1("deli_blue")
-fig_dab_BD2_df <- df_plotBD2("deli_blue")
+fig_dab_choiceviol_df <- df_plotviol("deli_blue", "choice")
+fig_dab_choicepoints_df <- df_plotpoints("deli_blue", "choice")
+fig_dab_sloviol_df <- df_plotviol("deli_blue", "slope")
+fig_dab_slopoints_df <- df_plotpoints("deli_blue", "slope")
+fig_dab_prob_df <- df_plotprob("deli_blue")
 #
 # Second step, create the plots
-fig_dar <- plotting(sp = "deli", col = "red", df_prob = fig_dar_AC_df, df_violin = fig_dar_BD1_df, df_points = fig_dar_BD2_df)
-fig_dab <- plotting(sp = "deli", col = "blue", df_prob = fig_dab_AC_df, df_violin = fig_dab_BD1_df, df_points = fig_dab_BD2_df)
+fig_dar <- plotting(sp = "deli", col = "red", 
+                    df_violin_1 = fig_dar_choiceviol_df, df_points_1 = fig_dar_choicepoints_df, 
+                    df_violin_2 = fig_dar_sloviol_df, df_points_2 = fig_dar_slopoints_df,
+                    df_prob = fig_dar_prob_df)
+fig_dab <- plotting(sp = "deli", col = "blue",
+                    df_violin_1 = fig_dab_choiceviol_df, df_points_1 = fig_dab_choicepoints_df,
+                    df_violin_2 = fig_dab_sloviol_df, df_points_2 = fig_dab_slopoints_df,
+                    df_prob = fig_dab_prob_df)
 #
@@
   annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 4.5, color = "black", fontface = "italic")
-ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
+ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 30, height = 20, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/fig_deli.png")
@@
 
-In _L.
-guichenoti_, we did not find any significant differences between hormone treatments (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the red group (@fig-guich A, B); and we did not find any significant effect of hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to blue either (@fig-guich C, D).
+Decision making in _L.
+guichenoti_ when the red ramps are the correct choice, was not affected by the hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_grControlCold, probright_grControlHot)) - mean(c(probright_grCORTCold, probright_grCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlCold, probright_grControlHot) - c(probright_grCORTCold, probright_grCORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_grControlHot, probright_grCORTHot)) - mean(c(probright_grControlCold, probright_grCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlHot, probright_grCORTHot) - c(probright_grControlCold, probright_grCORTCold)), 3)`) or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(probright_grControlHot - probright_grCORTHot) - mean(probright_grControlCold - probright_grCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_grControlHot - probright_grCORTHot - (probright_grControlCold - probright_grCORTCold)), 3)`) (@fig-guich **A, B**).
+The same was observed when blue ramps were the correct choice (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_gbControlHot, probright_gbCORTHot)) - mean(c(probright_gbControlCold, probright_gbCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbControlHot, probright_gbCORTHot) - c(probright_gbControlCold, probright_gbCORTCold)), 3)`; β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_gbControlCold, probright_gbControlHot)) - mean(c(probright_gbCORTCold, probright_gbCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbControlCold, probright_gbControlHot) - c(probright_gbCORTCold, probright_gbCORTHot)), 3)`) (@fig-guich **C, D**).
+
+Learning slopes in _L.
+guichenoti_ was not influenced by hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) when red ramps was the correct choice (@fig-guich **A, B**).
+Temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the hormone-temperature interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) were not significant for _L.
+guichenoti_ assigned to blue ramps.
+However, CORT-treated lizards showed lower learning slopes than controls (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`) when the blue ramps were the correct choice (see @fig-guich **C, D**).
 
@@
 #| label: fig-guich
-#| fig.cap: "Results for Lampropholis guichenoti for both colour groups red (A,B) and blue (C, D).
-Panels A and C show the predicted probability of choosing the correct ramp first over trials.
-The lines represent the mean predicted probability of choosing the correct ramp first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+#| fig.cap: "Results for Lampropholis guichenoti for both colour groups red (A, B, C) and blue (D, E , F).
+Panels A and D show the predicted probability of choosing the correct ramp in the first trial (Decision first trial).
+In panels B and E, the distribution of the estimates of slopes per each treatment.
+In all A, B, D, and E the x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
 The different colours indicate the different treatments.
-Panels B and D show the distribution of the estimates of slopes per each treatment.
-The x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
-The different colours indicate the different treatments.
-Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
+Points and bars represent the mean and standard deviation of the mean of the estimates, respectively.
+Dashed lines indicate value 0.33 (the probability of choosing correctly by chance) in panesl A, D, and 0 in panels B, E.
+Panels C and F show the predicted probability of choosing the correct ramp first over trials.
+The lines represent the mean predicted probability of choosing the correct ramp for each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours indicate the different treatments."
 source(here("R", "func.R"))
@@
 ## Red
-fig_gar_AC_df <- df_plotAC("guich_red")
-fig_gar_BD1_df <- df_plotBD1("guich_red")
-fig_gar_BD2_df <- df_plotBD2("guich_red")
+fig_gar_choiceviol_df <- df_plotviol("guich_red", "choice")
+fig_gar_choicepoints_df <- df_plotpoints("guich_red", "choice")
+fig_gar_sloviol_df <- df_plotviol("guich_red", "slope")
+fig_gar_slopoints_df <- df_plotpoints("guich_red", "slope")
+fig_gar_prob_df <- df_plotprob("guich_red")
 ## Blue
-fig_gab_AC_df <- df_plotAC("guich_blue")
-fig_gab_BD1_df <- df_plotBD1("guich_blue")
-fig_gab_BD2_df <- df_plotBD2("guich_blue")
+fig_gab_choiceviol_df <- df_plotviol("guich_blue", "choice")
+fig_gab_choicepoints_df <- df_plotpoints("guich_blue", "choice")
+fig_gab_sloviol_df <- df_plotviol("guich_blue", "slope")
+fig_gab_slopoints_df <- df_plotpoints("guich_blue", "slope")
+fig_gab_prob_df <- df_plotprob("guich_blue")
 #
 # Second step, create the plots
-fig_gar <- plotting(sp = "guich", col = "red", df_prob = fig_gar_AC_df, df_violin = fig_gar_BD1_df, df_points = fig_gar_BD2_df)
-fig_gab <- plotting(sp = "guich", col = "blue", df_prob = fig_gab_AC_df, df_violin = fig_gab_BD1_df, df_points = fig_gab_BD2_df)
+fig_gar <- plotting(sp = "guich", col = "red", 
+                    df_violin_1 = fig_gar_choiceviol_df, df_points_1 = fig_gar_choicepoints_df, 
+                    df_violin_2 = fig_gar_sloviol_df, df_points_2 = fig_gar_slopoints_df,
+                    df_prob = fig_gar_prob_df)
+fig_gab <- plotting(sp = "guich", col = "blue",
+                    df_violin_1 = fig_gab_choiceviol_df, df_points_1 = fig_gab_choicepoints_df,
+                    df_violin_2 = fig_gab_sloviol_df, df_points_2 = fig_gab_slopoints_df,
+                    df_prob = fig_gab_prob_df)
 #
@@
   annotate("text", x = 0.5, y = 0.985, label = "Lampropholis guichenoti", size = 4.5, color = "black", fontface = "italic")
-ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 25, height = 18, units = "cm", dpi = 600)
+ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 30, height = 20, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/fig_guich.png")
@@
 
-Finally, we also did not find any significant differences when we compared the estimated slopes between species for red group (mean β~_L.
+Overall, decision making did not differ between species when the red ramps were the correct choice (mean β~_L.
+delicata_~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI β~_L.
+delicata_~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]; mean β~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI β~_L.
+guichenoti_~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]; β~_L.
+delicata_~ - β~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`) or when the blue ramps were the correct choice (mean β~_L.
+delicata_~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean β~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI β~_L.
+guichenoti_~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; β~_L.
+delicata_~ - β~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`).
+
+When we average learning rates across treatments, we did not find any significant differences when we compared between species when the red ramp was the correct choice (mean β~_L.
 delicata_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)), 3)`, 95% CI β~_L.
@@
 delicata_~ - β~_L.
-guichenoti_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the blue group (mean β~_L.
+guichenoti_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) neither when the blue ramps were the correct choice (mean β~_L.
 delicata_~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~_L.
@@
 source(here("R", "func.R"))
+#
+# Modyfying a parameter for later (see p_format function in func.R)
+equal <- FALSE
 #
@@
 source(here("R", "func.R"))
-# First we estimate the probability of choosing right in the first trial using the intercepts from the posteriors
-## 1) L. delicata
-### Group = red
-probright_drCORTCold <- exp(deli_red$b_Intercept)/(1+exp(deli_red$b_Intercept))
-probright_drControlCold <- exp(deli_red$b_cortControl + deli_red$b_Intercept)/(1+exp(deli_red$b_cortControl + deli_red$b_Intercept))
-probright_drCORTHot <- exp(deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$b_tempHot + deli_red$b_Intercept))
-probright_drControlHot <- exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept))
-### Group = blue
-probright_dbCORTCold <- exp(deli_blue$b_Intercept)/(1+exp(deli_blue$b_Intercept))
-probright_dbControlCold <- exp(deli_blue$b_cortControl + deli_blue$b_Intercept)/(1+exp(deli_blue$b_cortControl + deli_blue$b_Intercept))
-probright_dbCORTHot <- exp(deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$b_tempHot + deli_blue$b_Intercept))
-probright_dbControlHot <- exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept))
-## 2) L. guichenoti
-### Group = red
-probright_grCORTCold <- exp(guich_red$b_Intercept)/(1+exp(guich_red$b_Intercept))
-probright_grControlCold <- exp(guich_red$b_cortControl + guich_red$b_Intercept)/(1+exp(guich_red$b_cortControl + guich_red$b_Intercept))
-probright_grCORTHot <- exp(guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$b_tempHot + guich_red$b_Intercept))
-probright_grControlHot <- exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept))
-### Group = blue
-probright_gbCORTCold <- exp(guich_blue$b_Intercept)/(1+exp(guich_blue$b_Intercept))
-probright_gbControlCold <- exp(guich_blue$b_cortControl + guich_blue$b_Intercept)/(1+exp(guich_blue$b_cortControl + guich_blue$b_Intercept))
-probright_gbCORTHot <- exp(guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$b_tempHot + guich_blue$b_Intercept))
-probright_gbControlHot <- exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept))
-#
-# Second we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species
+# First we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species (see results chunk)
 prob_df <- data.frame(
@@
   set_header_labels(prob_choice_Blue = "Prob Blue", 
-                    p_value_Blue = "p-value Blue", 
+                    p_value_Blue = "pmcmc Blue", 
                     prob_choice_Red = "Prob Red", 
-                    p_value_Red = "p-value Red") %>%
+                    p_value_Red = "pmcmc Red") %>%
   italic(j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
@@
 #### Preliminary analyses
-```{r, modelsage}
-#| label: modelsage
+```{r, modelsprel}
+#| label: modelprel
 # Fitting the models for L. delicata and L. guichenoti including age as a covariate
@@
 species <- c("delicata", "guichenoti")
+# + (-1+group|obs)
 #
@@
 model_prel_guich <- models[["guichenoti"]]
-#
-summary(model_prel_deli)
-summary(model_prel_guich)
 ```

### 2024-09-23 ms.qmd
Updates

@@
 gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial + guich_blue$'b_Trial:cortControl' + guich_blue$'b_Trial:tempHot')
-```
-
-We found that the rate of learning was lower when the blue ramps were the correct choice compared to the red ramps, for _L.
-delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc = `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
-guichenoti_ (mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
-However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see _Supplementary Material_) that could be affecting the estimated slopes.
-As such, we analyzed the differences between treatments for each group separately.
-
-For those _L.
-delicata_ assigned to group red, we did not find any significant differences between hormones (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
-Similarly, those assigned to blue were not afected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
+#
+# Modyfying a parameter for the results later (see p_format function in func.R)
+equal <- TRUE
+```
+
+The probability of choosing correctly in the first trial when the correct ramp was blue not different to the probability of choosing correctly when the correct ramp was red for _L.
+delicata_ (mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, see @fig-deli); neither for _L.
+guichenoti_, the probability of choosing correctly was similar between blue or red ramps (mean P~Blue~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, see @fig-guich).
+**However, the P>0.33 in which cases: Table Suppl Mat**
+
+There was no significant effect of the colour of the correct ramp in _L.
+delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), nor in _L.
+guichenoti_ (mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
+**However, because of the potential bias towards blue in the initial choice that could be affecting the estimated slopes we analyzed the differences between treatments for each ramp colour separately.**
+
+Decision making in _L.
+delicata_ was not impacted by the hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_drControlCold, probright_drControlHot)) - mean(c(probright_drCORTCold, probright_drCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlCold, probright_drControlHot) - c(probright_drCORTCold, probright_drCORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_drControlHot, probright_drCORTHot)) - mean(c(probright_drControlCold, probright_drCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlHot, probright_drCORTHot) - c(probright_drControlCold, probright_drCORTCold)), 3)`) or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(probright_drControlHot - probright_drCORTHot) - mean(probright_drControlCold - probright_drCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_drControlHot - probright_drCORTHot - (probright_drControlCold - probright_drCORTCold)), 3)`) when red ramps were the correct choice (see @fig-deli A).
+There was no significant effect of hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_dbControlCold, probright_dbControlHot)) - mean(c(probright_dbCORTCold, probright_dbCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbControlCold, probright_dbControlHot) - c(probright_dbCORTCold, probright_dbCORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_dbControlHot, probright_dbCORTHot)) - mean(c(probright_dbControlCold, probright_dbCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbControlHot, probright_dbCORTHot) - c(probright_dbControlCold, probright_dbCORTCold)), 3)`) or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(probright_dbControlHot - probright_dbCORTHot) - mean(probright_dbControlCold - probright_dbCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_dbControlHot - probright_dbCORTHot - (probright_dbControlCold - probright_dbCORTCold)), 3)`) when blue ramps were the correct choice (see @fig-deli D).
+
+Learning slopes in _L.
+delicata_ assigned to red ramps did not show significant effects of the hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold, dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold, dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli B, C).
+Similarly, those assigned to blue were not afected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold, dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold, dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli E, F).
 
@@
   annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 4.5, color = "black", fontface = "italic")
-ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
+ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 28, height = 15, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/fig_deli.png")
@@
 
-In _L.
-guichenoti_, we did not find any significant differences between hormone treatments (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the red group (@fig-guich A, B); and we did not find any significant effect of hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to blue either (@fig-guich C, D).
+Decision making in _L.
+guichenoti_ when the red ramps are the correct choice, was not affected by the hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_grControlCold, probright_grControlHot)) - mean(c(probright_grCORTCold, probright_grCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlCold, probright_grControlHot) - c(probright_grCORTCold, probright_grCORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_grControlHot, probright_grCORTHot)) - mean(c(probright_grControlCold, probright_grCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlHot, probright_grCORTHot) - c(probright_grControlCold, probright_grCORTCold)), 3)`) or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(probright_grControlHot - probright_grCORTHot) - mean(probright_grControlCold - probright_grCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_grControlHot - probright_grCORTHot - (probright_grControlCold - probright_grCORTCold)), 3)`) (@fig-guich A).
+The same was observed when blue ramps were the correct choice (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_gbControlHot, probright_gbCORTHot)) - mean(c(probright_gbControlCold, probright_gbCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbControlHot, probright_gbCORTHot) - c(probright_gbControlCold, probright_gbCORTCold)), 3)`; β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_gbControlCold, probright_gbControlHot)) - mean(c(probright_gbCORTCold, probright_gbCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbControlCold, probright_gbControlHot) - c(probright_gbCORTCold, probright_gbCORTHot)), 3)`) (@fig-guich D).
+
+Learning slopes in _L.
+guichenoti_ was not influenced by hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold, gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold, gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) when red ramps was the correct choice (@fig-guich B, C).
+Temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the hormone-temperature interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) were not significant for _L.
+guichenoti_ assigned to blue ramps.
+However, CORT-treated lizards showed lower learning slopes than controls (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold, gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold, gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`) when the blue ramps were the correct choice (see @fig-guich E, F).
 
@@
   annotate("text", x = 0.5, y = 0.985, label = "Lampropholis guichenoti", size = 4.5, color = "black", fontface = "italic")
-ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 25, height = 18, units = "cm", dpi = 600)
+ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 28, height = 15, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/fig_guich.png")

### 2024-09-23 .vdoc.r

@@ -1,0 +1,923 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the experiment. Panel A shows the early environment manipulation (see methods for ). In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks. Panel C shows the habituation process with the three different stages. And in panel D, the associative task with the three different 3D printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2024-09-23 R/func.r

@@ -162,10 +162,10 @@ format_p <- function(x, n) {
 }
 ####################
 ####################
-# Function to create each df for the probability figure (plots A, C fig-deli and fig-guich)
-#' @title df_plotAC
+# Function to create each df for the probability figure (plots C, F fig-deli and fig-guich)
+#' @title df_plotprob
 #' @param data to select the df, levels are: "deli_red", "deli_blue", "guich_red", "guich_blue" 
-df_plotAC <- function(data){
+df_plotprob <- function(data){
   if (data == "deli_red"){
     df <- as.data.frame(deli_red)
   } else if (data == "deli_blue"){
@@ -222,24 +222,69 @@ df_plotAC <- function(data){
     SE_Predicted_prob = sd(Value)
     ) %>%
   ungroup() %>%
-  mutate(
-    Treatment = factor(Treatment,
-                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
-    ) %>%
 data.frame()
-  return(fig_df)
+  if(data == "deli_red"){
+    final_fig_df <- fig_df %>%
+      mutate(Treatment = factor(Treatment, 
+        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"),
+        labels = c("CORT-Cold" = paste0("CORT-Cold (n = ", n_list$delicata_Red_CORT_Cold, ")"),
+                  "Control-Cold" = paste0("Control-Cold (n = ", n_list$delicata_Red_Control_Cold, ")"),
+                  "CORT-Hot" = paste0("CORT-Hot (n = ", n_list$delicata_Red_CORT_Hot, ")"),
+                  "Control-Hot" = paste0("Control-Hot (n = ", n_list$delicata_Red_Control_Hot, ")"))
+      )) %>%
+    data.frame()
+  } else if(data == "deli_blue"){
+    final_fig_df <- fig_df %>%
+      mutate(Treatment = factor(Treatment, 
+        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"),
+        labels = c("CORT-Cold" = paste0("CORT-Cold (n = ", n_list$delicata_Blue_CORT_Cold, ")"),
+                  "Control-Cold" = paste0("Control-Cold (n = ", n_list$delicata_Blue_Control_Cold, ")"),
+                  "CORT-Hot" = paste0("CORT-Hot (n = ", n_list$delicata_Blue_CORT_Hot, ")"),
[…]

### 2024-10-09 Others/ms_version_choice.qmd
Updates

--- 2024-09-22 ms.qmd
@@
 Glucocorticoids and the thermal environments are therefore predicted to have interactive effects on the development of learning functions in animals.
-Here, we investigated the combined effects of corticosterone (CORT) - the main GC in reptiles - and elevated temperature during development on learning in juveniles of two species of lizards, _Lampropholis delicata_ and _L.
+Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles - and incubation temperature on associative learning, using two species of lizards, _Lampropholis delicata_ and _L.
 guichenoti_.
-We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then subjected juveniles to a colour-associative learning task.
+We manipulated CORT levels and temperature in a 2x2 factorial design, and then subjected lizards to a colour-associative learning task.
 We predicted that elevated CORT and low temperatures would impair associative learning.
-**However, both species learned the task at the same rate independently of treatment.
-This suggests these two species may have evolved mechanisms to maintain learning abilities despite prenatal challegnes.
-We also found that lizards did not learn when food rewards were associated with blue-coloured ramps, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.**
+However, both species showed similar learning rates independently of treatment.
+This suggests these two species may have evolved mechanisms to maintain learning abilities despite prenatal challenges.
+We also found that learning rates where lower when food rewards were associated with blue-coloured ramps, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
 
@@
 However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014].
-These variations can further affect population dynamics, as differences in learning ability may lead to unequal responses to environmental pressures [@ward2016ecological; @welklin2024spatial].
+These variations can be product of innate preferences or perceptual biases that can affect the way information is acquired or the decision-making process [@toure2022colour].
+Yet, when researchers investigate how factors like age or sex influence learning, they often overlook the potential effects of these factors on perceptual biases.
+
+Regardless, interindividual differences in cognition can lead to unequal responses to environmental pressures, with potential effects on population dynamics [@ward2016ecological; @welklin2024spatial].
 For example, fast learners may better exploit novel resources or avoid new dangerous stimuli, while those with lower learning capabilities might struggle to adapt to environmental changes.
 This could affect their survival and reproductive output, ultimately influencing population growth rates and stability [@ward2016ecological; @welklin2024spatial].
-Therefore, understanding the factors that shape learning is crucial to predict how populations will respond to novel circumstances.
-
-Developmental conditions are especially relevant in shaping learning abilities because the brain is highly susceptible to environmental inputs during early stages of life [@zhu_prenatal_2004].
+Therefore, understanding the factors that shape cognition is crucial to predict how populations will respond to novel circumstances.
+
+Developmental conditions are especially relevant in shaping cognition because the brain is highly susceptible to environmental inputs during early stages of life [@zhu_prenatal_2004].
 Impacts on brain development can have long-lasting effects on cognition, potentially influencing an individual's ability to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
@@
 In addition to the environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-In ectotherms, early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits including growth, metabolism, or learning abilities [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
+In ectotherms, early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits including growth, metabolism, or cognition [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
 For instance, Port Jackson sharks (_Heterodontus portusjacksoni_) incubated at 23.6ºC took fewer days to reach a learning criterion in a numerical learning task than those incubated at 20.6ºC [@vila_pouca_quantity_2019].
@@
 
-Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - and incubation temperature on learning in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - and incubation temperature on cognition in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 #### Subjects  
-_Lampropholis delicata and _L.
+_Lampropholis delicata_ and _L.
 guichenoti_ are small [∼35-55 mm snout-vent length (SVL)], oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011].
@@
 
-We used the posterior distributions of parameters to test for differences in learning rate between treatments and species.
-Slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
-Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
-p~mcmc~ test the hypothesis that slopes and slopes contrasts are different from zero.
+We used the posterior distributions of parameters to test for differences in learning rates between treatments and species.
+These learning rates were the estimated slopes of the ‘trial’ and its interaction with hormone and temperature treatments.
+Learning rates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
+
+Because perception can play a role in the learning process [@toure2022colour], we also tested if lizards were biased towards the assigned colour.
+We estimated the predicted probability of choosing the correct ramp first in the first trial (hereafter also referred to as Decision making) using the intercepts from our posterior distributions.
+This probability was estimated by using the formula:
+$$\text{Probability} = \frac{e^{Intercept}}{1 + e^{Intercept}}$$
+
+We used p~mcmc~ to test the hypotheses that learning rates and contrasts were different from zero, and that probability of choosing correctly in the first trial was higher than expected by chance (0.33).
 We considered statistical significant if p~mcmc~ < 0.05.
@@
 gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial + guich_blue$'b_Trial:cortControl' + guich_blue$'b_Trial:tempHot')
-```
-
-We found that the rate of learning was lower when the blue ramps were the correct choice compared to the red ramps, for _L.
-delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc = `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
-guichenoti_ (mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
-However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see _Supplementary Material_) that could be affecting the estimated slopes.
-As such, we analyzed the differences between treatments for each group separately.
-
-For those _L.
-delicata_ assigned to group red, we did not find any significant differences between hormones (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
-Similarly, those assigned to blue were not afected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
+#
+# Modyfying a parameter for the results later (see p_format function in func.R)
+equal <- TRUE
+```
+
+Decision making when the correct ramp was red was not different to the probability of choosing correctly when the correct ramp was blue for _L.
+delicata_ (mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]; mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, see @fig-deli).
+nor for _L.
+guichenoti_ (mean P~Red~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]; mean P~Blue~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, see @fig-guich).
+However, in both species, the probability of choosing the correct ramp when the ramp was blue was significantly higher than expected by chance (0.33) only when the correct ramp was blue (see @fig-deli A,C; @fig-guich A, C; and see Table 2 in _Supplementary Material_).
+
+We found that the rate of learning was not different when the correct ramp was red or blue for _L.
+delicata_ (mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), nor for _L.
+guichenoti_ (mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
+
+Decision making in _L.
+delicata_ was not impacted by the CORT (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_drControlCold, probright_drControlHot)) - mean(c(probright_drCORTCold, probright_drCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlCold, probright_drControlHot) - c(probright_drCORTCold, probright_drCORTHot)), 3)`), incubation temperature (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_drControlHot, probright_drCORTHot)) - mean(c(probright_drControlCold, probright_drCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlHot, probright_drCORTHot) - c(probright_drControlCold, probright_drCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_drControlHot - probright_drCORTHot) - mean(probright_drControlCold - probright_drCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_drControlHot - probright_drCORTHot - (probright_drControlCold - probright_drCORTCold)), 3)`) when red ramps were the correct choice (see @fig-deli A).
+When blue ramps were the correct choice, there was no significant effect of hormone (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_dbControlCold, probright_dbControlHot)) - mean(c(probright_dbCORTCold, probright_dbCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbControlCold, probright_dbControlHot) - c(probright_dbCORTCold, probright_dbCORTHot)), 3)`), temperature (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_dbControlHot, probright_dbCORTHot)) - mean(c(probright_dbControlCold, probright_dbCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbControlHot, probright_dbCORTHot) - c(probright_dbControlCold, probright_dbCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_dbControlHot - probright_dbCORTHot) - mean(probright_dbControlCold - probright_dbCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_dbControlHot - probright_dbCORTHot - (probright_dbControlCold - probright_dbCORTCold)), 3)`) either (see @fig-deli D).
+
+Learning rates for those _L.
+delicata_ assigned to red ramps did show any significant effects of CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold, dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold, dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli B, C).
+Similarly, those assigned to blue were not affected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold, dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold, dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli E, F).
 
@@
   annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 4.5, color = "black", fontface = "italic")
-ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
+ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 20, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/fig_deli.png")
@@
 
-In _L.
-guichenoti_, we did not find any significant differences between hormone treatments (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the red group (@fig-guich A, B); and we did not find any significant effect of hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to blue either (@fig-guich C, D).
+Decision making in _L.
+guichenoti_ when the red ramps are the correct choice, was not affected by the hormone treatment (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_grControlCold, probright_grControlHot)) - mean(c(probright_grCORTCold, probright_grCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlCold, probright_grControlHot) - c(probright_grCORTCold, probright_grCORTHot)), 3)`), temperature treatment (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_grControlHot, probright_grCORTHot)) - mean(c(probright_grControlCold, probright_grCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlHot, probright_grCORTHot) - c(probright_grControlCold, probright_grCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_grControlHot - probright_grCORTHot) - mean(probright_grControlCold - probright_grCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_grControlHot - probright_grCORTHot - (probright_grControlCold - probright_grCORTCold)), 3)`; see @fig-guich A).
+When blue ramps were the correct choice, neither CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_gbControlCold, probright_gbControlHot)) - mean(c(probright_gbCORTCold, probright_gbCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbControlCold, probright_gbControlHot) - c(probright_gbCORTCold, probright_gbCORTHot)), 3)`) incubation temeprature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_gbControlHot, probright_gbCORTHot)) - mean(c(probright_gbControlCold, probright_gbCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbControlHot, probright_gbCORTHot) - c(probright_gbControlCold, probright_gbCORTCold)), 3)`; ), or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_gbControlHot - probright_gbCORTHot) - mean(probright_gbControlCold - probright_gbCORTCold), 3)`) have significant effects (@fig-guich D).
+
+Learning rates in _L.
+guichenoti_ were not influenced by hormone treatment (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold, gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold, gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature treatment (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) when red ramps were the correct choice (@fig-guich B, C).
+Similarly, CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold, gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold, gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or theirthe interaction interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) were not significant for _L.
+guichenoti_ assigned to blue ramps (see @fig-guich E, F).
 
@@
   annotate("text", x = 0.5, y = 0.985, label = "Lampropholis guichenoti", size = 4.5, color = "black", fontface = "italic")
-ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 25, height = 18, units = "cm", dpi = 600)
+ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 25, height = 20, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/fig_guich.png")
@@
 
-Finally, we also did not find any significant differences when we compared the estimated slopes between species for red group (mean β~_L.
+Overall, decision making did not differ between species when the red ramps were the correct choice (mean P~_L.
+delicata_~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~_L.
+delicata_~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]; mean P~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI P~_L.
+guichenoti_~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]; Contrast between probabilities: P~_L.
+delicata_~ - P~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`) or when the blue ramps were the correct choice (mean P~_L.
+delicata_~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P ~_L.
+delicata_~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI P~_L.
+guichenoti_~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; P~_L.
+delicata_~ - P~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`).
+
+When we average learning rates across treatments, we did not find any significant differences between species when the red ramp was the correct choice (mean β~_L.
 delicata_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)), 3)`, 95% CI β~_L.
@@
 guichenoti_~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, 95% CI β~_L.
-guichenoti_~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.975), 3)`]; β~_L.
+guichenoti_~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~_L.
 delicata_~ - β~_L.
-guichenoti_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the blue group (mean β~_L.
+guichenoti_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) neither when the blue ramps were the correct choice (mean β~_L.
 delicata_~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~_L.
@@
 guichenoti_~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~_L.
-guichenoti_~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; β~_L.
+guichenoti_~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; Contrast between slopes: β~_L.
 delicata_~ - β~_L.
@@
 delicata_ and _L.
-guichenoti_ is robust to elevations in prenatal CORT and incubation temperature.
-We predicted that elevating CORT levels in eggs or incubating them at colder temperatures would decrease learning slopes, and that warmer incubation temperatures would relax the effects of CORT elevations.
+guichenoti_ is robust to increased exposure to prenatal CORT and incubation temperature.
+We predicted that elevating CORT levels in eggs or incubating them at colder temperatures would decrease learning rates, and that warmer incubation temperatures would relax the effects of CORT elevations.
 In contrast to our predictions, both species learned to associate a colour with a food reward at the same rate regardless of the experimental treatments.
@@
 
-In addition, we found that the learning rates varied depending on the colour assigned to the correct choice, at least for _L.
-delicata_, with lizards assigned to blue ramps showing lower learning slopes than in the red group.
-This outcome manifests the need to consider the potential effects of colour biases in the design of cognitive tasks.
+In addition, we did not find any effect of treatment on Decision making, considered here as the probability of choosing correctly in the first trial.
+However, we found that this probability was higher that the one expected by chance exclusively when the correct ramp was blue in three of the prenatal treatments in _L.
+delicata_, and for CORT-Cold incubated _L.
+guichenoti_.
 
@@
 Prenatal CORT was predicted to have a negative effect on learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn; @bebus_associative_2016].
-However, we did not find any significant difference between hormone treatments in either of the two species.
+However, we did not find any significant difference in learning rates between hormone treatments in either of the two species.
 Our results are consistent with other experiments that showed no influence of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016; @farrell_developmental_2016] and suggest that _L.
 delicata_ and _L.
-guichenoti_ may have evolved some strategies to buffer the impacts of prenatal stress.
+guichenoti_ may have evolved strategies to buffer the impacts of prenatal stress.
 
@@
 GCs are known to have hormetic effects.
-Generally, low elevations or short exposure to GCs improve the rate at which animals learn while high concentrations or exposure to GCs during long periods have the opposite effects [@du_dynamic_2009; @mcewen_brain_2012].
-When using the same dose and application methods in eggs of _L.
-delicata_, @crino2024eggs found CORT treatment had sustained effects on mass and mitochondrial activity, but not baseline CORT.
-In contrast, lower CORT concentration did not affect mass or mitochondrial activity, but increased CORT baseline levels [@crino2024eggs].
+Generally, low concentrations or short exposure to GCs have been shown to improve the rate at which animals learn while high concentrations or exposure to GCs during long periods have the opposite effects [@du_dynamic_2009; @mcewen_brain_2012].
 This suggests that high elevations in CORT could affect learning through permanent changes in brain function (programmatic effects) while lower doses can result in lifelong elevation of baseline CORT, affecting learning through activational effects.
@@
 delicata_ and _L.
-guichenoti_ is robust to the programmatic effects of high CORT elevations, but we cannot exclude the possibility that lower concentrations may affect learning abilities.
-
-Conversely, the absence of significant effects of prenatal CORT on learning could be due to the cognitive task employed, as some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
-GCs action involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed unevenly in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
+guichenoti_ is robust to the programmatic effects of elevated CORT exposure, but we cannot exclude the possibility that lower concentrations may affect learning abilities.
+
+Conversely, the absence of significant effects of prenatal CORT on learning could be due to the cognitive task employed.
+Some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
+GCs actions involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed differentialy in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
 For instance, in european starlings (_Sturnus vulgaris_), males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn].
@@
 #### Effect of incubation temperature on learning
-We also predicted hot-incubated lizards to perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+We predicted hot-incubated lizards would perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
 Furthermore, the opposite pattern was found only in studies that employed temperatures far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020], and it is unclear how such conditions relate to wild environments.
@@
 Our results, therefore, do not align with the outcome observed in previous experiments.
-However, the effect of prenatal temperature on cognition, and brain physiology and structure has been investigated only in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how thermal early environment can affect cognitive abilities.
-According to our observations, the impact of incubation temperature on learning may not be as widespread across reptiles as we may think.
+However, the effect of prenatal temperature on cognition, and brain physiology and structure has been investigated only in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how early thermal environment can affect cognitive abilities.
+Our results suggest that the impact of incubation temperature on learning may not be as widespread across reptiles as we think.
 
 Alternatively, other factors, such as sex-dependent effects, could be affecting our findings.
-We did not include sex as a predictor for several reasons: first, lizards were tested before sexual maturation [@joss1985reproductive]; and second, previous studies have found weak evidence for sex-dependent learning in reptiles [@szabo_sex_meta].
-In fact, in the eastern three-lined skink (_Bassiana dupeyerri_) the effect of incubation temperature on learning is not sex-dependent [@amiel_hotter_2012; @clark_colour_2014].
-However, there is previous evidence for interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
-Notably, in _B.
+Not only temperature is a prominent factor in environmental sex determination in reptiles [@pieau1996temperature], but also previous studies have documented interactive effects of incubation temperature and sex on brain physiology in leopard geckos (_Eublepharis macularius_) [@coomber_independent_1997; @sakata_neural_2000].
+In contrast,  @szabo_sex_meta meta-analysis found weak evidence for sex-dependent learning in reptiles, and in the eastern three-lined skink (_Bassiana dupeyerri_) the effect of incubation temperature on learning is not sex-dependent [@amiel_hotter_2012; @clark_colour_2014].
+However, in @szabo_sex_meta the authors did not explore the interactive effects of sex and incubation temperature, and in _B.
 dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal, where individuals under cold incubation temperatures develop male phenotypes while retaining female genotypes [@quinn2009isolation].
-As a result, even when examining the interactive effects of sex and temperature in this species, the results could be confounded by the mismatch between genotype and phenotype [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Although sex-reversal does not occur in _L.
-delicata_ or _L.
-guichenoti_, not accounting for sex in our analyses could be masking potential interactions between temperature and sex in shaping learning abilities [see @coomber_independent_1997; @sakata_neural_2000].
+Therefore, even when examining the interactive effects of sex and temperature in this species, the results could be confounded by the mismatch between genotype and phenotype [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Here, we did not include sex as a predictor because lizards were tested before sexual maturation [@joss1985reproductive], but not accounting for sex in our analyses could be masking potential interactions between temperature and sex in shaping learning abilities [see @coomber_independent_1997; @sakata_neural_2000].
 Future research should investigate the potential interactive impacts of sex and incubation temperature on cognitive abilities.
@@
 #### Effect of colour on learning
-The colour of the ramp associated with the attainable cricket (i.e.
-the correct choice) influences learning slopes in _L.
-delicata_, but not _L.
-guichenoti_.
-_L.
-delicata_ learned the task when the reward was associated to the red ramp but not when the ramp was blue.
-In contrast, _L.
-guichenoti_ showed similar results despite the colour of the correct ramp.
-This indicates that _L.
-delicata_ were not able to associate the blue ramp with the reward.
+We did not find any significant effects of the colour of the correct ramp on learning rates in either species.
+However, Table 1 in the _Supplementary Material_ shows that the learning rates are not different from zero in most of the _L.
+delicata_ lizards, and CORT-Cold _L.
+guichenoti_ (see also @fig_deli B, E; @fig-guich B, E).
+In contrasts, learning rates when the correct ramp was red were different from zero in all treatments.
 However, our results could be a consequence of an initial bias in lizards' choice.
-The analyses presented in the Supplemenatry Material show that, overall, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue ramp.
-These lizards show learning slopes not different from zero, but high probabilities of choosing the correct ramp also in the first trials (see @fig-deli).
+The analyses presented in Table 2 in _Supplemenatry Material_ (but also see @fig-deli A, C; @fig-guich A, C) show that the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue ramp.
+Those lizards showing learning rates not different from zero, also exhibited higher probabilities of choosing the correct ramp also in the first trials.
 
@@
 This outcome contrasts with our initial predictions, indicating that the learning skills of these lizards may be more robust than anticipated under varying early life conditions.
-We also found significant effects of the colour employed in the task on learning rates in _L.
-delicata_, but not in _L.
+We also found significant effects of the colour employed in the task on learning rates in most _L.
+delicata_ and some _L.
 guichenoti_.
@@
 
-#### Estimates of reversal learning slopes for all the different treatments per each task, specie, and group.
-Table 1.
-Estimates of learning slopes for all the different treatments per each task, specie, and group.
+#### Estimates of learning rates for all the different treatments per each task, specie, and group.
+Table 2.
+Estimates of learning rates for all the different treatments per each task, specie, and group.
 Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
@@
 In bold, those values that are significant (p~mcmc~ <0.05).
+
 ```{r, tbl-data, results='asis'}
 #| label: tbl-data
-#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+#| tbl-cap: "Estimates of learning rates for all the different treatments per each task, species, and group.
 Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
@@
 In bold, those values that are significant (pmcmc <0.05)"
-source(here("R", "func.R"))
-#
+source("./R/func.R")
+#
+# Modyfying a parameter for later (see p_format function in func.R)
+equal <- FALSE
 ############################## CREATING BIG DF FOR TABLE ##############################
@@
 Second, we tested the hypothesis that the estimated probability was higher than 0.33 (the probability expected by chance of choosing the correct ramp) using pmcmc.
-If the estimated probability is above 0.33 we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes.
+If the estimated probability is above 0.33 we consider it as an indication that there was a preference towards that colour that could be affecting learning rates.
 The results per treatment are summarized in Table 2.
 
-Table 2.
+Table 1.
 Probability of choosing the correct ramp in the first trial when the correct ramp was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
@@
 source(here("R", "func.R"))
-# First we estimate the probability of choosing right in the first trial using the intercepts from the posteriors
-## 1) L. delicata
-### Group = red
-probright_drCORTCold <- exp(deli_red$b_Intercept)/(1+exp(deli_red$b_Intercept))
-probright_drControlCold <- exp(deli_red$b_cortControl + deli_red$b_Intercept)/(1+exp(deli_red$b_cortControl + deli_red$b_Intercept))
-probright_drCORTHot <- exp(deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$b_tempHot + deli_red$b_Intercept))
-probright_drControlHot <- exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept))
-### Group = blue
-probright_dbCORTCold <- exp(deli_blue$b_Intercept)/(1+exp(deli_blue$b_Intercept))
-probright_dbControlCold <- exp(deli_blue$b_cortControl + deli_blue$b_Intercept)/(1+exp(deli_blue$b_cortControl + deli_blue$b_Intercept))
-probright_dbCORTHot <- exp(deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$b_tempHot + deli_blue$b_Intercept))
-probright_dbControlHot <- exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept))
-## 2) L. guichenoti
-### Group = red
-probright_grCORTCold <- exp(guich_red$b_Intercept)/(1+exp(guich_red$b_Intercept))
-probright_grControlCold <- exp(guich_red$b_cortControl + guich_red$b_Intercept)/(1+exp(guich_red$b_cortControl + guich_red$b_Intercept))
-probright_grCORTHot <- exp(guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$b_tempHot + guich_red$b_Intercept))
-probright_grControlHot <- exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept))
-### Group = blue
-probright_gbCORTCold <- exp(guich_blue$b_Intercept)/(1+exp(guich_blue$b_Intercept))
-probright_gbControlCold <- exp(guich_blue$b_cortControl + guich_blue$b_Intercept)/(1+exp(guich_blue$b_cortControl + guich_blue$b_Intercept))
-probright_gbCORTHot <- exp(guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$b_tempHot + guich_blue$b_Intercept))
-probright_gbControlHot <- exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept))
-#
-# Second we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species
+#
+# Modyfying a parameter for later (see p_format function in func.R)
+equal <- FALSE
+# First we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species (see results chunk)
 prob_df <- data.frame(
@@
 colour_table
+#
+# Modyfying a parameter for later (see p_format function in func.R)
+equal <- TRUE
 ```
@@
 cat("\\newpage")
-```
-
-#### Preliminary analyses
-```{r, modelsage}
-#| label: modelsage
-# Fitting the models for L. delicata and L. guichenoti including age as a covariate
-#
-data_prel <- data_clean %>%
-  mutate(age.start = as.numeric(age.start)-mean(as.numeric(age.start)))
-#
-refit2 = FALSE
-formula <- FC_associative ~ age.start + group*trial_associative + trial_associative*cort*temp + 
-                            (1 + trial_associative|lizard_id) + (1|clutch)
-species <- c("delicata", "guichenoti")
-#
-models <- list() # Create an empty list to store the models
-for(s in species){
-    # Subset the data for the species
-    data_species <- data_prel %>%
-    filter(species == s)
-    model_file <- paste0("output/models/model_prel_", s, ".rds")
-# Fit the model only if it has not been fit yet (if refit2 = TRUE)
-  if(refit2 == TRUE){
-    # Fit the model
-    model <- brm(formula,
-                data = data_species,
-                family = bernoulli(link = "logit"),
-                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
-    # Write the model to a file
-    saveRDS(model, file = model_file)
-  } else {
-      # Read the model from a file
-      model <- readRDS(file = model_file)
-  }
-  # Save the model to the list
-  models[[paste0(s)]] <- model
-}
-#
-model_prel_deli <- models[["delicata"]]
-model_prel_guich <- models[["guichenoti"]]
-#
-summary(model_prel_deli)
-summary(model_prel_guich)
 ```

### 2024-10-09 ms.qmd
Updates

--- 2024-09-22 ms.qmd
@@
 ---
-title: "Early environmental conditions do not impact associative learning in two lizard species"
+title: "Cognitive processes are robust to early environmental conditions in two lizard species"
 format:
@@
 
-Pablo Recio^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^
+Pablo Recio^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Kristoffer H. Wild^1,3^, Christopher R. Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^
 
@@
 Animals must acquire new information through learning to adjust their behaviour adaptively.
-However, learning ability can be constrained by the conditions experienced during early stages of development, when the brain is especially susceptible to environmental inputs.
-Temperature is a pervasive mechanism of phenotypic plasticity in ectotherms, exerting direct effects on growth, metabolism, or learning.
-In vertebrates, abrupt thermal changes can trigger a chronic stress, which is mediated by glucocorticoids that can be transmitted to the offspring, potentially impacting their learning abilities.
-Glucocorticoids and the thermal environments are therefore predicted to have interactive effects on the development of learning functions in animals.
-Here, we investigated the combined effects of corticosterone (CORT) - the main GC in reptiles - and elevated temperature during development on learning in juveniles of two species of lizards, _Lampropholis delicata_ and _L.
+However, learning ability can be constrained by conditions experienced during early stages of development, when the brain is especially susceptible to environmental inputs.
+Temperature can result in phenotypically plastic adjustments to growth, metabolism, and learning in ectotherms.
+In vertebrates, abrupt thermal changes can also trigger chronic stress, which is mediated by glucocorticoids that can be transmitted to offspring, potentially impacting their learning abilities.
+Glucocorticoids and thermal environments are therefore predicted to have interactive effects on the development of learning in ectotherms.
+Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles - and incubation temperature on associative learning, using two species of lizards, _Lampropholis delicata_ and _L.
 guichenoti_.
-We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then subjected juveniles to a colour-associative learning task.
+We manipulated CORT levels and temperature in a 2x2 factorial design, and then subjected lizards to a colour-associative learning task.
 We predicted that elevated CORT and low temperatures would impair associative learning.
-**However, both species learned the task at the same rate independently of treatment.
-This suggests these two species may have evolved mechanisms to maintain learning abilities despite prenatal challegnes.
-We also found that lizards did not learn when food rewards were associated with blue-coloured ramps, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.**
+However, both species showed similar learning rates independently of treatment.
+Our results suggest that these two species may have evolved mechanisms to maintain learning performance despite prenatal challenges.
+**We also found that learning rates where slower when food rewards were associated with blue-coloured ramps, a possible effect of developmental environment on the visual-sensory system, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.**
 
@@
 These processes are fundamental to foraging, mate selection, antipredatory strategies, and social behaviours, all of which are crucial for survival and reproduction [@dukas_evolutionary_2004].
-Particularly, learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
+Learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
 However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014].
-These variations can further affect population dynamics, as differences in learning ability may lead to unequal responses to environmental pressures [@ward2016ecological; @welklin2024spatial].
+Interindividual differences in learning can lead to unequal responses to environmental pressures, with potential effects on population dynamics [@ward2016ecological; @welklin2024spatial].
 For example, fast learners may better exploit novel resources or avoid new dangerous stimuli, while those with lower learning capabilities might struggle to adapt to environmental changes.
@@
 
-Developmental conditions are especially relevant in shaping learning abilities because the brain is highly susceptible to environmental inputs during early stages of life [@zhu_prenatal_2004].
-Impacts on brain development can have long-lasting effects on cognition, potentially influencing an individual's ability to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
-For example, the state of the mother can influence offspring phenotype beyond genetic transmission through nest-site selection, provisioning, or the transmission of hormones or nutrients [i.e., 'maternal effects' @moore_mothers_2019]; and the developing brain is not exempt of these effects.
+Variation in learning is thought to be a product of an individual's capacity to form associations between stimuli through memory formation.
+However, differences in learning among individuals can also be a consequence of innate preferences or perceptual biases that influence how information is acquired and affect the decision-making process [@toure2022colour].
+The brain's integration of information and the establishment of new connections is a complex process, involving interactions among various nuclei to generate responses [@dukas_evolutionary_2004].
+Consequently, any impact on specific brain regions or their interactions can directly influence learning through memory formation or alterations in decision-making.
+
+Developmental conditions are especially relevant in shaping cognitive abilities because the brain is highly susceptible to environmental inputs during early stages of life [@zhu_prenatal_2004].
+Impacts on brain development can have long-lasting effects on cognition, potentially influencing an individual's capacity to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
+For example, the state of the mother can influence offspring phenotype beyond genetic transmission through nest-site selection, provisioning, or the transmission of hormones or nutrients [i.e., 'maternal effects' @moore_mothers_2019]; and the developing brain is also susceptible to these effects.
 
@@
 Under stressful situations, animals react by instigating adaptive physiological and behavioural adjustments mediated by GCs.
-These GCs can be transmitted directly from the parents to their offspring with different effects on offspring phenotype [@Crino_2023].
-Elevations in GCs during early stages of development typically result in altered neurogenesis, brain structure, and metabolic activity that in most cases are related to decreased learning abilities [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009; @eaton2015mild; @farrell_developmental_2015-learn; @farrell_developmental_2016].
-For instance, prenatal stress in rats (_Rattus norvegicus_) induced reduction of neurogenesis in the dentate gyrus associated to impairments in hippocampal-related spatial tasks [@lemaire_prenatal_2000].
-However, factors like sex or the nature of the learning task can affect the direction and magnitude of the effects of prenatal exposure to elevated GCs [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016; @farrell_developmental_2016].
+These GCs can be transmitted directly from parents to their offspring with different effects on offspring phenotype [@Crino_2023].
+Elevation in GCs during early stages of development typically result in altered neurogenesis, brain structure, and metabolic activity that in most cases are related to decreased learning abilities [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009; @eaton2015mild; @farrell_developmental_2015-learn; @farrell_developmental_2016].
+For instance, prenatal stress in rats (_Rattus norvegicus_) suppresses neurogenesis in the dentate gyrus and is associated to impairments in hippocampal-related spatial tasks [@lemaire_prenatal_2000].
+Factors such as sex or the nature of the learning task can also affect the direction and magnitude of the effects of prenatal exposure to elevated GCs [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016; @farrell_developmental_2016].
 Because the effects of prenatal GCs on learning can be context-dependent, it is crutial to conduct studies across diverse taxa and experimental conditions to fully understand these effects.
@@
 In addition to the environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-In ectotherms, early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits including growth, metabolism, or learning abilities [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
+In ectotherms, the early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits including growth, metabolism, or cognition [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
 For instance, Port Jackson sharks (_Heterodontus portusjacksoni_) incubated at 23.6ºC took fewer days to reach a learning criterion in a numerical learning task than those incubated at 20.6ºC [@vila_pouca_quantity_2019].
@@
 This implies that the effects of GCs and temperature could be interdependent, with the impact of one factor being modulated by the other.
-However, the interactive effects of GCs and temperature on learning abilities remain unexplored.
-
-Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - and incubation temperature on learning in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+However, the interactive effects of GCs and temperature on learning abilities remain unexplored, yet an understanding of how temperature and GC’s interact is particularly relevant in the context of global climate change [@vinogradov2024inbreeding].
+
+Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - and incubation temperature on cognition in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 Post-incubation, juveniles were subjected to a colour-associative task to assess their learning abilities.
-We hypothesized that prenatal CORT levels and thermal environment will induce sustained effects on brain's physiology, ultimately impacting learning of the association task.
-We predicted that individuals exposed to high levels of CORT or low temperatures will learn slower than control individuals or those incubated at higher temperatures [@zhu_prenatal_2004; @amiel_hotter_2012; @eaton2015mild; @amiel_effects_2017].
-Additionally, we predicted that incubation at high temperatures will mitigate the impact of CORT on skinks' performance, while cold incubation temperatures were expected to enhance the effects of CORT.
+We hypothesized that prenatal CORT levels and thermal environment would induce sustained effects on brain physiology, ultimately impacting learning of an association task.
+We predicted that individuals exposed to high levels of CORT or low temperatures would learn slower than control individuals or those incubated at higher temperatures [@zhu_prenatal_2004; @amiel_hotter_2012; @eaton2015mild; @amiel_effects_2017].
+Additionally, we predicted that incubation at high temperatures would mitigate the impact of CORT on learning performance, while cold incubation temperatures were expected to enhance the effects of CORT.
 This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
@@
 #### Statistical analyses  
-We performed analyses for species separately.
+We performed analyses for each species separately.
 Preliminary analyses showed a significant effect of the colour.
@@
 
-We used the posterior distributions of parameters to test for differences in learning rate between treatments and species.
-Slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
-Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
-p~mcmc~ test the hypothesis that slopes and slopes contrasts are different from zero.
+Learning rates were the estimated slopes of ‘trial’ and its interaction with hormone and temperature treatments.
+We used the posterior distributions of parameters to test for differences in learning rates between treatments and species.
+Slopes directly measure the change in the probability of choosing the correct dish across trials.
+Learning rates greater than zero, indicating that lizards were improving over trails, were considered as evidence of learning, while those less or equal to zero were not.
+
+Decision making, in contrast, is considered the average probability of choosing correct at a given trial.
+We estimated the predicted probability of choosing the correct ramp in the first trial using the intercepts from our posterior distributions following the formula:
+
+$$
+\text{Probability}_{\text{(Trial)}} = \frac{e^{(\text{Intercept } + \text{ Slope } \times \text{ Trial})}}{1 + e^{(\text{Intercept } + \text{ Slope } \times \text{ Trial})}}
+$$
+
+In our case, we were interested in estimating the probability of correct choice at early stages of learning [P~(1)~] because perception can play a role in the learning process [@toure2022colour].
+It also allowed us to test if lizards were biased towards the assigned colour.
+
+We calculated the p~mcmc~ to test the hypothesis that learning rates and contrasts were different from zero, and that the probability of choosing correctly in the first trial was higher than expected by chance (0.33).
 We considered statistical significant if p~mcmc~ < 0.05.
@@
 Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
-However, due to natural mortality (n = 11), incompletion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we had a final sample size of 81 lizards.
+However, due to natural mortality (n = 11), failing to pass the training stage (n = 1), or lack of motivation during the learning tasks (n = 3), we had a final sample size of 81 lizards.
 Final sample sizes per treatment and species are listed in @fig-deli and @fig-guich (figures for both species with the raw data are included in the _Supplementary Material_).
@@
 gab_ControlHot <- (guich_blue$'b_Trial:cortControl:tempHot' + guich_blue$b_Trial + guich_blue$'b_Trial:cortControl' + guich_blue$'b_Trial:tempHot')
-```
-
-We found that the rate of learning was lower when the blue ramps were the correct choice compared to the red ramps, for _L.
-delicata_ (mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc = `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), but not for _L.
-guichenoti_ (mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).
-However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see _Supplementary Material_) that could be affecting the estimated slopes.
-As such, we analyzed the differences between treatments for each group separately.
-
-For those _L.
-delicata_ assigned to group red, we did not find any significant differences between hormones (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B).
-Similarly, those assigned to blue were not afected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).
+#
+# Rename some of the posteriors and obtain estimates for the "decision making" for each group and treatment. This "decision making" consists of the probability of choosing right in the first trial. 
+## 1) L. delicata
+### Group = red
+probright_drCORTCold <- exp(deli_red$b_Intercept + dar_CORTCold)/(1+exp(deli_red$b_Intercept + dar_CORTCold))
+probright_drControlCold <- exp(deli_red$b_cortControl + deli_red$b_Intercept + dar_ControlCold)/(1+exp(deli_red$b_cortControl + deli_red$b_Intercept + dar_ControlCold))
+probright_drCORTHot <- exp(deli_red$b_tempHot + deli_red$b_Intercept + dar_CORTHot)/(1+exp(deli_red$b_tempHot + deli_red$b_Intercept + dar_CORTHot))
+probright_drControlHot <- exp(deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept + dar_ControlHot)/(1+exp(deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept + dar_ControlHot))
+### Group = blue
+probright_dbCORTCold <- exp(deli_blue$b_Intercept + dab_CORTCold)/(1+exp(deli_blue$b_Intercept + dab_CORTCold))
+probright_dbControlCold <- exp(deli_blue$b_cortControl + deli_blue$b_Intercept + dab_ControlCold)/(1+exp(deli_blue$b_cortControl + deli_blue$b_Intercept + dab_ControlCold))
+probright_dbCORTHot <- exp(deli_blue$b_tempHot + deli_blue$b_Intercept + dab_CORTHot)/(1+exp(deli_blue$b_tempHot + deli_blue$b_Intercept + dab_CORTHot))
+probright_dbControlHot <- exp(deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept + dab_ControlHot)/(1+exp(deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept + dab_ControlHot))
+## 2) L. guichenoti
+### Group = red
+probright_grCORTCold <- exp(guich_red$b_Intercept + gar_CORTCold)/(1+exp(guich_red$b_Intercept + gar_CORTCold))
+probright_grControlCold <- exp(guich_red$b_cortControl + guich_red$b_Intercept + gar_ControlCold)/(1+exp(guich_red$b_cortControl + guich_red$b_Intercept + gar_ControlCold))
+probright_grCORTHot <- exp(guich_red$b_tempHot + guich_red$b_Intercept + gar_CORTHot)/(1+exp(guich_red$b_tempHot + guich_red$b_Intercept + gar_CORTHot))
+probright_grControlHot <- exp(guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept + gar_ControlHot)/(1+exp(guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept + gar_ControlHot))
+### Group = blue
+probright_gbCORTCold <- exp(guich_blue$b_Intercept + gab_CORTCold)/(1+exp(guich_blue$b_Intercept + gab_CORTCold))
+probright_gbControlCold <- exp(guich_blue$b_cortControl + guich_blue$b_Intercept + gab_ControlCold)/(1+exp(guich_blue$b_cortControl + guich_blue$b_Intercept + gab_ControlCold))
+probright_gbCORTHot <- exp(guich_blue$b_tempHot + guich_blue$b_Intercept + gab_CORTHot)/(1+exp(guich_blue$b_tempHot + guich_blue$b_Intercept + gab_CORTHot))
+probright_gbControlHot <- exp(guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept + gab_ControlHot)/(1+exp(guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept + gab_ControlHot))
+#
+# Modyfying a parameter for the results later (see p_format function in func.R)
+equal <- TRUE
+```
+
+#### Early developmental environments do not influence visual-sensory systems to impact decision making
+
+**Decision making when the correct ramp was red was not different to the probability of choosing correctly when the correct ramp was blue for _L.
+delicata_ (mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]; mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, see @fig-deli).
+nor for _L.
+guichenoti_ (mean P~Red~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]; mean P~Blue~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, see @fig-guich).
+However, in both species, the probability of choosing the correct ramp when the ramp was blue was significantly higher than expected by chance (0.33) only when the correct ramp was blue (see @fig-deli A,C; @fig-guich A, C; and see Table 2 in _Supplementary Material_).
+We found that the rate of learning was not different when the correct ramp was red or blue for _L.
+delicata_ (mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), nor for _L.
+guichenoti_ (mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).**
+
+_Lampropholis delicata_: Decision making in _L.
+delicata_ was not impacted by the CORT (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_drControlCold, probright_drControlHot)) - mean(c(probright_drCORTCold, probright_drCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlCold, probright_drControlHot) - c(probright_drCORTCold, probright_drCORTHot)), 3)`), incubation temperature (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_drControlHot, probright_drCORTHot)) - mean(c(probright_drControlCold, probright_drCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlHot, probright_drCORTHot) - c(probright_drControlCold, probright_drCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_drControlHot - probright_drCORTHot) - mean(probright_drControlCold - probright_drCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_drControlHot - probright_drCORTHot - (probright_drControlCold - probright_drCORTCold)), 3)`) when red ramps were the correct choice (see @fig-deli A).
+When blue ramps were the correct choice, there was no significant effect of hormone (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_dbControlCold, probright_dbControlHot)) - mean(c(probright_dbCORTCold, probright_dbCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbControlCold, probright_dbControlHot) - c(probright_dbCORTCold, probright_dbCORTHot)), 3)`), temperature (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_dbControlHot, probright_dbCORTHot)) - mean(c(probright_dbControlCold, probright_dbCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbControlHot, probright_dbCORTHot) - c(probright_dbControlCold, probright_dbCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_dbControlHot - probright_dbCORTHot) - mean(probright_dbControlCold - probright_dbCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_dbControlHot - probright_dbCORTHot - (probright_dbControlCold - probright_dbCORTCold)), 3)`) either (see @fig-deli D).
+
+_Lampropholis guichenoti_: Decision making in _L.
+guichenoti_ when the red ramps are the correct choice, was not affected by the hormone treatment (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_grControlCold, probright_grControlHot)) - mean(c(probright_grCORTCold, probright_grCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlCold, probright_grControlHot) - c(probright_grCORTCold, probright_grCORTHot)), 3)`), temperature treatment (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_grControlHot, probright_grCORTHot)) - mean(c(probright_grControlCold, probright_grCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlHot, probright_grCORTHot) - c(probright_grControlCold, probright_grCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_grControlHot - probright_grCORTHot) - mean(probright_grControlCold - probright_grCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_grControlHot - probright_grCORTHot - (probright_grControlCold - probright_grCORTCold)), 3)`; see @fig-guich A).
+When blue ramps were the correct choice, neither CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(probright_gbControlCold, probright_gbControlHot)) - mean(c(probright_gbCORTCold, probright_gbCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbControlCold, probright_gbControlHot) - c(probright_gbCORTCold, probright_gbCORTHot)), 3)`) incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(probright_gbControlHot, probright_gbCORTHot)) - mean(c(probright_gbControlCold, probright_gbCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbControlHot, probright_gbCORTHot) - c(probright_gbControlCold, probright_gbCORTCold)), 3)`; ), or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_gbControlHot - probright_gbCORTHot) - mean(probright_gbControlCold - probright_gbCORTCold), 3)`) have significant effects (@fig-guich D).
 
@@
 #| label: fig-deli
-#| fig.cap: "Results for Lampropholis delicata for both colour groups red (A,B) and blue (C, D).
-Panels A and C show the predicted probability of choosing the correct ramp first over trials.
-The lines represent the mean predicted probability of choosing the correct ramp first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+#| fig.cap: "Results for Lampropholis delicata for both colour groups red (A, B, C) and blue (D, E , F).
+Panels A and D show the predicted probability of choosing the correct ramp in the first trial (Decision first trial).
+In panels B and E, the distribution of the estimates of slopes per each treatment.
+In all A, B, D, and E the x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
 The different colours indicate the different treatments.
-Panels B and D show the distribution of the estimates of slopes per each treatment.
-The x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
-The different colours indicate the different treatments.
-Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
+Points and bars represent the mean and standard deviation of the mean of the estimates, respectively.
+Dashed lines indicate value 0.33 (the probability of choosing correctly by chance) in panesl A, D, and 0 in panels B, E.
+Asterisks indicate significant results (p~mcmc~ < 0.05).
+Panels C and F show the predicted probability of choosing the correct ramp first over trials.
+The lines represent the mean predicted probability of choosing the correct ramp for each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours indicate the different treatments."
 source(here("R", "func.R"))
@@
 ## Red
-fig_dar_AC_df <- df_plotAC("deli_red")
-fig_dar_BD1_df <- df_plotBD1("deli_red")
-fig_dar_BD2_df <- df_plotBD2("deli_red")
+fig_dar_prob_df <- df_plotprob("deli_red")
+fig_dar_choiceviol_df <- df_plotviol("deli_red", "choice")
+fig_dar_choicepoints_df <- df_plotpoints("deli_red", "choice")
+fig_dar_sloviol_df <- df_plotviol("deli_red", "slope")
+fig_dar_slopoints_df <- df_plotpoints("deli_red", "slope")
 ## Blue
-fig_dab_AC_df <- df_plotAC("deli_blue")
-fig_dab_BD1_df <- df_plotBD1("deli_blue")
-fig_dab_BD2_df <- df_plotBD2("deli_blue")
+fig_dab_choiceviol_df <- df_plotviol("deli_blue", "choice")
+fig_dab_choicepoints_df <- df_plotpoints("deli_blue", "choice")
+fig_dab_sloviol_df <- df_plotviol("deli_blue", "slope")
+fig_dab_slopoints_df <- df_plotpoints("deli_blue", "slope")
+fig_dab_prob_df <- df_plotprob("deli_blue")
 #
 # Second step, create the plots
-fig_dar <- plotting(sp = "deli", col = "red", df_prob = fig_dar_AC_df, df_violin = fig_dar_BD1_df, df_points = fig_dar_BD2_df)
-fig_dab <- plotting(sp = "deli", col = "blue", df_prob = fig_dab_AC_df, df_violin = fig_dab_BD1_df, df_points = fig_dab_BD2_df)
+fig_dar <- plotting(sp = "deli", col = "red", 
+                    df_violin_1 = fig_dar_choiceviol_df, df_points_1 = fig_dar_choicepoints_df, 
+                    df_violin_2 = fig_dar_sloviol_df, df_points_2 = fig_dar_slopoints_df,
+                    df_prob = fig_dar_prob_df) +
+          annotate("text", x = 0.42, y = c(0.29,0.48,0.68,0.87), label = "*", size = 8, color = "black")
+fig_dab <- plotting(sp = "deli", col = "blue",
+                    df_violin_1 = fig_dab_choiceviol_df, df_points_1 = fig_dab_choicepoints_df,
+                    df_violin_2 = fig_dab_sloviol_df, df_points_2 = fig_dab_slopoints_df,
+                    df_prob = fig_dab_prob_df) +
+          annotate("text", x = 0.2, y = c(0.29,0.48,0.68,0.87), label = "*", size = 8, color = "black") +
+          annotate("text", x = 0.42, y = 0.87, label = "*", size = 8, color = "black")
 #
@@
   annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 4.5, color = "black", fontface = "italic")
-ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
+ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 28, height = 22, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/fig_deli.png")
@@
 
-In _L.
-guichenoti_, we did not find any significant differences between hormone treatments (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the red group (@fig-guich A, B); and we did not find any significant effect of hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to blue either (@fig-guich C, D).
+#### Early developmental environments do not impact the rates of learning across species
+
+_Lampropholis delicata_: Learning rates for those _L.
+delicata_ assigned to red ramps did not show any significant effects of CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dar_ControlCold, dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold, dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli B, C).
+Similarly, those assigned to blue were also not affected by CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(dab_ControlCold, dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold, dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli E, F).
+
+_Lampropholis guichenoti_: Learning rates in _L.
+guichenoti_ were not influenced by hormone treatment (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold, gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold, gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature treatment (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) when red ramps were the correct choice (@fig-guich B, C).
+Similarly, CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold, gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold, gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or theirthe interaction interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) were not significant for _L.
+guichenoti_ assigned to blue ramps (see @fig-guich E, F).
 
@@
 #| label: fig-guich
-#| fig.cap: "Results for Lampropholis guichenoti for both colour groups red (A,B) and blue (C, D).
-Panels A and C show the predicted probability of choosing the correct ramp first over trials.
-The lines represent the mean predicted probability of choosing the correct ramp first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+#| fig.cap: "Results for Lampropholis guichenoti for both colour groups red (A, B, C) and blue (D, E , F).
+Panels A and D show the predicted probability of choosing the correct ramp in the first trial (Decision first trial).
+In panels B and E, the distribution of the estimates of slopes per each treatment.
+In all A, B, D, and E the x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
 The different colours indicate the different treatments.
-Panels B and D show the distribution of the estimates of slopes per each treatment.
-The x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
-The different colours indicate the different treatments.
-Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
+Points and bars represent the mean and standard deviation of the mean of the estimates, respectively.
+Dashed lines indicate value 0.33 (the probability of choosing correctly by chance) in panesl A, D, and 0 in panels B, E.
+Asterisks indicate significant results (p~mcmc~ < 0.05).
+Panels C and F show the predicted probability of choosing the correct ramp first over trials.
+The lines represent the mean predicted probability of choosing the correct ramp for each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours indicate the different treatments."
 source(here("R", "func.R"))
@@
 ## Red
-fig_gar_AC_df <- df_plotAC("guich_red")
-fig_gar_BD1_df <- df_plotBD1("guich_red")
-fig_gar_BD2_df <- df_plotBD2("guich_red")
+fig_gar_choiceviol_df <- df_plotviol("guich_red", "choice")
+fig_gar_choicepoints_df <- df_plotpoints("guich_red", "choice")
+fig_gar_sloviol_df <- df_plotviol("guich_red", "slope")
+fig_gar_slopoints_df <- df_plotpoints("guich_red", "slope")
+fig_gar_prob_df <- df_plotprob("guich_red")
 ## Blue
-fig_gab_AC_df <- df_plotAC("guich_blue")
-fig_gab_BD1_df <- df_plotBD1("guich_blue")
-fig_gab_BD2_df <- df_plotBD2("guich_blue")
+fig_gab_choiceviol_df <- df_plotviol("guich_blue", "choice")
+fig_gab_choicepoints_df <- df_plotpoints("guich_blue", "choice")
+fig_gab_sloviol_df <- df_plotviol("guich_blue", "slope")
+fig_gab_slopoints_df <- df_plotpoints("guich_blue", "slope")
+fig_gab_prob_df <- df_plotprob("guich_blue")
 #
 # Second step, create the plots
-fig_gar <- plotting(sp = "guich", col = "red", df_prob = fig_gar_AC_df, df_violin = fig_gar_BD1_df, df_points = fig_gar_BD2_df)
-fig_gab <- plotting(sp = "guich", col = "blue", df_prob = fig_gab_AC_df, df_violin = fig_gab_BD1_df, df_points = fig_gab_BD2_df)
+fig_gar <- plotting(sp = "guich", col = "red", 
+                    df_violin_1 = fig_gar_choiceviol_df, df_points_1 = fig_gar_choicepoints_df, 
+                    df_violin_2 = fig_gar_sloviol_df, df_points_2 = fig_gar_slopoints_df,
+                    df_prob = fig_gar_prob_df) +
+          annotate("text", x = 0.42, y = c(0.29,0.48,0.68,0.87), label = "*", size = 8, color = "black")
+fig_gab <- plotting(sp = "guich", col = "blue",
+                    df_violin_1 = fig_gab_choiceviol_df, df_points_1 = fig_gab_choicepoints_df,
+                    df_violin_2 = fig_gab_sloviol_df, df_points_2 = fig_gab_slopoints_df,
+                    df_prob = fig_gab_prob_df) +
+          annotate("text", x = 0.2, y = c(0.48,0.87), label = "*", size = 8, color = "black")  +
+          annotate("text", x = 0.42, y = c(0.29,0.68,0.87), label = "*", size = 8, color = "black")
 #
@@
 
-Finally, we also did not find any significant differences when we compared the estimated slopes between species for red group (mean β~_L.
+#### Contrasting impacts of early developmental environments on decision making and learning in _Lampropholis delicata_ and _Lampropholis guichenoti_
+
+Overall, decision making did not differ between species when the red ramps (mean P~_L.
+delicata_~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~_L.
+delicata_~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]; mean P~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI P~_L.
+guichenoti_~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]; Contrast between probabilities: P~_L.
+delicata_~ - P~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`) or the blue ramps were the correct choice (mean P~_L.
+delicata_~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P ~_L.
+delicata_~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI P~_L.
+guichenoti_~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; P~_L.
+delicata_~ - P~_L.
+guichenoti_~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`).
+
+We also did not find any significant differences in learning rates between species when the red ramp (mean β~_L.
 delicata_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)), 3)`, 95% CI β~_L.
@@
 guichenoti_~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, 95% CI β~_L.
-guichenoti_~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.975), 3)`]; β~_L.
+guichenoti_~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.975), 3)`]; Contrast between slopes: β~_L.
 delicata_~ - β~_L.
-guichenoti_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the blue group (mean β~_L.
+guichenoti_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or blue ramp was the correct choice (mean β~_L.
 delicata_~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~_L.
@@
 
-Associative learning in _L.
-delicata_ and _L.
-guichenoti_ is robust to elevations in prenatal CORT and incubation temperature.
-We predicted that elevating CORT levels in eggs or incubating them at colder temperatures would decrease learning slopes, and that warmer incubation temperatures would relax the effects of CORT elevations.
-In contrast to our predictions, both species learned to associate a colour with a food reward at the same rate regardless of the experimental treatments.
-This suggests that these species may have evolved mechanisms to buffer against early environmental stressors and maintain learning performance despite prenatal challenges.
-
-In addition, we found that the learning rates varied depending on the colour assigned to the correct choice, at least for _L.
-delicata_, with lizards assigned to blue ramps showing lower learning slopes than in the red group.
-This outcome manifests the need to consider the potential effects of colour biases in the design of cognitive tasks.
-
-#### Effect of prenatal CORT on learning
+We predicted that elevated CORT levels in eggs or incubating them at colder temperatures would decrease learning rates, and that warmer incubation temperatures would relax the negative effects of CORT on learning.
+In contrast to our predictions, both species learned to associate a colour with a food reward at the same rate regardless of the experimental treatment.
+These findings suggest that both species may have evolved mechanisms to buffer against early environmental stressors and maintain learning performance despite prenatal challenges.
+While we also did not find any effect of treatment on decision making there was a clear bias towards the colour blue irrespective of the treatment, though this pattern differed between the species.
+We discuss the implications of these findings below.
+
+#### Learning is not impacted by prenatal corticosterone exposure   
 Prenatal CORT was predicted to have a negative effect on learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn; @bebus_associative_2016].
-However, we did not find any significant difference between hormone treatments in either of the two species.
+However, we did not find any significant difference in learning rates between hormone treatments in either of the two species.
 Our results are consistent with other experiments that showed no influence of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016; @farrell_developmental_2016] and suggest that _L.
 delicata_ and _L.
-guichenoti_ may have evolved some strategies to buffer the impacts of prenatal stress.
+guichenoti_ may have evolved strategies to buffer the impacts of prenatal stress.
 
@@
 delicata_ and _L.
-guichenoti_ is robust to the programmatic effects of high CORT elevations, but we cannot exclude the possibility that lower concentrations may affect learning abilities.
-
-Conversely, the absence of significant effects of prenatal CORT on learning could be due to the cognitive task employed, as some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
-GCs action involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed unevenly in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
+guichenoti_ is robust to the programmatic effects of elevated CORT exposure, but we cannot exclude the possibility that different concentrations than the one used here may affect learning abilities.
+
+Conversely, the absence of significant effects of prenatal CORT on learning could be due to the cognitive task employed.
+Some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
+GC actions involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed differentialy in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
 For instance, in european starlings (_Sturnus vulgaris_), males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn].
 Similarly, scrub-jays (_Aphelocoma coerulescens_) that have lower CORT levels as nestlings performed better on an associative learning test as adults but not on a reversal-learning task [@bebus_associative_2016].
-We must acknowledge the possibility that prenatal CORT does not affect the brain regions involved in coding associative learning in _L.
+Our results suggest that prenatal CORT does not affect the brain regions involved in coding associative learning in _L.
 delicata_ and _L.
-guichenoti_, and future studies should focus on examining the effect of early-life stress on different cognitive domains.
-
-#### Effect of incubation temperature on learning
-We also predicted hot-incubated lizards to perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Furthermore, the opposite pattern was found only in studies that employed temperatures far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020], and it is unclear how such conditions relate to wild environments.
+guichenoti_ but we cannot rule out the possibility that other cognitive domains, such as spatial learning, might be affected.
+Future studies should focus on examining the differential effects of early-life stress on different cognitive domains.
+
+#### Incubation temperature does not affect learning
+We predicted hot-incubated lizards would perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+While the opposite pattern has been found in some studies, these employed temperatures far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020].
+As such, it is unclear how such conditions relate to wild environments.
 In _L.
@@
 guichenoti_, associative learning appears to be robust to incubation temperature.
-Our results, therefore, do not align with the outcome observed in previous experiments.
-However, the effect of prenatal temperature on cognition, and brain physiology and structure has been investigated only in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how thermal early environment can affect cognitive abilities.
-According to our observations, the impact of incubation temperature on learning may not be as widespread across reptiles as we may think.
-
-Alternatively, other factors, such as sex-dependent effects, could be affecting our findings.
-We did not include sex as a predictor for several reasons: first, lizards were tested before sexual maturation [@joss1985reproductive]; and second, previous studies have found weak evidence for sex-dependent learning in reptiles [@szabo_sex_meta].
-In fact, in the eastern three-lined skink (_Bassiana dupeyerri_) the effect of incubation temperature on learning is not sex-dependent [@amiel_hotter_2012; @clark_colour_2014].
-However, there is previous evidence for interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
-Notably, in _B.
-dupeyerri_ exposure to cold temperatures during incubation can induce sex-reversal, where individuals under cold incubation temperatures develop male phenotypes while retaining female genotypes [@quinn2009isolation].
-As a result, even when examining the interactive effects of sex and temperature in this species, the results could be confounded by the mismatch between genotype and phenotype [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Although sex-reversal does not occur in _L.
-delicata_ or _L.
-guichenoti_, not accounting for sex in our analyses could be masking potential interactions between temperature and sex in shaping learning abilities [see @coomber_independent_1997; @sakata_neural_2000].
-Future research should investigate the potential interactive impacts of sex and incubation temperature on cognitive abilities.
-Nevertheless, conducting such studies poses challenges due to the substantial sample sizes necessary.
-
-#### Effect of colour on learning
-The colour of the ramp associated with the attainable cricket (i.e.
-the correct choice) influences learning slopes in _L.
-delicata_, but not _L.
-guichenoti_.
-_L.
-delicata_ learned the task when the reward was associated to the red ramp but not when the ramp was blue.
-In contrast, _L.
-guichenoti_ showed similar results despite the colour of the correct ramp.
-This indicates that _L.
-delicata_ were not able to associate the blue ramp with the reward.
-However, our results could be a consequence of an initial bias in lizards' choice.
-The analyses presented in the Supplemenatry Material show that, overall, the estimated probability of choosing the correct ramp in the first trial was higher than expected by chance for those animals assigned to the blue ramp.
-These lizards show learning slopes not different from zero, but high probabilities of choosing the correct ramp also in the first trials (see @fig-deli).
-
-Because there was a possibility that this bias towards blue ramps was a byproduct of the habituation process, we compared the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during habituation (see _Supplementary Material_).
-We found no similarities between the white and blue ramps, so we consider that preference towards blue ramps did not arise as a derivate from trining the lizards with the white ramps.
-Rather, it seems likely that lizards innately prefer the blue ramps.
-Some animals bias their attention towards colours they are familiar with [@putman2017fear - the 'species confidence hypothesis'].
+Our results, therefore, do not align with previous studies.
+However, the effect of prenatal temperature on cognition, and brain physiology and structure has been investigated only in a small number of species [see @coomber_independent_1997; @sakata_neural_2000; @amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014; @amiel_effects_2017; @dayananda_incubation_2017; @abayarathna_effects_2020], limiting our understanding on how early thermal environment can affect cognitive abilities.
+Our results suggest that the impact of incubation temperature on learning may not be as widespread across reptiles as we think.
+
+#### Visual-sensory bias is not dependent on early environment    
+We found strong evidence for a visual/sensory bias towards choosing the blue feeding ramp during the initial stages of decision making.
+While this effect appeared to be stronger in _L.
+delicata_ compared to _L.
+guichenoti_, the bias was not the result of experiencing different early environmental conditions.
+What created an initial bias towards blue?
+One possibility might be that the bias towards blue ramps was a byproduct of the training phase where the blue ramp was more similar to the white training ramp compared to the green and red ramps.
+However, this hypothesis is unlikely given that the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during training phase meant that the white training phase ramp was more similar to the green colour rather than blue (see _Supplementary Material_).
+It seems more likely that lizards innately prefer the blue ramps.
+Some animals bias their attention towards colours they are familiar with [@putman2017fear - the ‘species confidence hypothesis’].
 For instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
@@
 guichenoti_ before; and blue colouration is not considered to be involved in intraspecific communication in these species [@torr1996patterns; @chapple_biology_2014].
-Regardless, our results demonstrate that _L.
-delicata_ has a bias toward blue colours and highlights the need to consider the colours used in associative learning paradigms.
-
-#### Learning rates between species
+Regardless, our results demonstrate that, at least in _L.
+delicata_, there is a bias toward blue colours highlighting the need to consider the colours used in associative learning paradigms carefully.
+
+#### Learning rates between species did not vary  
 We did not see any significant difference in learning rates when both species were compared.
@@
 #### Conclusion
-Our results revealed that associative learning abilities in _L.
+Our results revealed that associative learning abilities and decision making in _L.
 delicata_ and _L.
@@
 
-Future research should continue exploring the potential effects of prenatal corticosterone (CORT) and temperature on cognitive function, but with a focus on interactions between early environmental factors and sex, as well as the type of cognitive tasks employed.
+Future research should continue exploring the potential effects of prenatal corticosterone (CORT) and temperature on other cognitive functions.
 Furthermore, it is crucial to explore how these treatments influence brain function at a neurological level.
@@
 ## Authors’ contributions
-P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.H.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, funding acquisition, writing—review and editing; B.M: data collection, writing—review and editing; A.Y.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
+PR: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; DCL: data collection, writing—review and editing; OC: conceptualization, methodology, writing—review and editing; KW: conceptualization, writing—review and editing; CF: conceptualization, methodology, funding acquisition, writing—review and editing; BM: data collection, writing—review and editing; AP: data collection, writing—review and editing; DN: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
 All authors gave final approval for publication and agreed to be held accountable for the work performed therein.
@@
 ## Funding
-This work was supported by a National Australian University fellowship (P.R.), the Australian Research Council (grant no.
-DP210101152) to D.N.
-and C.F., and the ACT Herpetological Association grant to P.R.
+This work was supported by a National Australian University fellowship (PR), the Australian Research Council (grant no. DP210101152) to DN and CF, and the ACT Herpetological Association grant to PR.
 
@@
 
-#### Estimates of reversal learning slopes for all the different treatments per each task, specie, and group.
+#### Estimates of learning rates for all the different treatments per each task, specie, and group.
 Table 1.
-Estimates of learning slopes for all the different treatments per each task, specie, and group.
+Estimates of learning rates for all the different treatments per each task, specie, and group.
 Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
@@
 #### Colour preference
-To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercepts  from our posterior distributions.
-We first estimated the predicted probability of choosing the correct ramp first in the first trial, by using the formula:
-$$\text{Probability} = \frac{e^{Intercept}}{1 + e^{Intercept}}$$
-
-Second, we tested the hypothesis that the estimated probability was higher than 0.33 (the probability expected by chance of choosing the correct ramp) using pmcmc.
-If the estimated probability is above 0.33 we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes.
-The results per treatment are summarized in Table 2.
+To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the values from our posterior distributions.
+We estimated the predicted probability of choosing the correct ramp first in the first trial (see Statistical analyses) and tested the hypothesis that this estimated probability was higher than expected by chance (i.e.
+0.33) using p~mcmc~.
+If the estimated probability is above 0.33 we consider it as an indication that there was a preference towards that colour that could be affecting learning rates.
 
@@
   theme_classic() +
-  ylab("Achromatic Contrast (dL") +
+  ylab("Achromatic Contrast (dL)") +
   xlab("ramp Colours Comparison") +

### 2024-10-09 .vdoc.r

@@ -1,923 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-cat("\\newpage")
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of the experiment. Panel A shows the early environment manipulation (see methods for ). In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks. Panel C shows the habituation process with the three different stages. And in panel D, the associative task with the three different 3D printed ramps. White lids in D show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be the main data base used (data_clean).
-write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
-    for(k in 1:length(hormone)){
-      for(l in 1:length(temperature)){
[…]

### 2024-10-09 R/func.r

@@ -150,7 +150,7 @@ format_dec <- function(x, n) {
 #' @param n The number of decimals
 format_p <- function(x, n) {
   if(equal == TRUE){
-    e <- "="
+    e <- "= "
   } else if(equal == FALSE){
     e <- ""  
   }
@@ -441,7 +441,7 @@ plotting <- function(sp, col, df_violin_1, df_points_1, df_violin_2, df_points_2
                         "CORT-Cold (n = 5)"
       )
       img <- readPNG("./Others/Red.png")
-      
+
     } else if (col == "blue"){
       lab <- c("D", "E", "F")
             custom_values <- c("CORT-Cold (n = 6)" = "#00008B",
@@ -525,7 +525,7 @@ plotting <- function(sp, col, df_violin_1, df_points_1, df_violin_2, df_points_2
     axis.text.x = element_text(size = 9, family = "Times"),
     axis.text.y = element_blank(),
     legend.position = "none"
-  ) 
+  )
   # Third part of the plot (C, F), the estimated probability per treatments over trial
   plot3 <- ggplot(df_prob, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +
   geom_line(linewidth = 1) +
@@ -548,6 +548,6 @@ plotting <- function(sp, col, df_violin_1, df_points_1, df_violin_2, df_points_2
   #
   # Combine them
   plot <- plot_grid(plot1, plot2, plot3, labels = lab, nrow = 1, rel_widths = c(0.23, 0.23, 0.54), label_x = 0, label_y = 0.95) +
-    annotation_custom(rasterGrob(img), xmin = 0.8, xmax = 0.98, ymin = 0.75, ymax = 0.98)
+    annotation_custom(rasterGrob(img), xmin = 0.8, xmax = 0.98, ymin = 0.8, ymax = 0.98)
   return(plot)
 }

### 2024-10-31 ms.qmd
Updates

@@
     bibliography: "./bib/refs.bib"
-    csl: "./bib/animal-cognition.csl"
+    csl: "./bib/behavioral-ecology.csl"
 execute:
@@
 ## Abstract
-Animals must acquire new information through learning to adjust their behaviour adaptively.
+Animals must acquire new information through learning to adjust their behavior adaptively.
 However, learning ability can be constrained by conditions experienced during early stages of development, when the brain is especially susceptible to environmental inputs.
@@
 guichenoti_.
-We manipulated CORT levels and temperature in a 2x2 factorial design, and then subjected lizards to a colour-associative learning task.
+We manipulated CORT levels and temperature in a 2x2 factorial design, and then subjected lizards to a color-associative learning task.
 We predicted that elevated CORT and low temperatures would impair associative learning.
@@
 Our results suggest that these two species may have evolved mechanisms to maintain learning performance despite prenatal challenges.
-**We also found that learning rates where slower when food rewards were associated with blue-coloured ramps, a possible effect of developmental environment on the visual-sensory system, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.**
+We also found that decision making in both species were affected by the color of the ramps.
+Overall, we observed a preference towards blue-colored ramps, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
 
@@
 Cognition is a set of processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
-These processes are fundamental to foraging, mate selection, antipredatory strategies, and social behaviours, all of which are crucial for survival and reproduction [@dukas_evolutionary_2004].
-Learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
+These processes are fundamental to foraging, mate selection, antipredatory strategies, and social behaviors, all of which are crucial for survival and reproduction [@dukas_evolutionary_2004].
+Learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioral_2012; @buchanan_condition_2013].
 However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014].
@@
 In vertebrates, GCs regulate metabolism and maintain homeostasis in response to disturbances [i.e., ‘the stress response’ @sapolsky_how_2000].
-Under stressful situations, animals react by instigating adaptive physiological and behavioural adjustments mediated by GCs.
+Under stressful situations, animals react by instigating adaptive physiological and behavioral adjustments mediated by GCs.
 These GCs can be transmitted directly from parents to their offspring with different effects on offspring phenotype [@Crino_2023].
@@
 We manipulated CORT levels in the eggs and then incubated them at two different temperatures in a 2X2 factorial design.
-Post-incubation, juveniles were subjected to a colour-associative task to assess their learning abilities.
+Post-incubation, juveniles were subjected to a color-associative task to assess their learning abilities.
 We hypothesized that prenatal CORT levels and thermal environment would induce sustained effects on brain physiology, ultimately impacting learning of an association task.
@@
 The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the sides and a water dish on the other.
-These arenas were placed in two rooms in 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
+These arenas were placed in two rooms in 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behavior during the experiment (see details below).
 Although the conditions in the experimental rooms were identical to the colony room, the number of lizards per species and treatment in each rack was counterbalanced to control for any potential effect of the room or the position of the lizard in the rack.
@@
 #### Learning  
-To estimate learning skills, we tested each lizard's ability to locate a food reward in a colour-associative learning task (@fig-Methods C, D).
+To estimate learning skills, we tested each lizard's ability to locate a food reward in a color-associative learning task (@fig-Methods C, D).
 First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical in size and shape to the ones used during the associative task.
@@
 A trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials to ensure lizards were feeding consistently.
-This phase lasted 38 days until all the lizards learned to eat from the ramp; only in one case did we decide not to use the lizard because its behaviour was not consistent over the course of the training phase.
-
-During the associative learning phase, we trained lizards to associate colour with a food reward (@fig-Methods D).
-This test was like the third stage of the training phase, but here lizards were presented with three 3D printed ramps that differed in colour.
-Ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
+This phase lasted 38 days until all the lizards learned to eat from the ramp; only in one case did we decide not to use the lizard because its behavior was not consistent over the course of the training phase.
+
+During the associative learning phase, we trained lizards to associate color with a food reward (@fig-Methods D).
+This test was like the third stage of the training phase, but here lizards were presented with three 3D printed ramps that differed in color.
+Ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colors [@Baden_Osorio_2019_Vert_vision].
 The food reward (small, frozen, *A.
@@
 This way, we controlled for the use of prey chemical cues, as the lids had a series of small holes on the top to allow the release of those chemicals.
-To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was blue, while the other group was assigned the red ramp as correct.
-In all trials, the position of the ramps was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
+To control for potential color preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was blue, while the other group was assigned the red ramp as correct.
+In all trials, the position of the ramps was changed randomly to ensure subjects were using color rather than spatial cues for the association.
 Lizards were tested in this task once a day for 35 days.
@@
 We performed analyses for each species separately.
-Preliminary analyses showed a significant effect of the colour.
-As such, we decided to split the data by colour (blue or red).
+Preliminary analyses showed a significant effect of the color.
+As such, we decided to split the data by color (blue or red).
 Therefore, we ran a total of four different Bayesian multilevel models using the _brm_ function from the brms package [@burkner2017brms] in R (version 2.8.2) [@R].
@@
 
-In our case, we were interested in estimating the probability of correct choice at early stages of learning [P~(1)~] because perception can play a role in the learning process [@toure2022colour].
-It also allowed us to test if lizards were biased towards the assigned colour.
+In our case, we were interested in estimating the probability of correct choice at early stages of learning [P~(1)~] because perception can play a role in the learning process [@toure2022color].
+It also allowed us to test if lizards were biased towards the assigned color.
 
@@
 
-**Decision making when the correct ramp was red was not different to the probability of choosing correctly when the correct ramp was blue for _L.
-delicata_ (mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]; mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, see @fig-deli).
-nor for _L.
-guichenoti_ (mean P~Red~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]; mean P~Blue~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, see @fig-guich).
-However, in both species, the probability of choosing the correct ramp when the ramp was blue was significantly higher than expected by chance (0.33) only when the correct ramp was blue (see @fig-deli A,C; @fig-guich A, C; and see Table 2 in _Supplementary Material_).
-We found that the rate of learning was not different when the correct ramp was red or blue for _L.
-delicata_ (mean β~Red~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI β~Red~ = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; mean β~Blue~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, see @fig-deli), nor for _L.
-guichenoti_ (mean β~Red~ = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI β~Red~ = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; mean β~Blue~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI β~Blue~ = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; Contrast between slopes: β~Blue~ - β~Red~ = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, see @fig-guich).**
-
-_Lampropholis delicata_: Decision making in _L.
+_Lampropholis delicata_: _L.
+delicata_ that were given the blue ramp as the correct choice had a `r format_dec(((mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) / mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot))) - 1) * 100, 1)`% increase in the probability of choosing the right ramp on trial 1 compared to lizards assigned to the red ramps (mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]), suggesting a bias towards blue.
+A blue bias was also supported by initial choices differing significantly from chance, and this was consistent across all treatments (i.e., P > 0.33; Table 2 in _Supplementary Material_).
+However, this difference in the probability of choosing correct between red and blue ramps was not significant, likely due to of small sample sizes (Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, see @fig-deli).
+
+Decision making in _L.
 delicata_ was not impacted by the CORT (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_drControlCold, probright_drControlHot)) - mean(c(probright_drCORTCold, probright_drCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlCold, probright_drControlHot) - c(probright_drCORTCold, probright_drCORTHot)), 3)`), incubation temperature (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_drControlHot, probright_drCORTHot)) - mean(c(probright_drControlCold, probright_drCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlHot, probright_drCORTHot) - c(probright_drControlCold, probright_drCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_drControlHot - probright_drCORTHot) - mean(probright_drControlCold - probright_drCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_drControlHot - probright_drCORTHot - (probright_drControlCold - probright_drCORTCold)), 3)`) when red ramps were the correct choice (see @fig-deli A).
@@
 
-_Lampropholis guichenoti_: Decision making in _L.
+_Lampropholis guichenoti_: when the correct ramps were blue, _L.
+guichenoti_ had a `r format_dec(((mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)) / mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot))) - 1) * 100, 1)`% increase in the probability of choosing the right ramp on trial 1 compared to red ramps (mean P~Blue~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot), 0.975), 3)`]).
+However, the difference was not significant (Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)) - mean(c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot) - c(probright_grCORTCold, probright_grControlCold, probright_grCORTHot, probright_grControlHot)), 3)`, see @fig-guich).
+
+Decision making in _L.
 guichenoti_ when the red ramps are the correct choice, was not affected by the hormone treatment (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_grControlCold, probright_grControlHot)) - mean(c(probright_grCORTCold, probright_grCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlCold, probright_grControlHot) - c(probright_grCORTCold, probright_grCORTHot)), 3)`), temperature treatment (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_grControlHot, probright_grCORTHot)) - mean(c(probright_grControlCold, probright_grCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlHot, probright_grCORTHot) - c(probright_grControlCold, probright_grCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_grControlHot - probright_grCORTHot) - mean(probright_grControlCold - probright_grCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_grControlHot - probright_grCORTHot - (probright_grControlCold - probright_grCORTCold)), 3)`; see @fig-guich A).
@@
 #| label: fig-deli
-#| fig.cap: "Results for Lampropholis delicata for both colour groups red (A, B, C) and blue (D, E , F).
+#| fig.cap: "Results for Lampropholis delicata for both color groups red (A, B, C) and blue (D, E , F).
 Panels A and D show the predicted probability of choosing the correct ramp in the first trial (Decision first trial).
@@
 In all A, B, D, and E the x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
-The different colours indicate the different treatments.
+The different colors indicate the different treatments.
 Points and bars represent the mean and standard deviation of the mean of the estimates, respectively.
@@
 The lines represent the mean predicted probability of choosing the correct ramp for each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
-The different colours indicate the different treatments."
+The different colors indicate the different treatments."
 source(here("R", "func.R"))
@@
 #| label: fig-guich
-#| fig.cap: "Results for Lampropholis guichenoti for both colour groups red (A, B, C) and blue (D, E , F).
+#| fig.cap: "Results for Lampropholis guichenoti for both color groups red (A, B, C) and blue (D, E , F).
 Panels A and D show the predicted probability of choosing the correct ramp in the first trial (Decision first trial).
@@
 We predicted that elevated CORT levels in eggs or incubating them at colder temperatures would decrease learning rates, and that warmer incubation temperatures would relax the negative effects of CORT on learning.
-In contrast to our predictions, both species learned to associate a colour with a food reward at the same rate regardless of the experimental treatment.
+In contrast to our predictions, both species learned to associate a color with a food reward at the same rate regardless of the experimental treatment.
 These findings suggest that both species may have evolved mechanisms to buffer against early environmental stressors and maintain learning performance despite prenatal challenges.
-While we also did not find any effect of treatment on decision making there was a clear bias towards the colour blue irrespective of the treatment, though this pattern differed between the species.
+While we also did not find any effect of treatment on decision making there was a clear bias towards the color blue irrespective of the treatment, though this pattern differed between the species.
 We discuss the implications of these findings below.
@@
 One possibility might be that the bias towards blue ramps was a byproduct of the training phase where the blue ramp was more similar to the white training ramp compared to the green and red ramps.
-However, this hypothesis is unlikely given that the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during training phase meant that the white training phase ramp was more similar to the green colour rather than blue (see _Supplementary Material_).
+However, this hypothesis is unlikely given that the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during training phase meant that the white training phase ramp was more similar to the green color rather than blue (see _Supplementary Material_).
 It seems more likely that lizards innately prefer the blue ramps.
-Some animals bias their attention towards colours they are familiar with [@putman2017fear - the ‘species confidence hypothesis’].
+Some animals bias their attention towards colors they are familiar with [@putman2017fear - the ‘species confidence hypothesis’].
 For instance, dark and light blue T-shirts were associated with lower flight initiation distances and higher capture rates in Western fence lizards where blue is used in intraspecific communication [@putman2017fear].
-Nevertheless, to the best of our knowledge, there has been no reported colour bias in _L.
+Nevertheless, to the best of our knowledge, there has been no reported color bias in _L.
 delicata_ or _L.
-guichenoti_ before; and blue colouration is not considered to be involved in intraspecific communication in these species [@torr1996patterns; @chapple_biology_2014].
+guichenoti_ before; and blue coloration is not considered to be involved in intraspecific communication in these species [@torr1996patterns; @chapple_biology_2014].
 Regardless, our results demonstrate that, at least in _L.
-delicata_, there is a bias toward blue colours highlighting the need to consider the colours used in associative learning paradigms carefully.
+delicata_, there is a bias toward blue colors highlighting the need to consider the colors used in associative learning paradigms carefully.
 
@@
 This outcome contrasts with our initial predictions, indicating that the learning skills of these lizards may be more robust than anticipated under varying early life conditions.
-We also found significant effects of the colour employed in the task on learning rates in most _L.
+We also found significant effects of the color employed in the task on learning rates in most _L.
 delicata_ and some _L.
 guichenoti_.
-These results seem to be a consequence of an innate colour bias and highlights the importance of carefully selecting the colour employed when testing cognition using visual stimuli.
+These results seem to be a consequence of an innate color bias and highlights the importance of carefully selecting the color employed when testing cognition using visual stimuli.
 
@@
 ) %>%
-  pivot_wider(names_from = Group, values_from = c(Mean, CI, pmcmc)) %>% #To divide by colour
+  pivot_wider(names_from = Group, values_from = c(Mean, CI, pmcmc)) %>% #To divide by color
   select(Specie, Treatment, Mean_Red, CI_Red, pmcmc_Red, Mean_Blue, CI_Blue, pmcmc_Blue) %>% #To order the columns in the way I want for the table
@@
 
-#### Colour preference
-To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the values from our posterior distributions.
+#### color preference
+To test if lizards were biased towards the assigned color as our preliminary analyses suggested, we employed the values from our posterior distributions.
 We estimated the predicted probability of choosing the correct ramp first in the first trial (see Statistical analyses) and tested the hypothesis that this estimated probability was higher than expected by chance (i.e.
 0.33) using p~mcmc~.
-If the estimated probability is above 0.33 we consider it as an indication that there was a preference towards that colour that could be affecting learning rates.
+If the estimated probability is above 0.33 we consider it as an indication that there was a preference towards that color that could be affecting learning rates.
 
@@
 #################
-colour_table <- flextable(table_df) %>%
+color_table <- flextable(table_df) %>%
   bold(~ `p_value_Blue` < 0.05, ~ `p_value_Blue` + prob_choice_Blue) %>%
@@
 autofit()
-colour_table
+color_table
 #
@@
 To test if the bias towards blue was something acquired during training, we compared the light spectrum of the ramps used in the associative task and the white ones used during habituation.
-We took three measurements of ten ramps per colour with a spectophotometer, and then analysed the spectrum and the perceived differences in colour using the package pavo.
+We took three measurements of ten ramps per color with a spectophotometer, and then analysed the spectrum and the perceived differences in color using the package pavo.
 The spetrum of each type of ramp are shown in @fig-spectrum; the perceived chromatic constrasts between ramps are shown in @fig-perceived1 and @fig-perceived2.
@@
 #| label: fig-spectrum
-#| fig.cap: "Light spectrum of the ramps used in the associative task and the white ones used during habituation. The different colours represent the different ramps."
+#| fig.cap: "Light spectrum of the ramps used in the associative task and the white ones used during habituation. The different colors represent the different ramps."
 #
@@
   procspec(specs, opt = "smooth" , span = 0.2, fixneg = "addmin") 
-# Plot smoothed raw data as reflectance curve with approximate rgb colours
+# Plot smoothed raw data as reflectance curve with approximate rgb colors
 plot(specs, type = "o", col = spec2rgb(specs))
@@
 #                             
-# Calculate colour distances between all ramp measurements
+# Calculate color distances between all ramp measurements
 coldistance_feeders <- coldist(feeders_lizardview,achro = TRUE, noise = "neural", n = c(1, 1, 3.5, 6),  weber = 0.1)
@@
 #
-# Plot the colour differences between the ramps: 
+# Plot the color differences between the ramps: 
 # Note - above 1 is expected to be visually different under the selected visual system (here, lizard view)
@@
   ylab("Chromatic Contrast (dS)") +
-  xlab("ramp Colours Comparison") +
+  xlab("ramp colors Comparison") +
  scale_fill_manual(values =c("B/G" = 'steelblue',  "B/R" = 'purple', "B/W" = 'lightblue', "G/R" = 'brown', "G/W" = 'lightgreen', "R/W" = 'red')) +
@@
   ylab("Achromatic Contrast (dL)") +
-  xlab("ramp Colours Comparison") +
+  xlab("ramp colors Comparison") +
  scale_fill_manual(values =c("B/G" = 'steelblue',  "B/R" = 'purple', "B/W" = 'lightblue', "G/R" = 'brown', "G/W" = 'lightgreen', "R/W" = 'red')) +
@@
 Model formula for task is:  
-Choice  ~ Trial*cort*temp + (1 + Trial|lizard_id)  
+Choice  ~ Trial * cort * temp + (1 + Trial|lizard_id)  
 Plots for the different models of the associative task:  

### 2024-10-31 ms.qmd
Updates

@@
 Kristoffer H. Wild ORCID: 0000-0001-6714-3311  
-Chris Friesen ORCID: 0000-0001-5338-7454  
+Christopher R. Friesen ORCID: 0000-0001-5338-7454  
 Basile Mauclaire ORCID:  
@@
 Animals must acquire new information through learning to adjust their behavior adaptively.
-However, learning ability can be constrained by conditions experienced during early stages of development, when the brain is especially susceptible to environmental inputs.
+However, learning ability can be constrained by conditions experienced during the early stages of development, when the brain is especially susceptible to environmental inputs.
 Temperature can result in phenotypically plastic adjustments to growth, metabolism, and learning in ectotherms.
-In vertebrates, abrupt thermal changes can also trigger chronic stress, which is mediated by glucocorticoids that can be transmitted to offspring, potentially impacting their learning abilities.
-Glucocorticoids and thermal environments are therefore predicted to have interactive effects on the development of learning in ectotherms.
-Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles - and incubation temperature on associative learning, using two species of lizards, _Lampropholis delicata_ and _L.
+In vertebrates, abrupt thermal changes can also trigger chronic stress, mediated by glucocorticoids (GCs) that can be transmitted to offspring, potentially impacting their learning abilities.
+GCs and thermal environments are, therefore, predicted to have interactive effects on the development of learning in ectotherms.
+Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles - and incubation temperature on associative learning using two species of lizards, _Lampropholis delicata_ and _L.
 guichenoti_.
@@
 Our results suggest that these two species may have evolved mechanisms to maintain learning performance despite prenatal challenges.
-We also found that decision making in both species were affected by the color of the ramps.
-Overall, we observed a preference towards blue-colored ramps, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
+We also found that color affected decision-making in both species.
+Overall, we observed a preference towards blue, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
 
 ## Introduction
-Cognition is a set of processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
+Cognition is a set of processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision-making [@shettleworth].
 These processes are fundamental to foraging, mate selection, antipredatory strategies, and social behaviors, all of which are crucial for survival and reproduction [@dukas_evolutionary_2004].
-Learning - the acquisition of new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioral_2012; @buchanan_condition_2013].
+Learning - acquiring and consolidating new information [@dukas_evolutionary_2004] - is essential for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
 However, the capacity to acquire information varies among individuals, shaped by factors such as age, sex, and the developmental environment [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014].
-Interindividual differences in learning can lead to unequal responses to environmental pressures, with potential effects on population dynamics [@ward2016ecological; @welklin2024spatial].
+Interindividual differences in learning can lead to unequal responses to environmental conditions, potentially affecting population dynamics [@ward2016ecological; @welklin2024spatial].
 For example, fast learners may better exploit novel resources or avoid new dangerous stimuli, while those with lower learning capabilities might struggle to adapt to environmental changes.
-This could affect their survival and reproductive output, ultimately influencing population growth rates and stability [@ward2016ecological; @welklin2024spatial].
+Learning rate could affect their survival and reproductive output, ultimately influencing population growth rates and stability [@ward2016ecological; @welklin2024spatial].
 Therefore, understanding the factors that shape learning is crucial to predict how populations will respond to novel circumstances.
 
-Variation in learning is thought to be a product of an individual's capacity to form associations between stimuli through memory formation.
-However, differences in learning among individuals can also be a consequence of innate preferences or perceptual biases that influence how information is acquired and affect the decision-making process [@toure2022colour].
-The brain's integration of information and the establishment of new connections is a complex process, involving interactions among various nuclei to generate responses [@dukas_evolutionary_2004].
+Variation in learning is usually considered a product of an individual's capacity to form associations between stimuli through memory formation [@dukas_evolutionary_2004].
+However, differences in learning among individuals can also result from innate preferences or perceptual biases that influence how information is acquired and affect the decision-making process [@toure2022colour].
+The brain's integration of information and the establishment of new connections is a complex process involving interactions among various nuclei to generate responses [@dukas_evolutionary_2004].
 Consequently, any impact on specific brain regions or their interactions can directly influence learning through memory formation or alterations in decision-making.
@@
 
-Glucocorticoids (GCs) are a class of steroid hormone that are particularly relevant in this context.
+Glucocorticoids (GCs) are a class of steroid hormones that are particularly relevant in this context.
 In vertebrates, GCs regulate metabolism and maintain homeostasis in response to disturbances [i.e., ‘the stress response’ @sapolsky_how_2000].
-Under stressful situations, animals react by instigating adaptive physiological and behavioral adjustments mediated by GCs.
-These GCs can be transmitted directly from parents to their offspring with different effects on offspring phenotype [@Crino_2023].
-Elevation in GCs during early stages of development typically result in altered neurogenesis, brain structure, and metabolic activity that in most cases are related to decreased learning abilities [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009; @eaton2015mild; @farrell_developmental_2015-learn; @farrell_developmental_2016].
-For instance, prenatal stress in rats (_Rattus norvegicus_) suppresses neurogenesis in the dentate gyrus and is associated to impairments in hippocampal-related spatial tasks [@lemaire_prenatal_2000].
+Under stressful situations, animals react by initiating adaptive physiological and behavioral adjustments mediated by GCs.
+These GCs can be transmitted directly from parents to their offspring with various effects on offspring phenotype [@Crino_2023].
+Elevation in GCs during early stages of development typically results in altered neurogenesis, brain structure, and metabolic activity that, in most cases, are related to decreased learning abilities [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009; @eaton2015mild; @farrell_developmental_2015-learn; @farrell_developmental_2016].
+For instance, prenatal stress in rats (_Rattus norvegicus_) suppresses neurogenesis in the dentate gyrus, which is associated with impairments in hippocampal-related spatial tasks [@lemaire_prenatal_2000].
 Factors such as sex or the nature of the learning task can also affect the direction and magnitude of the effects of prenatal exposure to elevated GCs [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016; @farrell_developmental_2016].
-Because the effects of prenatal GCs on learning can be context-dependent, it is crutial to conduct studies across diverse taxa and experimental conditions to fully understand these effects.
+Because the effects of prenatal GCs on learning can be context-dependent, it is crucial to conduct studies across diverse taxa and experimental conditions to understand these effects fully.
 
 In addition to the environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-In ectotherms, the early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits including growth, metabolism, or cognition [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
-For instance, Port Jackson sharks (_Heterodontus portusjacksoni_) incubated at 23.6ºC took fewer days to reach a learning criterion in a numerical learning task than those incubated at 20.6ºC [@vila_pouca_quantity_2019].
+In ectotherms, the early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits, including growth, metabolism, or cognition [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
+For instance, Port Jackson sharks (_Heterodontus portusjacksoni_) incubated at 23.6ºC took fewer days to master a numerical learning task than those incubated at 20.6ºC [@vila_pouca_quantity_2019].
 In skinks, high incubation temperatures are generally associated with faster learning rates [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]; but velvet geckos (_Amalosia lesueurii_) incubated at temperatures beyond their natural thermal range are worse learners than those incubated at colder temperatures [@dayananda_incubation_2017; @abayarathna_effects_2020].
-The effects of incubation temperature in reptiles are likely mediated by changes in neural structure and function, as high temperatures increase neural density and metabolic activity in the brain [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021].
-
-GCs can play a pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
+Changes in neural structure and function likely mediate the effects of incubation temperature in reptiles, as high temperatures increase neural density and metabolic activity in the brain [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021].
+
+GCs can play a pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023], potentially fostering natural interactions between temperature and GCs.
 Additionally, GCs and temperatures can act upon similar physiological mechanisms [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021].
-This implies that the effects of GCs and temperature could be interdependent, with the impact of one factor being modulated by the other.
-However, the interactive effects of GCs and temperature on learning abilities remain unexplored, yet an understanding of how temperature and GC’s interact is particularly relevant in the context of global climate change [@vinogradov2024inbreeding].
+Therefore, the effects of GCs and temperature may be interdependent, with the impact of one factor being modulated by the other.
+However, the interactive effects of GCs and temperature on learning abilities remain unexplored, yet understanding of how temperature and GC’s interact is particularly relevant in global climate change [@vinogradov2024inbreeding].
 
@@
 Post-incubation, juveniles were subjected to a color-associative task to assess their learning abilities.
-We hypothesized that prenatal CORT levels and thermal environment would induce sustained effects on brain physiology, ultimately impacting learning of an association task.
+We hypothesized that prenatal CORT levels and thermal environment would induce sustained effects on brain physiology, ultimately impacting the learning of an association task.
 We predicted that individuals exposed to high levels of CORT or low temperatures would learn slower than control individuals or those incubated at higher temperatures [@zhu_prenatal_2004; @amiel_hotter_2012; @eaton2015mild; @amiel_effects_2017].
 Additionally, we predicted that incubation at high temperatures would mitigate the impact of CORT on learning performance, while cold incubation temperatures were expected to enhance the effects of CORT.
-This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
+The interactive effects of CORT and temperature may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
 
@@
 delicata* lays 1-6 eggs in only one clutch per season, *L.
-guichenoti* clutches are smaller (1-5 eggs per clutch) and they usually lay two clutches per season [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014].
+guichenoti* clutches are smaller (1-5 eggs per clutch), and they usually lay two clutches per season [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014].
 Previous studies exploring behavioral differences between the two species have found _L.
@@
 *Breeding colony* -- We tested juveniles from a 2019-established lab breeding colony.
-A a total of 270 and 180 adults of *L.
+A total of 270 and 180 adults of *L.
 delicata* and *L.
-guichenoti* respectively, were housed in plastic containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+guichenoti*, respectively, were housed in plastic containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
 Enclosures were lined with non-stick matting, shelter, and several small water dishes.
 Water is given daily, and they were fed approximately 40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
-Crickets were dusted with calcium weekly and multivitamin and calcium biweekly.
-To ensure a temperature gradient, we used a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
+Crickets were dusted with calcium weekly and multivitamins and calcium biweekly.
+We used a heat chord and a heat lamp following a 12 h light:12 h dark cycle to ensure a temperature gradient.
 Room temperatures were set to 22-24 ºC, and the warm side of enclosures was usually at 32-34 ºC.
@@
 These boxes were placed in one side of the communal enclosures (see above).
-We checked for the presence of eggs in the boxes three days a week (Monday, Wednesday, and Friday).
-After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001g error).
-Then we assigned individual IDs to the clutch and each egg.
+We checked for eggs in the boxes three days a week (Monday, Wednesday, and Friday).
+After collection, we measured the length and width of eggs with a digital caliper to the nearest 0.1 mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001 g error).
+Then, we assigned individual IDs to the clutch and each egg.
 Eggs were treated with CORT or vehicle (see CORT and Temperature Manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
@@
 
-*Hatchlings* -- After hatching, we measured juveniles' SVL and Tail Length (TL) with a ruler to the nearest mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001g error).
+*Hatchlings* -- After hatching, we measured juveniles' snout-to-vent length (SVL) and tail length (TL) with a ruler to the nearest mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001 g error).
 Hatchlings were then housed individually in small enclosures (18.7L x 13.2W x 6.3H cm) provided with non-stick matting, shelter, and a water dish.
@@
 
-Two weeks prior to the training phase (see details below), lizards were moved to the experimental arena for acclimatisation.
-The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the sides and a water dish on the other.
-These arenas were placed in two rooms in 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behavior during the experiment (see details below).
+Two weeks prior to the training phase (see details below), lizards were moved to the experimental arena for acclimatization.
+The arenas were individual medium-size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the sides and a water dish on the other.
+These arenas were placed in two rooms in 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475), allowing us to record their behavior during the experiment (see details below).
 Although the conditions in the experimental rooms were identical to the colony room, the number of lizards per species and treatment in each rack was counterbalanced to control for any potential effect of the room or the position of the lizard in the rack.
-During acclimatisation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin, and water was supplied *ad libitum*.
+During acclimatization and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamins, and water was supplied *ad libitum*.
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
@@
 #### CORT and Temperature Manipulation  
-To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (‘Cold’ - 23ºC ± 3ºC or ‘Hot’ - 28ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
+To empirically test the effect of early environment, we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (‘Cold’ - 23ºC ± 3ºC or ‘Hot’ - 28ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
 We topically dosed eggs with a CORT solution (10pg/mL) or a control treatment (100% ethanol).
@@
 After the treatment, the eggs were incubated in one of the two previously mentioned temperature regimes (‘Cold’ or ‘Hot’) until hatching.
-The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
+The number of eggs per clutch assigned to each hormone and temperature treatment was counterbalanced in both species.
 
@@
 domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods C, Stage 1); the second stage where the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods C, Stage 2); and the third where the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp (@fig-Methods C, Stage 3).
-Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later, when we took it away.
-At the end of each trial, we recorded whether the cricket had been consumed or not.
+Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
+At the end of each trial, we recorded whether the cricket had been consumed.
 A trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials to ensure lizards were feeding consistently.
-This phase lasted 38 days until all the lizards learned to eat from the ramp; only in one case did we decide not to use the lizard because its behavior was not consistent over the course of the training phase.
+This phase lasted 38 days until all the lizards learned to eat from the ramp; only in one case did we decide not to use the lizard because its behavior inconsistent throughout  the course of the training phase.
 
 During the associative learning phase, we trained lizards to associate color with a food reward (@fig-Methods D).
-This test was like the third stage of the training phase, but here lizards were presented with three 3D printed ramps that differed in color.
+This test was like the third stage of the training phase, but here, lizards were presented with three 3D-printed ramps that differed in color.
 Ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colors [@Baden_Osorio_2019_Vert_vision].
@@
 domestica* crickets) was placed inside the wells of the three ramps, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
-This way, we controlled for the use of prey chemical cues, as the lids had a series of small holes on the top to allow the release of those chemicals.
+This way, we controlled for prey chemical cues, as the lids had a series of small holes on the top to allow the release of those chemicals.
 To control for potential color preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was blue, while the other group was assigned the red ramp as correct.
@@
 #| fig.cap: "Experimental design of the experiment.
-Panel A shows the early environment manipulation (see methods for ).
-In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks.
-Panel C shows the habituation process with the three different stages.
-And in panel D, the associative task with the three different 3D printed ramps.
+Panel A shows the early environment manipulation (see Methods).
+In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks.
+Panel C shows the habituation process in three different stages.
+In panel D, the associative task is done with the three different 3D-printed ramps.
 White lids in D show the ramps where the food reward was not attainable."
@@
 
-The experiment took place between the 6^th^ of March to the 17^th^ of May 2023, and tests were performed between 11 AM to 12 PM when the lizards were active.
-Trials in the learning phase were recorded with CCTV systems always using the same camera per individual.
+The experiment occurred between the 6^th^ of March to the 17^th^ of May 2023, and tests were performed between 1100 to 1200 when the lizards were active.
+Trials in the learning phase were recorded with CCTV systems, always using the same camera per individual.
 We recorded whether the animal chose the correct ramp first or not.
@@
 These trials were scored as NA.
-We excluded from our analyses those individuals that did not perform consistently as defined as not choosing in less than 20 out of 35 trials (~57%).
-For each lizard, we considered their first trial to be the first one where a choice was made.
+We excluded from our analyses those individuals that performed inconsistently, as defined as not choosing in less than 20 out of 35 trials (~57%).
+We considered each lizard's first trial to be the first one where a choice was made.
 
@@
 We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
-We checked that all MCMC chains converged (R~hat~ < 1.2) and were mixing effectively to ensure we had >1000 effective samples from the posterior distribution.
+We checked that all MCMC chains converged (R~hat~ < 1.2) and mixed effectively to ensure we had >1000 effective samples from the posterior distribution.
 
@@
 The error structure was modeled using a Bernoulli distribution with a logit link function [family = Bernoulli(link = 'logit')].
-We included a random intercept and slope (trial) for each lizard in our models.
+We included each lizard's random intercept and slope (trial) in our models.
 We also incorporated the clutch identity as a random factor.
@@
 guichenoti_ lays up to two [@joss1985reproductive; @chapple_know_2011; @chapple_biology_2014].
-Since egg collection was done during half of the breeding season, each clutch likely came from a unique mother, and so, clutch identity captures potential maternal effects.
+Since egg collection was done during half of the breeding season, each clutch likely came from a unique mother, so clutch identity captures potential maternal effects.
 In addition, previous studies indicate that clutches are typically fertilized by a single male, although sperm storage can occur [@kar2024heritability].
-Considering our partial split-clutch design and the expectation that maternal effects are likely to be more pronounced than paternal effects in these species, incorporating clutch as a random factor should effectively account for parental condition.
+Considering our partial split-clutch design and the expectation that maternal effects are likely more pronounced than paternal effects in these species, incorporating clutch as a random factor should effectively account for parental condition.
 
@@
 Slopes directly measure the change in the probability of choosing the correct dish across trials.
-Learning rates greater than zero, indicating that lizards were improving over trails, were considered as evidence of learning, while those less or equal to zero were not.
-
-Decision making, in contrast, is considered the average probability of choosing correct at a given trial.
+Learning rates greater than zero, indicating that lizards were improving over trails, were considered evidence of learning, while those less or equal to zero were not.
+
+Decision-making, in contrast, is considered the average probability of choosing correctly in a given trial.
 We estimated the predicted probability of choosing the correct ramp in the first trial using the intercepts from our posterior distributions following the formula:
@@
 
-In our case, we were interested in estimating the probability of correct choice at early stages of learning [P~(1)~] because perception can play a role in the learning process [@toure2022color].
+In our case, we were interested in estimating the probability of correct choice at the early stages of learning [P~(1)~] because perception can play a role in the learning process [@toure2022colour].
 It also allowed us to test if lizards were biased towards the assigned color.
@@
 We calculated the p~mcmc~ to test the hypothesis that learning rates and contrasts were different from zero, and that the probability of choosing correctly in the first trial was higher than expected by chance (0.33).
-We considered statistical significant if p~mcmc~ < 0.05.
+We considered statistical significance as p~mcmc~ < 0.05.
 
@@
 
-Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
+We started with 96 lizards, 48 per species and 12 per treatment per species.
 However, due to natural mortality (n = 11), failing to pass the training stage (n = 1), or lack of motivation during the learning tasks (n = 3), we had a final sample size of 81 lizards.
@@
 #
-# Rename some of the posteriors and obtain estimates for the "decision making" for each group and treatment. This "decision making" consists of the probability of choosing right in the first trial. 
+# Rename some of the posteriors and obtain estimates for the "decision-making" for each group and treatment. This "decision-making" consists of the probability of choosing right in the first trial. 
 ## 1) L. delicata
@@
 
-#### Early developmental environments do not influence visual-sensory systems to impact decision making
+#### Early developmental environments do not influence visual-sensory systems to impact decision-making
 
 _Lampropholis delicata_: _L.
-delicata_ that were given the blue ramp as the correct choice had a `r format_dec(((mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) / mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot))) - 1) * 100, 1)`% increase in the probability of choosing the right ramp on trial 1 compared to lizards assigned to the red ramps (mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]), suggesting a bias towards blue.
+delicata_ that were given the blue ramp as the correct choice had an `r format_dec(((mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) / mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot))) - 1) * 100, 1)`% increase in the probability of choosing the right ramp on trial 1 compared to lizards assigned to the red ramps (mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]), suggesting a bias towards blue.
 A blue bias was also supported by initial choices differing significantly from chance, and this was consistent across all treatments (i.e., P > 0.33; Table 2 in _Supplementary Material_).
-However, this difference in the probability of choosing correct between red and blue ramps was not significant, likely due to of small sample sizes (Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, see @fig-deli).
-
-Decision making in _L.
+However, this difference in the probability of correctly choosing between red and blue ramps was not significant, likely due to small sample sizes (Contrast between probabilities: P~Blue~ - P~Red~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) - mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot) - c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, see @fig-deli).
+
+Decision-making in _L.
 delicata_ was not impacted by the CORT (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_drControlCold, probright_drControlHot)) - mean(c(probright_drCORTCold, probright_drCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlCold, probright_drControlHot) - c(probright_drCORTCold, probright_drCORTHot)), 3)`), incubation temperature (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_drControlHot, probright_drCORTHot)) - mean(c(probright_drControlCold, probright_drCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlHot, probright_drCORTHot) - c(probright_drControlCold, probright_drCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_drControlHot - probright_drCORTHot) - mean(probright_drControlCold - probright_drCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_drControlHot - probright_drCORTHot - (probright_drControlCold - probright_drCORTCold)), 3)`) when red ramps were the correct choice (see @fig-deli A).
@@
 
-Decision making in _L.
+Decision-making in _L.
 guichenoti_ when the red ramps are the correct choice, was not affected by the hormone treatment (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_grControlCold, probright_grControlHot)) - mean(c(probright_grCORTCold, probright_grCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlCold, probright_grControlHot) - c(probright_grCORTCold, probright_grCORTHot)), 3)`), temperature treatment (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_grControlHot, probright_grCORTHot)) - mean(c(probright_grControlCold, probright_grCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlHot, probright_grCORTHot) - c(probright_grControlCold, probright_grCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_grControlHot - probright_grCORTHot) - mean(probright_grControlCold - probright_grCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_grControlHot - probright_grCORTHot - (probright_grControlCold - probright_grCORTCold)), 3)`; see @fig-guich A).
@@
 #| label: fig-deli
-#| fig.cap: "Results for Lampropholis delicata for both color groups red (A, B, C) and blue (D, E , F).
+#| fig.cap: "Results for Lampropholis delicata for both color groups red (A, B, C) and blue (D, E, F).
 Panels A and D show the predicted probability of choosing the correct ramp in the first trial (Decision first trial).
@@
 Points and bars represent the mean and standard deviation of the mean of the estimates, respectively.
-Dashed lines indicate value 0.33 (the probability of choosing correctly by chance) in panesl A, D, and 0 in panels B, E.
+Dashed lines indicate value 0.33 (the probability of choosing correctly by chance) in panels A, D, and 0 in panels B, E.
 Asterisks indicate significant results (p~mcmc~ < 0.05).
 Panels C and F show the predicted probability of choosing the correct ramp first over trials.
-The lines represent the mean predicted probability of choosing the correct ramp for each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+The lines represent the mean predicted probability of choosing the correct ramp for each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained using the slope and intercept estimates from the posterior distributions.
 The different colors indicate the different treatments."
@@
 guichenoti_ were not influenced by hormone treatment (β~Control~ - β~CORT~ = `r format_dec(mean(c(gar_ControlCold, gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold, gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature treatment (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) when red ramps were the correct choice (@fig-guich B, C).
-Similarly, CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold, gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold, gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or theirthe interaction interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) were not significant for _L.
+Similarly, CORT (β~Control~ - β~CORT~ = `r format_dec(mean(c(gab_ControlCold, gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold, gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or their interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) were not significant for _L.
 guichenoti_ assigned to blue ramps (see @fig-guich E, F).
@@
 #| label: fig-guich
-#| fig.cap: "Results for Lampropholis guichenoti for both color groups red (A, B, C) and blue (D, E , F).
+#| fig.cap: "Results for Lampropholis guichenoti for both color groups red (A, B, C) and blue (D, E, F).
 Panels A and D show the predicted probability of choosing the correct ramp in the first trial (Decision first trial).
@@
 
-#### Contrasting impacts of early developmental environments on decision making and learning in _Lampropholis delicata_ and _Lampropholis guichenoti_
-
-Overall, decision making did not differ between species when the red ramps (mean P~_L.
+#### Contrasting impacts of early developmental environments on decision-making and learning in _Lampropholis delicata_ and _Lampropholis guichenoti_
+
+Overall, decision-making did not differ between species when the red ramps (mean P~_L.
 delicata_~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~_L.
@@
 
-We also did not find any significant differences in learning rates between species when the red ramp (mean β~_L.
+We also found no significant differences in learning rates between species when the red ramp (mean β~_L.
 delicata_~ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)), 3)`, 95% CI β~_L.
@@
 These findings suggest that both species may have evolved mechanisms to buffer against early environmental stressors and maintain learning performance despite prenatal challenges.
-While we also did not find any effect of treatment on decision making there was a clear bias towards the color blue irrespective of the treatment, though this pattern differed between the species.
+While we also did not find any effect of treatment on decision-making, there was a clear bias towards the color blue irrespective of the treatment, though this pattern differed between the species.
 We discuss the implications of these findings below.
@@
 Prenatal CORT was predicted to have a negative effect on learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild; @farrell_developmental_2015-learn; @bebus_associative_2016].
-However, we did not find any significant difference in learning rates between hormone treatments in either of the two species.
+However, we found no significant difference in learning rates between hormone treatments in either species.
 Our results are consistent with other experiments that showed no influence of prenatal GCs on learning abilities [@szuran_water_1994; @bebus_associative_2016; @farrell_developmental_2016] and suggest that _L.
@@
 Generally, low concentrations or short exposure to GCs have been shown to improve the rate at which animals learn while high concentrations or exposure to GCs during long periods have the opposite effects [@du_dynamic_2009; @mcewen_brain_2012].
-This suggests that high elevations in CORT could affect learning through permanent changes in brain function (programmatic effects) while lower doses can result in lifelong elevation of baseline CORT, affecting learning through activational effects.
+Thus, high elevations in CORT could affect learning through permanent changes in brain function (programmatic effects), while lower doses can result in lifelong elevation of baseline CORT, affecting learning through activational effects.
 Our findings indicate that associative learning in _L.
 delicata_ and _L.
-guichenoti_ is robust to the programmatic effects of elevated CORT exposure, but we cannot exclude the possibility that different concentrations than the one used here may affect learning abilities.
+guichenoti_ is robust to the programmatic effects of elevated CORT exposure.
+However, we cannot exclude the possibility that concentrations different from the one used here may affect learning abilities.
 
@@
 Some studies show that the impact of GCs can vary between brain regions [@lemaire_prenatal_2000].
-GC actions involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed differentialy in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
-For instance, in european starlings (_Sturnus vulgaris_), males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds when the stimuli tested was acoustic [@farrell_developmental_2015-learn].
-Similarly, scrub-jays (_Aphelocoma coerulescens_) that have lower CORT levels as nestlings performed better on an associative learning test as adults but not on a reversal-learning task [@bebus_associative_2016].
+GC actions involve genomic and nongenomic mechanisms that implicate different types of receptors that can be distributed differentially in the various regions of the brain [@mcewen_brain_2012], and may be related to the learning performance in distinct tasks.
+For instance, in European starlings (_Sturnus vulgaris_), males stressed during early stages of development performed worse in a visual associative learning task, but show no differences with control birds with acoustic stimuli [@farrell_developmental_2015-learn].
+Similarly, scrub-jays (_Aphelocoma coerulescens_) with lower CORT levels as nestlings performed better on an associative learning test as adults but not on a reversal-learning task [@bebus_associative_2016].
 Our results suggest that prenatal CORT does not affect the brain regions involved in coding associative learning in _L.
 delicata_ and _L.
-guichenoti_ but we cannot rule out the possibility that other cognitive domains, such as spatial learning, might be affected.
-Future studies should focus on examining the differential effects of early-life stress on different cognitive domains.
+guichenoti_, but we cannot rule out the possibility that other cognitive domains, such as spatial learning, might be affected.
+Future studies should examine the differential effects of early-life stress on different cognitive domains.
 
 #### Incubation temperature does not affect learning
-We predicted hot-incubated lizards would perform better in the associative learning task, since most of the studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-While the opposite pattern has been found in some studies, these employed temperatures far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020].
+We predicted hot-incubated lizards would perform better in the associative learning task, since most studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+While the opposite pattern has been found in some studies, their incubation temperatures were far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020].
 As such, it is unclear how such conditions relate to wild environments.
@@
 delicata_ and _L.
-guichenoti_, associative learning appears to be robust to incubation temperature.
+guichenoti_, associative learning appears robust to incubation temperature.
 Our results, therefore, do not align with previous studies.
@@
 #### Visual-sensory bias is not dependent on early environment    
-We found strong evidence for a visual/sensory bias towards choosing the blue feeding ramp during the initial stages of decision making.
-While this effect appeared to be stronger in _L.
+We found strong evidence for a visual/sensory bias towards choosing the blue feeding ramp during the initial stages of decision-making.
+While this effect appeared stronger in _L.
 delicata_ compared to _L.
-guichenoti_, the bias was not the result of experiencing different early environmental conditions.
+guichenoti_, the bias did not result from experiencing different early environmental conditions.
 What created an initial bias towards blue?
-One possibility might be that the bias towards blue ramps was a byproduct of the training phase where the blue ramp was more similar to the white training ramp compared to the green and red ramps.
+One possibility might be that the bias towards blue ramps was a byproduct of the training phase where the blue ramp was more similar to the white training ramp than the green or red ramps.
 However, this hypothesis is unlikely given that the light spectrum and the perceived chromatic differences between the ramps used in the associative task and the ones used during training phase meant that the white training phase ramp was more similar to the green color rather than blue (see _Supplementary Material_).
@@
 Regardless, our results demonstrate that, at least in _L.
-delicata_, there is a bias toward blue colors highlighting the need to consider the colors used in associative learning paradigms carefully.
+delicata_, there is a bias toward blue colors, highlighting the need to consider the colors used in associative learning paradigms carefully.
 
 #### Learning rates between species did not vary  
-We did not see any significant difference in learning rates when both species were compared.
+We did not see any significant difference in learning rates when comparing both species.
 This result supports previous studies that found similar learning abilities in _L.
@@
 guichenoti_ [@bezzina2014does].
-In the experiment conducted by @bezzina2014does, both species failed to complete the associative learning task under the authors' criterion, while in our experiment both species completed the task, exhibiting similar learning rates.
+In the experiment conducted by @bezzina2014does, both species failed to complete the associative learning task under the authors' criterion, while in our experiment, both species completed the task, exhibiting similar learning rates.
 Complexity, experimental design, or the criterion employed to define learning could be the major cause of the discrepancies between ours and @bezzina2014does.
-Developing common strategies and approaches to assess learning in animals could help understand how learning abilities are shaped in different taxa or under different environments.
+Developing common strategies and approaches to assess animal learning could help understand how learning abilities are shaped in different taxa or environments.
 
 #### Conclusion
-Our results revealed that associative learning abilities and decision making in _L.
+Our results revealed that associative learning abilities and decision-making in _L.
 delicata_ and _L.
@@
 guichenoti_.
-These results seem to be a consequence of an innate color bias and highlights the importance of carefully selecting the color employed when testing cognition using visual stimuli.
+These results seem to be a consequence of an innate color bias and highlight the importance of carefully selecting the color employed when testing cognition using visual stimuli.
 
@@
 ## Authors’ contributions
-PR: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; DCL: data collection, writing—review and editing; OC: conceptualization, methodology, writing—review and editing; KW: conceptualization, writing—review and editing; CF: conceptualization, methodology, funding acquisition, writing—review and editing; BM: data collection, writing—review and editing; AP: data collection, writing—review and editing; DN: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
+PR: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; DCL: data collection, writing—review and editing; OC: conceptualization, methodology, writing—review and editing; KW: conceptualization, writing—review and editing; CRF: conceptualization, methodology, funding acquisition, writing—review and editing; BM: data collection, writing—review and editing; AP: data collection, writing—review and editing; DN: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
 All authors gave final approval for publication and agreed to be held accountable for the work performed therein.
@@
 ## Funding
-This work was supported by a National Australian University fellowship (PR), the Australian Research Council (grant no. DP210101152) to DN and CF, and the ACT Herpetological Association grant to PR.
+This work was supported by a National Australian University fellowship (PR), the Australian Research Council (grant no. DP210101152) to DN and CRF, and the ACT Herpetological Association grant to PR.
 
@@
 
-#### Estimates of learning rates for all the different treatments per each task, specie, and group.
+#### Estimates of learning rates for all the different treatments per each task, species, and group.
 Table 1.
-Estimates of learning rates for all the different treatments per each task, specie, and group.
+Estimates of learning rates for all the different treatments per each task, species, and group.
 Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
@@
 table_df <- data.frame(
-  Specie = rep(specie, each = length(group) * length(treatments)),
+  Species = rep(specie, each = length(group) * length(treatments)),
   Group = rep(rep(group, each = length(treatments)), times = length(specie)),
@@
   pivot_wider(names_from = Group, values_from = c(Mean, CI, pmcmc)) %>% #To divide by color
-  select(Specie, Treatment, Mean_Red, CI_Red, pmcmc_Red, Mean_Blue, CI_Blue, pmcmc_Blue) %>% #To order the columns in the way I want for the table
+  select(Species, Treatment, Mean_Red, CI_Red, pmcmc_Red, Mean_Blue, CI_Blue, pmcmc_Blue) %>% #To order the columns in the way I want for the table
 data.frame()
@@
 
-#### color preference
+#### Color preference
 To test if lizards were biased towards the assigned color as our preliminary analyses suggested, we employed the values from our posterior distributions.
@@
 table_df <- merge(prob_df, comp_pval, by ="column") %>%
-  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
+  mutate(Species = gsub(".*_(d|g).*", "\\1",column)) %>%
   mutate(Group = gsub(".*_(dr|db|gr|gb).*", "\\1",column)) %>%
@@
                     labels = c("CORTCold" = "CORT-Cold", "ControlCold" = "Control-Cold", "CORTHot" = "CORT-Hot", "ControlHot" = "Control-Hot"))) %>%
-  mutate(Specie = factor(Specie,
+  mutate(Species = factor(Species,
                 levels = c("d", "g"),
@@
   pivot_wider(names_from = Group, values_from = c(prob_choice, p_value)) %>% #To split the df in Red and Blue
-  select(Specie, Treatment, prob_choice_Red, p_value_Red, prob_choice_Blue, p_value_Blue) %>%
-  arrange(Specie, Treatment) %>% # To arrange the rows the way I wantdata.frame()
+  select(Species, Treatment, prob_choice_Red, p_value_Red, prob_choice_Blue, p_value_Blue) %>%
+  arrange(Species, Treatment) %>% # To arrange the rows the way I wantdata.frame()
 data.frame()
@@
 To test if the bias towards blue was something acquired during training, we compared the light spectrum of the ramps used in the associative task and the white ones used during habituation.
-We took three measurements of ten ramps per color with a spectophotometer, and then analysed the spectrum and the perceived differences in color using the package pavo.
+We took three measurements of ten ramps per color with a spectophotometer, and then analyzed the spectrum and the perceived differences in color using the package pavo.
 The spetrum of each type of ramp are shown in @fig-spectrum; the perceived chromatic constrasts between ramps are shown in @fig-perceived1 and @fig-perceived2.

### 2024-10-31 .vdoc.r

@@ -1,0 +1,900 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the experiment. Panel A shows the early environment manipulation (see Methods). In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks. Panel C shows the habituation process with the three different stages. And in panel D, the associative task with the three different 3D printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
[…]

### 2024-10-31 ms.qmd
Updates

@@
 Animals must acquire new information through learning to adjust their behavior adaptively.
-However, learning ability can be constrained by conditions experienced during the early stages of development, when the brain is especially susceptible to environmental inputs.
-Temperature can result in phenotypically plastic adjustments to growth, metabolism, and learning in ectotherms.
-In vertebrates, abrupt thermal changes can also trigger chronic stress, mediated by glucocorticoids (GCs) that can be transmitted to offspring, potentially impacting their learning abilities.
+However, learning ability can be constrained by conditions experienced during early development, when the brain is especially susceptible to environmental conditions.
+For example, temperature can result in phenotypically plastic adjustments to growth, metabolism, and learning in ectotherms.
+In vertebrates, thermal conditions can increase the production of glucocorticoid (GCs) - ‘stress’ hormones.
+Maternal GCs can be transmitted to offspring during development, potentially impacting their learning abilities.
 GCs and thermal environments are, therefore, predicted to have interactive effects on the development of learning in ectotherms.
@@
 guichenoti_.
-We manipulated CORT levels and temperature in a 2x2 factorial design, and then subjected lizards to a color-associative learning task.
+We manipulated CORT levels and temperature in a 2x2 factorial design, and then subjected juveniles to a color-associative learning task.
 We predicted that elevated CORT and low temperatures would impair associative learning.
@@
 We also found that color affected decision-making in both species.
-Overall, we observed a preference towards blue, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
+Overall, we observed a non-learned preference towards blue, underscoring the need to carefully select the color used in cognitive tests involving visual stimuli.
 
@@
 Interindividual differences in learning can lead to unequal responses to environmental conditions, potentially affecting population dynamics [@ward2016ecological; @welklin2024spatial].
-For example, fast learners may better exploit novel resources or avoid new dangerous stimuli, while those with lower learning capabilities might struggle to adapt to environmental changes.
+For example, fast learners may better exploit novel resources or avoid new dangerous stimuli, while those with lower learning capabilities might struggle to adapt to environmental changes [@ward2016ecological].
 Learning rate could affect their survival and reproductive output, ultimately influencing population growth rates and stability [@ward2016ecological; @welklin2024spatial].
-Therefore, understanding the factors that shape learning is crucial to predict how populations will respond to novel circumstances.
+Therefore, understanding the factors that shape learning is crucial to predict how populations will respond to novel conditions.
 
@@
 
-Developmental conditions are especially relevant in shaping cognitive abilities because the brain is highly susceptible to environmental inputs during early stages of life [@zhu_prenatal_2004].
+Because the brain is highly susceptible to environmental inputs during early stages of life, developmental conditions are especially relevant in shaping cognitive abilities  [@zhu_prenatal_2004].
 Impacts on brain development can have long-lasting effects on cognition, potentially influencing an individual's capacity to learn and adapt to new environments [@lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @abayarathna_effects_2020].
@@
 
-Glucocorticoids (GCs) are a class of steroid hormones that are particularly relevant in this context.
-In vertebrates, GCs regulate metabolism and maintain homeostasis in response to disturbances [i.e., ‘the stress response’ @sapolsky_how_2000].
+Glucocorticoids (GCs) are a class of steroid hormones that are particularly relevant in phenotypic plasticity.
+In vertebrates, GCs regulate metabolism and maintain homeostasis in response to disturbances [i.e., ‘the stress response’ @sapolsky_how_2000; @picard_mitochondrial_2014].
 Under stressful situations, animals react by initiating adaptive physiological and behavioral adjustments mediated by GCs.
-These GCs can be transmitted directly from parents to their offspring with various effects on offspring phenotype [@Crino_2023].
+These GCs can be transmitted directly from parents to their offspring with various effects on offspring phenotype [reviewed by @Crino_2023].
 Elevation in GCs during early stages of development typically results in altered neurogenesis, brain structure, and metabolic activity that, in most cases, are related to decreased learning abilities [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009; @eaton2015mild; @farrell_developmental_2015-learn; @farrell_developmental_2016].
@@
 In addition to the environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-In ectotherms, the early thermal environment is a pervasive mechanism of phenotypic plasticity, influencing a broad spectrum of traits, including growth, metabolism, or cognition [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
-For instance, Port Jackson sharks (_Heterodontus portusjacksoni_) incubated at 23.6ºC took fewer days to master a numerical learning task than those incubated at 20.6ºC [@vila_pouca_quantity_2019].
+In ectotherms, the early thermal environment is a mechanism of phenotypic plasticity, influencing a broad spectrum of traits, including growth, metabolism, or cognition [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @noble_developmental_2018; @abayarathna_effects_2020].
+For instance, Port Jackson sharks (_Heterodontus portusjacksoni_) incubated at warmer temperatures took fewer days to master a numerical learning task than those incubated at cooler [@vila_pouca_quantity_2019].
 In skinks, high incubation temperatures are generally associated with faster learning rates [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]; but velvet geckos (_Amalosia lesueurii_) incubated at temperatures beyond their natural thermal range are worse learners than those incubated at colder temperatures [@dayananda_incubation_2017; @abayarathna_effects_2020].
@@
 Additionally, GCs and temperatures can act upon similar physiological mechanisms [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021].
-Therefore, the effects of GCs and temperature may be interdependent, with the impact of one factor being modulated by the other.
+Therefore, the effects of GCs and temperature may be interdependent.
 However, the interactive effects of GCs and temperature on learning abilities remain unexplored, yet understanding of how temperature and GC’s interact is particularly relevant in global climate change [@vinogradov2024inbreeding].
 
-Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - and incubation temperature on cognition in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+Here, we investigated the combined effects of prenatal corticosterone (CORT) - the main GC in reptiles - and incubation temperature on cognition in two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 Post-incubation, juveniles were subjected to a color-associative task to assess their learning abilities.
-We hypothesized that prenatal CORT levels and thermal environment would induce sustained effects on brain physiology, ultimately impacting the learning of an association task.
+We hypothesized that prenatal CORT levels and thermal environment would impact the learning of an association task.
 We predicted that individuals exposed to high levels of CORT or low temperatures would learn slower than control individuals or those incubated at higher temperatures [@zhu_prenatal_2004; @amiel_hotter_2012; @eaton2015mild; @amiel_effects_2017].
 Additionally, we predicted that incubation at high temperatures would mitigate the impact of CORT on learning performance, while cold incubation temperatures were expected to enhance the effects of CORT.
-The interactive effects of CORT and temperature may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
+The interactive effects of CORT and temperature may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild]; and second, the elevated metabolic rate associated with higher temperatures could accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
 
@@
 Then, we assigned individual IDs to the clutch and each egg.
-Eggs were treated with CORT or vehicle (see CORT and Temperature Manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
+Eggs were treated with a CORT or control treatment (see CORT and Temperature Manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
 The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
@@
 
-*Hatchlings* -- After hatching, we measured juveniles' snout-to-vent length (SVL) and tail length (TL) with a ruler to the nearest mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001 g error).
+*Hatchlings* -- Immediately after hatching, we measured lizards' snout-to-vent length (SVL) and tail length (TL) with a ruler to the nearest mm, and mass using a digital scale (OHAUS, Model spx123; ± 0.001 g error).
 Hatchlings were then housed individually in small enclosures (18.7L x 13.2W x 6.3H cm) provided with non-stick matting, shelter, and a water dish.
@@
 
-Two weeks prior to the training phase (see details below), lizards were moved to the experimental arena for acclimatization.
+Two weeks prior to the training phase (see details below), 1.5 to 5 months old lizards (see details in Statistical Analyses and Supplementary Material) were moved to the experimental arena for acclimatization.
 The arenas were individual medium-size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the sides and a water dish on the other.
@@
 #### CORT and Temperature Manipulation  
-To empirically test the effect of early environment, we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (‘Cold’ - 23ºC ± 3ºC or ‘Hot’ - 28ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
-We topically dosed eggs with a CORT solution (10pg/mL) or a control treatment (100% ethanol).
+To empirically test the effect of early environment, we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (‘Cold’ - 23 ± 3 ºC or ‘Hot’ - 28 ± 3 ºC) in a 2x2 factorial design (@fig-Methods A).
+We topically dosed eggs with a CORT solution (10 pg/mL) or a control treatment (100% ethanol).
 Corticosterone treatments were made by dissolving crystalline corticosterone (Sigma, Cat.
@@
 To estimate learning skills, we tested each lizard's ability to locate a food reward in a color-associative learning task (@fig-Methods C, D).
-First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical in size and shape to the ones used during the associative task.
+First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical in size and shape to the ones used during the associative task (@fig-Methods B).
 We divided the training phase into three stages: the first stage where lizards had to eat a small, frozen cricket (*A.
@@
 #| label: fig-Methods
-#| fig.cap: "Experimental design of the experiment.
-Panel A shows the early environment manipulation (see Methods).
+#| fig.cap: "Experimental design of the study.
+Panel A shows the early environment manipulation.
 In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks.
@@
 We started with 96 lizards, 48 per species and 12 per treatment per species.
-However, due to natural mortality (n = 11), failing to pass the training stage (n = 1), or lack of motivation during the learning tasks (n = 3), we had a final sample size of 81 lizards.
+However, due to mortality (n = 11), failing to pass the training stage (n = 1), or lack of motivation during the learning tasks (n = 3), we had a final sample size of 81 lizards.
 Final sample sizes per treatment and species are listed in @fig-deli and @fig-guich (figures for both species with the raw data are included in the _Supplementary Material_).
@@
 
-_Lampropholis delicata_: _L.
-delicata_ that were given the blue ramp as the correct choice had an `r format_dec(((mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) / mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot))) - 1) * 100, 1)`% increase in the probability of choosing the right ramp on trial 1 compared to lizards assigned to the red ramps (mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]), suggesting a bias towards blue.
+_Lampropholis delicata_: individuals given the blue ramp as the correct choice had an `r format_dec(((mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)) / mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot))) - 1) * 100, 1)`% increase in the probability of choosing the right ramp on trial 1 compared to lizards assigned to the red ramps (mean P~Blue~ = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, 95% CI P~Blue~ = [`r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), 0.975), 3)`]; mean P~Red~ = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, 95% CI P~Red~ = [`r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.025), 3)` , `r format_dec(quantile(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), 0.975), 3)`]), suggesting a bias towards blue.
 A blue bias was also supported by initial choices differing significantly from chance, and this was consistent across all treatments (i.e., P > 0.33; Table 2 in _Supplementary Material_).
@@
 
-Decision-making in _L.
+Decision-making by _L.
 delicata_ was not impacted by the CORT (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_drControlCold, probright_drControlHot)) - mean(c(probright_drCORTCold, probright_drCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlCold, probright_drControlHot) - c(probright_drCORTCold, probright_drCORTHot)), 3)`), incubation temperature (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_drControlHot, probright_drCORTHot)) - mean(c(probright_drControlCold, probright_drCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drControlHot, probright_drCORTHot) - c(probright_drControlCold, probright_drCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_drControlHot - probright_drCORTHot) - mean(probright_drControlCold - probright_drCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_drControlHot - probright_drCORTHot - (probright_drControlCold - probright_drCORTCold)), 3)`) when red ramps were the correct choice (see @fig-deli A).
@@
 
-Decision-making in _L.
+Decision-making by _L.
 guichenoti_ when the red ramps are the correct choice, was not affected by the hormone treatment (P~Control~ - P~CORT~ = `r format_dec(mean(c(probright_grControlCold, probright_grControlHot)) - mean(c(probright_grCORTCold, probright_grCORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlCold, probright_grControlHot) - c(probright_grCORTCold, probright_grCORTHot)), 3)`), temperature treatment (P~Hot~ - P~Cold~ = `r format_dec(mean(c(probright_grControlHot, probright_grCORTHot)) - mean(c(probright_grControlCold, probright_grCORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_grControlHot, probright_grCORTHot) - c(probright_grControlCold, probright_grCORTCold)), 3)`) or their interaction ([(P~Control-Hot~ - P~CORT-Hot~) - (P~Control-Cold~ - P~CORT-Cold~)] = `r format_dec(mean(probright_grControlHot - probright_grCORTHot) - mean(probright_grControlCold - probright_grCORTCold), 3)`, p~mcmc~ `r format_p(pmcmc(probright_grControlHot - probright_grCORTHot - (probright_grControlCold - probright_grCORTCold)), 3)`; see @fig-guich A).
@@
 
-We predicted that elevated CORT levels in eggs or incubating them at colder temperatures would decrease learning rates, and that warmer incubation temperatures would relax the negative effects of CORT on learning.
+We predicted that elevated CORT levels in eggs or incubating them at colder temperatures would decrease learning rates, and that warmer incubation temperatures would suppress the negative effects of CORT on learning.
 In contrast to our predictions, both species learned to associate a color with a food reward at the same rate regardless of the experimental treatment.
-These findings suggest that both species may have evolved mechanisms to buffer against early environmental stressors and maintain learning performance despite prenatal challenges.
-While we also did not find any effect of treatment on decision-making, there was a clear bias towards the color blue irrespective of the treatment, though this pattern differed between the species.
+These findings suggest that both species may have developed mechanisms to buffer against early environmental stressors and maintain learning performance on colour-associative tasks despite prenatal challenges.
+While we did not find any effect of treatment on decision-making, there was a clear bias towards the color blue irrespective of the treatment, though this pattern differed between the species.
 We discuss the implications of these findings below.
@@
 delicata_ and _L.
-guichenoti_ may have evolved strategies to buffer the impacts of prenatal stress.
-
-Alternatively, our observations could be obscured by other variables that are known to influence the extent and direction of these outcomes.
-[@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016; @farrell_developmental_2016].
-GCs are known to have hormetic effects.
+guichenoti_ may have developed strategies to buffer the impacts of prenatal stress.
+
+Alternatively, our observations could be obscured by other variables that are known to influence the extent and direction of the effects of GCs [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016; @farrell_developmental_2016].
+GCs are known to have hormetic effects [@du_dynamic_2009].
 Generally, low concentrations or short exposure to GCs have been shown to improve the rate at which animals learn while high concentrations or exposure to GCs during long periods have the opposite effects [@du_dynamic_2009; @mcewen_brain_2012].
@@
 While the opposite pattern has been found in some studies, their incubation temperatures were far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020].
-As such, it is unclear how such conditions relate to wild environments.
+As such, it is unclear how such these extreme conditions relate to wild environments.
 In _L.
 delicata_ and _L.
-guichenoti_, associative learning appears robust to incubation temperature.
+guichenoti_, associative learning appears robust to incubation temperature because of the lack of detectable effect temperature had on learning.
 Our results, therefore, do not align with previous studies.
@@
 #### Learning rates between species did not vary  
-We did not see any significant difference in learning rates when comparing both species.
+We did not see any difference in learning rates when comparing both species.
 This result supports previous studies that found similar learning abilities in _L.

### 2024-10-31 .vdoc.r

@@ -1,900 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-cat("\\newpage")
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of the experiment. Panel A shows the early environment manipulation (see Methods). In panel B, the measurements of the 3D-printed ramps employed in the habituation and learning tasks. Panel C shows the habituation process with the three different stages. And in panel D, the associative task with the three different 3D printed ramps. White lids in D show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/LEARN_FIG1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be the main data base used (data_clean).
-write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
[…]

### 2024-11-01 .vdoc.r
Create .vdoc.r

@@ -1,0 +1,900 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
[…]

### 2025-03-30 ms.qmd
Updates
Updates EcoEvoRxiv
updates

@@
 title: "Cognitive processes are robust to early environmental conditions in two lizard species"
-format:
 docx: 
@@
 Christopher R. Friesen ORCID: 0000-0001-5338-7454  
-Basile Mauclaire ORCID:  
+Basile Mauclaire ORCID: 0000-0003-3956-6055   
 Amelia Y. Peardon ORCID: 0009-0005-6227-8379  
@@
 The interactive effects of CORT and temperature may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @eaton2015mild]; and second, the elevated metabolic rate associated with higher temperatures could accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time.
+In contrast, glucocorticoids in endotherms are associated with increased energy demands[e.g., @rubalcaba2022body], which could lead to higher CORT production in lizards incubated at warmer temperatures.
+However, previous research on _L.
+delicata_ [@crino2024eggs] has found that cold-incubated lizards had higher baseline CORT levels, suggesting that cooler incubation temperatures may increase the potential effects of CORT exposure.
 
@@
 Eggs were treated with a CORT or control treatment (see CORT and Temperature Manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
-The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
+The cups were covered with cling wrap to retain moisture and left in LABWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
 Eggs were then checked three times a week for hatchlings.
@@
 After the treatment, the eggs were incubated in one of the two previously mentioned temperature regimes (‘Cold’ or ‘Hot’) until hatching.
+These temperatures represent the upper and lower limit of the natural incubation temperatures [@qualls2000post; @cheetham2011embryonic].
 The number of eggs per clutch assigned to each hormone and temperature treatment was counterbalanced in both species.
@@
 Trials in the learning phase were recorded with CCTV systems, always using the same camera per individual.
+All the videos were analysed by the same observer (PR) who was blind to the treatment of the lizards.
 We recorded whether the animal chose the correct ramp first or not.
@@
 guichenoti_ is robust to the programmatic effects of elevated CORT exposure.
-However, we cannot exclude the possibility that concentrations different from the one used here may affect learning abilities.
+Similarly, exposing embryos at different stages of development could impact the effects of CORT.
+However, we cannot exclude the possibility that concentrations different from the one used here or exposure at different developmental times does affect learning.
 
@@
 #### Incubation temperature does not affect learning
-We predicted hot-incubated lizards would perform better in the associative learning task, since most studies demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-While the opposite pattern has been found in some studies, their incubation temperatures were far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020].
+We predicted hot-incubated lizards would perform better in the associative learning task, since most studies in other species demonstrate enhanced learning abilities when eggs are incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+These studies employed incubation temperatures within natural nesting thermal limits.
+In contrast, in those studies where cold-incubated lizards outperformed hot incubated ones, the incubation temperatures employed in the hot condition were far above the natural thermal range of the species in their hot treatments [@dayananda_incubation_2017; @abayarathna_effects_2020].
 As such, it is unclear how such these extreme conditions relate to wild environments.
@@
 We did not see any difference in learning rates when comparing both species.
-This result supports previous studies that found similar learning abilities in _L.
+Since both species occupy similar habitats and have similar ecology [@chapple_know_2011; @chapple2013divergent; @chapple_biology_2014], it may not be surprising that cognitive abilities are similar between both species.
+Nonetheless, previous studies have shown that _L.
+guichenoti_ is less prone to explore novel environments than _L.
+delicata_, which may be related to the success of _L.
+delicata_ as an invasive species compared to _L.
+guichenoti_ [@chapple_know_2011].
+Our results show that the ability of L.
+delicata to colonize new areas seems not to be related to learning abilities.
+Our findings support previous studies that found similar learning abilities in _L.
 delicata_ and _L.

### 2025-05-14 ms.qmd
updates

@@
 #| label: cleaning
-source(here("R", "1_data_process.R"))
+source(here::here("R", "1_data_process.R"))
 # Once we run this code, the result will be the main data base used (data_clean).
@@
   ) 
-print(dScomparisons)
+ggsave("./output/figures/dScomparisons.tif", plot= dScomparisons, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/dScomparisons.tif")
 ```
@@
   )
-print(dLcomparisons)
+ggsave("./output/figures/dLcomparisons.tif", plot= dLcomparisons, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/dLcomparisons.tif")
 ```
@@
 plot_age <- plot_grid(plot_age_deli, plot_age_guich, ncol = 1)
-ggsave("./output/figures/plot_age.png", plot=plot_age, width = 25, height = 18, units = "cm", dpi = 600)
+ggsave("./output/figures/plot_age.tif", plot=plot_age, width = 25, height = 18, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/plot_age.png")

### 2025-05-14 .vdoc.1e293d6a-8cb5-49c2-98de-9f35e5012763.r

@@ -1,0 +1,901 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.20062d06-5397-4bc5-b21e-542430f02b58.r

@@ -1,0 +1,901 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(herehere::("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
[…]

### 2025-05-14 .vdoc.29e65d66-8519-48c0-86dc-ab9b6a3a8840.r

@@ -1,0 +1,900 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.363ab9bc-6e57-4732-a0e1-ec99ef7ae572.r

@@ -1,0 +1,901 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.702c3981-5abd-4b0e-8d59-af1c3b2ef6e6.r

@@ -1,0 +1,901 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here::here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.928a1810-a836-4468-a9a5-43ad38818130.r

@@ -1,0 +1,909 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.a1cfc0c7-90ff-473f-888b-be6abcf3e558.r

@@ -1,0 +1,901 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.a3f395ff-5ae2-4b8f-b2a5-89c0e9c02fdc.r

@@ -1,0 +1,901 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here::here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.bbac098e-71a4-4f45-b020-fbcae20e373a.r

@@ -1,0 +1,902 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.f765cb3d-d376-4598-ade7-a01c5d2cb4ca.r

@@ -1,0 +1,900 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]

### 2025-05-14 .vdoc.ffbf8140-de95-405e-b9cf-e9f16865a38b.r

@@ -1,0 +1,901 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of the study. Panel A shows the early environment manipulation. In panel B, the measurements of the 3D-printed ramps that were employed in the habituation and learning tasks. Panel C shows the habituation process in three different stages. In panel D, the associative task is done with the three different 3D-printed ramps. White lids in D show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/LEARN_FIG1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleaning
+source(here("R", "1_data_process.R"))
+# Once we run this code, the result will be the main data base used (data_clean).
+write.csv(data_clean, file= "./output/databases_clean/data_clean.csv")
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_clean.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
[…]
